### 2021-04-28 CL/CoverLetter.tex
Initial Overleaf Import

%
% harvard-letter.tex - an example latex file to illustrate harvardletter.cls
%
% Copyright 2019, Ahmad Zareei (ahmad@seas.harvard.edu)
%

\documentclass[11pt]{harvardletter}
\usepackage{color}
\usepackage{soul}

\newcommand{\EM}[1]{\noindent \color{cyan} (EM: #1)\normalcolor}
\newcommand{\KB}[1]{{\color{red}{Katia: #1}}}
\newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}

% \name{\includegraphics{./Signature.eps}} % used as signature, if no signature is specified

\signature{\vspace{-10mm}\includegraphics[height=0.4in]{Signature.eps} \\\textbf{Ariel Amir}\\ \textit{Thomas D. Cabot Associate Professor of Applied Mathematics and Applied Physics,} \\ \textit{School of Engineering and Applied Sciences,}\\ \textit{Harvard University} \\ \textit{Phone: (617) 495-5818}\\ \textit{Email: arielamir@seas.harvard.edu}}

\date{} % if no date specified, today's date is used

% \subject{This is the subject of the letter} % optional subject line

\begin{document}

\begin{letter}{}
  %              {Prof. ... .... \\ 
  %              Harvard University\\ 
  %              Cambridge, MA 02148}

\hfill{March 21, 2021}
\vspace{20mm}

% \begin{table}
%     \centering
    \begin{tabular}{l l }
        \small{Title:}  & \textbf{\small{Temporal Evolution of flow in Porous Materials: From Homogenization to Instability}} \vspace{2mm} \\ 
        \small{Authors:}  & \small{Ahmad Zareei$^1$, Pan Deng$^1$, and Ariel Amir$^{1,2}$* (*corresponding author)} \vspace{2mm} \\
        \small{Affiliations:} & \small{$^1$Harvard John A. Paulson School of Engineering and Applied Sciences, Harvard University} \\
        & \small{$^2$Kavli Institute, Harvard University}
    \end{tabular}
% \end{table}

\vspace{5mm}

\opening{Dear Editor,}

We are excited to submit our work, ``Temporal Evolution of flow in Porous Materials: From Homogenization to Instability'' for consideration as an article in the \emph{Physical Review Letters}. In this study, we demonstrate that ....

As such, our study suggests that

For reviewers, we suggest the following experts:

\textbf{Karen Alim},Max Planck Institute for Dynamics and Self-Organization, G\"ottingen, Germany, \texttt{k.alim@tum.de}

\vspace{5mm}

\underline{\textbf{\small{This material has not been published and is not under consideration for publication elsewhere.}}}

\vspace{5mm}

We thank you for your consideration and look forward to hearing from you.

\vspace{5mm}

\closing{Sincerely,}

% \encl{manuscript.pdf}
% \ps{Please see the enclosed file.}
% \cc{Dr. Ahmad Zareei}

\end{letter}

\end{document}

### 2021-04-28 Figs/random_network/Porous - Instability/combined.tex
Initial Overleaf Import

\input{definitions.tex}
\def\d{\text{d}}
\def\vep{\varepsilon}
\def\ep{\epsilon}
\def\la{\langle}
\def\ra{\rangle}
\def\th{\theta}
\usepackage{tikz}
\usepackage{circuitikz}
\usepackage{float}
\usepackage{hyperref}
\newcommand{\AZ}[1]{{\color{red}{Ahmad: #1}}}
\newcommand{\red}[1]{{\color{red}{#1}}}
\title{Porous Media Project}
\author{Ahmad}
\date{}

\begin{document}
\maketitle

\tableofcontents

\section{Introduction}
%
In order to study the porous media, we introduce a model that captures
flow behavior through a porous material. We consider the porous media
as a network of pores that are connected together through
connections. The schematic of our model is shown in
Fig. \ref{porous-schematic}. We use a random resistor networks on a
structured grid as our model to study the flow behavior. Each node
represents a pore and each edge represents the throats between
pores. We use simple Poiseuille flow through pipes to model fluid flow
through pipes. In each pipe with diameter $d$, length $L$, and pressure difference
of $\Delta P$ on both sides, results in a flow $Q$, where
%
\begin{align}
    \frac{\Delta P}{L}  = \frac{128}{\pi} \frac{\mu Q}{d^4} 
\end{align}
%
where $\mu$ is the viscosity of the fluid. The above relation is known
as Darcy's law.

%
\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{./Figs/porous-schematic}
  \caption{Schematic of the network model for porous media: (a) a
    sample cross section of a porous media. (b) The porous media can
    be considered as a network of pores connected through resistive
    connections. (c) The random network obtained from porous
    media. (d) Reordering the porous media network on a structured
    grid. (e) The ordered structured network used where the
    connections are assumed to be random resistors.} \label{porous-schematic}
\end{figure}
%

\section{Numerical Simulation}
%
We consider a network of tubes with a random distribution of diameters
as shown in Fig. {porous-schematic}e. Darcy's law is obtained thought
the momentum equation and relates the pressure and the flow through
the pipes. Furthermore, at each node the summation of the inflows
should add up to zero (conservation of mass). Using this a system of
equations $AP=B$ is obtained where $P$ is the vector of pressures at
nodes, $A$ is sparse where the nonzero elements are
% 
\begin{align}
  A_{ii} &= \sum_{j \text{ neighbors of } i} \frac{\pi }{128 \mu L} d_{ij}^4 \\
   A_{ij} &= 
  \begin{cases}
    -\frac{\pi }{128 \mu L} d_{ij}^4, \quad \text{if }j \text{ is
      neighbor of }i\\
    0, \quad \text{otherwise}
  \end{cases}
\end{align}
%
Note that if all the pipes have the same diameter, then the flow is
only in the horizontal pipes, and vertical pipes will carry no flow.

\subsection*{Numerical results}
%
We consider a 2d network of pipes, and a pressure difference between
the left and right nodes. We further assume different distribution of
pipe diameters and find the flow $q$ in the pipes. When the pipes are
all the same diameter, then the velocities in the pipes are either $0$
or some nonzero value. As we increase the randomness in the pipes, we
observe that the PDF of velocities starts to follow an exponential
tail trend. Interestingly, if the disorder in pipes diameter is large
enough, the PDF of velocities in the pipes, no matter what
distribution we pick follows the same distribution. 
%
\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\textwidth]{./Figs/distribution}
  \caption{PDF of normalized velocities of the pipes in a random
    network of pipes, $v$ is the velocity in the pipe, $Q$ is the
    total flux, $N$ is the number of pipes in the vertical direction,
    $\langle A\rangle$ is the average of the area of the pipe. Note that
    $N\langle A\rangle$ is the average area carrying the flow $Q$. } \label{pdf-result}
\end{figure}

\section{Analytical results}
%
\label{sec:analytical}
In order to describe the universality observed above, we introduce the
following mode. First, instead of using the structured rectangular
grid, we use a structured diagonal grid. This will simplify the
analytical model (see Fig. \ref{grid-result}).

%
\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth]{./Figs/grid-analytica}
  \caption{Schematic of grids: (a) The structured rectangular grid
    used in the numerical simulation. (b) The structured diagonal grid
    used in the analytical model. } \label{grid-result}
\end{figure}
%
We assume that the total flow to node $i$ at level $L$ is noted by
$Q(L,i)$. This flow is then redistributed to the neighboring nodes at
the level $L+1$. We assume that this redistribution is done by weights
$w_{ij}$ as
%
\begin{align}
  Q(L+1,j) = \sum_i w_{ij} Q(L,i) = w_{i,i+1} Q(L,i+1) + w_{i,i} Q(L,i) \label{total-flow}
\end{align}
%
where $\sum_{j} w_{ij} = 1$ (since the total outflow from node $i$ is
$\sum_j q_iw_{ij}$ and this value should add up to $q_i$). We assume
that $w_{ij}$ are drawn from a distribution $\eta(w)$. Since $\eta(w)$
is a distribution, then $\int \eta(w) dw = 1$. Furthermore, since
$\sum_jw_{ij} = 1$, we can conclude that
%
\begin{align}
  \sum_j w_{ij}=1 \to N {E}[w_{ij}] = 1 \to E[w_{ij}] = 1/N \to {\int w\eta(w) dw = 1/N}
\end{align}
%

Now we use the technique of mean field analysis for a general
distribution of $\eta(w)$ to find the distribution of $Q$ at the
layers. The values of $Q(D,i)$ are not independent for neighboring
sites; however, the mean field approximation ignores these
correlations. We have
%
\begin{align}
  P_L (Q) = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P_{L-1}(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp
\end{align}
%
The constraint that $Q$'s emanating downward should add up to one is
in the definition of $\eta(w)$. The only approximation in the above
equation is that we neglect the possible correlation between the
values of $Q$ among ancestors. If we take the Laplace transform of
the above equation, we obtain
%
\begin{align}
  \tilde P(s) & \equiv \int_0^{\infty} P(Q) e^{-Qs} dQ\\
  \xrightarrow{\int_0^{\infty} (\cdot) e^{-Qs} dQ}  P (Q) & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp \\
  \tilde P(s) & = \int_0^{\infty} \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp e^{-Qs}dQ \\
              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j e^{-\sum w_{j}Q_{j}} P(Q_j)\right\}   \\
              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \tilde P(s w_j) \right\} \\
  & = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N}
\end{align}
%
Or to summarize
%
\begin{align}
  \boxed{\tilde P(s) = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N}} \label{eq:main-laplace}
\end{align}
%
Note that in the above equation $N$ determines the number of
neighboring sites and in our structured diamond grid $N=2$. The above
equation is recursively converges to a distribution.  If we set
$\eta(w) = \delta(w-1/2)$, then the flow at each node has probability of
$1/2$ to move up or down. As a result the flow at a given depth $L$
will be homogeneous as $P_L(Q) = \delta (Q-\bar{Q})$ where $\bar{Q}$
is the average of input fluid flow. This case is the same as the same
diameter which results in a singular solution in the structured grid.

\subsection*{$P(Q)$ decays faster than $Q^{-n}$ for any $n$}
We first show that $P(Q)$ decays faster than any power of $Q$ for any
weight distributions. We expand the Laplace transform as
%
\begin{align}
  \tilde P(s) = 1 + \sum_j \tilde P_{j} s^{j}
\end{align}
%
Inserting this expansion into Eq. \eqref{eq:main-laplace}, we obtain
%
\begin{align}
  1 + \sum_j \tilde P_{j} s^{j}  & = \lp  \int_0^1 d w \eta(w) \lb 1 + \sum_j \tilde P_{j} (sw)^{j}\rb    \rp^{N} \\
 & = \lp  1 + \sum_j \tilde P_j \langle w^{j}\rangle  s^{j}   \rp^{N}
\end{align}
%
where $\langle w^j \rangle = \int_0^1 \eta(w) w^j dw$ is the $j$-th
moment of the weights $w$. In the above equation we can observe that
%
\begin{align}
  P_j \lp N \langle w^j\rangle -1 \rp = G(P_{j-1}, P_{j-1}, \cdots, P_1)
\end{align}
%
In the above equation $P_j$ can only diverge only if $N\langle w^j
\rangle -1$ is zero. If $w$ can only be zero and one, then $\langle
w^j\rangle =\langle w \rangle = 1/N$ and the coefficient can become
zero! Other than this special distribution where $0 \leq w \leq 1$,
then
%
\begin{align}
  & w\in [0,1] \rightarrow w>w^2>w^3> \cdots \\
  & \forall k>1 \rightarrow \langle w^k \rangle < \langle w \rangle = \frac{1}{N} 
\end{align}
%
which means that $N\langle w^j \rangle -1$ is not zero and as a result
$P_j$ is finite. $P_j$ on the other hand is the $j$-th moment or
$\langle Q^j\rangle$ and it is finite. If $P\approx Q^{-n}$, then the
$n$-th moment will not be finite i.e. $\langle Q^{n+1}\rangle =
P_{n+1}$ is not finite. We can then conclude that $P(Q)$ should go to
zero faster than any $Q^{-n}$ as $Q\to \infty$! In other words $d \log
P(Q) / d \log Q \to -\infty$ as $Q\to \infty$.

\subsection*{Exponential Decay}
%
The main governing equation for a diamond grid is 
%
\begin{align}
  \tilde P(s) = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{2} 
\end{align}
%
In order to have an approximation for $\eta(w)$ we do the following:
At each node there are two nodes where the flux is distributed by
$w_1$ and $w_2$. Lets assume that $w_1$ is uniformly distributed
between $0$ and $1$. As a result $w_2 = 1-w_1$ (since conservation of
mass $w_1 + w_2 = 1$). Now $\eta(w)$ can be found as
%
\begin{align}
  & \eta(w) = M \int_0^1 dw_1 \delta(1-w_1-w) =  M, \\
  \text{since }& \int_0^1 \eta(w) dw = 1 \to M =1 \\
  & \eta (w) = 1
\end{align}
%
Just for completeness, if there are three connections ($N=3$), then we
have
%
\begin{align}
  \eta(w) & = M \int_0^1 dw_1 \int_0^1 dw_2 \delta(1-w_1-w_2 - w)\\
          & = M(1-w)  \to \int_0^1\eta(w) dw = 1 \to M = \frac{1}{2} \\
  & \eta(w) = \frac{1}{2} (1-w)
\end{align}
%
As a result the main equation simplifies to
%
\begin{align}
  \tilde P(s) = \lp  \int_0^1 d w  \tilde P(s w)  \rp^{2} 
\end{align}
%
In order to solve the above equation, we assume $\tilde V (s) =
\sqrt{\tilde{P}(s)}$.
%
\begin{align}
  \tilde{V}(s) & = \int_0^1 dw \tilde V (sw) = \int_0^s \frac{du}{s}  \tilde{V}^{2}(u) \\
  s\tilde{V}(s) & = \int_0^s du  \tilde{V}^2(u) \\
\end{align}
%
Taking the differentiation with respect to $s$ yields
%
\begin{align}
  \tilde{V}(s) + s \frac{d \tilde{V}(s)}{d s} = \tilde{V}^2(s) \\
  \frac{d \tilde{V}}{\tilde{V}^2-\tilde{V}} = \frac{ds}{s}  \\
  \log\lp \frac{1-\tilde{V}}{\tilde{V}} \rp  = \log(s)\\
  \tilde{V}(s) = \frac{1}{1+Cs} 
\end{align}
%
We set the mean to $1$ i.e.,
%
\begin{align}
  \int_0^{\infty} Q P(Q) dQ = 1 \to \frac{d\tilde{P}}{ds}|_{s=0}  = -1\\
  \frac{d \tilde{V}}{ds}  = \frac{1}{2 \sqrt{\tilde{P}(s)}} \frac{d \tilde{P}(s)}{d s}   \to \frac{d\tilde{V}(s)}{ds}|_{s=0} =\frac{-1}{2} \\
  \frac{d\tilde{V}(s)}{ds} = \frac{-C}{(1+Cs)^{2}}|_{s=0} = -C = \frac{-1}{2}  \to C=\frac{1}{2} 
\end{align}
%
As a result, we have
%
\begin{align}
  \tilde{P}(s) = \lp\frac{1}{1+s/2} \rp^2 \\
  P(Q) = 4Q e^{-2Q}
\end{align}
%
We can then show that for a uniform distribution of $w$'s, the PDF of
$Q$'s become an exponential tail. For other distribution of $w$'s, we
similarly find a similar trend. Actually, we should that the PDF of
$Q$ should decay faster than any power law for any distribution of
$w$. Note that the only parameter that determines the the PDF of the
flow is the average flux. This shows that why we observe the universal
behaviour for pdf.

\section{Continuous Limit}
%
In the previous section (\S \ref{sec:analytical}), we used a toy model
to describe the flow behavior. The main equation connecting the flow
at different layers was Eq. \eqref{total-flow}. In this section, we
are interested to see what a continuous limit of the above model will
be. Consider Eq. \eqref{total-flow} as
%
\begin{align}
  Q(i,j+1) = w_{i-1,j} Q(i-1,j) + w_{i+1,j} Q(i+1,j) 
\end{align}
%
where we had a constraint on the weights as 
%
\begin{align}
  w_{i-1,j} + w_{i+1,j} = 1
\end{align}
%
Now, lets assume that these weights are perturbations around the a
uniform distribution such that
%
\begin{align}
  w_{i\pm 1,j}= \frac{1}{2}( 1 \pm v_{i\pm 1,j})
\end{align}
%
with th above assumption, we find that
%
\begin{align}
  Q(i,j+1) & = \frac{1}{2} \left( 1 - v_{i- 1,j}\right) Q(i-1,j) + \frac{1}{2} \left( 1 + v_{i+ 1,j}\right) Q(i+1,j)  \\
  Q + L_y \frac{\p Q}{\p y } + L^2_y \frac{\p^{2}Q}{\p y^2}  & = \frac{1}{2} (1-v + L_x \frac{\p v}{\p x}  ) \left( Q - L_x \frac{\p Q}{\p x} +   \frac{1}{2} L_x^2 \frac{\p Q^2}{\p x^2}\right) \nonumber\\
 & \qquad   +\frac{1}{2}  (1+v + L_x \frac{\p v}{\p x} )\left( Q + L_x \frac{\p Q}{\p x} + \frac{1}{2}L_x^2 \frac{\p^2 Q}{\p x^2} \right)  \\
  L_y \frac{\p Q}{\p y } & = L_x v \frac{\p Q}{\p x} + L_x \frac{\p v}{\p x} Q + \frac{L^2_x}{2} \frac{\p^{2}Q}{\p x^2}  \\
  \frac{\p Q}{\p y}    & = \frac{L_{x}}{L_{y}} \frac{\p }{\p x} \left( v Q \right)  + \frac{L^2_x}{2L_y} \frac{\p^{2}Q}{\p x^2}  
\end{align}
%
Assuming that $L_x = L_y $ (similar length scales in both directions),
we find that
%
\begin{align}
\boxed{\frac{\p Q}{\p y}  = \frac{\p}{\p x} \left( v Q\right) + D \frac{\p^{2} Q}{\p x^2}  }
\end{align}
%
which is a convection-diffusion equation.  It seems that $y$ direction
(the direction where flow propagates into the porous medium) acts
similar to time. As the flow moves inward, the $Q$ diffuses in the $x$
direction, and convects with velocity $v$.

\section{Network Evolution}
%
Any changes to the micro-structure in a porous medium, such as solute
retention during polymer flow (effectively" clogging" some pores in
the network), affects the pore-level flow and alters the bulk
behavior. In this section, we want to study the effect of such
evolution in the network. The radius of the pipes in the network, can
reduce (due to clogging) or increase (due to erosion). The rate of
such reduction (or increase) can depend on flux, or shear rate, or
velocity, or etc. We can simplify these models with all the models
with the following equation
%
\begin{align}
  \frac{dR}{dt}  \propto \pm \frac{Q}{R^{n}} 
\end{align}
%
where $n=0,2,3$ corresponds to proportionality with flow rate,
velocity, shear gradient respectively. The plus sign corresponds to
erosion, and the negative sign corresponds to the clogging. In order
to study the effect of the above equation in whole network, we first
study the effect in a two parallel/series case.

\subsection{Erosion}
%
In erosion the rate of change of radius reads as
%
\begin{align}
  \frac{d r}{dt} & = \alpha \frac{Q}{r^{n}} 
\end{align}
%
Here, note that each pipe with radius $R$ acts as a resistor, we have
Poissoulle flow equation that relates the flow $Q$ to pressure
difference $\Delta P$ as
%
\begin{align}
  Q & = \frac{-\pi r^{4}}{8\mu L}  \Delta P\\
  Q & = -C(r) \Delta P, \quad C (r) = \frac{\pi r^{4}}{8\mu L} = {\beta}{r^{4}} 
\end{align}

\subsubsection*{Two pipes in series}

We consider two pipes in series as shown in
Fig. \ref{figure:resistor-series-1}. We are interested to see what
happens two the resistors for different initial conditions? How does
the values of the resistors evolve? What happens to the pressure
distribution at the note in between?
%
\begin{figure}[h]
  \begin{center}
    \begin{circuitikz}\draw
      (0,0) node[anchor=east] {$P_{l}$} to [short,o-] (0.1,0)
       to[R=$1/C_{1}$,-*] (2,0)  node [anchor=north] {$P_m$}
       to[R=$1/C_2$] (4,0)
       to[short,-o] (4.1,0) node [anchor=west] {$P_r$}; % The resistor
    \end{circuitikz}
    \caption{Two resistors at series}\label{figure:resistor-series-1}
  \end{center}
\end{figure}
%

We first simulate the results numerically to see what happens. The
results are shown in Fig. \ref{toy-series}. As it can be seen, for any
initial conditions the pressure at the middle point, converges to
$(P_l + P_{r})/2$ which basically means that the flow is homogenized.
%
\begin{figure}[!h]
  \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-series}}
\caption{Toy model for two pipes in series. In each iteration, we
  change the radius of the pipe as $r_{\text{new}} = r_{\text{old}} +
  \alpha Q/r_{\text{old}}^n$. For all different cases of $n$ the
  middle pressure converges to $(P_l + P_r)/2$.}
\label{toy-series}
\end{figure}  
%

We now show why this convergence happens. If the two pipes are in
series, then $Q$ is always the same in these two pipes. Therefore
%
%
\begin{align}
  \frac{d r}{dt} & = \alpha \frac{Q}{r^{n}} \\
  r^{n}{d r} & = \alpha {Q} dt \\
  \frac{1}{n+1} r^{n+1} -  \frac{1}{n+1} r_0^{n+1} & = \alpha Q t\\
  r & = \lp (n+1)\alpha Q t + r_0^{n+1}\rp ^{\frac{1}{n+1}} \\
  C_i & = \beta \lp (n+1)\alpha Q t + r_{i,0}^{n+1}\rp ^{\frac{4}{n+1}}
\end{align}
%
So the pressure at the middle point becomes as 
%
\begin{align}
  Q &= \frac{1}{1/C_{1} + 1/C_2}   \Delta P = \text{const.}, \\
  P_m - P_l &= \frac{Q}{C_{1}}   \\
  \frac{P_{m}-P_l}{P_r - P_l} & = \frac{1/C_{1}}{1/C_{1} + 1/C_2} = \frac{C_{2}}{C_{1} + C_2}  
\end{align}
%
Combining the results we find that
%
\begin{align}
  &\boxed{\frac{P_{m}-P_l}{P_r - P_l} = \frac{\beta \lp (n+1)\alpha Q t + r_{2,0}^{n+1}\rp ^{\frac{4}{n+1}}}{\beta \lp (n+1)\alpha Q t + r_{1,0}^{n+1}\rp ^{\frac{4}{n+1}} + \beta \lp (n+1)\alpha Q t + r_{2,0}^{n+1}\rp ^{\frac{4}{n+1}}} } \\
  &\lim_{t\to\infty} \frac{P_{m}-P_l}{P_r - P_l}  = \frac{1}{2} 
\end{align}
%
Note that for any power of $n$ the pressure in the middle point as $t\to\infty$
converges to $(P_l+P_r)/2$.

\newpage
\subsubsection*{Two Parallel Pipes Case}
%
Now assume two pipes in parallel as shown in
Fig. \ref{figure:resistor-series-par}. We first simulate the results
to see what happens for different initial conditions. The results for
different initial values of $r_1,r_2$ are shown in Fig. \ref{toy-par}.
%
\begin{figure}[!h]
  \begin{center}
    \begin{circuitikz}
      \draw
      (-0.5,0) node[anchor=east] {$P_{l}$} to [short] (0.1,0)
      -- (0.1,0.5) 
       to[R=$1/C_1$] (2,0.5)  -- (2,0) to [short] (2.5,0) node
       [anchor=west] {$P_r$};
      \draw
      (0.1,0)  --(0.1,-0.5) 
       to[R=$1/C_2$] (2,-0.5)  -- (2,0);
    \end{circuitikz} 
    \caption{Two resistors parallel together} \label{figure:resistor-series-par}
  \end{center}
\end{figure}
%

\begin{figure}[!h]
  \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-par}}
  \caption{Toy model for two pipes in parallel. In each iteration, we
    change the radius of the pipe as
    $r_{\text{new}} = r_{\text{old}} + \alpha
    Q_{i}/r_{\text{old}}^n$. When $n<3$, all of the flow eventually
    passes from either top or bottom pipe. When $n=3$, the flow
    proportion remains the same. When $n>3$, the flow homogenizes
    where half of the total flow i.e. $Q/2$ passes from top and the
    other half from bottom pipe.}
\label{toy-par}
\end{figure}

Now, we start to model to see why this happens. Initially, we note
that
%
\begin{align}
  Q_1 = C_1 \Delta P, \quad \text{ and }\quad Q_2 = C_2 \Delta P \\
  Q = (C_1 + C_2) \Delta P
\end{align}
%
We change the radius of each pipe according to its flow, as a result,
we have
%
\begin{align}
  \frac{dr_{1}}{dt}  = \alpha \frac{Q_{1}}{r_{1}^n}, \qquad  \frac{dr_{2}}{dt}  = \alpha \frac{Q_{2}}{r_{2}^n} \\
  r_1^n \frac{dr_{1}}{dt}  + r_2^n \frac{dr_{2}}{dt}  = \alpha (Q_1 + Q_2) = \alpha Q  
\end{align}
%
On the other hand, we know that
%
\begin{align}
  \Delta P = \frac{Q_{1}}{C_{1}}  = \frac{Q_{2}}{C_{2}} \\
  \Delta P = \frac{Q_{1}}{\beta r_1^{4}}  = \frac{Q_{2}}{\beta r_2^{4}}   \\
  \frac{dr_{i}}{dt}  = \alpha \frac{Q_{i}}{r^{n}_{i}} = \frac{\alpha \beta \Delta P}{r^{n-4}_{i}}   
\end{align}
%

We have
%
\begin{align}
  &r_{1}^{n-4} \frac{dr_{1}}{dt} = r_2^{n-4}\frac{dr_{2}}{dt}\\
  &\text{if }n=3, \quad \to \log(\frac{r_{1}}{r_{1,0}}) = \log(\frac{r_{2}}{r_{2,0}}), \to r_1 = \gamma r_2 \\
  & \text{if }n\neq 3, \quad r_1^{n-3} - r_2^{n-3} = \gamma
\end{align}
%
where $\gamma$ is a constant. In the above equation, without loss of
generality, we can assume that $r_{1}>r_2$ and $\gamma$ is
positive. Now, looking at the other part of the equation, we have
%
\begin{align}
  \frac{dr_{2}}{dt}  & =  \frac{\alpha \beta \Delta P}{r^{n-4}_{2}} \\
                     & = \frac{\alpha \beta }{r^{n-4}_{2}} \frac{Q}{\beta (r_{2}^{4} + r_1^4)} = \frac{\alpha Q}{r^{n}_{2} + r_{2}^{n-4} r_1^{4}} \\
                     & = \frac{\alpha Q}{r^{n}_{2} + r_{2}^{n-4} \lp r_2^{n-3} + \gamma \rp^{\frac{4}{n-3} }}\\
  \lb r^{n}_{2} + r_{2}^{n-4} \lp r_2^{n-3} + \gamma \rp^{\frac{4}{n-3} }\rb dr_2 & = \alpha Q dt\\
  \frac{1}{n+1} \lb r_2^{n+1} + \lp r_2^{n-3} + \gamma\rp^{\frac{n+1}{n-3} } \rb  & = \alpha Qt + C\\
  r_2^{n+1} + \lp r_2^{n-3} + \gamma\rp^{\frac{n+1}{n-3} }  & = (n+1)\lp \alpha Qt + C\rp \\
  r_2^{n+1} + r_{1}^{n+1} = At+B
\end{align}
%
So the two set of equations summarizes to
%
\begin{align}
  & \begin{cases}
    r_1^{n-3} - r_2^{n-3} = \gamma \quad \text{ if }n \neq 3,   \\
    r_1 = \gamma r_{2} \quad \text{ if } n=3
  \end{cases}\\
  & r_1^{n+1} + r_2^{n+1} = At + B
\end{align}
%
The plot for the solution to the above equations for different values
of $n\neq 3$ and also the separate solution for $n=3$ is shown in the
following figure.  
%

\begin{figure}[!h]
  \centerline{\includegraphics[width=0.8\textwidth]{./Figs/par_resistors}}
  \caption{Analytical solution for $r_1$ and $r_2$ for parallel
    resistors. For different $n$ the solution changes. Specifically,
    if $n<3$, then one of the diameters stops varying while the other
    one increases in size. If $n=3$, the both grow together, and if
    $n>3$ then they both increase in size. }
\label{anal-par}
\end{figure}

\subsubsection*{General Case}
%
In a general case, the resistors can be divided into series and
parallel resistors. Using that in each section, we only need to look
at the parallel resistors and determine the channelling. The resistors
in series do not affect the channelling to occur. They only contribute
tot he homogenization. Parallel resistors however, in the case of
$n>3$ result in channeling. Note that at some places, we might need to
use $\Delta-Y$ conversion to find the equivalent resistors. It can be
shown that the channeling can still be described using $\Delta-Y$
conversion.

\subsubsection{Some Corrections to Series and Parallel cases(Deng)}
\AZ{The case example here is the special case where $C_2=C_3$ in the series part and also $C_\text{eq}=C1$ where $C_\text{eq}$ is the equivalent resistor resulted from $C_1$ and $C_2$. This special case always results in the same fluid flux in the resistors. This special case can also be observed from the diagonal contour line present in Fig. \ref{anal-par}. } Numerical simulations show different result here for more complex cases other than naive parallel or series cases. For example for the following case Fig \ref{resistor-par-series21}.
\begin{figure}[ht]
    \begin{center}
    \begin{circuitikz}
      \draw
      (-0.5,0) node[anchor=east] {$P_{l}$} to [short] (0.1,0)
      -- (0.1,0.5) 
       to[R=$1/C_1$] (2,0.5)  --  (4,0.5)  -- (4,0) to [short] (4.5,0) node
       [anchor=west] {$P_r$};
      \draw
      (0.1,0)  --(0.1,-0.5) 
       to[R=$1/C_2$] (2,-0.5) to[R=$1/C_{3}$] (4,-0.4)--(4,0);
    \end{circuitikz} 
    \caption{Parallel/Series Case (Deng)} \label{resistor-par-series21}
  \end{center}

\end{figure}
The simulations are similar to previous ones that keep the flow constant while increasing the radius proportional to $Q/r^n $. It now shows that the flow does not need to be homogeneous through top and bottom tubes. A special case can be easily analytically calculated. Set $C_{1}(t=0) = 2, C_{2}(t=0)=C_{3}(t=0) = 1$, and let $n=7$, in this case 
\begin{equation}
    \frac{dC_i}{dt} = 4Q_i/C_i
\end{equation}
and $C_2=C_3$ will always hold, and it is not difficult to solve $C_1$ and $C_2$
\begin{align}
    \frac{dC_1}{dt} = \frac{8Q}{C_2+2C_1} \\
    \frac{dC_2}{dt} = \frac{4Q}{C_2+2C_1},
\end{align}
where $Q$ is the total flow. In fact we do not need to solve these simple equations and it is clear that at the end we get $C_2=C_3=1/2 C_1$ since $\frac{dC_1}{dC_2} = 2$. However, this means at the end $Q_1/Q = 4/5$ instead of $1/2$.

Intuitively, the failure of equalization of flow is due to the non-linearity of erosion law, which voids the common sense that two resistors in series can be combined as one. Therefore we expect the conclusions in this paper could be affected by the network structure.
\subsubsection{More general numerical results of Fig. \ref{resistor-par-series21}}
In general as we set $\frac{dr_i}{dt} = Q_i/r_i^n$ and $C_i = r_i^4$, in the network of Fig. \ref{resistor-par-series21} we have 
\begin{align}
    \frac{dC_1}{dt} &= \frac{4QC_1^{(7-n)/4}}{\Delta} \\
    \frac{dC_2}{dt} &= \frac{4QC_2^{(7-n)/4}C_3}{\Delta(C_2+C_3)} \\
    \frac{dC_3}{dt} &= \frac{4QC_3^{(7-n)/4}C_2}{\Delta(C_2+C_3)},
\end{align}
where $\Delta = C_1+\frac{C_2C_3}{C_2+C_3}$, the ratio $Q_1/Q_2 = C_1(C_2+C_3)/(C_2C_3)$. Fig. \ref{toy-par-series-eros} are the numerical result for $n=5$ and $n=7$ with $C_2(t=0)=C_3(t=0)=1$ and changing $C_1(t=0)$. $Q_1/Q_2$ are not converging to 1 in either case.  
\begin{figure}[H]
  \centerline{\includegraphics[width=1\textwidth]{Figs/par_series_12.png}}
  \caption{For different n and $C_1(t=0)$, the simple network under erosion yields different $Q_1/Q_2$.}
\label{toy-par-series-eros}
\end{figure}  
\newpage
\subsection{Clogging}
%
In clogging, the rate of change of radius reads as
%
\begin{align}
  \frac{dr}{dt } = -\alpha \frac{Q}{r^{n}} 
\end{align}
%
Similar to the erosion, we first study a simplified model with two
pipes in series and parallel.

\subsubsection*{Series}
%
We consider the following pattern for the resistors
(Fig. \ref{figure:resistor-series-clogging}). We first simulate for different initial conditions, and look at the
middle pressure over long time. Since the radius is decreasing, we
need to set a maximum amount of reduction. Since the radius cannot
become negative. For different initial conditions we look at the
middle pressure, and we observe that no matter what power of $n$ is,
the middle pressure remains almost unchanged. If the minimum threshold
is hit, then some jumps can be observed, however, the total behavior
is such that the ratio of the middle pressure remains almost similar.

%
\begin{figure}[!h]
  \begin{center}
    \begin{circuitikz}\draw
      (0,0) node[anchor=east] {$P_{l}$} to [short,o-] (0.1,0)
       to[R=$1/C_{1}$,-*] (2,0)  node [anchor=north] {$P_m$}
       to[R=$1/C_2$] (4,0)
       to[short,-o] (4.1,0) node [anchor=west] {$P_r$}; % The resistor
    \end{circuitikz}
    \caption{Two resistors at series}\label{figure:resistor-series-clogging}
  \end{center}
\end{figure}
%

% 
\begin{figure}[H]
  \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-series-clog}}
  \caption{Toy model for two pipes in series. In each iteration, we
    change the radius of the pipe as
    $r_{\text{new}} = r_{\text{old}} - \alpha
    Q_{i}/r_{\text{old}}^n$. Note that we set a maximum change of
    $\Delta r = \min{1,r}$.}
\label{toy-series-clog}
\end{figure}

\subsubsection*{Parallel}
%
We also study the behavior when the pipes are in parallel (See
Fig. \ref{figure:resistor-par-clogging}). The numerical results of the
simulations are shown in Fig. \ref{toy-par-clog}. The behavior is
again very similar to the two pipes in series. We again find a similar
trend where the ratio of the $Q$'s remains unchanged. 
%
\begin{figure}[H]
  \begin{center}
    \begin{circuitikz}
      \draw
      (-0.5,0) node[anchor=east] {$P_{l}$} to [short] (0.1,0)
      -- (0.1,0.5) 
       to[R=$1/C_1$] (2,0.5)  -- (2,0) to [short] (2.5,0) node
       [anchor=west] {$P_r$};
      \draw
      (0.1,0)  --(0.1,-0.5) 
       to[R=$1/C_2$] (2,-0.5)  -- (2,0);
    \end{circuitikz} 
    \caption{Two resistors parallel together} \label{figure:resistor-par-clogging}
  \end{center}
\end{figure}

%
\begin{figure}[H]
  \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-par-clog}}
  \caption{Toy model for two pipes in series. In each iteration, we
    change the radius of the pipe as
    $r_{\text{new}} = r_{\text{old}} - \alpha
    Q_{i}/r_{\text{old}}^n$. Note that we set a maximum change of
    $\Delta r = \min{1,r}$.}
\label{toy-par-clog}
\end{figure}

\subsection{Generalization of Erosion Law(Deng)}
Here is a naive guess of how the exponent of erosion law can change the network topology. We can assume the erosion law  
\begin{align}
    C &= a r^m \\
    \frac{dr}{dt} &= \frac{b Q}{r^n},
\end{align}
where $a,b,m,n$ are some constants. It can be derived that it is equivalent to
\begin{equation}
    \frac{dC}{dt} \propto QC^{1-\frac{n+1}{m}}.
\end{equation}
Particularly in previous series/parallel cases, $m=4$ and $n$ varies. We observed that $n<3$ leads to channeling while $n>3$ leads to homogeneity. Therefore, a reasonable guess is with the erosion law 
\begin{equation}
    \frac{dC}{dt} \propto Q^\alpha C^\beta,
\end{equation}
when $\alpha = 1$, the sign of $\beta$ will determine the channeling behavior. And the simulations as shown in Fig. \ref{fig:erosionExp} confirm the guess. Furthermore, we can see the change of flow distribution in terms of $P(Q)$, the distribution of flow in every resistor, as shown in Fig \ref{fig:PQ}. The exponential tail remains in the simulations for the $\beta = 0$ case. We do not have a theoretical explanation why the exponential tail remains in the $\beta = 0$ case.
\begin{figure}[H]
  \centerline{\includegraphics[width=1\textwidth]{./Figs/erosionExp.png}}
  \caption{A grid network erosion simulations with different $\beta$ exponents. Top left is the initial flow distribution for every simulation (T=1) and the rest are final distributions of the flow. We can easily distinguish the channeling ($\beta>0$) and homogenization behavior ($\beta<0$) from the results. }
\label{fig:erosionExp}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width = 0.8\textwidth]{Figs/PQ.png}
    \caption{The flow distribution of networks in Fig \ref{fig:erosionExp} for different $\beta$'s. It is easy to distinguish channeling ($\beta = 1$), homogeneity ($\beta = -1$) and exponential tail ($\beta = 0$) from the flow distributions at the end of simulations. The delta function at $0$ is due to the resistors connecting vertically, which are perpendicular to the average flow.}
    \label{fig:PQ}
\end{figure}

\newpage

\section{Permeability modification model}
%
All the models introduced above represent different scenarios where
the clogging/erosion might happen. The question, however remains that
what could be a microscopic model? What it can predicts? and is there
a proxy (bulk property) that can be observed to study the microscopic
model?

We propose the following microscopic model: The polymers passing through pores are dragged by the flow. There are
two forces competing when a polymer adheres to the surface of a pore
(1) The drag force on the particle coming from flow, and (2)
ionic/VanderWaals or whatever force that tries to adhere the particles
to the surface. A particle attaches to the surface if the drag force
exerted by the fluid flow around it is smaller than the
VanderWaals/ionic force.

For simplicity, I assume that the force is ionic with a force distance
profile of $F= K/X^2$, where $K$ is a constant and $X$ is the
distance. I assume that polymers have an effective radius of $d_{p}$
and fluid viscosity is $\mu$ and the flow rate is $Q$. This model
states that the particle attaches to the surface when
%%
\begin{align}
    F_{\text{drag}} &\leq F_{\text{ionic}}\\
    6\pi \mu d_{p} \frac{2Q}{\pi R^2} \lp 1- \frac{r^2}{R^2} \rp & \leq \frac{K}{(R-r)^2} \\
    1 - \frac{r^2}{R^2} & \leq \lp \frac{K }{12 \mu  d_{p} Q} \rp \frac{1}{\lp 1 - r/R \rp^2} \\
    1 & \leq \frac{r^2}{R^2} + \alpha \frac{1}{\lp 1-r/R\rp ^2}
\end{align}
%
where $\alpha = K/\lp 12\mu d_pQ \rp$ is a factor that compares the ionic force and viscous
force. Note that it depends on the flux rate. If we define
$x = 1- r/R$ we obtain
%
\begin{align}
    1 &\leq (1-x)^{2} + \frac{\alpha}{x^2} \\
    x^2- x^2(1-x)^{2} &\leq \alpha \\
    x^2 (1- (1-x)^2) & \leq \alpha \\
    x^3(2-x) & \leq \alpha \\
    \text{if } x\ll1 \to x & \leq \lp \frac{\alpha}{2}\rp^{1/3}
\end{align}
%
%
\begin{figure}[H]
  \centering
  \includegraphics[width=4cm]{./Figs/model2.jpg}
  \caption{Flow in the pipe}
\end{figure}
%
As a result the distance is proportional to $\alpha^{1/3}$. Note that
$\alpha$ depends on $1/Q$.  Now, lets
find the flux passing through this adsorption layer (any polymer in
this layer would attach to the surface)
%
%
\begin{align}
  \text{volume}/\text{time} &= \frac{1}{2} R \alpha ^{1/3} \cdot \frac{Q}{R^{3}} R\a^{1/3} \cdot 2\pi R = \pi Q \a^{2/3}  = \pi \lp \frac{K  }{12 \mu  d_{p}} \rp^{2/3} Q^{1/3} \\
  \text{volume}/\text{time} & \propto {Q^{1/3}} 
\end{align}
%
Now, if we assume that the number of polymers passing through the area
cause clogging of the pipe and change the total area of the pipe, then
we find that

%
\begin{align}
  d (\pi R^2) \propto Q^{1/3} \quad \to \quad R dR \propto Q^{1/3}
\end{align}
%
We also know that $k = \pi R^4/8l^2$, as a result
%
\begin{align}
  dk \propto R^{3} dR \\
  dk \propto R^2 Q^{1/3} \\
  dk \propto Q^{1/3}
\end{align}

\subsection*{Experimental Results}
%
In Shima's paper, we report a figure that shows the evolution of
permeability $k$ per volume of polymer $V_{pol}$ that passes through
the porous media. Basically we are plotting $\Delta k$ versus $Q$
passing through the porous media. The figure and best polynomial fit
is shown blow
%
%
\begin{figure}[H]
  \centering
  \includegraphics[width=0.55\textwidth]{./Figs/k-evolution.eps}
  \caption{$k$ versus volume of fluid passed through a porous media}
\end{figure}

\section{Foam Relaxation and Non-monotonic Aging}
%
So far the observation is that no matter how much disorder we
introduce in the size distribution of pipe diameters, no relaxation
behavior can be observed in a structured random network of tubes. If
we prune the network, near the percolation limit, the slow $log(t)$
dynamics is observable, however, it seems to be very unlikely that it
is the case. We need to introduce a toy model that can capture this
behavior. My intuition is that the relaxation is due to aging of the
adhesion of pore surfaces attaching to each other due to compression.
%

\subsection{Modeling}
%
We assume a network of pores, as we did before. The network of the pores are shown in Fig. \ref{fig:relaxation-network}. The pores are with different size. the connections are also with different sizes. 
%
\begin{figure}[H]
  \centering
  \includegraphics[width=0.55\textwidth]{./Figs/relaxation_grid}
  \caption{An example of pores connected with different sizes and different resistors} \label{fig:relaxation-network}
\end{figure}
%
On a structured grid, we initialize a random distribution of pore sizes, with random resistor connections. For each pore, we have a four neighbors. We first  need to determine the initial pressure of the pores. \red{I don't have a good way to initialize the pressures, for now, I consider them to be the same amount. It could also depend on the initial volume.} Due to Darcy's law we have
%
\begin{align}
    Q_{ij} = \frac{\pi r_{ij}^4}{8 \mu L_{ij}} \left( {P_i - P_j}\right) = \frac{P_i - P_j}{R_{ij}}, \qquad R_{ij} \equiv \frac{8 \mu L_{ij}}{\pi r_{ij}^4}
\end{align}
%
Where $r_{ij}$ and $L_{ij}$ are radius and length of the resistors connecting the pores. $Q_{ij}$ represents the outflux from node $i$ to node $j$. At each time for each pore, we can calculate the total out-flux of the flow is as 
%
\begin{align}
    Q_i = \sum_{j \in N(i)} Q_ij = \sum_{j \in N(i)} \frac{\pi r_{ij}^4}{8 \mu L_{ij}} \left( {P_i - P_j}\right)
\end{align}
%
where $N(i)$ represents the neighbors of $i$-th node. After calculating the total outflux, we need to find an equation on how to update the pressure of the pore $P_i$. If we assume that ideal gas law, we have
%
\begin{align}
    P_i V_i = m_i RT \quad \dot{m_i} = - \rho Q_i \quad \text{(minus sign is since } Q_i \text{ is out-flux)} 
    \end{align}
%
Assuming a constant density, we have
%
\begin{align}
    \frac{d P_i}{dt} = \frac{RT}{V_i} \frac{d m_i}{dt}  = -\frac{\rho RT}{V_i} Q_i \\
    \frac{d P_i}{dt} = - \frac{\rho RT}{V_i} \sum_{j \in N(i)} \frac{P_i - P_j}{R_{ij}}  
\end{align}
%
In the matrix format this can be written as 
%
\begin{align}
\frac{d\mathbf{P}}{dt} = \mathbf{D} \cdot \mathbf{A} \cdot \mathbf{P}\\
\mathbf{P} = \begin{bmatrix} P_1 \\ \vdots \\ P_n
\end{bmatrix}\\
\mathbf{D} = \text{diag}(\frac{-\rho R T}{V_1},\cdots, \frac{-\rho R T}{V_n})\\
[\mathbf{A}]_{ij} = -\frac{1}{R_{ij}}, \quad [\mathbf{A}]_{ii} = \sum_{i\in N(i)} \frac{1}{R_{ij}}
\end{align}
%
To solve the above equations, we expand the LHS to obtain
%
\begin{align}
    \frac{d\mathbf{P}}{dt} = \mathbf{D} \cdot \mathbf{A} \cdot \mathbf{P} \\
    \frac{\mathbf{P}_{n+1}- \mathbf{P}_n}{\Delta t} = \mathbf{D} \cdot \mathbf{A} \cdot \left( \theta \mathbf{P}_{n+1} + (1-\theta) \mathbf{P}_{n}\right) \\    
    \left( \mathbf{I} - \theta\Delta t \mathbf{D}\mathbf{A} \right) \mathbf{P}_{n+1} = \left( \mathbf{I} + (1-\theta) \Delta t \mathbf{D} \mathbf{A}\right) \mathbf{P}_n
\end{align}
%
Note that $0 \leq \theta \leq 1$. Having $\theta = 0$, the solution becomes explicit forward Euler, and $\theta = 1$, the equations become implicit method. Note that for a given geometry $\mathbf{D}$ and $\mathbf{A}$ are fixed and the solution can be obtained through matrix multiplication as
%
\begin{align}
 \mathbf{P}_{n+1} = \left( \mathbf{I} - \theta\Delta t \mathbf{D}\mathbf{A} \right)^{-1} \left( \mathbf{I} + (1-\theta) \Delta t \mathbf{D} \mathbf{A}\right) \mathbf{P}_n
\end{align}
%
Using the above relations, I found that the relaxation does not happen over multiple decades. It seems very unlikely that the porous structure is causing this slow relaxation. 
\begin{figure}[H]
  \centering
  \includegraphics[width=0.55\textwidth]{./Figs/relaxation-porous.eps}
  \caption{Mean pressure relaxation in a random network of pores with a constant pore size and random pore size.} \label{relaxation}
\end{figure}

Looking at the microgrpah image of open-cell foams (as shown in Fig. \ref{micrograph}), it seems unlikely that the fluid is playing a role in this. 
%
\begin{figure}[H]
  \centering
  \includegraphics[width=0.45\textwidth]{./Figs/micrograph-open-cell.png}
  \caption{Micrograph showing cellular microstructure of a polyester urethane foam (100 ppi) (Taken from \cite{gong2005compressive}) } \label{micrograph}
\end{figure}
%
I believe that since the material is visco-elastic, the response is due to the polymer structure that have a large relaxation times.

\section{Distribution of Resistor-level response}
%
We consider a random resistor network. In this network, we remove a single resistor, remove it from the network. The permeability changes. We then record the PDF of the change in permeability. 
The result looks as follows
%

\section{Flow-Chains: Force-Chains}
%
We observe patterns similar to force-chains observed in granular
materials, but in porous media. See Fig. \ref{flow-chain}. For a movie
of this behavior see
\href{https://www.youtube.com/watch?v=E8sVcxipNio}{this link}.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.45\textwidth]{./Figs/flowchain1}
  \includegraphics[width=0.45\textwidth]{./Figs/flowchain2}
  \caption{Force chain behavior in porous media.} \label{flow-chain}
\end{figure}

\end{document}

### 2021-04-28 Figs/random_network/Porous - Instability/prl_paper.tex
Initial Overleaf Import

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{Instability and Porous Evolution}% Force line breaks with \\
\thanks{A footnote to the article title}%

% \author{}
% \altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with \\
% \author{}%
%  \email{}
% \affiliation{% SEAS, Pierce Hall, Harvard University}%

% \collaboration{MUSO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
We study the dynamics of pore network evolution.

% \begin{description}
% \item[Usage] Secondary publications and information retrieval purposes.
% \item[PACS numbers] May be entered using the \verb+\pacs{#1}+ command.
% \item[Structure] You may use the \texttt{description} environment to structure your abstract; use the optional argument of the \verb+\item+ command to give the category of each item.
% \end{description}

\end{abstract}

% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents
\section{Introduction}
%
Fluid flow through a porous medium can dynamical change the pore-level micro-structure by eroding and/or material deposition/sedimentation. Such  changes to micro-structure and solid boundaries affect local fluid flow as well as bulk behaviors. These processes of erosion or deposition in porous media play essential role in many environmental and industrial applications such as groundwater remediation and precipitation of minerals in rocks, bio-film growth in water filtration, or enhanced oil recovery with polymer flooding, water-deriven erosion. The structures of such porous media are usually highly disordered with a hetereogeneous distribution of pore-level flow velocities.

% Albeit there is an abundance of applications, the evolution of structures exposed to erosion and deposition is in general not easily predictable and usually requires the use of numerical techniques.

% However, this process is difficult to model due to diverse processes that may arise, including particle advection through the pore space by fluid flow, adsorption and deposition onto the solid matrix, and erosion or resuspension.

\begin{itemize}
\item Importance of porous media
\item importance of dynamics in porous media
\item we study evolution with a network model
\end{itemize}

\begin{figure}[h]
    % \centering
    \includegraphics[width = 0.45\textwidth]{Figs/Fig1.eps}
    \caption{(a) An example of a porous media; (b) The real network of pores, and a structured grid equivalent case (c) The PDF of velocities for various distribution of diameters.}\label{fig:fig1}
\end{figure}

\section{Methods}
%
Flow through pores and throats of a porous medium can be modeled using a network of tubes with varying radii ( Fig. \ref{fig:fig1}a,b). In this network, the pores are represented with nodes, and the throats are modeled as simple tubes where the diameters/length can be random. where they approximate the flow resistance between the pores. A structured network of nodes with a random distribution of flow resistances for edges has shown to be a valid approximate model that correctly captures the exponential distribution of velocities of a porous medium. Here we consider this similar model to obtain some insights of structural change effects. We consider a fluid with density $\rho$ and kinematic viscosity $\mu$ flowing through the pores. We consider low Reynolds fluid or Poiseuille flow. In each tube Darcy's law hold $ P_i - P_j  = \frac{128 \mu L_{ij} }{\pi d_{ij}^4} Q_{ij}$ where $P_i,P_j$ represents pressures at pores $i,j$, and $d_{ij}, L_{ij}, Q_{ij}$ are respectively the radius, length, and fluid flow rate in the tube connecting pores $i$ and $j$. We then consider a network grid and assume a pressure difference between nodes left and the right boundary. Due to conservation of mass at each node, the total flow into a node should add up to zero. Solving for conservation of mass at all nodes, a system of equations can be obtained, where the solution is the pressures at all nodes. Using pressure values at the nodes, the flow rate in each tube is then obtained using Darcy's law. Considering different distribution of radius/length of the tubes, we find that the for any distribution, with large enough disorder the distribution of normalized fluid flux in the tubes collapses on a universal curve where $P(\hat{q}) \propto e^{-\alpha \hat{q}}$ for large $\hat{q}$ where $\hat{q}$ is the normalized fluid flux $\hat{q} = {q}/\langle q \rangle$. This can be simply proved using a mean field approximation (See supp material).

\newpage
% Fig.2: network evolution for different parameters powers of n
\onecolumngrid
\begin{figure*}[h]
    % \centering
    \includegraphics[width = 1\textwidth]{Figs/ErosionSim.png}
    \caption{Erosion  simulations on a grid and a random network. (a)On a triangular grid network, we initialize every tube with a random radius uniformly distributed. The flow distribution is indicated by line width and transparency, the color gradient indicates the pressure field from the high pressure at the left boundary (red) to the low pressure at the right boundary (blue). (b) Different final states after 300 times iteration of erosion cases with different $n$'s. Channeling and homogenization are obvious in $n=1$ case and $n=6$ case respectively. The transition happens at $n=3$, which does not change the flow density distribution horizontally. (c) With the same number of points in the grid network, the position of every point is uniformly randomly distributed and we create the network using Delaunay triangulation to avoid crossed tube in 2D graph. Random radius is then assigned to every tube. (d) Different final states after 300 times iteration of erosion cases with different $n$'s. Similar channeling and homogenization effect are observed for $n=1$ and $n=6$ respectively. The transition happens at $n=3$, which does not change the flow density distribution horizontally.    }
    \label{fig:ErosionFig}
\end{figure*}

\twocolumngrid
% Fig 3: toy model
% Fig 4: phase transition

\section{Results}
\subsection{Simulation results for grid networks and random networks}
We run simulations on grid networks and random 2D networks. Both show similar results. For erosion cases, $n=3$ is a critical point that the final states will retain the exponential tail of flow distribution. When $n<3$, the erosion law yields channelling effect which strengthens a few tube faster than the rest. When $n>3$, the 
\section{Conclusion}

\bibliography{ref.bib}

\end{document}
%

### 2021-04-28 Figs/random_network/Porous - Instability/shear_rate_homogenity.tex
Initial Overleaf Import

--- 2021-04-28 Figs/random_network/Porous - Instability/combined.tex
@@
 \usepackage{circuitikz}
-\usepackage{float}
-\usepackage{hyperref}
-\newcommand{\AZ}[1]{{\color{red}{Ahmad: #1}}}
-\newcommand{\red}[1]{{\color{red}{#1}}}
-\title{Porous Media Project}
+
+\title{Network Evolution}
 \author{Ahmad}
-\date{}
-
+%-------------------------------------------------------------------
 \begin{document}          
@@
 
-\tableofcontents
+In this report, we study the erosion or clogging in a porous media. We consider the porous material as a network of pores connected through
 
-\section{Introduction}
+\section{Toy Model 1 - Erosion }
 %
-In order to study the porous media, we introduce a model that captures
-flow behavior through a porous material. We consider the porous media
-as a network of pores that are connected together through
-connections. The schematic of our model is shown in
-Fig. \ref{porous-schematic}. We use a random resistor networks on a
-structured grid as our model to study the flow behavior. Each node
-represents a pore and each edge represents the throats between
-pores. We use simple Poiseuille flow through pipes to model fluid flow
-through pipes. In each pipe with diameter $d$, length $L$, and pressure difference
-of $\Delta P$ on both sides, results in a flow $Q$, where
-%
-\begin{align}
-    \frac{\Delta P}{L}  = \frac{128}{\pi} \frac{\mu Q}{d^4} 
-\end{align}
-%
-where $\mu$ is the viscosity of the fluid. The above relation is known
-as Darcy's law.
-
-%
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\textwidth]{./Figs/porous-schematic}
-  \caption{Schematic of the network model for porous media: (a) a
-    sample cross section of a porous media. (b) The porous media can
-    be considered as a network of pores connected through resistive
-    connections. (c) The random network obtained from porous
-    media. (d) Reordering the porous media network on a structured
-    grid. (e) The ordered structured network used where the
-    connections are assumed to be random resistors.} \label{porous-schematic}
-\end{figure}
-%
-
-\section{Numerical Simulation}
-%
-We consider a network of tubes with a random distribution of diameters
-as shown in Fig. {porous-schematic}e. Darcy's law is obtained thought
-the momentum equation and relates the pressure and the flow through
-the pipes. Furthermore, at each node the summation of the inflows
-should add up to zero (conservation of mass). Using this a system of
-equations $AP=B$ is obtained where $P$ is the vector of pressures at
-nodes, $A$ is sparse where the nonzero elements are
-% 
-\begin{align}
-  A_{ii} &= \sum_{j \text{ neighbors of } i} \frac{\pi }{128 \mu L} d_{ij}^4 \\
-   A_{ij} &= 
-  \begin{cases}
-    -\frac{\pi }{128 \mu L} d_{ij}^4, \quad \text{if }j \text{ is
-      neighbor of }i\\
-    0, \quad \text{otherwise}
-  \end{cases}
-\end{align}
-%
-Note that if all the pipes have the same diameter, then the flow is
-only in the horizontal pipes, and vertical pipes will carry no flow.
-
-\subsection*{Numerical results}
-%
-We consider a 2d network of pipes, and a pressure difference between
-the left and right nodes. We further assume different distribution of
-pipe diameters and find the flow $q$ in the pipes. When the pipes are
-all the same diameter, then the velocities in the pipes are either $0$
-or some nonzero value. As we increase the randomness in the pipes, we
-observe that the PDF of velocities starts to follow an exponential
-tail trend. Interestingly, if the disorder in pipes diameter is large
-enough, the PDF of velocities in the pipes, no matter what
-distribution we pick follows the same distribution. 
-%
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.6\textwidth]{./Figs/distribution}
-  \caption{PDF of normalized velocities of the pipes in a random
-    network of pipes, $v$ is the velocity in the pipe, $Q$ is the
-    total flux, $N$ is the number of pipes in the vertical direction,
-    $\langle A\rangle$ is the average of the area of the pipe. Note that
-    $N\langle A\rangle$ is the average area carrying the flow $Q$. } \label{pdf-result}
-\end{figure}
-
-\section{Analytical results}
-%
-\label{sec:analytical}
-In order to describe the universality observed above, we introduce the
-following mode. First, instead of using the structured rectangular
-grid, we use a structured diagonal grid. This will simplify the
-analytical model (see Fig. \ref{grid-result}).
-
-%
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=1.0\textwidth]{./Figs/grid-analytica}
-  \caption{Schematic of grids: (a) The structured rectangular grid
-    used in the numerical simulation. (b) The structured diagonal grid
-    used in the analytical model. } \label{grid-result}
-\end{figure}
-%
-We assume that the total flow to node $i$ at level $L$ is noted by
-$Q(L,i)$. This flow is then redistributed to the neighboring nodes at
-the level $L+1$. We assume that this redistribution is done by weights
-$w_{ij}$ as
-%
-\begin{align}
-  Q(L+1,j) = \sum_i w_{ij} Q(L,i) = w_{i,i+1} Q(L,i+1) + w_{i,i} Q(L,i) \label{total-flow}
-\end{align}
-%
-where $\sum_{j} w_{ij} = 1$ (since the total outflow from node $i$ is
-$\sum_j q_iw_{ij}$ and this value should add up to $q_i$). We assume
-that $w_{ij}$ are drawn from a distribution $\eta(w)$. Since $\eta(w)$
-is a distribution, then $\int \eta(w) dw = 1$. Furthermore, since
-$\sum_jw_{ij} = 1$, we can conclude that
-%
-\begin{align}
-  \sum_j w_{ij}=1 \to N {E}[w_{ij}] = 1 \to E[w_{ij}] = 1/N \to {\int w\eta(w) dw = 1/N}
-\end{align}
-%
-
-Now we use the technique of mean field analysis for a general
-distribution of $\eta(w)$ to find the distribution of $Q$ at the
-layers. The values of $Q(D,i)$ are not independent for neighboring
-sites; however, the mean field approximation ignores these
-correlations. We have
-%
-\begin{align}
-  P_L (Q) = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P_{L-1}(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp
-\end{align}
-%
-The constraint that $Q$'s emanating downward should add up to one is
-in the definition of $\eta(w)$. The only approximation in the above
-equation is that we neglect the possible correlation between the
-values of $Q$ among ancestors. If we take the Laplace transform of
-the above equation, we obtain
-%
-\begin{align}
-  \tilde P(s) & \equiv \int_0^{\infty} P(Q) e^{-Qs} dQ\\
-  \xrightarrow{\int_0^{\infty} (\cdot) e^{-Qs} dQ}  P (Q) & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp \\
-  \tilde P(s) & = \int_0^{\infty} \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp e^{-Qs}dQ \\
-              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j e^{-\sum w_{j}Q_{j}} P(Q_j)\right\}   \\
-              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \tilde P(s w_j) \right\} \\
-  & = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N}
-\end{align}
-%
-Or to summarize
-%
-\begin{align}
-  \boxed{\tilde P(s) = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N}} \label{eq:main-laplace}
-\end{align}
-%
-Note that in the above equation $N$ determines the number of
-neighboring sites and in our structured diamond grid $N=2$. The above
-equation is recursively converges to a distribution.  If we set
-$\eta(w) = \delta(w-1/2)$, then the flow at each node has probability of
-$1/2$ to move up or down. As a result the flow at a given depth $L$
-will be homogeneous as $P_L(Q) = \delta (Q-\bar{Q})$ where $\bar{Q}$
-is the average of input fluid flow. This case is the same as the same
-diameter which results in a singular solution in the structured grid.
-
-\subsection*{$P(Q)$ decays faster than $Q^{-n}$ for any $n$}
-We first show that $P(Q)$ decays faster than any power of $Q$ for any
-weight distributions. We expand the Laplace transform as
-%
-\begin{align}
-  \tilde P(s) = 1 + \sum_j \tilde P_{j} s^{j}
-\end{align}
-%
-Inserting this expansion into Eq. \eqref{eq:main-laplace}, we obtain
-%
-\begin{align}
-  1 + \sum_j \tilde P_{j} s^{j}  & = \lp  \int_0^1 d w \eta(w) \lb 1 + \sum_j \tilde P_{j} (sw)^{j}\rb    \rp^{N} \\
- & = \lp  1 + \sum_j \tilde P_j \langle w^{j}\rangle  s^{j}   \rp^{N}
-\end{align}
-%
-where $\langle w^j \rangle = \int_0^1 \eta(w) w^j dw$ is the $j$-th
-moment of the weights $w$. In the above equation we can observe that
-%
-\begin{align}
-  P_j \lp N \langle w^j\rangle -1 \rp = G(P_{j-1}, P_{j-1}, \cdots, P_1)
-\end{align}
-%
-In the above equation $P_j$ can only diverge only if $N\langle w^j
-\rangle -1$ is zero. If $w$ can only be zero and one, then $\langle
-w^j\rangle =\langle w \rangle = 1/N$ and the coefficient can become
-zero! Other than this special distribution where $0 \leq w \leq 1$,
-then
-%
-\begin{align}
-  & w\in [0,1] \rightarrow w>w^2>w^3> \cdots \\
-  & \forall k>1 \rightarrow \langle w^k \rangle < \langle w \rangle = \frac{1}{N} 
-\end{align}
-%
-which means that $N\langle w^j \rangle -1$ is not zero and as a result
-$P_j$ is finite. $P_j$ on the other hand is the $j$-th moment or
-$\langle Q^j\rangle$ and it is finite. If $P\approx Q^{-n}$, then the
-$n$-th moment will not be finite i.e. $\langle Q^{n+1}\rangle =
-P_{n+1}$ is not finite. We can then conclude that $P(Q)$ should go to
-zero faster than any $Q^{-n}$ as $Q\to \infty$! In other words $d \log
-P(Q) / d \log Q \to -\infty$ as $Q\to \infty$.
-
-\subsection*{Exponential Decay}
-%
-The main governing equation for a diamond grid is 
-%
-\begin{align}
-  \tilde P(s) = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{2} 
-\end{align}
-%
-In order to have an approximation for $\eta(w)$ we do the following:
-At each node there are two nodes where the flux is distributed by
-$w_1$ and $w_2$. Lets assume that $w_1$ is uniformly distributed
-between $0$ and $1$. As a result $w_2 = 1-w_1$ (since conservation of
-mass $w_1 + w_2 = 1$). Now $\eta(w)$ can be found as
-%
-\begin{align}
-  & \eta(w) = M \int_0^1 dw_1 \delta(1-w_1-w) =  M, \\
-  \text{since }& \int_0^1 \eta(w) dw = 1 \to M =1 \\
-  & \eta (w) = 1
-\end{align}
-%
-Just for completeness, if there are three connections ($N=3$), then we
-have
-%
-\begin{align}
-  \eta(w) & = M \int_0^1 dw_1 \int_0^1 dw_2 \delta(1-w_1-w_2 - w)\\
-          & = M(1-w)  \to \int_0^1\eta(w) dw = 1 \to M = \frac{1}{2} \\
-  & \eta(w) = \frac{1}{2} (1-w)
-\end{align}
-%
-As a result the main equation simplifies to
-%
-\begin{align}
-  \tilde P(s) = \lp  \int_0^1 d w  \tilde P(s w)  \rp^{2} 
-\end{align}
-%
-In order to solve the above equation, we assume $\tilde V (s) =
-\sqrt{\tilde{P}(s)}$.
-%
-\begin{align}
-  \tilde{V}(s) & = \int_0^1 dw \tilde V (sw) = \int_0^s \frac{du}{s}  \tilde{V}^{2}(u) \\
-  s\tilde{V}(s) & = \int_0^s du  \tilde{V}^2(u) \\
-\end{align}
-%
-Taking the differentiation with respect to $s$ yields
-%
-\begin{align}
-  \tilde{V}(s) + s \frac{d \tilde{V}(s)}{d s} = \tilde{V}^2(s) \\
-  \frac{d \tilde{V}}{\tilde{V}^2-\tilde{V}} = \frac{ds}{s}  \\
-  \log\lp \frac{1-\tilde{V}}{\tilde{V}} \rp  = \log(s)\\
-  \tilde{V}(s) = \frac{1}{1+Cs} 
-\end{align}
-%
-We set the mean to $1$ i.e.,
-%
-\begin{align}
-  \int_0^{\infty} Q P(Q) dQ = 1 \to \frac{d\tilde{P}}{ds}|_{s=0}  = -1\\
-  \frac{d \tilde{V}}{ds}  = \frac{1}{2 \sqrt{\tilde{P}(s)}} \frac{d \tilde{P}(s)}{d s}   \to \frac{d\tilde{V}(s)}{ds}|_{s=0} =\frac{-1}{2} \\
-  \frac{d\tilde{V}(s)}{ds} = \frac{-C}{(1+Cs)^{2}}|_{s=0} = -C = \frac{-1}{2}  \to C=\frac{1}{2} 
-\end{align}
-%
-As a result, we have
-%
-\begin{align}
-  \tilde{P}(s) = \lp\frac{1}{1+s/2} \rp^2 \\
-  P(Q) = 4Q e^{-2Q}
-\end{align}
-%
-We can then show that for a uniform distribution of $w$'s, the PDF of
-$Q$'s become an exponential tail. For other distribution of $w$'s, we
-similarly find a similar trend. Actually, we should that the PDF of
-$Q$ should decay faster than any power law for any distribution of
-$w$. Note that the only parameter that determines the the PDF of the
-flow is the average flux. This shows that why we observe the universal
-behaviour for pdf.
-
-\section{Continuous Limit}
-%
-In the previous section (\S \ref{sec:analytical}), we used a toy model
-to describe the flow behavior. The main equation connecting the flow
-at different layers was Eq. \eqref{total-flow}. In this section, we
-are interested to see what a continuous limit of the above model will
-be. Consider Eq. \eqref{total-flow} as
-%
-\begin{align}
-  Q(i,j+1) = w_{i-1,j} Q(i-1,j) + w_{i+1,j} Q(i+1,j) 
-\end{align}
-%
-where we had a constraint on the weights as 
-%
-\begin{align}
-  w_{i-1,j} + w_{i+1,j} = 1
-\end{align}
-%
-Now, lets assume that these weights are perturbations around the a
-uniform distribution such that
-%
-\begin{align}
-  w_{i\pm 1,j}= \frac{1}{2}( 1 \pm v_{i\pm 1,j})
-\end{align}
-%
-with th above assumption, we find that
-%
-\begin{align}
-  Q(i,j+1) & = \frac{1}{2} \left( 1 - v_{i- 1,j}\right) Q(i-1,j) + \frac{1}{2} \left( 1 + v_{i+ 1,j}\right) Q(i+1,j)  \\
-  Q + L_y \frac{\p Q}{\p y } + L^2_y \frac{\p^{2}Q}{\p y^2}  & = \frac{1}{2} (1-v + L_x \frac{\p v}{\p x}  ) \left( Q - L_x \frac{\p Q}{\p x} +   \frac{1}{2} L_x^2 \frac{\p Q^2}{\p x^2}\right) \nonumber\\
- & \qquad   +\frac{1}{2}  (1+v + L_x \frac{\p v}{\p x} )\left( Q + L_x \frac{\p Q}{\p x} + \frac{1}{2}L_x^2 \frac{\p^2 Q}{\p x^2} \right)  \\
-  L_y \frac{\p Q}{\p y } & = L_x v \frac{\p Q}{\p x} + L_x \frac{\p v}{\p x} Q + \frac{L^2_x}{2} \frac{\p^{2}Q}{\p x^2}  \\
-  \frac{\p Q}{\p y}    & = \frac{L_{x}}{L_{y}} \frac{\p }{\p x} \left( v Q \right)  + \frac{L^2_x}{2L_y} \frac{\p^{2}Q}{\p x^2}  
-\end{align}
-%
-Assuming that $L_x = L_y $ (similar length scales in both directions),
-we find that
-%
-\begin{align}
-\boxed{\frac{\p Q}{\p y}  = \frac{\p}{\p x} \left( v Q\right) + D \frac{\p^{2} Q}{\p x^2}  }
-\end{align}
-%
-which is a convection-diffusion equation.  It seems that $y$ direction
-(the direction where flow propagates into the porous medium) acts
-similar to time. As the flow moves inward, the $Q$ diffuses in the $x$
-direction, and convects with velocity $v$.
-
-\section{Network Evolution}
-%
-Any changes to the micro-structure in a porous medium, such as solute
-retention during polymer flow (effectively" clogging" some pores in
-the network), affects the pore-level flow and alters the bulk
-behavior. In this section, we want to study the effect of such
-evolution in the network. The radius of the pipes in the network, can
-reduce (due to clogging) or increase (due to erosion). The rate of
-such reduction (or increase) can depend on flux, or shear rate, or
-velocity, or etc. We can simplify these models with all the models
-with the following equation
-%
-\begin{align}
-  \frac{dR}{dt}  \propto \pm \frac{Q}{R^{n}} 
-\end{align}
-%
-where $n=0,2,3$ corresponds to proportionality with flow rate,
-velocity, shear gradient respectively. The plus sign corresponds to
-erosion, and the negative sign corresponds to the clogging. In order
-to study the effect of the above equation in whole network, we first
-study the effect in a two parallel/series case.
-
-\subsection{Erosion}
-%
-In erosion the rate of change of radius reads as
-%
-\begin{align}
-  \frac{d r}{dt} & = \alpha \frac{Q}{r^{n}} 
-\end{align}
-%
-Here, note that each pipe with radius $R$ acts as a resistor, we have
+In each pipe with radius $R$ which acts as a resistor, we have
 Poissoulle flow equation that relates the flow $Q$ to pressure
@@
 \end{align}
+%
+We now change the radius of the pipes according to
+%
+\begin{align}
+  \frac{d r}{dt} & = \alpha \frac{Q}{r^{n}} 
+\end{align}
+%
 
-\subsubsection*{Two pipes in series}
-
-We consider two pipes in series as shown in
-Fig. \ref{figure:resistor-series-1}. We are interested to see what
-happens two the resistors for different initial conditions? How does
-the values of the resistors evolve? What happens to the pressure
-distribution at the note in between?
+\subsection{Two in Series}
+%
+Now assume two pipes back to back as shown in Fig. \ref{figure:resistor-series-1}.
 %
@@
 %
-
-We first simulate the results numerically to see what happens. The
-results are shown in Fig. \ref{toy-series}. As it can be seen, for any
-initial conditions the pressure at the middle point, converges to
-$(P_l + P_{r})/2$ which basically means that the flow is homogenized.
-%
-\begin{figure}[!h]
-  \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-series}}
-\caption{Toy model for two pipes in series. In each iteration, we
-  change the radius of the pipe as $r_{\text{new}} = r_{\text{old}} +
-  \alpha Q/r_{\text{old}}^n$. For all different cases of $n$ the
-  middle pressure converges to $(P_l + P_r)/2$.}
-\label{toy-series}
-\end{figure}  
-%
-
-We now show why this convergence happens. If the two pipes are in
-series, then $Q$ is always the same in these two pipes. Therefore
+If the two pipes are in series, then $Q$ is always a
+constant. Therefore
 %
@@
   P_m - P_l &= \frac{Q}{C_{1}}   \\
+  P_r - P_l &= \frac{1}{1/C_{1} + 1/C_2} Q   \\
   \frac{P_{m}-P_l}{P_r - P_l} & = \frac{1/C_{1}}{1/C_{1} + 1/C_2} = \frac{C_{2}}{C_{1} + C_2}  
@@
 %
-Note that for any power of $n$ the pressure in the middle point as $t\to\infty$
-converges to $(P_l+P_r)/2$.
+Note that if $n+1<4$ (i.e. $n<3$) then the growth is much faster, and
+the limit is reached much faster; however, if $n\geq 3$ the growth
+becomes slower. The result of simulation is shown in the Fig.
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-series}}
+\caption{Toy model for two pipes in seris. In each iteration, we
+  change the radius of the pipe as $r_{\text{new}} = r_{\text{old}} +  \alpha Q/r_{\text{old}}^n$}
+\label{toy-series}
+\end{figure}
 
 \newpage
-\subsubsection*{Two Parallel Pipes Case}
+\subsection{Two Parallel Pipes Case}
 %
-Now assume two pipes in parallel as shown in
-Fig. \ref{figure:resistor-series-par}. We first simulate the results
-to see what happens for different initial conditions. The results for
-different initial values of $r_1,r_2$ are shown in Fig. \ref{toy-par}.
+Now assume two pipes in parallel as shown in Fig. \ref{figure:resistor-series-par}.
 %
-\begin{figure}[!h]
+\begin{figure}[ht]
   \begin{center}
@@
 %
-
-\begin{figure}[!h]
-  \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-par}}
-  \caption{Toy model for two pipes in parallel. In each iteration, we
-    change the radius of the pipe as
-    $r_{\text{new}} = r_{\text{old}} + \alpha
-    Q_{i}/r_{\text{old}}^n$. When $n<3$, all of the flow eventually
-    passes from either top or bottom pipe. When $n=3$, the flow
-    proportion remains the same. When $n>3$, the flow homogenizes
-    where half of the total flow i.e. $Q/2$ passes from top and the
-    other half from bottom pipe.}
-\label{toy-par}
-\end{figure}
-
-Now, we start to model to see why this happens. Initially, we note
-that
+In this case, first we have
 %
@@
 \begin{align}
-  \frac{dr_{2}}{dt}  & =  \frac{\alpha \beta \Delta P}{r^{n-4}_{2}} \\
+  \frac{dr_{2}}{dt}  & = \alpha \frac{Q_2}{r^4_{2}} =  \frac{\alpha \beta \Delta P}{r^{n-4}_{2}} \\
                      & = \frac{\alpha \beta }{r^{n-4}_{2}} \frac{Q}{\beta (r_{2}^{4} + r_1^4)} = \frac{\alpha Q}{r^{n}_{2} + r_{2}^{n-4} r_1^{4}} \\
@@
   \lb r^{n}_{2} + r_{2}^{n-4} \lp r_2^{n-3} + \gamma \rp^{\frac{4}{n-3} }\rb dr_2 & = \alpha Q dt\\
-  \frac{1}{n+1} \lb r_2^{n+1} + \lp r_2^{n-3} + \gamma\rp^{\frac{n+1}{n-3} } \rb  & = \alpha Qt + C\\
+  \frac{1}{n+1} \lb r_2^{n+1} + \lp r_2^{n-3} + \gamma\rp^{\frac{n+1}{n-3} }\rb  & = \alpha Qt + C\\
   r_2^{n+1} + \lp r_2^{n-3} + \gamma\rp^{\frac{n+1}{n-3} }  & = (n+1)\lp \alpha Qt + C\rp \\
@@
 \begin{align}
-  & \begin{cases}
-    r_1^{n-3} - r_2^{n-3} = \gamma \quad \text{ if }n \neq 3,   \\
-    r_1 = \gamma r_{2} \quad \text{ if } n=3
-  \end{cases}\\
-  & r_1^{n+1} + r_2^{n+1} = At + B
+  r_1^{n-3} - r_2^{n-3} &= \gamma \\
+  r_1^{n+1} + r_2^{n+1} &= At + B
 \end{align}
@@
 
-\begin{figure}[!h]
+\begin{figure}[h]
   \centerline{\includegraphics[width=0.8\textwidth]{./Figs/par_resistors}}
@@
 
-\subsubsection*{General Case}
+The result for numerical simulation is shown in Fig. \ref{toy-par}.
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-par}}
+\caption{Toy model for two pipes in parallel. In each iteration, we
+  change the radius of the pipe as $r_{\text{new}} = r_{\text{old}} +  \alpha Q_{i}/r_{\text{old}}^n$}
+\label{toy-par}
+\end{figure}
+
+Another way of seeing this and also generalize the results is to study the change of relative radius $\tilde{r}_1 = \frac{r_1}{r_1+r_2}$ under the assumptions 
+\begin{equation}
+    C_i = r_i^m, ~ \frac{dr_i}{dt}= \alpha \frac{Q_i}{r_i^n}.
+\end{equation}
+It can be easily derived that 
+\begin{equation}
+    \frac{d\tilde{r_1}}{dt} \propto \tilde{r}_1 (1-\tilde{r}_1) \frac{r_1^{m-n-1}-r_2^{m-n-1}}{r_1^m+r_2^m},
+\end{equation}
+which has  a fixed point at either 1.
+$\tilde{r_1} = 0$ or $1$ or 2.$r_1=r_2$.
+The first case is the channeling and the second case is the uniform.
+It can also be shown that if $m-n-1>0$ the system ends at channelling, otherwise uniform except when $m-n-1=0$ it will end up with no change of the relative radius.
+
+\newpage
+
+\subsection{Parallel and Series}
 %
-In a general case, the resistors can be divided into series and
-parallel resistors. Using that in each section, we only need to look
-at the parallel resistors and determine the channelling. The resistors
-in series do not affect the channelling to occur. They only contribute
-tot he homogenization. Parallel resistors however, in the case of
-$n>3$ result in channeling. Note that at some places, we might need to
-use $\Delta-Y$ conversion to find the equivalent resistors. It can be
-shown that the channeling can still be described using $\Delta-Y$
-conversion.
+Now, we assume a combination of both parallel and series case as shown
+in Fig. \ref{resistor-par-series}. The top and bottom series part,
+become more and more homogeneous for any flow that passes through
+them. However, the flow between top and bottom separates based on the
+power of $n$.
+%
+\begin{figure}[ht]
+  \begin{center}
+    \begin{circuitikz}
+      \draw
+      (-0.5,0) node[anchor=east] {$P_{l}$} to [short] (0.1,0)
+      -- (0.1,0.5) 
+       to[R=$1/C_1$] (2,0.5) to[R=$1/C_2$] (4,0.5) -- (4,0) to [short] (4.5,0) node
+       [anchor=west] {$P_r$};
+      \draw
+      (0.1,0)  --(0.1,-0.5) 
+       to[R=$1/C_3$] (2,-0.5) to[R=$1/C_{4}$] (4,-0.4)--(4,0);
+    \end{circuitikz} 
+    \caption{Parallel/Series Case} \label{resistor-par-series}
+  \end{center}
+\end{figure}
 
-\subsubsection{Some Corrections to Series and Parallel cases(Deng)}
-\AZ{The case example here is the special case where $C_2=C_3$ in the series part and also $C_\text{eq}=C1$ where $C_\text{eq}$ is the equivalent resistor resulted from $C_1$ and $C_2$.
-This special case always results in the same fluid flux in the resistors.
-This special case can also be observed from the diagonal contour line present in Fig.
-\ref{anal-par}.
-} Numerical simulations show different result here for more complex cases other than naive parallel or series cases.
-For example for the following case Fig \ref{resistor-par-series21}.
+\subsubsection{Corrections (Deng)}
+Numerical simulations show different result here for more complex cases other than naive parallel or series cases. For example for the following case Fig \ref{resistor-par-series21}.
 \begin{figure}[ht]
@@
   \end{center}
-
 \end{figure}
@@
 
-Intuitively, the failure of equalization of flow is due to the non-linearity of erosion law, which voids the common sense that two resistors in series can be combined as one.
-Therefore we expect the conclusions in this paper could be affected by the network structure.
-\subsubsection{More general numerical results of Fig. \ref{resistor-par-series21}}
-In general as we set $\frac{dr_i}{dt} = Q_i/r_i^n$ and $C_i = r_i^4$, in the network of Fig. \ref{resistor-par-series21} we have 
+\newpage
+\section{Toy Model - Clogging}
+%%
 \begin{align}
-    \frac{dC_1}{dt} &= \frac{4QC_1^{(7-n)/4}}{\Delta} \\
-    \frac{dC_2}{dt} &= \frac{4QC_2^{(7-n)/4}C_3}{\Delta(C_2+C_3)} \\
-    \frac{dC_3}{dt} &= \frac{4QC_3^{(7-n)/4}C_2}{\Delta(C_2+C_3)},
-\end{align}
-where $\Delta = C_1+\frac{C_2C_3}{C_2+C_3}$, the ratio $Q_1/Q_2 = C_1(C_2+C_3)/(C_2C_3)$.
-Fig.
-\ref{toy-par-series-eros} are the numerical result for $n=5$ and $n=7$ with $C_2(t=0)=C_3(t=0)=1$ and changing $C_1(t=0)$.
-$Q_1/Q_2$ are not converging to 1 in either case.
-\begin{figure}[H]
-  \centerline{\includegraphics[width=1\textwidth]{Figs/par_series_12.png}}
-  \caption{For different n and $C_1(t=0)$, the simple network under erosion yields different $Q_1/Q_2$.}
-\label{toy-par-series-eros}
-\end{figure}  
-\newpage
-\subsection{Clogging}
-%
-In clogging, the rate of change of radius reads as
-%
-\begin{align}
-  \frac{dr}{dt } = -\alpha \frac{Q}{r^{n}} 
+  \frac{d r}{dt} & = - \alpha \frac{Q}{r^{n}} 
 \end{align}
 %
-Similar to the erosion, we first study a simplified model with two
-pipes in series and parallel.
-
-\subsubsection*{Series}
+\subsection{Series - Numerical result}
 %
-We consider the following pattern for the resistors
-(Fig. \ref{figure:resistor-series-clogging}). We first simulate for different initial conditions, and look at the
-middle pressure over long time. Since the radius is decreasing, we
-need to set a maximum amount of reduction. Since the radius cannot
-become negative. For different initial conditions we look at the
-middle pressure, and we observe that no matter what power of $n$ is,
-the middle pressure remains almost unchanged. If the minimum threshold
-is hit, then some jumps can be observed, however, the total behavior
-is such that the ratio of the middle pressure remains almost similar.
-
+We assume the following pattern for the resistors \ref{figure:resistor-series-clogging}
 %
-\begin{figure}[!h]
+\begin{figure}[h]
   \begin{center}
@@
 %
-
+The numerical simulation results are shown in
+Fig. \ref{toy-series-clog}.
 %
-\begin{figure}[H]
+\begin{figure}[h]
   \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-series-clog}}
@@
 
-\subsubsection*{Parallel}
+\subsection{Parallel - Numerical result}
 %
-We also study the behavior when the pipes are in parallel (See
-Fig. \ref{figure:resistor-par-clogging}). The numerical results of the
-simulations are shown in Fig. \ref{toy-par-clog}. The behavior is
-again very similar to the two pipes in series. We again find a similar
-trend where the ratio of the $Q$'s remains unchanged. 
+We assume the following pattern for the resistors \ref{figure:resistor-par-clogging}
 %
-\begin{figure}[H]
+\begin{figure}[ht]
   \begin{center}
@@
 
+The numerical simulation results are shown in
+Fig. \ref{toy-par-clog}.
 %
-\begin{figure}[H]
+\begin{figure}[h]
   \centerline{\includegraphics[width=1\textwidth]{./Figs/toy-model-par-clog}}
@@
 
-\subsection{Generalization of Erosion Law(Deng)}
+\newpage
+
+\section{Localization Degree}
+%
+In channelling, sparsity of flow occurs. In other words, most of the
+flow passes through few pipes. The measures already used to calculate
+sparsity are the following
+%
+
+\begin{center}
+  \begin{tabular}{ |c|l|l| }
+    \hline
+  Measure & Definition & Description  \\ \hline
+    $\ell^{0}_{\ep}$  & $\#\{j, q_j \leq \ep \}$ & \\ \hline
+    $-\ell^p$ & $-\lp \sum_j q_j\rp^{1/p}$ & \\ \hline
+    $\ell^2/\ell^1$ & $\sqrt{\sum_j q_j^2}/\sum_j q_j$ &\\ \hline
+    $\kappa_4$ & $\sum_j q_j^4 / \lp \sum_{j} q^{2}_{j}\rp^2$ & \\ \hline
+    $-\log$ & $-\sum_j \log \lp 1 + q_j^2\rp $ & \\ \hline
+    $-\tanh_{a,b}$ & $-\sum_j \tanh \lp a q_j^b\rp$ & \\
+\hline                               
+\end{tabular}
+\end{center}
+
+The following measures I propose based on our problem
+%
+\begin{align}
+  \mathcal{L}_1 = \frac{1}{N - 1} \lp N - \frac{\lp \sum_{j} q_j\rp ^2}{\sum_jq^2_j} \rp\\
+  \mathcal{L}_2 = \frac{1}{N - 1} \lp N - \frac{\lp \sum_{j} q_j^{2}\rp^2}{{\sum_jq^4_j}} \rp    
+\end{align}
+%
+In the above measures if $q$ is uniform and the same everywhere, then
+the measure is $\mathcal{L}_1 = \mathcal{L_2} = 0$. The extreme
+heterogeneity case the measure goes toward $1$. The resulting videos
+are Movie S1 and S2.
+
+\section{Generalization of conductance erosion law (Deng)}
 Here is a naive guess of how the exponent of erosion law can change the network topology. We can assume the erosion law  
@@
 The exponential tail remains in the simulations for the $\beta = 0$ case.
-We do not have a theoretical explanation why the exponential tail remains in the $\beta = 0$ case.
-\begin{figure}[H]
+\begin{figure}[h]
   \centerline{\includegraphics[width=1\textwidth]{./Figs/erosionExp.png}}
-  \caption{A grid network erosion simulations with different $\beta$ exponents.
-Top left is the initial flow distribution for every simulation (T=1) and the rest are final distributions of the flow.
-We can easily distinguish the channeling ($\beta>0$) and homogenization behavior ($\beta<0$) from the results.
-}
+  \caption{A grid network erosion simulations with different $\beta$ exponents. Top left is the initial flow distribution for every simulation (T=1) and the rest are final distributions of the flow.}
 \label{fig:erosionExp}
@@
 
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 It is easy to distinguish channeling ($\beta = 1$), homogeneity ($\beta = -1$) and exponential tail ($\beta = 0$) from the flow distributions at the end of simulations.
-The delta function at $0$ is due to the resistors connecting vertically, which are perpendicular to the average flow.}
+}
     \label{fig:PQ}
@@
 
-\newpage
+\bibliography{ref}
 
-\section{Permeability modification model}
+\end{document}
+
+\section{Shear Rate Homogenity}
 %
-All the models introduced above represent different scenarios where
-the clogging/erosion might happen. The question, however remains that
-what could be a microscopic model? What it can predicts? and is there
-a proxy (bulk property) that can be observed to study the microscopic
-model?
-
-We propose the following microscopic model: The polymers passing through pores are dragged by the flow. There are
-two forces competing when a polymer adheres to the surface of a pore
-(1) The drag force on the particle coming from flow, and (2)
-ionic/VanderWaals or whatever force that tries to adhere the particles
-to the surface. A particle attaches to the surface if the drag force
-exerted by the fluid flow around it is smaller than the
-VanderWaals/ionic force.
-
-For simplicity, I assume that the force is ionic with a force distance
-profile of $F= K/X^2$, where $K$ is a constant and $X$ is the
-distance. I assume that polymers have an effective radius of $d_{p}$
-and fluid viscosity is $\mu$ and the flow rate is $Q$. This model
-states that the particle attaches to the surface when
-%%
+In the numerical simulation, we observe that after changing the radius
+of the pipes with the following dynamics 
+%
 \begin{align}
-    F_{\text{drag}} &\leq F_{\text{ionic}}\\
-    6\pi \mu d_{p} \frac{2Q}{\pi R^2} \lp 1- \frac{r^2}{R^2} \rp & \leq \frac{K}{(R-r)^2} \\
-    1 - \frac{r^2}{R^2} & \leq \lp \frac{K }{12 \mu  d_{p} Q} \rp \frac{1}{\lp 1 - r/R \rp^2} \\
-    1 & \leq \frac{r^2}{R^2} + \alpha \frac{1}{\lp 1-r/R\rp ^2}
+  \frac{d r}{dt } = \alpha \frac{Q}{r^{3}} 
 \end{align}
 %
-where $\alpha = K/\lp 12\mu d_pQ \rp$ is a factor that compares the ionic force and viscous
-force. Note that it depends on the flux rate. If we define
-$x = 1- r/R$ we obtain
+the flow becomes more homogeneous, i.e. the pressure versus the
+position becomes almost linear.
+
+\section{Two Pipe Study}
+%
+Let's consider two pipes connected as shown blow
+%
+\begin{figure}[h]
+ \centerline{\includegraphics[width=.4\textwidth]{./Figs/twopipes}}
+\caption{Two pipe model}
+\label{sup-fig4}
+\end{figure}  
+%
+We assume $P_0$ on one side and $P_1$ on the other side. The flow $Q$
+and pressure difference are related as follows
 %
 \begin{align}
-    1 &\leq (1-x)^{2} + \frac{\alpha}{x^2} \\
-    x^2- x^2(1-x)^{2} &\leq \alpha \\
-    x^2 (1- (1-x)^2) & \leq \alpha \\
-    x^3(2-x) & \leq \alpha \\
-    \text{if } x\ll1 \to x & \leq \lp \frac{\alpha}{2}\rp^{1/3}
+  &Q = -\frac{\pi r^4}{8\mu L} {\Delta P} \\
+  &\boxed{Q = \sigma (r) \Delta P, \quad \sigma(r) =   -\frac{\pi r^4}{8\mu L}}\\
+  & R(r) Q = \Delta P, \quad R(r) =  -\frac{8\mu L}{\pi r^4}
 \end{align}
 %
+For the two pipe system we have
 %
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=4cm]{./Figs/model2.jpg}
-  \caption{Flow in the pipe}
+\begin{align}
+  Q & = \sigma(r_1) (P_m - P_0) \\
+  Q & = \sigma (r_2) (P_1- P_m) \\
+  & \to \quad Q \lp \frac{1}{\sigma(r_{1})} + \frac{1}{\sigma(r_{2})}  \rp = P_1 - P_0
+\end{align}
+%
+Solving for pressure at the middle point we have $P_m $
+%
+\begin{align}
+  P_m = P_0 + \frac{{1}/{\sigma(r_{1})} }{{1 }/{\sigma(r_{1})} + {1}/{\sigma(r_{2})} } (P_1 - P_0) \\
+  \boxed{P_m = P_0 + \frac{\sigma(r_2)}{\sigma(r_1) + \sigma(r_2)} (P_1 - P_0)}
+\end{align}
+%
+Note that for the dynamics we know that
+%
+\begin{align}
+  & \boxed{\frac{d r}{dt } = \alpha \frac{Q}{r^{3}}}  \\
+  & r^3 \frac{d r}{d t}   = \alpha Q \\
+  & \frac{d}{dt} r^4 = \alpha Q  \\ 
+  & \boxed{\frac{d}{dt} \sigma(r) = \alpha \frac{\pi}{8\mu L} Q = \text{const.}}
+\end{align}
+%
+
+\begin{figure}[h]
+ \centerline{\includegraphics[width=.75\textwidth]{./Figs/shear-iterations}}
+\caption{Increasing conductivity at a constant rate}
+\label{sup-fig4}
+\end{figure}
+
+\subsection{General dependence}
+%
+Lets assume a general dynamics equation as
+%
+\begin{align}
+  & \frac{dr}{dt}  = \alpha \frac{Q}{r^{n}} \\
+  & r^3 \frac{d r}{d t}   = \alpha \frac{Q}{r^{n-3}}  \\
+  & \frac{d}{dt} r^4 = \alpha \frac{Q}{r^{n-3}} \\ 
+  & \boxed{\frac{d}{dt} \sigma(r) \propto \frac{Q}{\sigma^{(n-3)/4}}   }
+\end{align}
+%
+In the following I have the results for different N
+%
+% \begin{figure}[h]
+%   \centerline{\includegraphics[width=.5\textwidth]{./Figs/shear-iterations_n1}}
+%   \centerline{\includegraphics[width=.5\textwidth]{./Figs/shear-iterations_n2}}
+%   \centerline{\includegraphics[width=.5\textwidth]{./Figs/shear-iterations_n3}}
+%   \centerline{\includegraphics[width=.5\textwidth]{./Figs/shear-iterations_n4}}
+% \caption{Increasing conductivity at a constant rate}
+% \label{sup-fig4}
+% \end{figure}
+
+\subsection{Three in Series}
+%
+Now assume three pipes back to back as shown in Fig. \ref{figure:resistor-series-2}.
+%
+\begin{figure}[h]
+  \begin{center}
+    \begin{circuitikz}\draw
+      (0,0) node[anchor=east] {$P_{l}$} to [short,o-] (0.1,0)
+       to[R=$1/C_1$,-*] (2,0)  node [anchor=north] {$P_m$}
+       to[R=$1/C_2$] (4,0) to[R=$1/C_3$] (6,0) 
+       to[short,-o] (6.1,0) node [anchor=west] {$P_r$}; % The resistor
+    \end{circuitikz}
+    \caption{Three resistors at series}
+  \end{center}\label{figure:resistor-series-2}
 \end{figure}
 %
-As a result the distance is proportional to $\alpha^{1/3}$. Note that
-$\alpha$ depends on $1/Q$.  Now, lets
-find the flux passing through this adsorption layer (any polymer in
-this layer would attach to the surface)
-%
-%
 \begin{align}
-  \text{volume}/\text{time} &= \frac{1}{2} R \alpha ^{1/3} \cdot \frac{Q}{R^{3}} R\a^{1/3} \cdot 2\pi R = \pi Q \a^{2/3}  = \pi \lp \frac{K  }{12 \mu  d_{p}} \rp^{2/3} Q^{1/3} \\
-  \text{volume}/\text{time} & \propto {Q^{1/3}} 
+  Q &= \frac{1}{1/C_{1} + 1/C_2 + C_3}   \Delta P = \text{const.}, \\
+  P_m - P_l &= \frac{Q}{C_{1}}   \\
+  P_r - P_l &= \frac{Q}{1/C_{1} + 1/C_2 + 1/C_3}    \\
+  \frac{P_{m}-P_l}{P_r - P_l} & = \frac{1/C_{1}}{1/C_{1} + 1/C_2 + 1/C_3}  
 \end{align}
 %
-Now, if we assume that the number of polymers passing through the area
-cause clogging of the pipe and change the total area of the pipe, then
-we find that
-
-%
-\begin{align}
-  d (\pi R^2) \propto Q^{1/3} \quad \to \quad R dR \propto Q^{1/3}
-\end{align}
-%
-We also know that $k = \pi R^4/8l^2$, as a result
-%
-\begin{align}
-  dk \propto R^{3} dR \\
-  dk \propto R^2 Q^{1/3} \\
-  dk \propto Q^{1/3}
-\end{align}
-
-\subsection*{Experimental Results}
-%
-In Shima's paper, we report a figure that shows the evolution of
-permeability $k$ per volume of polymer $V_{pol}$ that passes through
-the porous media. Basically we are plotting $\Delta k$ versus $Q$
-passing through the porous media. The figure and best polynomial fit
-is shown blow
-%
-%
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.55\textwidth]{./Figs/k-evolution.eps}
-  \caption{$k$ versus volume of fluid passed through a porous media}
-\end{figure}
-
-\section{Foam Relaxation and Non-monotonic Aging}
-%
-So far the observation is that no matter how much disorder we
-introduce in the size distribution of pipe diameters, no relaxation
-behavior can be observed in a structured random network of tubes. If
-we prune the network, near the percolation limit, the slow $log(t)$
-dynamics is observable, however, it seems to be very unlikely that it
-is the case. We need to introduce a toy model that can capture this
-behavior. My intuition is that the relaxation is due to aging of the
-adhesion of pore surfaces attaching to each other due to compression.
-%
-
-\subsection{Modeling}
-%
-We assume a network of pores, as we did before.
-The network of the pores are shown in Fig.
-\ref{fig:relaxation-network}.
-The pores are with different size.
-the connections are also with different sizes.
-%
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.55\textwidth]{./Figs/relaxation_grid}
-  \caption{An example of pores connected with different sizes and different resistors} \label{fig:relaxation-network}
-\end{figure}
-%
-On a structured grid, we initialize a random distribution of pore sizes, with random resistor connections.
-For each pore, we have a four neighbors.
-We first  need to determine the initial pressure of the pores.
-\red{I don't have a good way to initialize the pressures, for now, I consider them to be the same amount.
-It could also depend on the initial volume.} Due to Darcy's law we have
-%
-\begin{align}
-    Q_{ij} = \frac{\pi r_{ij}^4}{8 \mu L_{ij}} \left( {P_i - P_j}\right) = \frac{P_i - P_j}{R_{ij}}, \qquad R_{ij} \equiv \frac{8 \mu L_{ij}}{\pi r_{ij}^4}
-\end{align}
-%
-Where $r_{ij}$ and $L_{ij}$ are radius and length of the resistors connecting the pores.
-$Q_{ij}$ represents the outflux from node $i$ to node $j$.
-At each time for each pore, we can calculate the total out-flux of the flow is as
-%
-\begin{align}
-    Q_i = \sum_{j \in N(i)} Q_ij = \sum_{j \in N(i)} \frac{\pi r_{ij}^4}{8 \mu L_{ij}} \left( {P_i - P_j}\right)
-\end{align}
-%
-where $N(i)$ represents the neighbors of $i$-th node.
-After calculating the total outflux, we need to find an equation on how to update the pressure of the pore $P_i$.
-If we assume that ideal gas law, we have
-%
-\begin{align}
-    P_i V_i = m_i RT \quad \dot{m_i} = - \rho Q_i \quad \text{(minus sign is since } Q_i \text{ is out-flux)} 
-    \end{align}
-%
-Assuming a constant density, we have
-%
-\begin{align}
-    \frac{d P_i}{dt} = \frac{RT}{V_i} \frac{d m_i}{dt}  = -\frac{\rho RT}{V_i} Q_i \\
-    \frac{d P_i}{dt} = - \frac{\rho RT}{V_i} \sum_{j \in N(i)} \frac{P_i - P_j}{R_{ij}}  
-\end{align}
-%
-In the matrix format this can be written as 
-%
-\begin{align}
-\frac{d\mathbf{P}}{dt} = \mathbf{D} \cdot \mathbf{A} \cdot \mathbf{P}\\
-\mathbf{P} = \begin{bmatrix} P_1 \\ \vdots \\ P_n
-\end{bmatrix}\\
-\mathbf{D} = \text{diag}(\frac{-\rho R T}{V_1},\cdots, \frac{-\rho R T}{V_n})\\
-[\mathbf{A}]_{ij} = -\frac{1}{R_{ij}}, \quad [\mathbf{A}]_{ii} = \sum_{i\in N(i)} \frac{1}{R_{ij}}
-\end{align}
-%
-To solve the above equations, we expand the LHS to obtain
-%
-\begin{align}
-    \frac{d\mathbf{P}}{dt} = \mathbf{D} \cdot \mathbf{A} \cdot \mathbf{P} \\
-    \frac{\mathbf{P}_{n+1}- \mathbf{P}_n}{\Delta t} = \mathbf{D} \cdot \mathbf{A} \cdot \left( \theta \mathbf{P}_{n+1} + (1-\theta) \mathbf{P}_{n}\right) \\    
-    \left( \mathbf{I} - \theta\Delta t \mathbf{D}\mathbf{A} \right) \mathbf{P}_{n+1} = \left( \mathbf{I} + (1-\theta) \Delta t \mathbf{D} \mathbf{A}\right) \mathbf{P}_n
-\end{align}
-%
-Note that $0 \leq \theta \leq 1$.
-Having $\theta = 0$, the solution becomes explicit forward Euler, and $\theta = 1$, the equations become implicit method.
-Note that for a given geometry $\mathbf{D}$ and $\mathbf{A}$ are fixed and the solution can be obtained through matrix multiplication as
-%
-\begin{align}
- \mathbf{P}_{n+1} = \left( \mathbf{I} - \theta\Delta t \mathbf{D}\mathbf{A} \right)^{-1} \left( \mathbf{I} + (1-\theta) \Delta t \mathbf{D} \mathbf{A}\right) \mathbf{P}_n
-\end{align}
-%
-Using the above relations, I found that the relaxation does not happen over multiple decades. It seems very unlikely that the porous structure is causing this slow relaxation. 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.55\textwidth]{./Figs/relaxation-porous.eps}
-  \caption{Mean pressure relaxation in a random network of pores with a constant pore size and random pore size.} \label{relaxation}
-\end{figure}
-
-Looking at the microgrpah image of open-cell foams (as shown in Fig. \ref{micrograph}), it seems unlikely that the fluid is playing a role in this. 
-%
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.45\textwidth]{./Figs/micrograph-open-cell.png}
-  \caption{Micrograph showing cellular microstructure of a polyester urethane foam (100 ppi) (Taken from \cite{gong2005compressive}) } \label{micrograph}
-\end{figure}
-%
-I believe that since the material is visco-elastic, the response is due to the polymer structure that have a large relaxation times.
-
-\section{Distribution of Resistor-level response}
-%
-We consider a random resistor network. In this network, we remove a single resistor, remove it from the network. The permeability changes. We then record the PDF of the change in permeability. 
-The result looks as follows
-%
-
-\section{Flow-Chains: Force-Chains}
-%
-We observe patterns similar to force-chains observed in granular
-materials, but in porous media. See Fig. \ref{flow-chain}. For a movie
-of this behavior see
-\href{https://www.youtube.com/watch?v=E8sVcxipNio}{this link}.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.45\textwidth]{./Figs/flowchain1}
-  \includegraphics[width=0.45\textwidth]{./Figs/flowchain2}
-  \caption{Force chain behavior in porous media.} \label{flow-chain}
-\end{figure}
-
-\end{document}

### 2021-04-28 old_files/dynamic-change.tex
Initial Overleaf Import

\input{definitions.tex}
\def\d{\text{d}}
\def\vep{\varepsilon}
\def\ep{\epsilon}
\def\la{\langle}
\def\ra{\rangle}
\def\th{\theta}

\title{Percolation}
\author{Ahmad}
%-------------------------------------------------------------------
\begin{document}          
\maketitle

\section{Permeability modification Model}
%
The polymers passing through pores are dragged by the flow. There are
two forces competing when a polymer adheres to the surface of a pore
(1) The drag force on the particle coming from flow, and (2)
ionic/VanderWaals or whatever force that tries to adhere the particles
to the surface. A particle attaches to the surface if the drag force
exerted by the fluid flow around it is smaller than the
VanderWaals/ionic force.

For simplicity, I assume that the force is ionic with a force distance
profile of $F= K/X^2$, where $K$ is a constant and $X$ is the
distance. I assume that polymers have an effective radius of $d_{p}$
and fluid viscosity is $\mu$ and the flow rate is $Q$. This model
states that the particle attaches to the surface when
%%
\begin{align}
    F_{\text{drag}} &\leq F_{\text{ionic}}\\
    6\pi \mu d_{p} \frac{2Q}{\pi R^2} \lp 1- \frac{r^2}{R^2} \rp & \leq \frac{K}{(R-r)^2} \\
    1 - \frac{r^2}{R^2} & \leq \lp \frac{K }{12 \mu  d_{p} Q} \rp \frac{1}{\lp 1 - r/R \rp^2} \\
    1 & \leq \frac{r^2}{R^2} + \alpha \frac{1}{\lp 1-r/R\rp ^2}
\end{align}
%
where $\alpha = K/\lp 12\mu d_pQ \rp$ is a factor that compares the ionic force and viscous
force. Note that it depends on the flux rate. If we define
$x = 1- r/R$ we obtain
%
\begin{align}
    1 &\leq (1-x)^{2} + \frac{\alpha}{x^2} \\
    x^2- x^2(1-x)^{2} &\leq \alpha \\
    x^2 (1- (1-x)^2) & \leq \alpha \\
    x^3(2-x) & \leq \alpha \\
    \text{if } x\ll1 \to x & \leq \lp \frac{\alpha}{2}\rp^{1/3}
\end{align}
%
%
\begin{figure}[h]
  \centering
  \includegraphics[width=4cm]{./Figs/model2.jpg}
  \caption{Flow in the pipe}
\end{figure}
%
As a result the thickness of the adsoption layer is proportional to
$\alpha^{1/3}$. Note that $\alpha$ depends on $1/Q$.  Now, lets find
the flux passing through this adsorption layer (any polymer in this
layer would attach to the surface and therefore I call this layer
adsoption layer)
%
%
\begin{align}
  \text{volume}/\text{time} &= \frac{1}{2} R \alpha ^{1/3} \cdot \frac{Q}{R^{3}} R\a^{1/3} \cdot 2\pi R = \pi Q \a^{2/3}  = \pi \lp \frac{K  }{12 \mu  d_{p}} \rp^{2/3} Q^{1/3} \\
  \text{volume}/\text{time} & \propto {Q^{1/3}} 
\end{align}
%
Now, if we assume that the number of polymers passing through this
area causes clogging, then the change in the total area of the pipe
will be proportional to the flux through adsorption layer

%
\begin{align}
  d (\pi R^2) \propto Q^{1/3} \quad \to \quad R dR \propto Q^{1/3} \label{eq:change-law} \\
  dR \propto \lp \frac{Q}{R^3}\rp^{1/3}
\end{align}
%
which means that the rate of change of the diameter is proportional to
the shear rate to the power of $1/3$. Note that we also know that
$k = \pi R^4/8l^2$, as a result
%
\begin{align}
  dk \propto R^{3} dR \\
  dk \propto R^2 Q^{1/3} \\
  dk \propto Q^{1/3}
\end{align}
%
which means the changes in the permeability is propotional to the
$Q^{1/3}$ passing through the porous media.

\subsection*{Experimental Results}
%
In Shima's paper, we report a figure that shows the evolution of
permeability $k$ per volume of polymer $V_{pol}$ that passes through
the porous media. Basically we are plotting $\Delta k$ versus $Q$
passing through the porous media. The figure and best polynomial fit
is shown blow
%
%
\begin{figure}[h]
  \centering
  \includegraphics[width=0.55\textwidth]{./Figs/k-evolution.eps}
  \caption{$k$ versus volume of fluid passing through}
\end{figure}

\subsection{Numerical Result}
%
I also ran a numerical simulation in which, I change the diameters
according to \ref{eq:change-law}. The result is as follows
%
\begin{figure}[h]
  \centering
  \includegraphics[width=0.55\textwidth]{./Figs/k-evolution-numerics.eps}
  \caption{$k$ versus volume of fluid passing through in numerical
    simulation. Note that the plateau is due to the max limit imposed
    for max reduction in diameter}
\end{figure}

%
\section{General Force term}
%
In this section we assume a general forcing term of type $F_{g} = K/X^n$, and
as a result find the coefficient function. 
%
\begin{align}
    F_{\text{drag}} &\leq  F_g \\
    6\pi \mu d_{p} \frac{2Q}{\pi R^2} \lp 1- \frac{r^2}{R^2} \rp & \leq \frac{K}{(R-r)^{n}} \\
    1 - \frac{r^2}{R^2} & \leq  \frac{K }{12 \mu  d_{p} Q R^{n-2}} \frac{1}{(1-r/R)^{n}}   \\
    1 -\frac{r^2}{R^2} &  \leq   \beta  \frac{1}{(1-r/R)^{n}}
\end{align}
%
where $\beta = {K }/{12 \mu d_{p} Q R^{n-2}} $. If we define $x = 1- r/R$ we obtain
%
\begin{align}
  1 - (1-x)^{2} & \leq \beta \frac{1}{x^{n}} \\
 x^{n+1} \lp 2 - x \rp  &\leq \beta  \\\
  x\ll 1 , \qquad x  & \leq \lp \frac{\beta}{2} \rp^{\frac{1}{n+1} } 
\end{align}
%
%
%
\begin{align}
  \text{volume}/\text{time} &= \frac{1}{2} R \lp \frac{\beta}{2} \rp^{\frac{1}{n+1} }  \cdot \frac{Q}{R^{3}} \lp R \frac{\beta}{2} \rp^{\frac{1}{n+1} } \cdot 2\pi R  \\
  \text{volume}/\text{time} &\propto  Q^{1 - \frac{2}{n+1} } R^{-2\frac{n-2}{n+1} } \\
  \text{volume}/\text{time} &\propto  Q^{\frac{n-1}{n+1} } R^{-2\frac{n-2}{n+1} -1}  R  \\
  \text{volume}/\text{time} &\propto  R  \lp \frac{Q}{R^{3}}   \rp ^{\frac{n-1}{n+1} }
\end{align}
%
%
\begin{align}
  d (\pi R^2) \propto R  \lp \frac{Q}{R^{3}}   \rp ^{\frac{n-1}{n+1} } \quad \to \quad \boxed{dR \propto \lp \frac{Q}{R^{3}}  \rp ^{\frac{n-1}{n+1} }}
\end{align}
%
If $k = \pi R^4/8l^2$, as a result
%
\begin{align}
  dk \propto R^{3} dR \\
  dk \propto R^3 \lp \frac{Q}{R^{3}}  \rp ^{\frac{n-1}{n+1} } \\
  \boxed{dk \propto Q^{\frac{n-1}{n+1}}}
\end{align}
%

\section{Force Consideration}
%
In \cite{montgomery2000analytical}, the authors have summarized
adhesion studies. They show that the interaction between a spherical
molecule and an infinite cylinder, results in the adhesion force of
%
\begin{align}
  F \propto \frac{1}{X^{2}} 
\end{align}
%
where $X$ is the distance between the molecule and the surface.

\section{Modelling Force}
%
Assuming a tube shape for the pores, the following figure appears
%
\begin{figure}[h]
  \centering
  \includegraphics[width=10cm]{./Figs/polymer-attachment}
  \caption{Polymer attachment to the surface. The polymer is assumed
    to be at distance $x$ to the boundary. We pick the coordinate
    system such that $\hat{z}$ is along the direction of the tube and
    the polymer is on the ${y}$-axis. }
\end{figure}
%
There are 3 different cases:
%
\begin{itemize}
\item \textbf{Constant attraction force}: The polymer is very small compared to the pore radius and is
  very close to the surface such that it does not feel the
  curvature. For particle, the pore is like a flat infintie plate that
  is atttacting the particle. If the attraction force is due to
  columb, then the attracting force is independen of distance and has
  a constant value.

\item If the particle feels the attraction force between an infinite
  cylinder with radius $R$ and a point particle with charge $q$ at
  distance $x$ from the edge can be calculated as 
%
  \begin{align}
    \text{symmetry } F_{x}= F_{z} = 0, \qquad F_y = \int_{-\infty}^{\infty} \int_0^{2 \pi} \frac{R\sin\th - R + x}{\lp R^{2} -2 R (R-x) \sin\th + z^2\rp^{3/2}} q \lambda R d\th   
  \end{align}
  %
  Using mathematica, so far, I was unable to find the leading power of
  force in terms of $x$.

\end{itemize}

\section{Lennard-Jones Force}
%
\begin{align}
    F_{\text{drag}} &\leq F_{LJ}\\
  6\pi \mu d_{p} \frac{2Q}{\pi R^2} \lp 1- \frac{r^2}{R^2} \rp & \leq 48\ep \lb \frac{\sigma^{12}}{(R-r)^{13}} - \frac{\sigma^{6}}{(R-r)^{7}}  \rb \\
  6\pi \mu d_{p} \frac{2Q}{\pi R^2} \lp 1- \frac{r^2}{R^2} \rp & \leq 48\ep \lb \frac{(\sigma/R)^{12}}{(1-r/R)^{13}} - \frac{(\sigma/R)^{6}}{(1-r/R)^{7}}  \rb \\
  6\pi \mu d_{p} \frac{2Q}{\pi R^2} \lp 1- (1-x)^2\rp & \leq 48\ep \lb \frac{(\sigma/R)^{12}}{x^{13}} - \frac{(\sigma/R)^{6}}{x^{7}}  \rb \\
  6\pi \mu d_{p} \frac{2Q}{\pi R^2} \lp 2x-x^2\rp x^{13} & \leq 48\ep \lb {(\sigma/R)^{12}} - {(\sigma/R)^{6}x^{5}}  \rb \\
  x\ll1 1 \to x \leq {(\sigma/R)^{6/5}} , \text{ or } x\leq c
\end{align}
%
which is a constant value. 
%
\begin{align}
  \text{volume}/\text{time} &= \frac{1}{2} R c \cdot \frac{Q}{R^{3}} R c \cdot 2\pi R = \pi Q c^{2}  \\
  \text{volume}/\text{time} & \propto {Q} 
\end{align}
%
%
\begin{align}
  d (\pi R^2) \propto Q \quad \to \quad R dR \propto Q \\
  dR \propto  \frac{Q}{R}
\end{align}
%
If $k = \pi R^4/8l^2$, as a result
%
\begin{align}
  dk \propto R^{3} dR \\
  dk \propto R^2 Q \\
  dk \propto Q
\end{align}
%

\bibliography{ref}

\end{document}

### 2021-04-28 old_files/main.tex
Initial Overleaf Import

\input{definitions.tex}
\def\d{\text{d}}
\def\vep{\varepsilon}
\def\ep{\epsilon}
\def\la{\langle}
\def\ra{\rangle}
\def\th{\theta}

\title{Percolation}
\author{Ahmad}
%-------------------------------------------------------------------
\begin{document}          
\maketitle

\section{Permeability modification Model}
%
The polymers passing through pores are dragged by the flow. There are
two forces competing when a polymer adheres to the surface of a pore
(1) The drag force on the particle coming from flow, and (2)
ionic/VanderWaals or whatever force that tries to adhere the particles
to the surface. A particle attaches to the surface if the drag force
exerted by the fluid flow around it is smaller than the
VanderWaals/ionic force.

For simplicity, I assume that the force is ionic with a force distance
profile of $F= K/X^2$, where $K$ is a constant and $X$ is the
distance. I assume that polymers have an effective radius of $d_{p}$
and fluid viscosity is $\mu$ and the flow rate is $Q$. This model
states that the particle attaches to the surface when
%%
\begin{align}
    F_{\text{drag}} &\leq F_{\text{ionic}}\\
    6\pi \mu d_{p} \frac{2Q}{\pi R^2} \lp 1- \frac{r^2}{R^2} \rp & \leq \frac{K}{(R-r)^2} \\
    1 - \frac{r^2}{R^2} & \leq \lp \frac{K }{12 \mu  d_{p} Q} \rp \frac{1}{\lp 1 - r/R \rp^2} \\
    1 & \leq \frac{r^2}{R^2} + \alpha \frac{1}{\lp 1-r/R\rp ^2}
\end{align}
%
where $\alpha = K/\lp 12\mu d_pQ \rp$ is a factor that compares the ionic force and viscous
force. Note that it depends on the flux rate. If we define
$x = 1- r/R$ we obtain
%
\begin{align}
    1 &\leq (1-x)^{2} + \frac{\alpha}{x^2} \\
    x^2- x^2(1-x)^{2} &\leq \alpha \\
    x^2 (1- (1-x)^2) & \leq \alpha \\
    x^3(2-x) & \leq \alpha \\
    \text{if } x\ll1 \to x & \leq \lp \frac{\alpha}{2}\rp^{1/3}
\end{align}
%
%
\begin{figure}[h]
  \centering
  \includegraphics[width=4cm]{./Figs/model2.jpg}
  \caption{Flow in the pipe}
\end{figure}
%
As a result the distance is proportional to $\alpha^{1/3}$. Note that
$\alpha$ depends on $1/Q$.  Now, lets
find the flux passing through this adsorbtion layer (any polymer in
this layer would attach to the surface)
%
%
\begin{align}
  \text{volume}/\text{time} &= \frac{1}{2} R \alpha ^{1/3} \cdot \frac{Q}{R^{3}} R\a^{1/3} \cdot 2\pi R = \pi Q \a^{2/3}  = \pi \lp \frac{K  }{12 \mu  d_{p}} \rp^{2/3} Q^{1/3} \\
  \text{volume}/\text{time} & \propto {Q^{1/3}} 
\end{align}
%
Now, if we assume that the number of polymers passing through the area
cause clogging of the pipe and change the total area of the pipe, then
we find that

%
\begin{align}
  d (\pi R^2) \propto Q^{1/3} \quad \to \quad R dR \propto Q^{1/3}
\end{align}
%
We also know that $k = \pi R^4/8l^2$, as a result
%
\begin{align}
  dk \propto R^{3} dR \\
  dk \propto R^2 Q^{1/3} \\
  dk \propto Q^{1/3}
\end{align}

\subsection*{Experimental Results}
%
In Shima's paper, we report a figure that shows the evolution of
permeability $k$ per volume of polymer $V_{pol}$ that passes through
the porous media. Basically we are plotting $\Delta k$ versus $Q$
passing through the porous media. The figure and best polynomial fit
is shown blow
%
%
\begin{figure}[h]
  \centering
  \includegraphics[width=0.55\textwidth]{./Figs/k-evolution.eps}
  \caption{$k$ versus volume of fluid}
\end{figure}

\newpage
\newpage
\newpage

\section{Universality argument}

If the pdf of $q$ follows an exponential tail, we have
%
\begin{align}
  f(q) \propto e^{-q/\lambda}
\end{align}
%
Doing the normalization, we find that
%
\begin{align}
  f(q) = \frac{1}{\lambda} e^{-q/\lambda} \text{such that} \int f(q) dq = 1
\end{align}
%
Setting the average $\langle Q \rangle = Q_0$, we obtain
%
\begin{align}
  \int q f(q) dq = \lambda = Q_{0}
\end{align}
%
We then obtain
%
\begin{align}
  f(q) = \frac{1}{Q_{0}} e^{-q/Q_0}
\end{align}
%
This means that as long as $Q_0$ is fixed, then the probability
distribution is fixed. However, the observation is that as the
clogging happens, the $f(q)$ broadens!

\section{Random Resistor Networks}
%
Consider the following random network
%
%
\begin{figure}[h]
  \centering
  \includegraphics[width=12cm]{./Figs/grid.eps}
  \caption{A random grid of pipes} \label{fig-grid}
\end{figure}
%
The diameter of each pipe is randomly chosen from a distribution
distribution. The Darcy law in each pipe reads as
%
\begin{align}
  \frac{\Delta P}{L}  = \frac{128}{\pi} \frac{\mu Q}{d^4} 
\end{align}
%
where $\Delta P$ is the pressure difference on both sides of the pipe,
$L$ is the length of the pipe, $\mu$ is viscosity, and $d$ is the
diameter of the pipe.
%

\section{Analysis}
%
Consider the following random network of pipes
%
\begin{figure}[h]
  \centering
  \includegraphics[width=12cm]{./Figs/grid2.eps}
  \caption{A random grid of pipes} \label{fig-grid}
\end{figure}
%
At each level, at each node, the flow from previous layers into that
node is considered as $Q(L,i)$.  This flow goes to the next layer
through the pipes that it is connected to. Some portion of it flows
through each pipe as
%
\begin{align}
  Q(L+1,j) = \sum_i w_{ij} Q(L,i) = w_{i,i+1} Q(L,i+1) + w_{i,i} Q(L,i) 
\end{align}
%
such that $\sum_{j} w_{ij} = 1$. Assuming that these $w_{ij}$ are
coming from a distribution $\eta(w)$, we know that
%
\begin{align}
 \boxed{ \int \eta(w) dw = 1 }
\end{align}
%
and from $\sum_jw_{ij} = 1$, we can conclude that
%
\begin{align}
  \sum_j w_{ij}=1 \to N {E}[w_{ij}] = 1 \to E[w_{ij}] = 1/N \to \boxed{\int w\eta(w) dw = 1/N}
\end{align}
%

Now we use the technique of mean field analysis for a general
distribution of $\eta(w)$ to find the distribution of $Q$ at the
layers. The values of $Q(D,i)$ are not independent for neighboring
sites; however, the mean field approximation ignores these
correlations.
%
\begin{align}
  P_L (Q) = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P_{L-1}(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp
\end{align}
%
The constraint that $Q$'s eminating downward should add up to one is
in the definition of $\eta(w)$. The only approximation in the above
equation is that we neglect the possible correlation between the
values of $Q$ among anscestors. If we take the laplace transform of
the above equation, we obtain
%
\begin{align}
  \tilde P(s) & \equiv \int_0^{\infty} P(Q) e^{-Qs} dQ\\
  \xrightarrow{\int_0^{\infty} (\cdot) e^{-Qs} dQ}  P (Q) & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp \\
  \tilde P(s) & = \int_0^{\infty} \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp e^{-Qs}dQ \\
              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j e^{-\sum w_{j}Q_{j}} P(Q_j)\right\}   \\
              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \tilde P(s w_j) \right\} \\
  & = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N}
\end{align}
%
Or to summarize
%
\begin{align}
  \tilde P(s) = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N} \label{eq:main-laplace}
\end{align}
%
Note that in the above calculation $N=2$. If we set $\eta(w) =
\delta(w-1/2)$, then the flow at each node has probality of $1/2$ to
move up or down. As a result the flow at a given depth $L$ will be
homogeneous as $P_L(Q) = \delta (Q-\bar{Q})$ where $\bar{Q}$ is the
average of input fluid flow.

\subsection*{$P(Q)$ decays faster than $Q^{-n}$ for any $n$}
We first show that $P(Q)$ decays faster than any power of $Q$ for any
weight distributions. We expand the Laplace transform as
%
\begin{align}
  \tilde P(s) = 1 + \sum_j \tilde P_{j} s^{j}
\end{align}
%
Inserting this expansion into Eq. \eqref{eq:main-laplace}, we obtain
%
\begin{align}
  1 + \sum_j \tilde P_{j} s^{j}  & = \lp  \int_0^1 d w \eta(w) \lb 1 + \sum_j \tilde P_{j} (sw)^{j}\rb    \rp^{N} \\
 & = \lp  1 + \sum_j \tilde P_j \langle w^{j}\rangle  s^{j}   \rp^{N}
\end{align}
%
where $\langle w^j \rangle = \int_0^1 \eta(w) w^j dw$ is the $j$-th
moment of the weights $w$. In the above equation we can observe that
%
\begin{align}
  P_j \lp N \langle w^j\rangle -1 \rp = G(P_{j-1}, P_{j-1}, \cdots, P_1)
\end{align}
%
In the above equation $P_j$ can only diverge only if $N\langle w^j
\rangle -1$ is zero. If $w$ can only be zero and one, then $\langle
w^j\rangle =\langle w \rangle = 1/N$ and the coefficient can become
zero! Other than this special distribution where $0 \leq w \leq 1$,
then
%
\begin{align}
  & w\in [0,1] \rightarrow w>w^2>w^3> \cdots \\
  & \forall k>1 \rightarrow \langle w^k \rangle < \langle w \rangle = \frac{1}{N} 
\end{align}
%
which means that $N\langle w^j \rangle -1$ is not zero and as a result
$P_j$ is finite. $P_j$ on the other hand is the $j$-th moment or
$\langle Q^j\rangle$ and it is finite. If $P\approx Q^{-n}$, then the
$n$-th moment will not be finite i.e. $\langle Q^{n+1}\rangle =
P_{n+1}$ is not finite. We can then conclude that $P(Q)$ should go to
zero faster than any $Q^{-n}$ as $Q\to \infty$! In other words $d \log
P(Q) / d \log Q \to -\infty$ as $Q\to \infty$.

\subsection*{Exponential Decay}
%
Since our calculation is for $N=2$, the main equation becomes
%
\begin{align}
  \tilde P(s) = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{2} 
\end{align}
%
In order to have an approximation for $\eta(w)$ we do the following:

At each node there are two nodes where the flux is distributed by
$w_1$ and $w_2$. Lets assume that $w_1$ is uniformly distributed
between $0$ and $1$. As a result $w_2 = 1-w_1$ (since conservation of
mass $w_1 + w_2 = 1$). Now $\eta(w)$ can be found as
%
\begin{align}
  & \eta(w) = M \int_0^1 dw_1 \delta(1-w_1-w) =  M, \\
  \text{since }& \int_0^1 \eta(w) dw = 1 \to M =1 \\
  & \eta (w) = 1
\end{align}
%
Just for completeness, if there are three connections ($N=3$), then we
have
%
\begin{align}
  \eta(w) & = M \int_0^1 dw_1 \int_0^1 dw_2 \delta(1-w_1-w_2 - w)\\
          & = M(1-w)  \to \int_0^1\eta(w) dw = 1 \to M = \frac{1}{2} \\
  & \eta(w) = \frac{1}{2} (1-w)
\end{align}
%
As a result the main equation simplifies to
%
\begin{align}
  \tilde P(s) = \lp  \int_0^1 d w  \tilde P(s w)  \rp^{2} 
\end{align}
%
In order to solve the above equation, we assume $\tilde V (s) =
\sqrt{\tilde{P}(s)}$.
%
\begin{align}
  \tilde{V}(s) & = \int_0^1 dw \tilde V (sw) = \int_0^s \frac{du}{s}  \tilde{V}^{2}(u) \\
  s\tilde{V}(s) & = \int_0^s du  \tilde{V}^2(u) \\
\end{align}
%
Taking the defferentiation with respect to $s$ yields
%
\begin{align}
  \tilde{V}(s) + s \frac{d \tilde{V}(s)}{d s} = \tilde{V}^2(s) \\
  \frac{d \tilde{V}}{\tilde{V}^2-\tilde{V}} = \frac{ds}{s}  \\
  \log\lp \frac{1-\tilde{V}}{\tilde{V}} \rp  = \log(s)\\
  \tilde{V}(s) = \frac{1}{1+Cs} 
\end{align}
%
We set the mean to $1$ i.e.,
%
\begin{align}
  \int_0^{\infty} Q P(Q) dQ = 1 \to \frac{d\tilde{P}}{ds}|_{s=0}  = -1\\
  \frac{d \tilde{V}}{ds}  = \frac{1}{2 \sqrt{\tilde{P}(s)}} \frac{d \tilde{P}(s)}{d s}   \to \frac{d\tilde{V}(s)}{ds}|_{s=0} =\frac{-1}{2} \\
  \frac{d\tilde{V}(s)}{ds} = \frac{-C}{(1+Cs)^{2}}|_{s=0} = -C = \frac{-1}{2}  \to C=\frac{1}{2} 
\end{align}
%
As a result, we have
%
\begin{align}
  \tilde{P}(s) = \lp\frac{1}{1+s/2} \rp^2 \\
  P(Q) = 4Q e^{-2Q}
\end{align}

\section{Continuous Model}
%
\section{Analysis}
%
Consider the following random network of pipes
%
In the previous descrete model we found that
%
\begin{align}
  Q(i,j+1) = w_{i-1,j} Q(i-1,j) + w_{i+1,j} Q(i+1,j) 
\end{align}
%
with the constraint that
%
\begin{align}
  w_{i-1,j} + w_{i+1,j} = 1
\end{align}
%
Lets now assume that
%
\begin{align}
  w_{i\pm 1,j}= \frac{1}{2}( 1 \pm v_{i\pm 1,j})
\end{align}
%
with th abive assumption, we find that
%
\begin{align}
  Q(i,j+1) & = \frac{1}{2} \left( 1 - v_{i- 1,j}\right) Q(i-1,j) + \frac{1}{2} \left( 1 + v_{i+ 1,j}\right) Q(i+1,j)  \\
  Q + L_y \frac{\p Q}{\p y } + L^2_y \frac{\p^{2}Q}{\p y^2}  & = \frac{1}{2} (1-v + L_x \frac{\p v}{\p x}  ) \left( Q - L_x \frac{\p Q}{\p x} +   \frac{1}{2} L_x^2 \frac{\p Q^2}{\p x^2}\right) \nonumber\\
 & \qquad   +\frac{1}{2}  (1+v + L_x \frac{\p v}{\p x} )\left( Q + L_x \frac{\p Q}{\p x} + \frac{1}{2}L_x^2 \frac{\p^2 Q}{\p x^2} \right)  \\
  L_y \frac{\p Q}{\p y } & = L_x v \frac{\p Q}{\p x} + L_x \frac{\p v}{\p x} Q + \frac{L^2_x}{2} \frac{\p^{2}Q}{\p x^2}  \\
  \frac{\p Q}{\p y}    & = \frac{L_{x}}{L_{y}} \frac{\p }{\p x} \left( v Q \right)  + \frac{L^2_x}{2L_y} \frac{\p^{2}Q}{\p x^2}  
\end{align}
%
Assuming that $L_x = L_y $(?), we find that
%
\begin{align}
  \frac{\p Q}{\p y}  = \frac{\p}{\p x} \left( v Q\right) + D \frac{\p^{2} Q}{\p x^2}  
\end{align}

\section{Polymer Adsorption Rate}
%
These polymers (particles) in the tube are dragged by the flow. There are two forces competing when a polymer adheres to the surface (1) The drag force on the particle coming from flow, and (2) ionic/VanderWaals or whatever force that tries to adhere the particles to the surface. A particle attaches to the surface if the drag force exerted by the fluid flow around it is smaller than the VanderWaals/ionic force.

This means that for a particle to adhere to the surface needs to be at a distance from the surface such that the drag force is smaller than the Van-der-Waals force (say $F_0$). If this happens then the polymer with some probability can adhere to the surface and the flow will not drag it away. This means that particles below this critical velocity.

\begin{align}
    v_\text{cr} = \frac{F_0}{6\pi \mu d}
\end{align}
%
Now, we know that the velocity profile is as 
%
\begin{align}
 v(r) = \frac{2Q}{\pi R^2} \lp 1 - \frac{r^2}{R^2}\rp   \\
 v_\text{cr} = \frac{2Q}{\pi R^2} \lp 1 - \frac{r_\text{cr}^2}{R^2}\rp   \\
 \frac{r_\text{cr}^2}{R^2} = 1 - \frac{v_\text{cr} \pi R^2}{2Q}
\end{align}
%
We are interested in the rate of volume of fluid passing between $r_\text{cr}$ and the boundary of the wall. This becomes
%
\begin{align}
    \text{volume}/\text{time} & = \int_{\text{cr}}^R \frac{2Q}{\pi R^2} \lp 1 - \frac{r^2}{R^2}\rp 2\pi r dr \\
    & = \lp \int_0^R - \int_0^{r_\text{cr}}\rp \frac{2Q}{\pi R^2} \lp 1 - \frac{r^2}{R^2}\rp 2\pi r dr \\
    & = Q - {2Q} \frac{r_\text{cr}^2}{R^2} \lp 1 - \frac{r_\text{cr}^2}{2R^2} \rp \\
    & = Q - {Q} \lp 1 - \frac{v_\text{cr} \pi R^2}{2Q} \rp  \lp 1 +  \frac{v_\text{cr} \pi R^2}{2Q}  \rp \\
    & = Q - {Q} \lp 1 - \frac{v^2_\text{cr} \pi^2 R^4}{4Q^2} \rp \\
    & = Q \lp 1-1+\frac{v^2_\text{cr} \pi^2 R^4}{4Q^2} \rp \\
    & = \frac{v^2_\text{cr} \pi^2 R^4}{4Q}
\end{align}
%

Another easy way to reach to the above calculation is the following 
%
\begin{figure}[h]
  \centering
  \includegraphics[width=4cm]{./Figs/model1.eps}
  \caption{Flow in the pipe}
\end{figure}
%
The shaded area around the tube can be calculated as 
%
\begin{align}
    \text{volume}/\text{time} = \frac{1}{2} v_\text{cr} \cdot \lp \frac{v_\text{cr}}{q/d^2} d \rp 2 \pi d = \frac{\pi v_\text{cr}^2 d^4}{q}
\end{align}
%
which is upto a factor close to what we obtained earlier.

\subsection{Modifying the model}
%
For simplicity, let's assume that the force is ionic as $F= K/x^2$. Our model says that
%
\begin{align}
    6\pi \mu d \frac{2Q}{\pi R^2} \lp 1- \frac{r^2}{R^2} \rp & \leq \frac{K}{(R-r)^2} \\
    1 - \frac{r^2}{R^2} & \leq \lp \frac{K \pi }{12 \mu \pi d Q} \rp \frac{1}{\lp 1 - r/R \rp^2} \\
    1 & \leq \frac{r^2}{R^2} + \alpha \frac{1}{\lp 1-r/R\rp ^2}
\end{align}
%
where $\alpha$ is a factor that compares the ionic force and viscous force and it depends on the flux rate. If we define $x = 1- r/R$ we obtain
%
\begin{align}
    1 \leq (1-x)^2 + \frac{\alpha}{x^2} \\
    x^2- x^2(1-x)^2 \leq \alpha \\
    x^2 (1- (1-x)^2) \leq \alpha \\
    x^3(2-x) \leq \alpha \\
    \text{if} x\ll1 \to x\leq \lp \frac{\alpha}{2}\rp^{1/3}
\end{align}
%
As a result the distance is proportional to $\alpha^{1/3}$. 
%
\begin{figure}[h]
  \centering
  \includegraphics[width=4cm]{./Figs/model2.eps}
  \caption{Flow in the pipe}
\end{figure}
%
Therefore, we obtain
%
\begin{align}
    \text{volume}/\text{time} = \frac{1}{2} \lp \frac{\alpha}{2}\rp^{1/3} \cdot  \frac{Q}{d^3}\lp \frac{\alpha}{2}\rp^{1/3} \cdot 2 \pi d = \frac{\pi}{2^{2/3}} \frac{Q \alpha^{2/3}}{d^2}
\end{align}
%
Note that in here $\alpha$ scales with $1/Q$.

\section{Derivation of Kozeny-Carman Equation}
%
Assuming a proous material we have
%
\begin{align}
    Q = -k \frac{A}{\mu} \frac{\Delta P}{L}
\end{align}
%
where $Q$ is the flow rate, $\Delta P$ is the pressure difference, $A$ is the cross-sectional area, $\mu$ is the fluid viscosity, and $L$ is the sample length and $k$ is called permeability.

The Kozney-Carman (KC) assumes that a porous media can be represented by a solid block permeated by parallel cylindrical tubes whose axes may be at an angle to the pressure gradient, so that the length of an individual pipe is larger than that of the block. To relate permeability $k$ to porosity in such idealized porous media we need to relate $Q$ to $\Delta P$. Each cylindrical pipe is circular with radius $r$. Poisulle flow for a pipe says 
%
\begin{align}
    Q = - \frac{\pi r^4}{8\mu} \frac{\Delta P}{l}
\end{align}
%
where $r$ is the radius of the pipe and $l$ is the length of the pipe. The porosoity $\phi$ and specific surface area $S$ can be related as 
%
\begin{align}
    \phi = \frac{\pi r^2 l}{A L}  = \frac{\pi r^2}{A } \tau
\end{align}
%
where $\tau$ is known as tortuosity (ratio of total flow path length to length of the sample). 
%
The surface area is then
%
\begin{align}
    S = \frac{2\pi r l}{A L} = \frac{2 \pi r^2 \tau}{A} \frac{1}{r} = \frac{2\phi}{r}
\end{align}
%
Using Poisulle flow in a tube we have
%
\begin{align}
    Q = - \frac{\pi r^4}{8\mu} \frac{\Delta P}{l} = - \frac{\pi r^4}{8A}\frac{L}{l} \frac{A}{\mu} \frac{\Delta P}{L} 
\end{align}
%
As a result the permeability becomes 
%
\begin{align}
    k & = \frac{\pi r^4}{8A} \frac{L}{l} = \frac{\pi r^4}{8A\tau} = \frac{1}{8} \frac{\pi r^2\tau}{A} \frac{1}{\tau^2}r^2 \\
    & = \frac{1}{8} \phi \frac{1}{\tau^2} \lp \frac{2\phi}{S}\rp^2 = \frac{\phi^3}{2S^2 \tau^2}
\end{align}
%
where remember that $S$ is the ratio of the total pore surface to the total volume of the porous sample, and $\tau$ is turtosity $l/L$.

Now assume $n$ spherical grains with radius $r$, the total volume is $n 4\pi R^3/3$ and the total surface area is $n 4 \pi R^2$. These grains occupy $1-\phi$ of the total volume. As a result we have
%
\begin{align}
    S = \frac{n 4\pi R^2}{4/3 \cdot n \cdot \pi R^3/(1-\phi) } = \frac{3(1-\phi)}{R}
\end{align}
%
putting all back into the equation, we obtain
%
\begin{align}
    k = \frac{\phi^3}{2S^2 \tau^2} = \frac{\phi^3 R ^2}{2\cdot 9 (1-\phi)^2\tau^2} = \frac{R^2}{18 \tau^2} \frac{\phi^3}{(1-\phi)^2}
\end{align}

As we can see in the simulations, the radius of the tubes does not change that much. If you make this equivalency for the tubes, we find that
%
\begin{align}
    S = S \to \frac{2\phi}{r} = \frac{3(1-\phi)}{R}\\
    \phi = 0.48,~~ R = 75\mu m \\
    r = 44\mu m
\end{align}
%
Looking at the voids, we see that the average pore radius in the experiment is only $13\mu m$. How that can be? How can a tube with 3 times the radius represent an average pore size of $13\mu m $. I argue that the void volume should be equal in these two cases.

\section{My Model}
%
\begin{align}
    Q_\text{tube} = - \frac{\pi r^4}{8\mu} \frac{\Delta P_\text{tube}}{l_\text{tube}}
\end{align}
%
Fore each tube. In total we know that
%
\begin{align}
    Q_\text{tot} = n \frac{\pi r^4}{8\mu} \frac{\Delta P_\text{tube}}{l_\text{tube}}
\end{align}
%
where $n$ is the density of the tubes. This density should be proportional to the area divided by the distance between these tubes. 
%
\begin{align}
    Q = \frac{1}{l^2} \frac{\pi r^4}{8} \frac{A}{\mu}\frac{\Delta P}{L}
\end{align}
%
As a result the permeability is 
%
\begin{align}
    k = \frac{\pi r^4}{8l^2}
\end{align}
%
The question now is how to relate this $r$ and $l$ to porosity and radius of packing objects.

\begin{align}
    \phi = \frac{\frac{A}{l^2} \pi r^2 L}{A L} = \frac{\pi r^2}{l^2}
\end{align}
%
As a result
%
\begin{align}
    k = \frac{l^2}{\pi} \phi^2
\end{align}

\section{Two pipe model}
%
In order to simplify the calculations, we run the two pipe
model. Assume the followig pipe structure
%
\begin{figure}[h]
 \centerline{\includegraphics[width=.5\textwidth]{./Figs/twopipes}}
\caption{Two pipe model}
\label{sup-fig4}
\end{figure}  
%
The ODE set is
%
\begin{align}
  P - P_0 = R(d_1) Q \\
  P_1 - P = R(d_2) Q \\
  R(d) = \frac{c}{d^4} 
\end{align}
%
which results in the following equation
%
\begin{align}
  P_1 - P_0 = \lp R(d_1) + R(d_2) \rp Q \\
  \text{set } P_{0} = 0 \quad \to \quad P_1  =  \lp R(d_1) + R(d_2) \rp Q 
\end{align}

\section{Numerical Simulation From the paper}

\begin{figure}[h]
 \centerline{\includegraphics[width=.9\textwidth]{./Figs/pdf_combined_final.eps}}
\caption{Gradual diameter reduction of tubes (i) at a constant rate, proportional to (ii) the local flux, (iii) local shear rate at the tube's wall, (iv) local velocity. The left figures correspond to gradual changes in probability distribution of magnitude of fluid flow velocity normalized by the interstitial velocity. At each iteration the diameters are reduced as $d_\text{new} = d_\text{old}-\alpha \delta$ where $\alpha$ is a constant value such that $\langle \alpha d \rangle/\langle d\rangle = 0.02\%$. Iterations are indexed by $m$. Figures on the right correspond to the collapse of probability distribution curves when normalized by the apparent velocity $U^\parallel$ which is calculated using inverse square scaling with the measured permeability.}
\label{sup-fig4}
\end{figure}

\subsection{manuscript}

We further develop a numerical model to examine the introduced normalization  in a random network of tubes and to obtain insights on the dynamics of local pore size changes.
% and then utilize permeability normalization
It has been shown that at low porosities $\phi<0.6$, a network of tubes with random diameters correctly captures flow behaviors of a porous medium~\cite{alim2017local}. 
% such as the exponential distribution of fluid velocity \cite{alim2017local}. 
We consider a network of tubes with a random distribution of diameters  as shown in Fig.~\ref{fig4}b. Assuming Poiseuille flow and solving for conservation of mass at all nodes, the fluid flow velocity in each tube is obtained  (see supplementary material for details). Considering different distribution of diameters (uniform, log-normal, or truncated normal) in 2D or 3D, an exponential tail for probability distribution function (PDF) of magnitude of fluid flow is observed which is in agreement with previous studies~\cite{alim2017local}. We now model a gradual polymer retention in the network of tubes with gradual reduction of tubes' diameters in iterations. We consider different diameter reduction rates: a (i) constant rate, or a rate proportional to the (ii) local flux, (iii) local shear rate, or (iv) local velocity. Among these different cases, we observe that a constant rate or a rate proportional to the local flux behaves similar to the experimental results. The gradual reduction of diameters broadens the PDF of velocity and furthermore the normalization of interstitial velocity using bulk permeability results in a decent collapse of probability distribution functions. (See Fig. \ref{fig4}c,d). In addition to the collapse of PDFs, changes in permeability, porosity, and average change of velocity are also consistent with the experimental results (see supplementary material for details). Although the numerical results closely approximate the experimental results, it should be noted that  the study here is insufficient to conclude any definite answer for the precise mechanism of diameter reduction.
% polymer retention in the tubes.

\subsection{supplumentary}
We use our approximate numerical model as a proxy to investigate the polymer adsorption rate in the pores. We gradually reduce  tubes' diameters through iterations while we monitor changes in the distribution of fluid flow velocity and examine if such changes preserve the scaling law introduced earlier. The rate of tube's diameter reduction $\delta$, which represent the polymer deposition in the pores, can be considered (i) constant ($\delta \propto 1$), (ii) proportional to the flux rate in the tube ($\delta \propto q$), (iii) proportional to shear rate at tube's wall ($\delta \propto q/d^3$), or even (iv) proportional the the velocity in the tube ($\delta \propto q/d^2$). For each process, we pick a uniform distribution of diameters with $\langle d\rangle =10,\sigma_r=0.5$ and obtain the flow rates throughout the pipes. We then reduce the tubes diameter  $d_\text{new} = d_\text{old} - \alpha \delta $ where  $\alpha$ is a constant chosen such that the normalized average of diameter reduction be 0.2\% i.e., $\langle \alpha \delta\rangle /\langle d\rangle = 0.2\%$. After this small diameter reduction, we recalculate the flow in the tubes and reiterate the process.  Each iteration is indexed by $m$ and the result for different diameter reduction procedures are shown in Fig. \ref{sup-fig4}~a,c,e,g.
% The probability distribution for magnitude of fluid velocity  normalized by interstitial velocity remains exponential decaying consistent with experimental measurements. 
In the case of constant diameter reduction  or diameter reduction proportional to the local flux, the probability distribution for magnitude of velocity remains exponential and the tail of distribution broadens slowly (see Fig. \ref{sup-fig4}a,c). However, when diameter reduction is  proportional to shear rate or velocity, the distribution starts to diverge from an exponential and extreme large values in the tail is observed (see Fig. \ref{sup-fig4}e,g). The results for normalizing the interstitial velocity using permeability values are shown in \ref{sup-fig4}~b,d,f,h for different cases. When the diameter reduction is at a constant rate or proportional to the local flux, the scaling law is conserved (see Fig. \ref{sup-fig4}~b,d); however, when the diameter reduction is proportional to the shear rate or tube's velocity the tail of the probability distribution fails to collapse on a single curve. Based on the above numerical experiments, the dynamics of polymer retention is consistent with the models of diameter reduction either at a constant rate or at a rate proportional to the local flux. We further compare the details of changes where in the experiments we found that the permeability decreases by $60\%$, while porosity only decreases by $20\%$, and average velocity increases by $70\%$. In the case where diameter reduces proportional to the local flux, we find that after $m=55$ iterations the permeability reduces by $60\%$, while the porosity decreases by $20\%$ and average velocity increases by $67\%$; while in the case of constant diameter reduction  after $m=100$ iterations, the permeability reduces by $60\%$, the porosity decreases by $30\%$, while the average velocity increases by $50\%$. As a result, the diameter reduction proportional to the flux rate better matches with the experimental results.

\newpage

\section{Percolation}

Percolation theory is about emergent conectivity properties of large
number of objects. The objects are extended spatially and the
positioning are statistically prescribed.

\textbf{Definition:} A cluster is a group of nearest neighboring occupied
sites.

\textbf{Definition}: The cluster number $n_s(p)$ denotes the number of
$s$-clusters per lattice site.

\textbf{Definition}: The percolation threshold $p_c$ is the
concentration (occupation probability) $p$ at which an infinite
cluster appears for the first time in an infinite lattice.

\textbf{Definition}: If $\Pi(p,L)$ denotes the probability that a
lattice of linear size $L$ percolates at concentration $L$, then
%
\begin{align}
  \lim_{L\to \infty}\Pi (p, L) =
  \begin{cases}
    0 & \text{if } p<p_c \\
    1 & \text{if } p\geq p_c
  \end{cases}
\end{align}
%

\section{Percolation in 1D}

Consider a 1d lattice of size $L$ where each site is occupied with the
probability $p$. Since the probability of occupying the sites are
independent, then the probability of all sites being occcupied is 
%
\begin{align}
  \Pi (p, L) = p^L
\end{align}
%
therefore
%
\begin{align}
  \lim_{p\to \infty} \Pi (p,L) = \lim_{L\to \infty} p^L  =
  \begin{cases}
    0 & \text{if } p <1 \\
    1 & \text{if } p =1
  \end{cases}
\end{align}
%
This implies that $p_c = 1$.

The number of $s$-clusters can be found as
%
\begin{align}
  n_s(p) = (1-p) p^s (1-p)
\end{align}
%
This expression can be re-written as 
%
\begin{align}
  n_s(p) & = (1-p) p^s (1-p) \\
         & = (1-p)^{2} p^s  \\
         & = (1-p)^{2} \exp(s \log (p) ) \\
         & = (p_c-p)^{2} \exp(-\frac{s}{s_{\zeta}})
\end{align}
%
where
%
\begin{align}
  s_{\zeta}  = - \frac{1}{\log(p)}  = -\frac{1}{\log(p_c - (p_c - p) )} 
\end{align}
%
As a result, when $p\to p_c$, then
%
\begin{align}
  s_{\zeta } \to \frac{1}{p_{c}-p}, \qquad p \to p_c. 
\end{align}
%
Therefore the $n_s(p)$ as $p\to p_c$ becomes
%
\begin{align}
  n_s(p) & \to (p_c-p) \exp( - (p_c-p) s) 
\end{align}
%
therefore if we plot $s^2 n_s (p) $ versus $s^2 (p_c-p)$ all the
graphs should collapse on each other if $p \to p_c$.

\textbf{Definition:} The critical exponent $\sigma $is defined as
%
\begin{align}
  s_{\zeta} \propto (p_c - p)^{\frac{1}{\sigma} }, \qquad p \to p_c
\end{align}
%

Next, we want to prove that
%
\begin{align}
  \sum_{s=1}^{\infty} s n_s(p) = p 
\end{align}
%
In the LHS, the $s n_s(p)$ is the probability that an arbitrary site
belongs to a $s$-cluster size. If we add these probabilities for all
cluster sizes, it should become the probability of the site being
occupied. To show this, we have
%
\begin{align}
  \sum_{s=1}^{\infty} s n_s(p) &= \sum _{s=1}^{\infty} s (1-p)^2 p^s \\
                               & = \sum_{s =1}^{\infty} (1-p)^2p \frac{\d}{\d p} p ^s \\
                               & = (1-p)^2 p \frac{\d }{\d p} \sum_{s = 1} ^{\infty} p^s \\
                               & = (1-p)^2 p \frac{\d }{\d p } \frac{p}{1-p} \\
  & = p.
\end{align}
%

The next question is, how large on average clusters are? At first, we
need to see what is the probability of a cluster with size $s$? We
know that the probability of a site belonging to a cluster size $s$ is
$sn_s(p)$, and the probability of that point belongs to any cluster
size is $p$. Therefore each point has the probability of $w_s = s n_s(p)/p$
belonging to a cluster size $s$ among all clusters. Therefore
%
\begin{align}
  w_s = \frac{s n_{s}(p)}{p} = \frac{ s n_{s}(p) }{ \sum_{s=1}^{\infty} s n_{s}(p)} 
\end{align}
%
Now, we can calculate the mean cluster size as
%
\begin{align}
  S(p) & = \sum_{s=1}^{\infty} s w_s(p) = \frac{\sum_{s=1}^{\infty} s^2 n_s(p) }{\sum s n_s(p) }   \\
       & = \frac{1}{p} (1-p)^2 (p \frac{\d}{\d p} ) (p \frac{\d }{\d p } ) \sum_{s=1}^{\infty} p^{s}\\
  & = \frac{1+p}{1-p} 
\end{align}

\textbf{Definition}: The correlation funtion or pair conectivity
$g(r)$ is the probability that a site at position $r$ from an occupied
site belongs to the same finite cluster. Note that clearly $g(r= 0) =
1$ since the site is already occupied.

In 1D, the correlation function is calculated as
%
\begin{align}
  g(r) = p \cdot p \cdot \cdots \cdot p =   p^r
\end{align}
%
We normally express this in an exponential form and find the critical
exponent as
%
\begin{align}
  & g(r) = p^r = \exp (r \log(p)) = \exp (-\frac{r}{\zeta})\\
  & \zeta = -\frac{1}{\log (p) } = -\frac{1}{\log\lb p_c - (p_c-p)\rb} \to (p_c-p)^{-1}, \quad p\to p_c  
\end{align}
%
The value of $\zeta$ is known as correlation length which diverges as
$p\to p_c$. In 1D, we found that $\zeta = s_{\zeta}$, where it is not
normally true; normally $s_{\zeta} \propto \zeta^D$ where $D$ is the
fractal dimention.

\textbf{Definition}: The critical exponent $\nu$ is defined by
%
\begin{align}
  \zeta \propto |p_c-p|^{\nu}, \qquad p \to p_c
\end{align}
%

??????? I don't know why, but it is aruged that
%
\begin{align}
  \sum_r g(r) = S(p) 
\end{align}

\section{Infinite Dimension}

Percolation in 1D and infinite dimension can be solved
analytically. The infinte dimension is similar to the Beth lattice.

\subsection{Beth Lattice}

In Beth lattice, each site (vortex) is connected to $z$ neighbors
(vortices). As a result each branch (edge) is connected to $z-1$ other
branches.

\begin{figure}[h]
  \centering
  \includegraphics[width=8cm]{beth-lattice}
  \caption{Beth Lattice with $z=3$. Source: wikipedia}
\end{figure}

The 1D case that we studied is essentially a Beth lattice with
$z=2$. The next question is why Beth lattice corresponds to $d=
\infty$? The reasons are

\begin{itemize}
\item (a) The number of surface sites relative to total number of
  sites approaches a constant as $d\to \infty$.

  The total number of sites in Beth lattice are number of sites from
  generation 0 plus number of sites in generation 1 added
  together. Assume we have a Beth lattice with $z=3$, and we go upto
  $g$ generations then
%
\begin{align}
  \text{total number of sites } & = 1 + 3 + 3\cdot 2 + 3 \cdot 2^2 + \cdots + 3 \cdot 2^{g-1} \\
                                & = 1 + 3(1 + 2 + 2^2 + 2^3 + \cdots + 2^{g-1}) \\
  & = 1 + 3 \frac{2^{g}-1 }{2-1}  = 3\cdot 2^g -2 
\end{align}
%
while the total number of surface sites (sites at the outer most
boundary) are $3\cdot 2^{g-1}$. Therefore
%
\begin{align}
  \frac{\text{Number of surface sites}}{\text{Total Num of sites}} = \frac{3\cdot 2^{g-1}}{3 \cdot 2^{g} - 2} \to \frac{1}{2}, \qquad g\to \infty  
\end{align}

Generally, the numbers are a s
%
\begin{align}
  \text{total number of sites} & = 1 + z (1 + (z-1) + (z-1)^{2} + \cdots + (z-1)^{g-1}) \\
  & = 1  + z \frac{(z-1)^{g} - 1 }{z - 2} 
\end{align}
%
therefore
%
\begin{align}
  \frac{\text{Number of surface sites}}{\text{Total Num of sites}} &= \frac{ z \cdot (z-1)^{g-1}}{1  + z \frac{(z-1)^{g} - 1 }{z - 2} } \\
                                                                   & =  \frac{(z-1)^g + (z-1)^{g-1}}{ \frac{z-2 + (z-1)^{g+1} + (z-1)^g - z }{z-2}  }  \\
                                                                   & \to  \frac{(z-2)(z-1)^g}{(z-1)^{g+1}} = \frac{z-2}{z-1} 
\end{align}

In a hypercube lattice of linear size $L$ when $d\to \infty$, the
surface in a $d$ dimension is proportional to $L^{d-1}$ and the volume
is proportional to $L^d$, therefore
%
\begin{align}
  \text{Surface} \propto \text{Volume}^{\frac{d-1}{d}}  = \text{Volume}^{1 - \frac{1}{d}}
\end{align}
%
therefore as $d\to \infty$, the ration of the surface to volume
becomes a constant.

\item (b) There are no closed loops in Bethe lattice. In a hypercube
  lattice the probability of finding a close loop is zero. Assume a
  $d$ dimension hypercube and a particle centered at a site. There are
  $2d$ nearest sites that the next particle can be placed. The next
  particles can be placed at $2d-1$ positions. Therefore assuming a 4
  point lattice, there are $2d (2d-1)^2$ possibilities. If now we want
  to put these 4 points in a lattice, we have $2d$ for the second
  particle, $2d-2$ positions for the third particle and only $1$
  position for the last particle. Therefore
  %
  \begin{align}
    \frac{\text{Number of loops}}{\text{Total number of chains}} = \frac{2d\cdot(2d-2)\cdot 1 }{2d (2d-1)^{2}}   \to 0, \qquad d\to \infty
  \end{align}

\end{itemize}

For these two reasons, a Bethe lattice is considered as infinite
dimension lattice.

\textbf{Question}. What is the occupation probability to make sure an
infinite path occurs in a Bethe lattice? Starting from the center,
there are $z-1$ neighbors, and assuming an occupation probability of
$p$, we have $p(z-1)$ occupied sites. We need to make sure that at
least one occupied site exists, therefore
%
\begin{align}
  p_c(z-1) = 1 \to p_c = \frac{1}{z-1} 
\end{align}
%

\textbf{Definition}: The strength of an infinite cluster $P(p)$ is the
probability that an arbitrary site belongs to an infinite cluster.

\section{Random Walk}

\subsection{Random Walk and Diffusion Equation}

If at time $t$ the probability distribution is as
$p(\mathbf{r},t)$. Now assume $\tau$ time later, we need to integrate
over all the space. We have
%
\begin{align}
  p(\mathbf{r},t + \tau ) = \int p(\mathbf{r}- \mathbf{l}, t) g(\mathbf{l}) \d \mathbf{l} 
\end{align}
%
To proceed we do the Taylor expansion, we find that
%
\begin{align}
  p(\mathbf{r}-\mathbf{l},t) \approx p(\mathbf{r},t) - \n p \cdot \mathbf{l} + \frac{1}{2}  \sum_{ij} \frac{\p^{2} p}{\p x_i \p x_j} l_i l_j \\
  p(\mathbf{r}, t+\tau) = p(\mathbf{r},t) + \tau \frac{\p p }{\p t} 
\end{align}
%
Therefore,
%
\begin{align}
  & p(\mathbf{r},t) + \tau \frac{\p p }{\p t}   = \nonumber \\
  & \qquad  \int \lb p(\mathbf{r},t) - \n p \cdot \mathbf{l} + \frac{1}{2}  \sum_{ij} \frac{\p^{2} p}{\p x_i \p x_j} l_i l_j \rb g(\mathbf{l}) \d \mathbf{l} \\
   & p(\mathbf{r},t) + \tau \frac{\p p }{\p t}   = \nonumber \\
  & \qquad   p (\mathbf{r},t) - \n p \cdot \int \mathbf{l}  g(\mathbf{l}) \d \mathbf{l} +  \int \frac{1}{2}  \sum_{ij} \frac{\p^{2} p}{\p x_i \p x_j} l_i l_j g(\mathbf{l}) \d \mathbf{l} 
\end{align}
%
If the diffusion process is isotropic, then there is no difference
between $\pm \mathbf{l}$, therefore the second term on the RHS
vanishes as
%
\begin{align}
  \int \mathbf{l} g(\mathbf{l}) \d \mathbf{l} = 0  
\end{align}
%
The relation therfore summarizes to
%
\begin{align}
  \tau \frac{\p p }{\p t}  = \frac{1}{2} \int \sum_{ij} \frac{\p^{2} p }{\p x_i \p x_j} l_il_j g(\mathbf{l}) \d \mathbf{l} 
\end{align}
%
If we assume that the diffusion is isotropic, i.e., $g(x,y,z) =
g(-x,y,z)$ and etc., then only the diagonal terms survive and we obtain
%
\begin{align}
  \tau \frac{\p p }{\p t}  = \frac{1}{2} \int \sum_{i} \frac{\p^{2} p }{\p x_i \p x_i} l_i^2 g(\mathbf{l}) \d \mathbf{l} \\
    \tau \frac{\p p }{\p t}  = \frac{1}{2} \sum_{i} \frac{\p^{2} p }{\p x_i \p x_i} \int  l_i^2 g(\mathbf{l}) \d \mathbf{l} 
\end{align}
%
We furthermore have that
%
\begin{align}
  \int l_i^2 g(\mathbf{l}) d \mathbf{l} = \frac{1}{3} \int \mathbf{l}\cdot \mathbf{l} g(\mathbf{l}) d \mathbf{l} = < \mathbf{l}^2>
\end{align}
%
Therefore, we finally obtain
%

\begin{align}
  \tau \frac{\p p }{\p t}  = \frac{1}{6} \n^2p < \mathbf{l}^2> \\
  \frac{\p p }{\p t}  = \frac{<\mathbf{l}^2>}{6\tau} \n^2p 
\end{align}
%
where we can summarize the final equation as
%
\begin{align}
  \frac{\p p}{\p \tau}  = D \n^2p
\end{align}
%
in which $D =  <\mathbf{l}^2> / 6\tau$ is the diffusion constant.

\subsection{Normal Diffusion}

There are various approaches to the diffusion equation. 
\subsubsection{Fick's law}
%
Diffusion was pioneered by Fick motivated by a biological application
(transport through membranes). By conservation law for total number of
particles, he derived the diffusion equtaion for concentration of
species as
%
\begin{align}
  \frac{\p c}{\p t} = D \frac{\p^{2} c}{\p x^2}  
\end{align}
%
The derivation is as follows: Assume we have $N(x)$ particles at
position $x$, and $N(x + \Delta x) $ at position $x+\Delta x$. The
cross section area in between these points is $A$. The question is how
many particles will pass through this cross sectional area. Half of
the particles at $x$ move to right and the other half to the
left. Same story for the particles at $x + \Delta x$. Therefore the
flux of molecules $J$ through the area $A$ during a short time $\tau$
is
%
\begin{align}
  J = \frac{ -\frac{1}{2} ( N(x+ \Delta x) - N(x)  }{A \tau} 
\end{align}
%
we define concentration $c \equiv {N(x) }/ {A \Delta x} $, therefore
the flux becomes
%
\begin{align}
  J = - \frac{\Delta x ^{2}}{2 \tau} \frac{ c(x + \Delta x) - c(x) }{\Delta x} = - D \frac{\p c }{\p x }  
\end{align}
%
therefore the flux is proportional to the diffusion constant $D \equiv
\Delta x ^2/2 \tau$ and the gradient of concentration.
%
Since the total number of particles are conserved, then
%
\begin{align}
  \frac{c(t+\Delta t) - c(t)}{\Delta t} = \frac{1}{\Delta t} \frac{\lp J(x) - J(x+\Delta x)\rp A\Delta t }{A \Delta x} =   - \frac{ J(x+\Delta x) - J(x) }{ \Delta x} 
\end{align}
%
Therefore the results summarizes to
%
\begin{align}
  \frac{\p c}{\p t}  = - \frac{\p J]}{\p t}, \qquad J = -D \frac{\p c}{\p x} 
\end{align}
%
or in one diffusion equation as
%
\begin{align}
  \frac{\p c}{\p t}  = D \frac{\p ^{2}c }{\p t^2} 
\end{align}
%

%
\textbf{Observations}:
%
\begin{itemize}
\item The same equation holds for the probability density (PDF)
  $p(x,t)$ to find a particle at position $x$ and time $t$
\item The PDF of the position of particles starting from a
  concentrated droplet in an unbounded medium is Gaussian with
  variance $2Dt$
\item It means that the particles mean squared displacement (MSD) in
  the $x$-direction grows proportionally with time $<x^2> = 2Dt$,
  where the coefficient of this proportionality is twice the diffusion
  constant $D$
\item The same is true for other coordinates, so the toal MSD grows as
  $<r^2> = 2dD t$, where $d$ is the dimension of the space. 
\end{itemize}

\subsubsection{Microscopic, molecular approach}

Done by Einstein! It is essentially a random walk. It samples
particles at discrete istant of time separated by interval $\tau$. How
does the known MSD behavior in diffusion emerges from such a model?

Assume the particle is taking steps $s_i$ at each time. The particle's
displacement is then given by
%
\begin{align}
  x(t) = \sum_1^{N(t)} s_i
\end{align}
%
where $N(t)$ is the total number of steps performed until time
$t$. From this picture, we get
%
\begin{align}
  \langle x(t)^2 \rangle= \la \lp \sum_1^{N(t)} s_i \rp^{2} \ra = \la \sum_{i,j = 1}^{N(t)} s_i s_j \ra = \la \sum_{i =1}^{N(t)} s_i^2 \ra + \la \sum_{i\neq j} s_i s_j\ra 
\end{align}
%
So the MSD is expressable through step correlation function $C_{ij} =
\la s_i s_{j }\ra $. Since the steps are assumed to be independent and
uncorrelated and symmetrically distributed around zero, the last term
vanishes . The mean squared displacement of each step is $\la s_i^2
\ra  = a^2$, thus
%
\begin{align}
  \la x(t) ^2 \ra = \sum_{i=1}^{N(t)} \la s_i^2\ra  = N(t) a^2 = \frac{a^{2}}{\tau} t
\end{align}
%
So the diffusion coefficient becomes as $D = a^2/2\tau$. The term $k
\equiv 1/\tau$ is the rate of steps or the mean number of steps per
unit time.

\subsubsection{Langevin Approach}

In this approach, paqrticles are moving in a fluid medium following
Newtonian Mechanics and under the influence of esxternal forces and
friction! The effect of thermal motion of the molecules and of the
surrounding medium are modeled with addisional random force term
(``noise''). The equation of motion is then
%
\begin{align}
  m\dot v = - \gamma v + f + \zeta (t) \label{eq-langevin}
\end{align}
%
where $m$ is the mass, $\gamma$ is the friction, and $\zeta$ is the
random force, and $f$ is the external force. From this equation
Langevin was able to derive MSD of the particles.

In order to solve the \eqref{eq-langevin} equation, lets first assume
there is no external force and no randomness. Therefore, the equation
is dominated by the viscous force and we have
%
\begin{align}
  m \dot v = -\gamma v
\end{align}
%
where the solution is
%
\begin{align}
  v(t) = \exp(-\gamma t /m) v(0)
\end{align}
%
which means that the velocity vanishes. We know that the average of
random particles should become $1/2 m \la v^2 \ra = 1/2 k_BT$, so the
particles are not only derived by the viscous term. Lets add the
random force, we have
%
\begin{align}
  m\dot v = - \gamma v + \zeta (t) 
\end{align}
%
Now that we have $\zeta (t)$ on the right hand side, we assume the
solution to have the following form
%
\begin{align}
  v(t) = e^{- \gamma t /m } b(t)
\end{align}
%
replacing back in the governing equation, we obtian
%
\begin{align}
  \dot b (t) = e^{\gamma t/m}\zeta (t) /m 
\end{align}
%
Note that the initial condition for $b(0) = v(0)$. The solution of $b(t)$ becomes as
%
\begin{align}
  b(t) = v(0) + \int_0^t e^{\gamma  s/m} \zeta(s) /m ~\d s 
\end{align}
%
putting everything together, the solution becomes as
%
\begin{align}
  v(t) =  e^{- \gamma/m t} v(0) + \int_0^t  e^{- \gamma (t-s)/m} \zeta (s) /m ~ \d s 
\end{align}
%
Now lets calculate the mean squared velocity, we have
%
\begin{align}
  \la v(t) \ra ^2 =  \la e^{- 2\gamma/m t} v(0)^2 \ra + 2 \la e^{- \gamma/m t} v(0)\cdot \int_0^t   e^{- \gamma (t-s)/m} \zeta (s) /m ~ \d s \ra + \la \int_0^t  \lp e^{- \gamma (t-s)/m} \zeta (s) /m ~ \d s\rp ^2 \ra
\end{align}
%
If we assume that $\la \zeta \ra = 0$, and $\la \zeta (t) \zeta (s)
\ra = 2 B \delta (t-s)  $, therefore the result become as
%
\begin{align}
  \la v(t)^{2} \ra & = \la e^{- 2\gamma/m t} v(0)^2 \ra + \int_0^t \int _0^t  e^{- \gamma (t-s)/m} e^{- \gamma (t-s')/m} \frac{ \la \zeta (s) \zeta (s') \ra}{m^2} ~ \d s ~ \d s' ~  \\
                  & = \la e^{- 2\gamma/m t} v(0)^2 \ra + \int_0^t \int _0^t  e^{- \gamma (t-s)/m} e^{- \gamma (t-s')/m} \frac{ 2 B \delta (s-s') }{m^2} ~ \d s ~ \d s' ~ \\
                  & = \la e^{- 2\gamma/m t} v(0)^2 \ra +  \int_0^t   e^{- 2\gamma (t-s)/m} \frac{ 2 B }{m^2} ~ \d s \\
  &  = e^{- 2\gamma/m t} v(0)^2  + \frac{B}{\gamma m} \lp 1 - e^{-2\gamma t/m }\rp
\end{align}

\subsection{1D - Random Walk - Characteristic Function}
%
In 1d random walk we have the following
%
\begin{align}
  x =
  \begin{cases}
    1, & \text{probability  } p \\
    -1 & \text{probability  } q
  \end{cases}
\end{align}
%
we define the characteristic function $\lambda(\th) = \la e^{i \theta x} \ra
$.  Therefore, 
% 
\begin{align}
  \lambda = p e^{i\theta} + q e^{-i\theta}
\end{align}
%
We can now find the probability of the object being at $j$th location
after $n$ steps by calculating the coefient of
%
\begin{align}
  P_n(j) = \frac{1}{2\pi} \int_{-\pi}^{\pi} \lp p e^{i\theta} + q e^{-i\theta} \rp^n e^{-ij\th}\d \th
\end{align}
%
which is giving out the coefficient corresponding to the $j$th
position. Noting that
%
\begin{align}
  \frac{1}{2\pi} \int_{-\pi}^{\pi} e^{-i\th n}\d \th = \delta_{n,0}
\end{align}
%
one can calculate the above expression. In the case of $p=q = 1/2$,
the expression reduces to
%
\begin{align}
  \lambda (\th) = \cos(\th). \to P_n(j) = \frac{1}{2\pi} \int_{-\pi}^{\pi} \cos\th^n e^{-ij \th}\d \th
\end{align}

\subsubsection{General case}

Assume the random walker picks its displacement per step by a
probability density function $p(x)$.

\newpage

\section{Poroelasticity}

The coupling between changes in stress and changes in fluid pressure
forms the subject of poroelasticity

There are two types of coupling:
%
\begin{itemize}
  \item Solid-to-Fluid Coupling: a change in applied stress produces a
    change in the fluid pressure. The magnitude of this coupling
    depends on the compressibility of the fluid. 
  \item Fluid-to-solid Coupling: A change in Fluid pressure changes the volume of porous material
\end{itemize}
%

Assumptions and terms usually used:
%
\begin{itemize}
\item fluid pressure and pore pressure are usually used
  interchangeably
 \item elastic wave propagation due to fluid-solid interaction is also
   usually ignored
\end{itemize}

\begin{itemize}
\item Poroelastic equations were derived by Biot
  \cite[][]{biot_general_1941,biot_theory_1955,biot_theory_1956}

  A review of Biot's approach is as follows:
  \begin{itemize}
  \item $\sigma$: isotropic applied stress, positive if tensile,
    negative if compressive
   \item $V$: the bulk volume
   \item $\ep = \delta V/V$ volumetric strain, positive in expansion,
     negative in contraction
   \item $\zeta$ increment in fluid content
   \item $p$ fluid pressure
   \end{itemize}
   Constitutive relations are
   %
   \begin{align}
     \ep &= a_{11} \sigma + a_{12} p \\
     \zeta &= a_{21} \sigma + a_{22} p 
   \end{align}
\end{itemize}

\begin{figure}[h]
  \centering
  \includegraphics[width=5cm]{Figs/poroelasticity-crumble}
  \caption{Example of a 2D structure considered for percolation
    problem, Lahini \textit{et al.}, PRL, 2017 } \label{fig-soft-hard}
\end{figure}

\subsection{Mandel Cryer Effect}

Model is as follows:
%
\begin{align}
  \sigma - \sigma_0 = \mathbf{C}: \lp \ep - \ep_0\rp - \alpha p \mathbf{I}\\
  \rho S \frac{\p p}{\p t} + \n . (\rho \mathbf{q}) = Q - \rho \a \frac{\p \ep_{v}}{\p t}\\
  \mathbf{q} = - \frac{k}{\mu} \n p 
\end{align}
%
where $\mathbf{C}$ is the stiffness tensor, $\sigma$ is the stress
tensor, $\ep$ is the strain tensor, $\rho$ is fluid density, $k$ is permeability, $\mu$ is fluid
viscosity, $S$ is the storage parameter, $\a$ is the Biot constant,
and $\ep_v$ is the volumetric strain.

\begin{figure}[h]
  \centering
  \includegraphics[width=15cm]{Figs/mandel-cryer-effect}
  \caption{Mandel-Cryer effect. Pore pressure versus time at the
    center of a poro-elastic cylinder. From p. 196, Herbert Wang, Theory of
    linear poroelasticity.} \label{fig-soft-hard}
\end{figure}

\newpage

\newpage

\section{Percolation and Structural Mechanics}

Assume we have a structure made of soft and hard materials on a 2D
lattice (see Fig. \ref{fig-soft-hard}). The proability of a site being
occupied as soft material is $p$ and the probability of the site being
occupied with hard material is $1-p$. The question is how does the
material property changes for different values of $p$? Obviously when
$p=1$, all the material is made of a soft material with its properties
and when $p=0$ the material is made of a hard material and its
properties is determined with the hard material.

\begin{figure}[h]
  \centering
  \includegraphics[width=5cm]{Figs/percolation-first}
  \caption{A 2D material with soft (yellow) and hard (black) material
    next to each other.} \label{fig-soft-hard}
\end{figure}

I would expect that the Elasticity of the 2D material have some sort
of transition from soft to hard that depends on the probability $p$.

\begin{figure}[h]
  \centering
  \includegraphics[width=10cm]{Figs/elasticity-percolation}
  \caption{Behavior of elasticity with percolation probability $p$} \label{fig-elasticity-percolation}
\end{figure}

\section{Elasticity}

Under action of a force, solid objects deform. Assuming a point in
solid at $\mathbf{x} = (x,y,z)$ will come to $\mathbf{X} =
(X,Y,Z)$. The vector $\mathbf{u} = \mathbf{x}- \mathbf{X}$ is then
known as displacement field. When the solid is elastic and the
displacement is small, the relation ship between stress $\sigma$, and
the strain tensor $\epsilon$ is given by Hooke's law as
%
\begin{align}
  \sigma_{ij} = \lambda \delta _{ij} \n . \mathbf{u} + 2\mu \epsilon _{ij} (\mathbf{u}) 
\end{align}
%
where the strain tensor is given as
%
\begin{align}
  \epsilon_{ij} (\mathbf{u}) = \frac{1}{2} \lp \frac{\p u_{i}}{\p x_{j}} + \frac{\p u_{j}}{\p x_{i}} \rp
\end{align}
%
The parameters $\lambda$ and $\mu$ are two constants (known as Lam\'e constants) that depend on
the material properties.

\textbf{Question}. How does Lam\'e constants relate to the famous
Yong and shear modul of elasticity $E, G$?

We define $\varepsilon_{ij} = \p u_i/ \p x_j$. Expanding the relation
we had, we see
%
\begin{align}
  \sigma_{11} & = \lambda (\vep_{11} + \vep_{22} + \vep_{33}) + \mu \lp \vep_{11} + \vep_{11}\rp \nonumber\\
             & = ( \lambda + 2\mu )\vep_{11}  + \lambda \vep_{22} + \lambda \vep_{33} \\
  \sigma_{12} & =  \mu ( \vep _{12} + \vep _{21}) \nonumber\\
             & = 2\mu \vep_{12} 
\end{align}
%
On the other hand, by the definition of Yong modulus $E$ and shear
modulus $G$ we have
%
\begin{align}
  \vep_{11} & = \frac{1}{E}  \lb \sigma_{11} - \nu \lp \sigma_{22} + \sigma_{33}\rp \rb \\
  \vep_{22} & = \frac{1}{E}  \lb \sigma_{22} - \nu \lp \sigma_{11} + \sigma_{33}\rp \rb \\
  \vep_{33} & = \frac{1}{E}  \lb \sigma_{33} - \nu \lp \sigma_{11} + \sigma_{22}\rp \rb \\
  \vep_{12} = \frac{\sigma_{12}}{2G}, & \qquad \vep_{23} = \frac{\sigma_{23}}{2G},  \qquad \vep_{13} = \frac{\sigma_{13}}{2G}
\end{align}
%
Comparing these two set of equations, one can find that
%
\begin{align}
 \mu = G \equiv \frac{E}{2(1+\nu)} , \qquad \lambda  = \frac{E\nu}{(1-2\nu)(1+\nu)} 
\end{align}
%
\section{Equilibrium Equation - Variational Format}
%
The equilibrium equation reads as
%
\begin{align}
  \frac{\p \sigma_{ij}}{\p x_{j}}  + F_i = \ddot u_i \to \frac{\p \sigma_{ij}}{\p x_{j}}  + F_i  = 0
\end{align}
%
where the second equation is assuming the static
equilibrium. Therefore the equation that we are solving is as
%
\begin{align}
   \n \cdot \sigma + \mathbf{F} =0
\end{align}
%
To get the variational form, we multiply both sides by a test function
and integrate over a test domain $\Omega$ to obtain
%
\begin{align}
  \int_{\Omega} \lp \n \cdot\sigma\rp \cdot ~\mathbf{v} ~\d x + \int_{\Omega} \mathbf{F} \cdot \mathbf{v} ~\d x = 0\\
  \int_{\partial \Omega} (\sigma \mathbf{n})\cdot \mathbf{v} ~\d s - \int_{\Omega} \sigma : \n \mathbf{v}~ \d x + \int_{\Omega} \mathbf{F} \cdot \mathbf{v} ~\d x = 0 \label{variational-equil}
\end{align}
%
Note that in the above equations we used the following divergence
identity from vector calculus: For an arbitrary domain $D$, tensor
$A_{ij}$ and vector $b_i$, the following identity holds
%
\begin{align}
  \int_D (\n \cdot \mathbf{A}) \cdot \mathbf{b} ~ \d x  = \int_{\p D} (\mathbf{An})\cdot \mathbf{b} ~\d s  - \int_D \mathbf{A}:\n \mathbf{v} ~\d x
\end{align}
%
where $\mathbf{n}$ is the normal vector to the boundary $\p D$ and $:$
denotes the double dot product as
%
\begin{align}
  \mathbf{X}: \mathbf{Y} = \sum_{ij} X_{ij}Y_{ij}
\end{align}
%
and the gradient of the vector defined as
%
\begin{align}
  \lp \n \mathbf{v} \rp_{ij} = \frac{\p v_{i}}{\p x_{j}} 
\end{align}
%
Now getting back to equation \eqref{variational-equil}, since stress
tensor is symmetric we have
%
\begin{align}
  \int_{\partial \Omega} (\sigma \mathbf{n})\cdot \mathbf{v} ~\d s - \int_{\Omega} \sigma : \n \mathbf{v}~ \d x + \int_{\Omega} \mathbf{F} \cdot \mathbf{v} ~\d x = 0 \\
  \int_{\partial \Omega} (\sigma \mathbf{n})\cdot \mathbf{v} ~\d s - \int_{\Omega} \sigma : \frac{1}{2} \lp \n \mathbf{v} + \n \mathbf{v}^{\top} \rp ~ \d x + \int_{\Omega} \mathbf{F} \cdot \mathbf{v} ~\d x = 0 \\
    \int_{\partial \Omega} (\sigma \mathbf{n})\cdot \mathbf{v} ~\d s - \int_{\Omega} \sigma : \ep(\mathbf{v}) ~ \d x + \int_{\Omega} \mathbf{F} \cdot \mathbf{v} ~\d x = 0
\end{align}
%
From the previous section we know that
%
\begin{align}
  \sigma_{ij} = \lambda \delta _{ij} \n . \mathbf{u} + 2\mu \epsilon _{ij} (\mathbf{u}) 
\end{align}
%
Using the above equation we obtain the following variational form
%
\begin{align}
      \int_{\partial \Omega} (\sigma \mathbf{n})\cdot \mathbf{v} ~\d s - \int_{\Omega} \lambda \n \cdot \mathbf{u} \n \cdot \mathbf{v} ~ \d x  - \int 2\mu \ep (\mathbf{u}) : \ep (\mathbf{v}) ~ \d x+ \int_{\Omega} \mathbf{F} \cdot \mathbf{v} ~\d x = 0
\end{align}
%
where the first equation is usually handled with the boundary
conditions. So, we solve the following variational form equation
%
\begin{align}
  & \int_{\Omega} \lambda \n \cdot \mathbf{u} \n \cdot \mathbf{v} ~ \d x  + \int 2\mu \ep (\mathbf{u}) : \ep (\mathbf{v}) ~ \d x - \int_{\Omega} \mathbf{F} \cdot \mathbf{v} ~\d x = 0\\
  & \text{subject to } \sigma \mathbf{n} = \mathbf{g} \text{ on some
  boundaries } \nonumber\\
  & \qquad \text{ and  } \mathbf{u} = \mathbf{u}_0 \text{ on other boundaries}
\end{align}

\section{Numerical Result}

In this section, I implement the finite element code discussed above
and test it for various cases.

\subsection{Initial Test - Simple tension}

The simple geometry is a 2D material in a rectangle shape with size
$2\times 20$ (see Fig. \ref{fig-simple-tension}). The physical constants are
%
\begin{align}
  E = 10^6, \qquad \nu = 0, \qquad \sigma_0 = 1000
\end{align}
%
\begin{figure}[h]
  \centering
  \includegraphics[width=8cm]{Figs/tension-simple}
  \put(-140,60){$E,\nu$}
  \put(3,60){$\sigma_0$}
  \caption{An isotropic material under simple
    tension} \label{fig-simple-tension}
\end{figure}
%
The expected tension at the end of the rod is
%
\begin{align}
  \delta l = \frac{ L \sigma_0 }{E} =\frac{20 \times 1000}{10^6} = 0.02   
\end{align}
%
The numerical value I got for the tension at the central point of the
material on the right hand side is $0.02$.
%
\begin{figure}[h]
  \centering
  \includegraphics[width=17cm]{Figs/tension-result}
  \caption{Simulation result of a rod under tension} \label{fig-tension-result}
\end{figure}

\section{Random Network}
%
Consider the following network of pipes
%
\begin{figure}[h]
  \centering
  \includegraphics[width=12cm]{./grid.eps}
  \caption{A random grid of pipes} \label{fig-grid}
\end{figure}
%
The diameter of each pipe is randomly chosen from a Gaussian
distribution. The Darcy law in each pipe reads as
%
\begin{align}
  \frac{\Delta P}{L}  = \frac{128}{\pi} \frac{\mu Q}{d^4} 
\end{align}
%
where $\Delta P$ is the pressure difference on both sides of the pipe,
$L$ is the length of the pipe, $\mu$ is viscosity, and $d$ is the
diameter of the pipe.

%\setcounter{page}{1}

\small{
\bibliography{./library.bib}}

\end{document}

### 2021-04-28 prl_paper.tex
Initial Overleaf Import

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}
%

\usepackage{xcolor}
\newcommand{\DP}[1]{\noindent \color{cyan} (DP: #1)\normalcolor}
\newcommand{\AZ}[1]{\noindent \color{purple} (AZ: #1)\normalcolor}
\newcommand{\add}[1]{\noindent \color{blue} #1 \normalcolor}
\newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}
\newcommand{\AM}[1]{\noindent \color{magenta} (AA: #1)\normalcolor}
\def\red{\textcolor{red}}
%
\begin{document}
%
\preprint{APS/123-QED}

\title{Temporal Evolution of flow in Pore-Networks:\\ From Homogenization to Instability} 
% Force line breaks with \\
% \thanks{A footnote to the article title}%

\author{Ahmad Zareei}
\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with \\
\author{Deng Pan}%
\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with
\author{Ariel Amir}%
\email{arielamir@seas.harvard.edu}
\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break  automatically or can be forced with
% need to figure out how to reference dagger

% \author{}
% \altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with \\
% \author{}%
%  \email{}
% \affiliation{% SEAS, Pierce Hall, Harvard University}%

% \collaboration{MUSO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
We study the dynamics of flow-networks in porous media using a pore-network model. First, we consider a class of erosion dynamics assuming a constitutive law depending on flow rate, local velocities, or shear stress at the walls. We show that depending on the erosion law, the flow may become uniform and homogenize, stay as it is, or become unstable and develop channels. By defining an order parameter capturing different behaviors we show that a phase transition occurs depending on the erosion dynamics. Using a simple model, we identify quantitative criteria to distinguish these regimes. Lastly, we show that pores clogging at the initial stages show analogous behaviors depending on clogging dynamics. % , however, due to the pore throat blockages and changes in the network connections the evolution diverges from its initial trend.

% \begin{description}
% \item[Usage] Secondary publications and information retrieval purposes.
% \item[PACS numbers] May be entered using the \verb+\pacs{#1}+ command.
% \item[Structure] You may use the \texttt{description} environment to structure your abstract; use the optional argument of the \verb+\item+ command to give the category of each item.
% \end{description}
\end{abstract}

% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% \tableofcontents %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% \section{Introduction} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% The fluids %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is a challenging problem and has many environmental and industrial applications~\cite{fraggedakis2015flow,sahimi2011flow,schlesinger1999carbon,herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous,duduta2011semi,sun2019hierarchical,marbach2016pruning,tero2010rules,alim2013random,heaton2010growth}.
% , such as oil recovery~\cite{fraggedakis2015flow,sahimi2011flow}, CO$_2$ sequestration~\cite{schlesinger1999carbon}, water filtration/separation~\cite{herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous}, energy storage~\cite{duduta2011semi,sun2019hierarchical}, or biological applications \cite{marbach2016pruning,tero2010rules,alim2013random,heaton2010growth}. 
The disordered pore structure of a porous medium results in a heterogeneously distributed fluid flow between the pores.
% Fluid flow in a porous medium is often heterogeneously distributed between the pores as a result of a highly disordered pore structure.
Due to the fluid flow, the pore structure can further change dynamically either through the erosion of pore boundary walls or deposition/sedimentation of material on the boundary of the pores. Such heterogeneous and dynamical changes of the solid structure affect the pore-level fluid flow which in turn affects the dynamical changes to the pore structure. This feedback mechanism along with the initial heterogeneous fluid flow complicates the dynamical process and makes it difficult to understand and predict the porous media behavior. Nonetheless, an understanding of the dynamical change is essential to improve any of the porous media applications where the pore network changes over time, applications such as groundwater remediation and precipitation of minerals in rocks~\cite{rad2013pore}, biofilm growth in water filtration, and protective filters \cite{herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous}, as well as enhanced oil recovery with polymer flooding \cite{lake2014fundamentals,parsa2020origin}, or water-driven erosion \cite{schorghofer2004spontaneous,mahadevan2012flow}.

% to the pore structure affects local fluid flow as well as bulk properties of the medium. 
% Understanding flow behavior is important to improve any of the the applications where the pore structure changes dynamically either by erosion of the boundary wall or deposition/sedimentation of material on the boundary. Changes in the micro-structure and solid boundaries affect local fluid flow as well as the bulk properties. The  erosion or deposition process in a porous media plays an essential role in many environmental and industrial applications such as groundwater remediation and precipitation of minerals in rocks, bio-film growth in water filtration and the design of protective filters,  as well as enhanced oil recovery with polymer flooding, water-driven erosion. The structures of such porous media are usually highly disordered with a heterogeneous distribution of pore-level flow velocities. 
%%

% Albeit there is an abundance of applications in understanding 
% Despite the importance of understanding flow evolution in porous structures exposed to erosion and deposition,it 
% \footnote{It can be shown that the rate of change in tube's radius in \cite{reddi2000permeability} assuming a dilute solution becomes proportional to local fluid velocity},

In light of the plethora of applications, it is surprising that the evolution of porous structures exposed to erosion and deposition has only been partially understood both theoretically and experimentally. In order to model erosion in porous materials, different models have been used where erosion is assumed to be locally proportional to different flow parameters. Some studies have focused on the erosion of the pore structure proportional to the shear stress at the walls \cite{jager2017channelization,ristroph2012sculpting,hacking1996shear,wan2004investigation}, or proportional to the power dissipated by the flow~\cite{steeb2007modeling,marot2012study,sibille2015internal}. 
More recently it has been shown that using a coarse-grained model with an erosion rate depending on the local pressure gradient, different branching instability can be reached in a porous material~\cite{derr2020flow,mahadevan2012flow}.  
Similarly, in clogging, deposition rate based on local fluid flux, velocity, or even at a constant rate independent of any flow parameters has been used~\cite{yang2017pore,reddi2000permeability,boccardo2014microscale}. In order to unify the different approaches, we use a general continuous model which allows us to study the effect of different erosion or clogging dynamics with a single constitutive law. Additionally, we use a network approach~\cite{alim2017local,fatt1956network, blunt2013pore,stoop2019disorder,bryant1993network} to study the flow dynamics in the porous media.  The network approach has the advantage of not requiring coarse-grained homogenization and is computationally simple allowing us to simulate larger domains.

% (which is the same as shear at the walls),
% to capture the flow dynamics

% Despite all of the different models, a consensus on the dynamics of erosion or clogging is missing.\red{focus more on the network model} The adventage versatile law network approach -> does not need homogenization or meanfield assumption

% Since the dynamics of erosion in a porous material is not well understood,

% A phenomenological discrete network-based model~\cite{alim2017local,fatt1956network, blunt2013pore,stoop2019disorder,bryant1993network} is used to model the hydrodynamically driven erosion or clogging in a porous material.
% In the network model, the pores are represented by spherical nodes connected with edges represented by cylindrical tubes.

The network of pores inside the solid structure is connected together through pore-throats that effectively show resistance to the fluid flow between the pores (Fig.~\ref{fig:fig1}a). In a network model, the pores/voids of the porous medium are represented by a two- or three-dimensional lattice of nodes. The edges between the nodes of the network represent the pore-throats between the pores and are modeled using cylindrical tubes characterized by their radius and length. 
Network-based models have successfully shown to capture key properties of fluid flow in a porous material such as the probability distribution of fluid flux~\cite{alim2017local}, the permeability scaling during clogging~\cite{shima2021}, or the first fluidized path in a porous structure~\cite{fraggedakis_chaparian_tammisola_2021}. 
% Using such network models, it has been shown that the probability distribution of fluid flux in a porous material is universal when the porous material is random enough. Furthermore, during the clogging process, the usage of Kozeny-Carman fails to correctly predict the porosity since all the length scales are not eroding at the same time (the erosion only happens at the corss sections and not along the length of a porous material). New relation based on the variation in porosity has been proposed that can successfully find the relation between porosity and permeability variation using such models which is verified experimentally.
The degradation of the solid skeleton (i.e., erosion) or deposition of material on the pore throats (i.e., clogging) in such networks is modeled by the change (increase or decrease) in the radius of the edges connecting the pores which ultimately translates in the changes in the flow resistance between the pores. Using a general local erosion law that can model different dynamics, we show a variety of behaviors are possible. The network can either move toward stability and homogenization, stay as it is with no significant change in network statistics, or become unstable and develop channels. Using numerical solutions with an erosion model on a random network we show the emergence of two behaviors and morphologies are possible through selective erosion and subsequent flow enhancement. Using a simplified model we capture the underlying physics and furthermore show a phase transition occurs depending on the parameters of the model. 
% Here, based on the porous network model, we link various erosion laws with different large-scale behaviors and show a variety of behaviors that can be observe
% In order to better understand the effect of different erosion dynamics in a porous based on local parameters, 
% network model has been successful in predicting the first open channeel \cite{fraggedakis_chaparian_tammisola_2021} and capturing the fluid flow distribution \cite{alim2017local}
% \cite{fatt1956network} 
% \cite{blunt2013pore}
% \cite{stoop2019disorder}
% Consequently, clogging effects are excluded from these assumptions. Thus, the eroded fines can be transported through the porous material within these statistically homogeneous distributed channels
% Albeit there is an abundance of applications, the evolution of structures exposed to erosion and deposition is in general not easily predictable and usually requires the use of numerical techniques.
% However, this process is difficult to model due to diverse processes that may arise, including particle advection through the pore space by fluid flow, adsorption and deposition onto the solid matrix, and erosion or resuspension.
% \begin{itemize}
% \item Importance of porous media
% \item importance of dynamics in porous media
% \item we study evolution with a network model
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
% \section{Methods \& Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\begin{figure}[h]
    % \centering
    \includegraphics[width = 0.45\textwidth]{Figs/Fig1_pppp.eps}
    \caption{(a) Cross section of a porous media obtained using  computerized tomography (CT) scan of a sandstone sample (CT image taken from \cite{akanji2010finite}). The scale in the bottom left shows $1$mm. The network of pores and throats is highlighted in blue. In the network model, the pores are represented with nodes and the throats between pores are approximated with tubes connecting the pores together. (b) Schematic of a topologically random network (i); and a structured diamond grid network (ii). The edge diameters in both networks are randomly distributed. The inset figure shows the conservation of mass at each node. (c) The universal probability distribution function (PDF) of fluid flux for a topologically random (in blue) or diamond network (red) with a highly disordered random net including uniform (triangles), log-normal (circles), and truncated normal (plus) distributions. The distribution parameters are chosen such that the coefficient of variation (the ratio of the standard deviation to the mean) becomes $0.5$ which results in a highly disordered pore throat distribution. Generally, in a highly disordered random network, the PDF of normalized fluid flux becomes independent of the network and follows a universal distribution with an exponential tail. }\label{fig:fig1}
\end{figure}
%
% \AZ{Things are not topoligically random }
% \AZ{random end }
% \AZ{structured allows for mean field theory}
% \AZ{the edges are the same - exponential where it is coming from}
% \AZ{boundary between phases, where the mean fields hold}

  % Flow through pores and throats of a porous medium can be modeled using a pore network model \cite{alim2017local,fatt1956network, blunt2013pore,stoop2019disorder}. In a network model, the pores/voids of porous medium are represented by a two- or three-dimensional lattice of nodes. The edges between the nodes of the network represent the pore-throat between the pores and are modeled using cylindrical tubes characterized by their radius and length (see Fig. \ref{fig:fig1}(a)). The pore-network model is well suited for the simulation of low-Reynolds fluid flow and has proved to capture the flow dynamics of porous media \cite{alim2017local} and also the first fluidized path \cite{fraggedakis_chaparian_tammisola_2021}. We use a structured/unstructured network with randomly distributed nodes and edge length. 
% It has been shown that flow through such network correctly captures the exponential tail for distribution of fluid velocities through a porous medium.

\textit{Methods and Results}-- We consider low-Reynolds fluid flow through the porous network, i.e.,  $\rho u r/\mu \ll 1$ where $\rho$ is the fluid density and $\mu$ is the kinematic viscosity, $u$ and $r$ are characteristic fluid velocity and pore radius. In such conditions, the fluid flow in each tube follows the Poiseuille law
 $ p_i - p_j  = ({8 \mu l_{ij}}/{\pi r_{ij}^4}) q_{ij}$ where $p_i,p_j$ represents pressures at neighboring nodes $i$, $j$, and $r_{ij}, l_{ij}, q_{ij}$ are respectively the radius, length, and fluid flow rate at the edge connecting pores $i$ and $j$. The coefficient ${\pi r_{ij}^4}/{8 \mu l_{ij}}$ which relates the fluid flux to the pressure difference can be considered as the conductance $C_{ij}$ of the edge $ij$ in the pore-network. In addition to Poiseuille flow at the edges,  the total incoming flow at a node should be equal to the total outgoing flow in order to conserve mass. The conservation of mass at pore $i$ can be written as $\sum_{j\in \mathcal{N}(i)} q_{ij} =0$ where $\mathcal{N}(i)$ represents all the neighboring nodes of node $i$. First, we consider a topologically random network of nodes constructed using a uniform distribution of $N_x\times N_y$ nodes in a planar domain $\left[0,L_x\right]\times \left[0,L_y\right]$ where the nodes connectivity are obtained using Delaunay triangulation (see Fig. \ref{fig:fig1}b(i) for a part of such network). The radius of the edges is considered as independent and identically distributed random variables sampled from a probability distribution that can be either uniform, log-normal, or a truncated normal distribution (see supplementary material S1 for more details).  Assuming a pressure difference between the boundary nodes at the left and the right boundary, the pressure at the nodes, and the fluid flow rate at the tubes can be obtained by solving the corresponding set of linear equations. We find that for large enough randomness in the edge radii (i.e., $\text{std}(r_{ij})/\text{mean}(r_{ij})\geq 0.5$), the PDF is well described by a single exponential distribution as shown in Fig. \ref{fig:fig1}c. The exponential form of the PDF reflects the relatively small number of edges with extremely large fluid fluxes. The exponential distribution of fluid flux obtained here is similar to the earlier experimental or numerical measurements~\cite{datta2013spatial,shima2021,alim2017local}.  Next, we consider a structured diamond-grid of pores (Fig. \ref{fig:fig1}b(ii)) which significantly simplifies the geometrical complexity of the network. First, we find that the PDF of normalized fluid flux remains unchanged in such networks for various distributions and in fact matches with an unstructured random network (Fig. \ref{fig:fig1}c). The diamond grid allows us to analytically track the propagation of fluid into the network and calculate the distribution of fluid flux using a mean-field approximation (see supplementary material S3). Using a similar idea proposed for the force distribution in granular materials~\cite{liu1995force,coppersmith1996model,alim2017local}, it can be shown that the PDF of normalized fluid flux inside a highly disordered porous material converges to a universal distribution with an exponential form, i.e., $p(\hat{q}) \propto e^{-\alpha \hat{q}}$ for large $\hat{q}$ where $\hat{q}$ is the normalized fluid flux $\hat{q} = {q}/\langle q \rangle$ (see supplementary materials S3). This result indicates that the diamond grid network of pores where cylindrical edges between the pores have a highly disordered distribution is sufficient to capture the statistics of a heterogeneous fluid flow inside a porous material.

 % In the following parts we show the results of a diamond grid, and the results for a random-graph is presented in the supplementary material.

%  independent of the pore structure, becomes exponentially distributed. 
%  Considering a random \AZ{needs explicit definition} or structured network with a random distribution of tube's radius/length (i.e., effectively their flow resistance) and a 
%  For a large enough randomness in the edge resistances between the pores $R_{ij}$, the probability distribution of flux in the tubes normalized by the average flux follows a universal curve with an exponential tail, i.e., $P(\hat{q}) \propto e^{-\alpha \hat{q}}$ for large $\hat{q}$ where $\hat{q}$ is the normalized fluid flux $\hat{q} = {q}/\langle q \rangle$ (See Fig. \ref{fig:fig1}c and supplementary material for more details). This PDF of fluid flux $q$ has been shown to correctly captures the exponential tail for the fluid flux in a porous medium \cite{alim2017local,shima2021}.
%

% Note that the flux $q_ij$ depends on the pressure gradient between nodes i.e. $(p_i-p_j)/l_{ij}$. On the other hand 
% We first start with a numerical model, where we assume a network of $200\times 100$ tubes in the horizontal and vertical direction on a diamond lattice \AZ{better motivation: explain and discuss the meanfield picture behind figure 1c} (similar results for a general \AZ{needs definition} random network is presented in the supplemental materials). 
\begin{figure}[!h]
    % \centering
    \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
    \caption{Erosion in a network of pipes. The initial condition is shown with the label $t=0$ in the first row. Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$. The erosion law is based on Eq. \eqref{eq:erosion-law} where different powers of $n$ correspond to different models of erosion. The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}
\end{figure}
%

In order to model erosion in porous media, we consider the abrasion in the throats which correspond to the change in the radius of the edges in the network. We model the dynamics of the change in the radius as 
%
\begin{align}
   \frac{dr_{ij}}{dt} = \alpha  \frac{|q_{ij}|^m}{r_{ij}^n} \label{eq:erosion-law}
\end{align}
%
\add{where $m,n,\alpha$ are constants. Different powers of $m$ and $n$ correspond to different physics in the erosion. Particularly, when $m=1$ and (i) $n=0$ the erosion depends on the amount of flux $q_{ij}$ passing through the edge; (ii) $n=2$ the erosion depends on the local velocities; (iii) $n=3$ the erosion depends on the shear force at the boundary of the throat.} \add{Additionally, $m=2$ and $n=6$ corresponds to the models considered in biological transport networks where the there the radius change has a quadratic dependence on wall shear stress~\cite{hu2013adaptation,ronellenfitsch2016global}.} We consider network of randomly distributed pores with  $N_x\times N_y$ pores in the horizontal and vertical directions. The randomly distributed points are connected using Delaunay triangulation. We initialize the network with a uniform random distribution of diameters within $[r_\text{min}, r_\text{max}]$ range with a large coefficient of variation such that  $\sigma_r/r_0\approx 0.5$ where $\sigma_r$ is the standard deviation, and $r_0 = \langle r \rangle$~\cite{alim2017local}. The flow inside the pores, PDF of flux in the tubes, and PDF of tube radii are shown in Fig. \ref{fig:fig2}. We assume a constant pressure difference between the left and the right boundaries. In each time step, we increase the local radius of the tubes based on the erosion law introduced in Eq. \eqref{eq:erosion-law}. Note that $r_{ij} (t+\delta t)  = r_{ij} (t)  + (\alpha \delta t)  q_{ij} (t)/ r^n_{ij} (t) $, where the coefficient $\alpha \delta t$ is chosen such that the maximum change in the radius at each time step is smaller than one-tenth  of the smallest tube's radius i.e. $\max (\Delta r_{ij}) \leq r_\text{min}/10$ of the smallest radius at the initial configuration.  This condition guarantees that at each step a small amount of material is eroded and there's no sudden change in the network. We further test the convergence by decreasing $\max(\Delta r_{ij})$ to half and we observe that the average relative change in the flux vector becomes $\aprrox 1.2\%$, and the PDFs remain intact without any change. We continue the simulations until $\langle r \rangle = 2 r_0$. 
%
The results of the simulations for different $n$ are shown in Fig. \ref{fig:fig2}. When $n=1$ or $2$,  the network develops channels. In such cases, the flow is dominated by a few edges carrying most of the flow while the rest of the network carries almost no flow. This can be seen in the PDF of the normalized radius which becomes bimodal. Furthermore, the PDF of the normalized fluid flux contains a small number of edges with very large flux values while the majority of the edges carry small flux. Contrary to $n=1,2$, when $n=3$ and the erosion depends on shear at the throats' boundary walls, we find that the flow patterns stay very close to the initial shape, however, with larger and exacerbated flux values. Although the maximum fluid flux increases, the PDF of normalized fluid fluxes remains almost exponential, and the PDF of diameters moves toward larger values. Increasing $n$ to larger values, $n=4$ or $5$, we find that the flow pattern in the network moves toward homogenization. Here, the tail of the normalized fluid flux distribution retracts and the distribution moves toward the average value. We further find that the PDF of the diameters moves toward the average and the coefficient of variation reduces. Running the simulations for longer times, we observe that the flow becomes completely uniform where only a single radius appears to carry the flow with the same fluid flux (i.e., the average value) for all the tubes in the network. In summary, we have observed a transition in the network behavior during erosion which happens at $n=3$: when $n<3$ the network moves toward developing channels, and when $n>3$ the erosion results in the homogenization of the flow.

\begin{figure}[!h]
    % \centering
    \includegraphics[width = 0.45\textwidth]{Figs/Fig3_new.png}
    \caption{Two tubes in (a) series  or (b) parallel configuration. When the tubes are in series configuration, the tubes have the same fluid flow rate $q$. The tube radius dynamically change with the erosion law $\dot{r_i}\propto q/r_i^n$. For any $n$, the normalized pressure at the junction between the tubes $\tilde p_m = (p_m - p_l)/(p_r-p_l)$ approaches $1/2$ which results in a homogenized pressure distribution  shown in (a$_2$). When the pipes are in parallel, however, the flow is distributed among the tubes based on their flow conductivity $C_1,C_2$. The local fluid flow rate then affects the erosion of the tub $\dot{r}_i\propto q_i/r_i^n$. When $n<3$ in the erosion law, the fluid flow eventually passes through a single tube, and channeling occurs; (b$_2$) when $n=3$, the flow ratio between the pipes does not change; and (b$_3$) when $n>3$ the flow ratio approaches $1/2$ which is the homogenization.(c) Order parameter $\mathcal{O}$ for different powers of $n$ plotted over time as the network structure is eroded and average edge radius is increasing $\langle r\rangle/r_0$. When $n<3$ the order parameter increases ($\mathcal{O}\to 1$) while the network is developing channels, and when $n>3$ the order parameter decreases ($\mathcal{O}\to 0$) while the network moves toward homogenization, and when $n=3$ the order parameter stays as it while the network statistics remains unchanged.}\label{fig:fig3}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Simplified Model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%

\textit{Simplified Model}-- In order to understand the underlying reason behind the transition in network behavior during erosion for different powers of $n$, we focus on a simplified model with only two tubes in parallel or series (see Fig. \ref{fig:fig3}a,b). First, assuming two cylindrical tubes with radii $r_1,r_2$ in series and connected back to back, the flow is the same for the two tubes $ q_1 = q_2 = q$ (Fig. \ref{fig:fig3}a). The radius of each tube then changes with $dr_i/dt = \alpha q/r_i^n$ where $i=1,2$. Each tube can be considered as a resistor where its conductivity  $C_i =\pi r_i^4/8\mu l_i$ changes over time. In similarity with resistor networks, the pressure difference $\Delta P_i$ acts analogous to the voltage difference and the fluid flux $q_i$ is analogous to the current where we have $q_i = C_i \Delta P_i$. When the cylindrical tubes are in series, we find that the conductivity of each tube changes as $dC_i/dt \propto C_i^{(n-3)/4}$. As a result, each tube's conductivity increases with a rate depending on $n$, i.e. the larger the $n$ the faster it moves toward larger values. If we consider the pressure at the junction between tubes, we find that this middle point pressure moves toward the average value of pressure on both sides (see Fig. \ref{fig:fig3}(a$_1$)). As a result, when the tubes are in series, the erosion results in a homogenized distribution of pressure. Contrary to tubes in series, when the tubes are in parallel (Fig. \ref{fig:fig3}b), the flow divides between the two tubes based on their conductivity i.e. $q_1/q_2 = C_1/C_2$. Since each tube's radius changes as $dr_i/dt = \alpha q_i/r_i^n$, the evolution of the fluid flow ratio becomes 
% %% 
\begin{align}
 \frac{d}{dt}\left( \frac{C_1}{C_2}\right) \propto  \frac{C_1}{C^{(n+1)/4}_2} \left( \left( \frac{C_1}{C_2}\right)^{\frac{n-3}{4}} - 1 \right). \label{eq:dyn-paral}
\end{align}
%a
When $n=3$ in Eq. \eqref{eq:dyn-paral}, the right-hand-side becomes zero and as a result the flow ratio $C_1/C_2$ remains constant and does not change. However, when $n\neq 3$, we find that $C_1/C_2 = 1$ is an equilibrium point. When $n>3$ this equilibrium solution is stable and the flow moves toward homogenization; however, when $n<3$ this equilibrium solution becomes unstable and the solution moves toward $C_1/C_2 \to 0$ or $\infty$ which means that the whole flow passes through one of the tubes. To summarize, when the tubes are in series any erosion law makes flow become more uniform; however, when the tubes are in parallel depending on the power $n$ the flow in the tubes can move toward becoming more uniform ($n>3$), stay the same ($n=3$), or move toward instability and channel development ($n<3$). Since a complex network includes both series and parallel connections, we expect that the whole network structure behaves in a similar manner and we observe a network transition between becoming uniform ($n<3$) to developing channels ($n>3$). This observation here is consistent with the numerical simulation results shown in Fig. \ref{fig:fig2}.  
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Phase transition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% From instability to homogenization
%

\textit{Phase transition}--  order to quantify the transition of the network between channeling instability and homogenization, we define an order parameter $\mathcal{O}$ that moves toward $0$ or $1$ if the network moves toward channeling or homogenization respectively. The order parameter is defined as 
%
\begin{align}
    \mathcal{O} = \frac{1}{N-1} \left( N - \frac{\left( \sum_{ij} q^2_{ij}\right)^2}{ \sum_{ij} q^4_{ij}}\right)
\end{align}
%
where $N$ is the number of edges.  The order parameter $\mathcal{O}=0 $ when the flux in all the edges become the same $q_{ij} = \bar{q}$. On the other hand, when fluid flux becomes highly localized with only a few edges with non-zero flux, $\mathcal{O}\to 1$.  We numerically calculated the order parameter $\mathcal{O}$ for the diamond-grid network during the erosion process. The results are shown in Fig. \ref{fig:fig3}c for different amounts of erosion measured by the increase in the average diameter $\langle r\rangle /r_0$. As shown in 
 Fig. \ref{fig:fig3}c, at $n\approx 3$ the order parameter, remains unchanged; however for $n>3$ the order parameter moves toward zero, where the flow becomes more uniform, and for $n<3$ the order parameter goes toward unity, where channels are developed. The transition in the order parameter indicates a phase transition at $n=3$ in the long-time behavior of the network which is in agreement with the toy model prediction and simulation results of Fig. \ref{fig:fig2}. 
%

\begin{figure}[!h]
    \centering
    \includegraphics[width = 0.45\textwidth]{Figs/Fig4_new33.png}
    \caption{Evolution of a randomly initialized network for various $m$ and $n$ until $\cdots$. The network is randomly initialized with $N_x=$ and $N_y=$. The red box and the blue box shows the prediction of the simplified  model for the fate of network either homogenization (blue) or channelization (red). It is seen that the toy model prediction matches with the simulation of the network. }\label{fig:fig4}
\end{figure}

\add{Next, we test our simplified model for additional values of $m$. We compare simulation of a randomly initiated network using general erosion dynamics given in Eq. \eqref{eq:erosion-law} and compare the network's simulation result with the prediction of simplified model (see Fig. \ref{fig:fig4}). Each box in Fig. \ref{fig:4} shows the final snapshot of a network simulation for a given $n$ and $m$. The simplified model prediction for each box is shown using the color of the bounding box (red for channelization and green for homogenization). It is seen that although the simplified model is based on the erosion dynamics of two edges in parallel or series configuration, it still can correctly predict the fate of the network for different values of $m$ and $n$ and capture the line separating channelinzation/homogenization (see the black line in Fig. \ref{fig:fig4} in the fate of the network}

 \add{In this manuscript, we mainly considered the case of $m=1$, since it directly corresponds to different physics of erosion in a network with different assumptions of erosion with a linear constant, fluid-flux, velocity, or shear rate dependence. . Considering $m=2$ in Eq. \eqref{eq:erosion-law}, the model aligns with the transport optimization in biological networks \cite{ronellenfitsch2016global,corson2010fluctuations,hu2013adaptation}. In addition to our erosion dynamics, in such biological transport networks, there is an extra constraint where the network is optimized to minimize its total cost function. Adding the additional constraints results in global/local minimum point in the network which can be found numerically. In addition to the constraints, the boundary condiitons are alos different, where in biological transport networks each node consumes a part of the incoming flow, however, in the erosion considered here there is no minimum point and the flow continually moves toward more and more erosion without any bounds. A similar transition given all the differences is observed in biological network modes. The simplified model introduced here captures the evolutional process toward either channelization or homogenization and can be used to determine the fate of the network. }

%%%
%\begin{figure}[h]
%    \centering
%    \includegraphics[width = 0.4\textwidth]{Figs/Fig4_clogging}
%    \caption{Phase transition at the power}
%    \label{fig:fig4-clogging}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Clogging Dynamics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5 
%
\textit{Clogging Dynamics}-- Besides erosion, another change in the network is the deposition/sedimentation of material on the boundary walls of the porous material. We name this dynamical change a ``clogging'' process as opposed to erosion. Contrary to erosion, the clogging behavior may cause some edges to block which effectively alters the network of connectivity and network behavior. This change in the connection between nodes through edges getting blocked can drastically alter porous structure behavior, e.g., causes a huge difference between effective and true porosity \cite{shima2021}. Despite the drastic change of network with blockages, we can still focus on the \textit{initial} change in the order parameter. The derivative of order parameter can be written as 
%
\begin{align}
    \frac{d\mathcal{O}}{dt} = \sum_{ij} \sum_{kl} \frac{\partial \mathcal{O}}{\partial q_{ij}} \frac{\partial q_{ij}}{\partial C_{kl}}  \frac{\partial C_{kl}}{\partial t} \label{eq:order-derivative}
\end{align}
%
where the last term changes sign from erosion to clogging, i.e., $\partial C_{kl}/\partial t = \pm \alpha \pi q_{kl} /r_{kl}^{n-3}\mu l_{kl}$ for erosion and clogging respectively. As a result, the magnitude of change in the order parameter equals that of erosion. Note that in Eq. \eqref{eq:order-derivative}, the second term depends on the network topology, and pore throat clogging results in the change of network topology at later times.
% The pore throat blockages results in the divergent of clogging results from just the negative of erosion. 
In short times, however, similar to the erosion, a phase transition exists at $n=3$. When  $n<3$ the network moves toward homogenization during the clogging process and when $n>3$ the flow moves toward the development of channeling instability. At later times, this initial trend, however, might not hold true due to the aforementioned complex changes in the connectivity network during the clogging process.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% \section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\textit{Conclusion}-- In summary, we analyzed the dynamics of the porous networks during erosion. We showed that depending on different erosion laws various network behaviors are observable. We used simple erosion laws, inspired by previously proposed models, and showed that depending on the rate of erosion the network can either move toward homogenization or toward developing a channeling instability. Next, we propose an order parameter to capture the phase transition behavior, and using a simplified model of two tubes we elucidated the physical origin of the phase transition behavior. 
In the case of clogging, since the network connectivity can vary significantly our approach does not hold at large times, however, the initial variation can be captured using our model where the results similarly show a behavior change at $n=3$. Our results signify the importance of local dynamics and feedback mechanism in long-time global behavior and complement similar feedback-induced studies for active conducting mediums~\cite{ocko2015feedback}.

% \add{phase transition from channeling to full blocking in active porous structures \cite{ocko2015feedback}}

\textit{Acknowledgments}-- We would like to acknowledge Kavli Institute for the fruitful discussions and also MRSEC  DMR-2011754 and DMR-1420570 for the support.

% \begin{figure}[h]
    % \centering
%     \includegraphics[width = 0.48\textwidth]{Figs/Fig2p_clogging.png}
%    \caption{Clogging in a network of pipes. The initial condition is shown with the label $t=0$ in the first row. Each row afterward corresponds to the simulation result after $N$ steps such that $\langle R_{t=N}\rangle=0.5 R_0$ where $R_0 = \langle R_{t=0}\rangle$; in other words the same amount of material is eroded in all cases. The erosion laws used here is $dR/dt = \alpha Q/R^n$ where $n$ varies for each row. The constant $\alpha$ in all cases are $1$ and time step $dt$ is chosen such that the maximum amount of increase in $R$ at each step is smaller than $0.01 R_0$. }\label{fig:fig2}
% \end{figure}

% \begin{itemize}
%    \item second order phase transition
%     \item intro
%    \item fig 4 for random network
%    \item clogging? 
% \end{itemize}

\bibliography{ref.bib}

\appendix

\end{document}

### 2021-04-28 supp.tex
Initial Overleaf Import

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
%  reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
% preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
%  aps,
%pra,
% prb,
% rmp,
% prstab,
prstper,
% floatfix,
]{revtex4-2}

\usepackage[usenames, dvipsnames]{color}
% Color Edits
\newcommand{\EM}[1]{\noindent \color{red} (AA: #1)\normalcolor}
\newcommand{\AZ}[1]{\noindent \color{blue} (AZ: #1)\normalcolor}

\usepackage{braket}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}
\usepackage[usenames, dvipsnames]{color}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\newcommand{\KB}[1]{\noindent \color{magenta} (KB: #1)\normalcolor}

\renewcommand{\thepage}{S\arabic{page}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\theequation}{S\arabic{equation}}
\def\lp{\left(}
\def\rp{\right)}
\def\lb{\left[}
\def\rb{\right]}
\begin{document}

\preprint{APS/123-QED}

\title{Temporal Evolution in the Networks of Porous Materials:\\ From Homogenization to Instability}% Force line breaks with \\
% \thanks{A footnote to the article title}%

\author{Ahmad Zareei}
\affiliation{ School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with \\
\author{Pan Deng}%
\affiliation{ School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with
\author{Ariel Amir}%
\email{arielamir@seas.harvard.edu}
\affiliation{ School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with
% need to figure out how to reference dagger

% \collaboration{MUSO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\maketitle
\section{Simulation algorithm}
%
In our simulations, we tested two types of network: a (i) diamond-grid network, and a (ii) topologically random network. In the diamond-grid network, we choose $N_x=200$ edges in the horizontal direction and $N_y=100$ edges in the vertical direction. The random network is created using uniformly distributed points with on average $N_x\times N_y$ edges in the horizontal and vertical directions. Note that the randomly distributed points are connected using a Delaunay triangulation. The diameter of each edge is sampled from either a uniform distribution in $r\in[1,14]$, log-normal distribution with $\mu=3,\sigma=0.48$, or truncated normal distribution with $\mathcal{N}(\mu=7.0,\sigma=3.6)$.   The external flow pressure is applied horizontally from left to right. An external pressure is then considered between the left-most nodes and the rightmost nodes ($p_\text{left}=10,p_\text{right}=0$). Assuming a Poiseuille flow in each edge, the fluid flow $q$ and pressure difference $\delta P_e$ in each edge is related through $q_e = C_e \delta P_e$, where $C_e = \pi r^4_e/8\mu L_e$,  $L_e$ is the length of the tube, and $\mu$ is the viscosity of the fluid. Let $\Delta$ be the transpose of the network's oriented incidence matrix. Note that the orientation of each edge is arbitrary since it only determines the positive direction of flow in that edge. Define $\ket{q_e}$ as the vector of flow through all the edges, then we have $\ket{q_e} = C_e\Delta \ket{P_n}$ where $\ket{P_n}$ is the vector of pressure at all the nodes. With a given boundary condition, we solve the equation through a modified nodal analysis as follows. The conservation of mass at each node can be written as 
%

\begin{align}
    \ket{q_n} = \Delta^\top \mathbf{C} \Delta \ket{P_n}, \label{eq:governeing}
\end{align}
%
where $\mathbf{C} = \text{diag}\left( C^{(1)}_e, C^{(2)}_e, \cdots,C^{(N_e)}_e\right)$ is a diagonal matrix of edge conductances, and $\ket{q_n}$ is the vector of total incoming flow to each node. Note that total incoming flow to an internal node is zero inside the network due to the conservation of mass, and is only non-zero at the boundary nodes. Renumbering the boundary nodes to $1,2,\cdots, N_{B}$, we can partition Eq. \eqref{eq:governeing} to obtain

\begin{align}
 \begin{bmatrix} {\Delta_{b}}^\top \mathbf{C} {\Delta_{b}}  & \vline &    {\Delta_{b}}^\top \mathbf{C} {\Delta_{n}} \\ \hline  
    {\Delta_{n}}^\top \mathbf{C} {\Delta_{b}} & \vline & {\Delta_{n}}^\top \mathbf{C} {\Delta_{n}}
    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ P_{N_B} \\  \hline  P_{N_B+1} \\ \vdots \\ P_{N_n}
    \end{bmatrix} = \begin{bmatrix} q^{BC}_1 \\ q^{BC}_2 \\ \vdots \\ q^{BC}_{N_B} \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \to 
    \begin{bmatrix} 
    \mathbf{A}_{bb} & \mathbf{A}_{bn} \\
    \mathbf{A}_{nb} & \mathbf{A}_{nn}       
    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ P^{BC}_{N_B} \\ \hline  P_{N_B+1} \\ \vdots \\ P_{N_n}
    \end{bmatrix} = \begin{bmatrix} q^{BC}_1 \\ q^{BC}_2 \\ \vdots \\ q^{BC}_{N_B}  \\ \hline  0 \\ \vdots \\ 0\end{bmatrix}, 
\end{align}
%
where $\mathbf{A}_{st} = \Delta^\top_s \mathbf{C}\Delta^\top_t$ and  $s,t\in\left\{a,b\right\}$. In summary the above equations simplifies to 
%
\begin{align}
    \begin{cases} 
        \mathbf{A}_{bb} \ket{P_{BC}} + \mathbf{A}_{bn}  \ket{P} = \ket{q_{BC}}, \\
    \mathbf{A}_{nb}\ket{P_{BC}} +  \mathbf{A}_{nn} \ket{P} = 0. 
    \end{cases} 
    % \\ \mathbf{A}_{nn} \ket{P_n} =- \mathbf{A}_{nb}\ket{P_{BC}} 
    \label{eq:main-network}
\end{align}
%
Solving the above equations results in the nodes' pressure and also the fluid flux at the boundary nodes. With the flux at each edge, $q_e$, the increase (decrease) of tube radius under erosion (clogging) is obtained as 
%
\begin{align}
    \frac{dr_e}{dt} \propto \pm  \frac{q_e}{r_e^n}.
\end{align}
%
We use simple forward Euler for time integration. For each iteration, we choose the time step $dt$ so that $\max(dr_e) = 0.1 r_0$, where $r_0$ is the smallest radius among all edges.

\newpage
\section{Additional Numerical Result}
%
\begin{figure}[h]
    % \centering
    \includegraphics[width = 0.75\textwidth]{Figs/Fig2_random-low.png}
    \caption{Ahmad's version: Erosion in a topologically random network of pipes. The first row shows the initial condition at $t=0$. Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$. The erosion law is based on Eq. (1) in the main text where different powers of $n$ correspond to different models of erosion. The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}
\end{figure}
%

\newpage
\section{Analytical results}
%
\label{sec:analytical}
%
As described in the main text, the PDF of flow in a topologically disordered network of tubes is the same as a structured diamond grid when the radius of the tubes is highly disordered. In this section, we show that the observed exponential distribution of fluid flux can be described using a mean-field approach on a structured grid. Basically, the random distribution of the diameters along with the conservation of mass in the network are the two main ingredients resulting in an exponential tail distribution. In a diamond grid, the incoming flow to a node is redistributed among the outgoing edges (since fluid mass is conserved). Due to the randomness in the tube's diameter, one can imagine that the redistribution of the incoming flow to a node between the outgoing edges is random variable. The only condition required to be hold here is that the incoming flux should be equal to the outgoing flux. This model for the flow can be mapped one to one to the problem of force fluctuations in a bead pack \cite{liu1995force,coppersmith1996model,alim2017local} as shown in Fig. \ref{grid-result}. In a bead pack, the force at each layer is redistributed to the next layer where the total force exerted on the next layer should equal to that of the previous layer. 
%
\begin{figure}[h]
  \centering
  \includegraphics[width=.75\textwidth]{./Figs/grid-analytica.eps}
  \caption{(a) Schematic of diamond grid network of tubes. The incoming flow to each node is redistributed among the outgoing edges. The thickness of the lines shows the fluid flux transferred in that edge. (b) Schematic diagram showing beads (represented with nodes) and their contacts to the neighboring sites (represented with edges). The thickness of the edges show the weight transferred through that contact.} \label{grid-result}
\end{figure}
%
Given the above conditions, the flow at layer $L+1$ at node $j$ can be obtained as 
%
\begin{align}
  q(L+1,j) = \sum_i w_{ij} q(L,i) = w_{i,i+1} q(L,i+1) + w_{i,i} q(L,i), \label{total-flow}
\end{align}
%
where $w_{ij}$ shows the weights by which the flow is redistributed. Note that since the total fluid flux is conserved, then  $\sum_{j} w_{ij} = 1$. 
% Next, we assume that the weights $w_{ij}$ are drawn from a distribution $\eta(w)$. Since $\eta(w)$ is a distribution, then $\int \eta(w) dw = 1$. Furthermore, since $\sum_jw_{ij} = 1$, we can conclude that
%
%\begin{align}
%  \sum_j w_{ij}=1 \to N {E}[w_{ij}] = 1 \to E[w_{ij}] = 1/N \to {\int w\eta(w) dw = 1/N}
% \end{align}
%
Assuming a general distribution of $\eta(w)$, we can use the mean-field approximation to find the distribution of $q$ at the layer $L$, i.e., $p_L(q)$. The values of $q(L,i)$ are not independent for neighboring
sites; however, in our mean-field approximation we ignore such
correlations. We find
%
\begin{align}
  p_L (q) = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dq_j p_{L-1}(q_j)\right\} \times \delta \left( \sum_j w_j q_{j} - q \right),
\end{align}
%
% The only approximation in the above equation is that we neglect the possible correlation between the values of $q$ among ancestors. 
where $N$ is the number of outgoing edges (e.g., in our structured diamond grid $N=2$) and $\delta(\cdot)$ is the Kronecker delta function. Note that the constraint that $q$'s emanating downward should add up to one is in the definition of $\eta(w)$. Taking the Laplace transform of the above equation and defining $\tilde p(s) & \equiv \int_0^{\infty} p(q) e^{-qs} dq$ we obtain
%
% \begin{align}
 % \tilde P(s) & \equiv \int_0^{\infty} P(Q) e^{-Qs} dQ\\
%   \xrightarrow{\int_0^{\infty} (\cdot) e^{-Qs} dQ}  P (Q) & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp \\
%   \tilde P(s) & = \int_0^{\infty} \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp e^{-Qs}dQ \\
  %            & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j e^{-\sum w_{j}Q_{j}} P(Q_j)\right\}   \\
%              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \tilde P(s w_j) \right\} \\
%   & = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N}
% \end{align}
%
% Or in summary
%
\begin{align}
  {\tilde P_L(s) = \lp  \int_0^1 d w \eta(w) \tilde P_{L-1}(s w)  \rp^{N}}. \label{eq:main-laplace}
\end{align}
%
The probability distribution at the layers converges to a distribution $\tilde P(s)$. The final solution for a structured diamond grid with two neighboring sites becomes $p(q) = 4q\exp(-2q)$ \cite{liu1995force,coppersmith1996model,alim2017local}, which is a distribution with an exponential tail.

\newpage

\begin{figure}[h]
    % \centering
    \includegraphics[width=0.75\textwidth]{Figs/randomNetworkErosion3.pdf}
    \caption{Deng's version: Erosion in a topologically random network of pipes. The initial condition is shown with the label $t=0$ in the first row. Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius. The erosion law is based on Eq. (1) in the main text where different powers of $n$ correspond to different models of erosion. The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}
\end{figure}

% \clearpage
% \newpage
\bibliography{ref}% Produces the bibliography via BibTeX.

\end{document}
%

%###############################################################
%###############################################################
%###############################################################
%###############################################################
%###############################################################
%###############################################################
%###############################################################

\newpage
\section{Clogging behavior at initial times}
% 
Considering a small change in the radius of edges, and as a result, the conductance of the edges $\mathbf{C}+\delta \mathbf{C}$, using Eq. \eqref{eq:main-network} we find that 
%
\begin{align}
    \ket{P'} &=  \ket{P} -  \left( \Delta_n^\top\mathbf{C} \Delta_n\right)^{-1}\left[  \left( \Delta_n^\top \delta \mathbf{C} \Delta_n\right)\ket{P} + \left( \Delta_n^\top\delta \mathbf{C} \Delta_b\right) \ket{P_{BC}}\right],
\end{align}
%
where we used the fact that for an invertible matrix $\mathbf{A}$ we have 
%
\begin{align}
    \left(\mathbf{A} + \delta \mathbf{A} \right)^{-1} = \mathbf{A}^{-1} - \left( \mathbf{A}^{-1} \delta \mathbf{A}\right) \mathbf{A}^{-1} + \left( \mathbf{A}^{-1}  \delta \mathbf{A}\right)^{2}\mathbf{A}^{-1}  + \cdots.
\end{align}
%
Calculating for the changes in the fluid flux, we find that 
%
\begin{align}
\ket{q'} & = \left( \mathbf{C}+ \delta \mathbf{C}  \right)\left( \Delta_b \ket{P_{BC}} +  \Delta_n \ket{P'} \right) \\
& = \ket{q} + \delta\mathbf{C} \mathbf{C}^{-1}\ket{q} - \mathbf{C} \Delta_n \left( \Delta_n^\top\mathbf{C} \Delta_n\right)^{-1}\left[  \left( \Delta_n^\top \delta \mathbf{C} \Delta_n\right)\ket{P} + \left( \Delta_n^\top\delta \mathbf{C} \Delta_b\right) \ket{P_{BC}}\right].
\end{align}
%
The above equation can then be used to study the evolution of order parameter in the networks. Note that during the blockage of pore-throats, the connectivity between the nodes changes and as a result network's connectivity matrix $\Delta$ changes and the above approximation will not hold anymore.

%###############################################################
%###############################################################
%###############################################################
%###############################################################
%###############################################################
%###############################################################
%###############################################################

% ****** End of file apssamp.tex ******

 If we set
$\eta(w) = \delta(w-1/2)$, then the flow at each node has probability of
$1/2$ to move to either of the neighboring sites. As a result the flow at a given depth $L$ will become homogeneous as $P_L(Q) = \delta (Q-\bar{Q})$ where $\bar{Q}$
is the average of input fluid flow. This results is the same as having the same
diameter for all the edges which results in a singular solution in the structured grid.
% 
\subsection*{$P(Q)$ decays faster than $Q^{-n}$ for any $n$}
We first show that $P(Q)$ decays faster than any power of $Q$ for any
weight distributions. We expand the Laplace transform using a Taylor expansion as 
%
\begin{align}
  \tilde P(s) = 1 + \sum_j \tilde P_{j} s^{j}.
\end{align}
%
Inserting this expansion into Eq. \eqref{eq:main-laplace}, we obtain
%
\begin{align}
  1 + \sum_j \tilde P_{j} s^{j}  & = \lp  \int_0^1 d w \eta(w) \lb 1 + \sum_j \tilde P_{j} (sw)^{j}\rb    \rp^{N}  = \lp  1 + \sum_j \tilde P_j \langle w^{j}\rangle  s^{j}   \rp^{N}
\end{align}
%
where $\langle w^j \rangle = \int_0^1 \eta(w) w^j dw$ is the $j$-th
moment of the weights $w$. In the above equation we can observe that
%
\begin{align}
  P_j \lp N \langle w^j\rangle -1 \rp = G(P_{j-1}, P_{j-1}, \cdots, P_1)
\end{align}
%
In the above equation $P_j$ can only diverge only if $N\langle w^j
\rangle -1=0$. If $w$ can only be zero and one, then $\langle
w^j\rangle =\langle w \rangle = 1/N$ and the coefficient can become
zero! Other than this special distribution, when $0 \leq w \leq 1$, then
%
\begin{align}
  & w\in [0,1] \rightarrow w>w^2>w^3> \cdots \\
  & \forall k>1 \rightarrow \langle w^k \rangle < \langle w \rangle = \frac{1}{N} 
\end{align}
%
which means that $N\langle w^j \rangle -1\neq 0$ and as a result
$P_j$ is finite. $P_j$ on the other hand is the $j$-th moment or
$\langle Q^j\rangle$ and it is finite. If $P\approx Q^{-n}$, then the
$n$-th moment will not be finite i.e. $\langle Q^{n+1}\rangle =
P_{n+1}$ is not finite. We can then conclude that $P(Q)$ should go to
zero faster than any $Q^{-n}$ as $Q\to \infty$! In other words $d \log
P(Q) / d \log Q \to -\infty$ as $Q\to \infty$.  
% 
\subsection*{Exponential Decay}
%
The main recursive governing equation for a diamond grid is  
%
\begin{align}
  \tilde P(s) = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{2} \label{eq:main-recur}
\end{align}
%
% In order to have an approximation for $\eta(w)$ we consider the following situation:
At each node there are two neighboring nodes where the flux is distributed by
$w_1$ and $w_2$ among them. Assuming that $w_1$ is uniformly distributed
between $0$ and $1$, then $w_2 = 1-w_1$ (due to  conservation of
mass $w_1 + w_2 = 1$). Now $\eta(w)$ can be obtained using 
%
\begin{align}
  & \eta(w) = M \int_0^1 dw_1 \delta(1-w_1-w) =  M, \\
  \text{since }& \int_0^1 \eta(w) dw = 1 \to M =1 \\
  & \eta (w) = 1
\end{align}
%
Just for completeness, if there are three neighboring connections ($N=3$), then we
have
%
\begin{align}
  \eta(w) & = M \int_0^1 dw_1 \int_0^1 dw_2 \delta(1-w_1-w_2 - w)\\
          & = M(1-w)  \to \int_0^1\eta(w) dw = 1 \to M = \frac{1}{2} \\
  & \eta(w) = \frac{1}{2} (1-w)
\end{align}
%
As a result Eq.~\eqref{eq:main-recur} simplifies to
%
\begin{align}
  \tilde P(s) = \lp  \int_0^1 d w  \tilde P(s w)  \rp^{2} 
\end{align}
%
In order to solve the above equation, we assume $\tilde V (s) =
\sqrt{\tilde{P}(s)}$.
%
\begin{align}
  \tilde{V}(s) & = \int_0^1 dw \tilde V (sw) = \int_0^s \frac{du}{s}  \tilde{V}^{2}(u) \\
  s\tilde{V}(s) & = \int_0^s du  \tilde{V}^2(u) \\
\end{align}
%
Taking the differentiation with respect to $s$ yields
%
\begin{align}
  \tilde{V}(s) + s \frac{d \tilde{V}(s)}{d s} = \tilde{V}^2(s) \\
  \frac{d \tilde{V}}{\tilde{V}^2-\tilde{V}} = \frac{ds}{s}  \\
  \log\lp \frac{1-\tilde{V}}{\tilde{V}} \rp  = \log(s)\\
  \tilde{V}(s) = \frac{1}{1+Cs} 
\end{align}
%
We set the mean to $1$ i.e.,
%
\begin{align}
  \int_0^{\infty} Q P(Q) dQ = 1 \to \frac{d\tilde{P}}{ds}|_{s=0}  = -1\\
  \frac{d \tilde{V}}{ds}  = \frac{1}{2 \sqrt{\tilde{P}(s)}} \frac{d \tilde{P}(s)}{d s}   \to \frac{d\tilde{V}(s)}{ds}|_{s=0} =\frac{-1}{2} \\
  \frac{d\tilde{V}(s)}{ds} = \frac{-C}{(1+Cs)^{2}}|_{s=0} = -C = \frac{-1}{2}  \to C=\frac{1}{2} 
\end{align}
%
As a result, we have
%
\begin{align}
  \tilde{P}(s) = \lp\frac{1}{1+s/2} \rp^2 \\
  P(Q) = 4Q e^{-2Q}
\end{align}
%
We can then show that for a uniform distribution of $w$'s, the PDF of
$Q$'s become an exponential tail. For other distribution of $w$'s, we
similarly find a similar trend which can be seen in the numerical simulations. 
% Actually, we showed that the PDF of $Q$ should decay faster than any power law for any distribution of
$w$. 
Note that in the distribution with exponential tail, the only parameter that determines the the PDF of the average fluid flow. This shows that why we observe the universal behaviour for the PDF of normalized fluid flux where the average of normalized fluid flux is unity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

For each resistor we know that
%
\begin{align}
    q_{e} = R_{e} \Delta P_{e}
\end{align}
%
Assume that matrix $\mathbf{C}$ relates the pressure at nodes to the pressure difference, where 
%
\begin{align}
    \ket{\Delta P_e} = \mathbf{C} \ket{P_n}, \quad \ket{q_e} = \mathbf{R} \ket{\Delta P_e}, \quad \ket{q_n} = \mathbf{C}^\top \ket{q_e} \\
    \ket{q_n} = \mathbf{C}^\top \mathbf{R} \mathbf{C}\ket{P_n}
\end{align}
%
\begin{align}
    \mathbf{C}^\top \mathbf{R} \mathbf{C}\begin{bmatrix} P_1 \\ P_2 \\ \vdots \\ P_n
    \end{bmatrix}
    = \ket{q} \to \begin{bmatrix} \mathbf{C_{b}}^\top \mathbf{R} \mathbf{C_{b}}  & \vline &    \mathbf{C_{b}}^\top \mathbf{R} \mathbf{C_{n}} \\ \hline  
    \mathbf{C_{n}}^\top \mathbf{R} \mathbf{C_{b}} & \vline & \mathbf{C_{n}}^\top \mathbf{R} \mathbf{C_{n}}
    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ \hline  P_n \\ \vdots \\ P_{N_n}
    \end{bmatrix} = \begin{bmatrix} q_1 \\ q_2 \\ \vdots \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \\
    \begin{bmatrix} 
    \mathbf{A}_{bb} & \mathbf{A}_{bn} \\
    \mathbf{A}_{nb} & \mathbf{A}_{nn}       
    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ \hline  P_n \\ \vdots \\ P_{N_n}
    \end{bmatrix} = \begin{bmatrix} q_1 \\ q_2 \\ \vdots \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \to \begin{cases} 
        \mathbf{A}_{bb} \ket{P_{BC}} + \mathbf{A}_{bn}  \ket{P_{n}} = \ket{q} \\
    \mathbf{A}_{nb}\ket{P_{BC}} +  \mathbf{A}_{nn} \ket{P_n} = 0 
    \end{cases} \\
     \mathbf{A}_{nn} \ket{P_n} =- \mathbf{A}_{nb}\ket{P_{BC}} \to \mathbf{A}_{nn} \ket{P_n} = \mathbf{b}
\end{align}

In solving our problem, we have 
%
\begin{align}
 \mathbf{C}_{n}^\top \mathbf{R} \mathbf{C}_{n}\ket{P} =     - \mathbf{C}_{n}^\top \mathbf{R} \mathbf{C}_{b}\ket{P}_{BC}  \to \mathbf{A}_{nn} \ket{P_n} = \mathbf{B}\ket{P}_{BC}
\end{align}
%
where $\mathbf{b}$ comes from the boundary conditions. When the pressures are found then $\ket{q} = \mathbf{R}\mathbf{C} \ket{P}$, we can obtain the new fluxes. Now the question is that if $\mathbf{R} = \mathbf{R}+\delta \mathbf{R}$, then what happens to the $\ket{q}$ with respect to the first order of perturbation? if we set $\mathbf{R} = \mathbf{R}+\delta \mathbf{R}$ then
%
\begin{align}
\mathbf{C}_{n}^\top \left( \mathbf{R} + \delta \mathbf{R} \right) \mathbf{C}_{n}\ket{P'} &= - \mathbf{C}_{n}^\top \left( \mathbf{R} + \delta \mathbf{R} \right) \mathbf{C}_{b}\ket{P}_{BC} \\
(\mathbf{A} + \delta \mathbf{A}) \ket{P'} &= (\mathbf{B} + \delta \mathbf{B})\ket{P_{BC}} \\
\ket{P'} &=(\mathbf{A} + \delta \mathbf{A})^{-1} (\mathbf{B} + \delta \mathbf{B})\ket{P_{BC}}  \\
\ket{P'} &= \left( \mathbf{A}^{-1} - \left( \mathbf{A}^{-1} \delta \mathbf{A}\right) \mathbf{A}^{-1}\right) (\mathbf{B} + \delta \mathbf{B})\ket{P_{BC}} \\
\ket{P'} &= \mathbf{A}^{-1} \mathbf{B} \ket{P_{BC}} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} - \mathbf{A}^{-1} \delta \mathbf{A} \mathbf{A}^{-1} \mathbf{B} \ket{P_{BC}} \\
\ket{P'} &= \ket{P} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} - \mathbf{A}^{-1} \delta \mathbf{A} \ket{P}
\end{align}
%
where we used the fact that 
%
\begin{align}
    \left(\mathbf{A} + \delta \mathbf{A} \right)^{-1} = \mathbf{A}^{-1} - \left( \mathbf{A}^{-1} \delta \mathbf{A}\right) \mathbf{A}^{-1} + \left( \mathbf{A}^{-1}  \delta \mathbf{A}\right)^{2}\mathbf{A}^{-1}  + \cdots
\end{align}
%
The fluid flow can then be obtained 
%
\begin{align}
    \ket{q'} = \left( \mathbf{R}+ \delta \mathbf{R}\right) \mathbf{C} \ket{P'}    \\
    \text{where} \quad \mathbf{A} = \mathbf{C}^\top\mathbf{R} \mathbf{C},\quad \delta \mathbf{A} = \mathbf{C}^\top \delta \mathbf{R} \mathbf{C}
\end{align}
%
Upto the first order, we find that
%
\begin{align}
    \ket{P'} &= \ket{P} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} - \mathbf{A}^{-1} \delta \mathbf{A} \ket{P} \\
    & = \left(\mathbf{I} - \mathbf{A}^{-1} \delta \mathbf{A}  \right) \ket{P} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} \\
    & = \left( \mathbf{I} - \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1} \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\right)\ket{P} -  \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1} \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}} \\
    & = \ket{P} -  \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right] 
\end{align}
%
Calculating the fluid flow, we obtain
%
\begin{align}
\ket{q'} & = \left( \mathbf{R}+ \delta \mathbf{R}  \right)\left( \mathbf{C}_b \ket{P_{BC}} +  \mathbf{C}_n \ket{P'} \right) \\
& = \left( \mathbf{R}+ \delta \mathbf{R}  \right)\left( \mathbf{C}_b \ket{P_{BC}} + \mathbf{C}_n \left\{ \ket{P} -  \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right] \right\} \right) \\
& = \mathbf{R}\left( \mathbf{C}_b \ket{P_{BC}} +  \mathbf{C}_n \ket{P} \right) + \delta \mathbf{R}\left( \mathbf{C}_b \ket{P_{BC}} +  \mathbf{C}_n \ket{P} \right) - \mathbf{R} \mathbf{C}_n \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right]  \\
& = \ket{q} + \delta\mathbf{R} \mathbf{R}^{-1}\ket{q} - \mathbf{R} \mathbf{C}_n \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right]
\end{align}

\newpage
\section{Example}
%

\begin{figure}
    \vspace{5mm}
    \centering
    \includegraphics[width=0.2\textwidth]{./Figs/fig1}
    \caption{An example of network structure for a network of pipes}
    \label{Fig:fig1}
\end{figure}
%
%
\begin{align}
    \ket{\Delta P_\text{e}} = \mathbf{C} \ket{P_n}, \quad  \ket{q_e} = \mathbf{R} \ket{\Delta P_e}, \quad \ket{q_n} = \mathbf{C}^\top \ket{q_e} \\
    \begin{bmatrix} \Delta p_e^1 \\ \Delta p_e^2 \\\Delta p_e^3 \\\Delta p_e^4 \\\Delta p_e^5 \\ \Delta p_e^6
    \end{bmatrix} = \begin{bmatrix} 
    -1 & 1 & 0 & 0 \\
     0 & -1 & 1 & 0 \\
     0 & 0 & -1 & 1 \\
    -1 & 0 & 0 & 1 \\
    -1 & 0 & 1 & 0 \\
     0 & -1 & 0 & 1
    \end{bmatrix}\begin{bmatrix} P_n^1 \\ P_n^2 \\  P_n^3 \\P_n^4\end{bmatrix}, \quad 
    \begin{bmatrix}
    q_e^1\\    q_e^2\\    q_e^3\\    q_e^4\\    q_e^5\\    q_e^6\\
    \end{bmatrix} = \begin{bmatrix}
    R_1 & 0 & 0 & 0 & 0 & 0 \\
    0 & R_2 & 0 & 0 & 0 & 0 \\
    0 & 0 & R_3 & 0 & 0 & 0 \\
    0 & 0 & 0 & R_4 & 0 & 0 \\
    0 & 0 & 0 & 0 & R_5 & 0 \\
    0 & 0 & 0 & 0 & 0 & R_6 
    \end{bmatrix}
    \begin{bmatrix} \Delta p_e^1 \\ \Delta p_e^2 \\\Delta p_e^3 \\\Delta p_e^4 \\\Delta p_e^5 \\ \Delta p_e^6
    \end{bmatrix} \\
    \begin{bmatrix}
    q_n^1 \\    q_n^2 \\    q_n^3 \\    q_n^4 \\
    \end{bmatrix}= \begin{bmatrix} 
    -1 & 0 & 0 & -1 & -1 & 0 \\
    1 & -1 & 0 & 0 & 0 & -1 \\
    0 & 1 & -1 & 1 & 0 & 0  \\
    0 & 0 & 1 & 1 & 0 & 1
    \end{bmatrix}\begin{bmatrix}
    q_e^1\\    q_e^2\\    q_e^3\\    q_e^4\\    q_e^5\\    q_e^6\\
    \end{bmatrix}
\end{align}

### 2021-04-28 Code/Code/customcolormap_preset.m

@@ -1,0 +1,33 @@
+% Helper function with presets.
+function J = customcolormap_preset(preset_name)
+
+    switch(preset_name)
+        case 'pasteljet'
+            J = customcolormap([0 .25 .5 .75 1], {'#9d0142','#f66e45','#ffffbb','#65c0ae','#5e4f9f'});
+        case 'red-yellow-blue'
+            J = customcolormap(linspace(0,1,11), {'#a60026','#d83023','#f66e44','#faac5d','#ffdf93','#ffffbd','#def4f9','#abd9e9','#73add2','#4873b5','#313691'});
+        case 'red-yellow-green'
+            J = customcolormap(linspace(0,1,11), {'#a60126','#d7302a','#f36e43','#faac5d','#fedf8d','#fcffbf','#d7f08b','#a5d96b','#68bd60','#1a984e','#006936'});
+        case 'red-white-blue'
+            J = customcolormap(linspace(0,1,11), {'#68011d','#b5172f','#d75f4e','#f7a580','#fedbc9','#f5f9f3','#d5e2f0','#93c5dc','#4295c1','#2265ad','#062e61'});
+        case 'orange-white-purple'
+            J = customcolormap(linspace(0,1,11), {'#7f3c0a','#b35807','#e28212','#f9b967','#ffe0b2','#f7f7f5','#d7d9ee','#b3abd2','#8073a9','#562689','#2f004d'});
+        case 'purple-white-green'
+            J = customcolormap(linspace(0,1,11), {'#410149','#762a84','#9b6fac','#c1a5cd','#e7d4e8','#faf6f7','#d7f1d6','#a6db9d','#5aae60','#1c7735','#014419'});
+        case 'pink-white-green'
+            J = customcolormap(linspace(0,1,11), {'#860454','#c51b7c','#dc75ab','#f0b7da','#ffdeef','#f8f7f7','#e5f4d9','#b9e084','#7fbc42','#4d921e','#276418'});
+        case 'brown-white-pool'
+            J = customcolormap(linspace(0,1,11), {'#523107','#523107','#bf812c','#e2c17e','#f3e9c4','#f6f4f4','#cae9e3','#81cdc1','#379692','#01665e','#003d2e'});
+        case 'white-yellow-red'
+            J = customcolormap([0 0.5 1],{'#cf1717','#c9cf17','#e0e0e0'});
+        case 'red-white-blue2'
[…]

### 2021-04-28 Code/Code/publishData.m

@@ -1,0 +1,287 @@
+set(0,'defaultAxesFontSize',10)
+fs = 12;
+figFolder = '../Figs/publish2d/'
+a = 0.2;
+T = 12001;
+dir = '../Data/Delaunay/100by50T12001d0.2/'
+R_c = 15;
+
+%% 
+for N = 1:5
+    
+    subdir = [dir, strcat('N',num2str(N,'%.1f')),strcat('a',num2str(a,'%.1f'))];
+    weightPs = [];
+    Rs = [];
+    for i = 1:12
+        graphData = fullfile(subdir,strcat('ST',num2str(i),'.mat'));
+        result = isfile(graphData);
+        if result
+            posData = fullfile(subdir,strcat('configArrayS',num2str(i),'.mat'));
+            timeData = fullfile(subdir,strcat('matLargeDataS',num2str(i),'.mat'));
+            close all
+            load(graphData);
+            load(timeData);
+            load(posData);
+
+        %     
+        %     ave = mean(abs(weightP));
+        % %     ave = mean(diameterP);
+        %     display(ave);
+        %     figure('Position',[100,100,2*300,300])
+        %     h = plot(A,'XData',points(2,:),'YData',points(1,:)); %  , 'EdgeLabel', A.Edges.Weight
+        % 
+        %     % h.EdgeCData= (A.Edges.Weight2 - A.Edges.Weight); %  ave
+        %     h.EdgeCData= (weightP)/ave;    
+        %     % c_limit = max(abs(max(A.Edges.Weight))/mean(A.Edges.Weight), abs(min(A.Edges.Weight))/mean(A.Edges.Weight));
+        %     caxis([-8,8]);
+        %     % colorbar;
+        %     h.LineWidth= 1;
+        %     h.NodeLabel='';
+        %     h.Marker='none'
+        %     h.EdgeAlpha = 1.0;
+        %     colormap(bluewhitered(256));
+        %     axis equal
+        %     box off
+        %     axis off
+        %     saveas(gcf,[subdir,'/Figs/','q_',timeData(1:end-4),'.pdf']) % ,'epsc')
+        % 
+        %  
+
+            close all
+            Rave_t = mean(transpose(R_t));
+            Rmax_t = max(transpose(R_t));
[…]

### 2021-04-28 Figs/random_network/Porous - Instability/Figs/matlab-codes/par_ser_erosion.m

@@ -1,0 +1,61 @@
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 10;
+
+% 
+%        --------1/C1 -------
+% ------|                    |----------
+%        ---1/C2 ----1/C3----
+% 
+%
+%
+%
+%        ---1/C1 ----1/C2---
+% ------|                    |----------
+%        ---1/C3 ----1/C4----
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        r1s = rand(1,1)*10+2;        
+        rs = rand(3,1)*5+1;
+        r1s = r1s(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            c3 = r3s(end).^4;
+            
+            Q1 = c1/(c1+c2*c3/(c2+c3))*Q;
+            Q23 = Q-Q1;
+
+            r1s = [r1s,r1s(end) + alpha*Q1/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q23/r2s(end).^n];
+            r3s = [r3s,r3s(end) + alpha*Q23/r3s(end).^n];            
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+        c3s = r3s.^4;
+
+        p1 = plot(c1s./(c1s+c2s.*c3s./(c2s+c3s)),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end

### 2021-04-28 Figs/random_network/Porous - Instability/Figs/matlab-codes/par_ser_erosion_pressure.m

@@ -1,0 +1,56 @@
+
+close all
+figure('Position',[100,100,750,650]);
+dP = 10;
+N = 1200 ;
+fs = 10;
+
+% 
+%        --------1/C1 -------
+% ------|                    |----------
+%        ---1/C2 ----1/C3----
+% 
+
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(2,1)*5+1;
+        portion = rand(1,1);
+        r1s = rs(1); r2s = rs(2)*portion;r3s = rs(2)*(1-portion);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            c3 = r3s(end).^4;
+            
+            Q1 = c1*dP;
+            Q23 = dP*(c2*c3)/(c2+c3);
+
+            r1s = [r1s,r1s(end) + alpha*Q1/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q23/r2s(end).^n];
+            r3s = [r3s,r3s(end) + alpha*Q23/r3s(end).^n];            
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+        c3s = r3s.^4;
+
+        p1 = plot(c1s./(c1s+c2s.*c3s./(c2s+c3s)),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end

### 2021-04-28 Figs/random_network/Porous - Instability/Figs/matlab-codes/plotting_func.m

@@ -1,0 +1,20 @@
+
+clear all
+close all
+fs = 19;
+gamma  = 1;
+n = 3;
+
+[x,y] = meshgrid(linspace(0,10,100),linspace(0,10,100));
+
+% contour(x.^((n-3)/(n+1)) - y.^((n-3)/(n+1)),[gamma/2,gamma,2*gamma])
+
+contour(x.^((n-3)/(n+1)) - y.^((n-3)/(n+1)),[-0.5:.1:0.5])
+
+
+
+xlabel('$r^{n+1}_1$','Interpreter','latex');
+ylabel('$r^{n+1}_2$','Interpreter','latex');
+set(gca,'TickLabelInterpreter','latex');
+set(gca,'fontSize',fs);
+title(sprintf('$n=%d$',n),'Interpreter','latex');

### 2021-04-28 Figs/random_network/Porous - Instability/Figs/matlab-codes/toy_model_par_clogging.m

@@ -1,0 +1,61 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 500 ;
+fs = 10;
+
+alphaS = [1e-3,1,1,10,50,200]*1e-4;
+
+
+Rmin = 1;
+Rmax = 6;
+maxRChange = 1-1e-1;
+
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(2,1)*(Rmax-Rmin)+Rmin;
+        r1s = rs(1); r2s = rs(2);
+        maxR1change = min(r1s-1e-3,maxRChange);
+        maxR2change = min(r2s-1e-3,maxRChange); 
+        
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            Q1 = c1/(c1+c2)*Q;
+            Q2 = c2/(c1+c2)*Q;
+            
+            dr1 = r1s(end) - alpha*Q1/r1s(end).^n;
+            dr1Cond = (r1s(1)-dr1(end))<maxR1change;              
+            dr2 = r2s(end) - alpha*Q2/r2s(end).^n;
+            dr2Cond = (r2s(1)-dr2(end))<maxR2change;
+            
+            r1s = [r1s,dr1*dr1Cond + r1s(end)*(1-dr1Cond)];
+            r2s = [r2s,dr2*dr2Cond + r2s(end)*(1-dr2Cond)]; 
+            
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        p1 = plot(c1s./(c1s+c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 Figs/random_network/Porous - Instability/Figs/matlab-codes/toy_model_par_erosion.m

@@ -1,0 +1,47 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 10;
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(3,1)*5+1;
+        r1s = rs(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            
+            Q1 = c1/(c1+c2)*Q;
+            Q2 = c2/(c1+c2)*Q;
+            r1s = [r1s,r1s(end) + alpha*Q1/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q2/r2s(end).^n];
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        p1 = plot(c1s./(c1s+c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 Figs/random_network/Porous - Instability/Figs/matlab-codes/toy_model_series_clogging.m

@@ -1,0 +1,57 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 2000 ;
+fs = 10;
+
+alphaS = [0.1,1,1,10,50,200]*1e-3;
+
+Rmin = 1;
+Rmax = 6;
+maxRChange = 1-1e-3;
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(2,1)*(Rmax-Rmin)+Rmin;
+        r1s = rs(1); r2s = rs(2);
+        maxR1change = min(r1s-1e-3,maxRChange);
+        maxR2change = min(r2s-1e-3,maxRChange);
+        
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            dr1 = r1s(end) - alpha*Q/r1s(end).^n;
+            dr1Cond = (r1s(1)-dr1)<maxR1change;            
+            dr2 = r2s(end) - alpha*Q/r2s(end).^n;
+            dr2Cond = (r2s(1)-dr2)<maxR2change;
+            
+            r1s = [r1s, dr1*dr1Cond + r1s(end)*(1-dr1Cond)];
+            r2s = [r2s, dr2*dr2Cond + r2s(end)*(1-dr2Cond)];
+
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+        c3s = r3s.^4;
+
+        p1 = plot((1./c1s)./(1./c1s+1./c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$(P_m - P_l) / (P_r - P_l )$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 Figs/random_network/Porous - Instability/Figs/matlab-codes/two_par_ser_erosion.m

@@ -1,0 +1,63 @@
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 10;
+
+%
+%        ---1/C1 ----1/C2---
+% ------|                    |----------
+%        ---1/C3 ----1/C4----
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(4,1)*5+1;
+        r1s = r1s(1); r2s = rs(2);r3s = rs(3);r4s = rs(4);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            c3 = r3s(end).^4;
+            c4 = r4s(end).^4;
+
+            C12 = c1*c2/(c1+c2);
+            C34 = c3*c4/(c3+c4);
+
+            
+            Q12 = C12/(C12+C34)*Q;
+            Q34 = Q-Q12;
+            
+            r1s = [r1s,r1s(end) + alpha*Q12/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q12/r2s(end).^n];
+            r3s = [r3s,r3s(end) + alpha*Q34/r3s(end).^n];            
+            r4s = [r4s,r4s(end) + alpha*Q34/r4s(end).^n];
+            
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+        c3s = r3s.^4;
+        c4s = r4s.^4;        
+
+        C12 = c1s.*c2s./(c1s+c2s);
+        C34 = c3s.*c4s./(c3s + c4s);
+        p1 = plot(C12./(C12+C34),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end

### 2021-04-28 Figs/random_network/Porous - Instability/Figs/plotting_func.m

@@ -1,0 +1,20 @@
+
+clear all
+close all
+fs = 19;
+gamma  = 1;
+n = 3;
+
+[x,y] = meshgrid(linspace(0,10,100),linspace(0,10,100));
+
+% contour(x.^((n-3)/(n+1)) + y.^((n-3)/(n+1)),[gamma/2,gamma,2*gamma])
+
+% contour(x.^((n-3)/(n+1)) + y.^((n-3)/(n+1)),[2:.1:3])
+
+
+
+xlabel('$r^{n+1}_1$','Interpreter','latex');
+ylabel('$r^{n+1}_2$','Interpreter','latex');
+set(gca,'TickLabelInterpreter','latex');
+set(gca,'fontSize',fs);
+title(sprintf('$n=%d$',n),'Interpreter','latex');

### 2021-04-28 Figs/random_network/Porous - Instability/Figs/toy_model_series.m

@@ -1,0 +1,48 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 10;
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(3,1)*5+1;
+        r1s = rs(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+
+            r1s = [r1s,r1s(end) + alpha*Q/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q/r2s(end).^n];
+            r3s = [r3s,r3s(end) + alpha*Q/r3s(end).^n];
+
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+        c3s = r3s.^4;
+
+        p1 = plot((1./c1s)./(1./c1s+1./c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$(P_m - P_l) / (P_r - P_l )$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 old_files/Figs/shear_rate_.m

@@ -1,0 +1,61 @@
+
+
+close all
+
+figure('Position',[100,100,800,500]);
+
+for i=1:200
+
+    Rs = rand(2,1)*5+1;
+    r1 = Rs(1); r2 = Rs(2);
+    c1 = r1.^4; c2 = r2.^4;
+    N = 5000 ; dc = 1;
+    c1s = linspace(c1,c1+N*dc,N+1);
+    c2s = linspace(c2,c2+N*dc,N+1);
+
+    p1 = plot(c2s./(c1s+c2s),'-k'); hold on;
+    p1.Color(4) = 0.2;
+    
+end
+
+xlim([0,4000]);
+
+xlabel('Iteration','Interpreter','latex');
+ylabel('$\sigma_2 / (\sigma_1 + \sigma_2)$','Interpreter','latex');
+set(gca,'TickLabelInterpreter','latex');
+set(gca,'fontSize',18);
+
+plot([0,4000],[0.5,0.5],'-r','LineWidth',3)
+
+%%
+
+
+figure('Position',[100,100,800,500]);
+
+for i=1:200
+
+    Rs = rand(2,1)*5+1;
+    r1 = Rs(1); r2 = Rs(2);
+    c1 = r1.^4; c2 = r2.^4;
+    N = 5000 ; dc = 1;
+    c1s = c1; c2s = c2;
+    n = 0.25;
+    for j = 1:N
+        Cmax = max(c1s(end)^n,c2s(end)^n);
+        c1s = [c1s,c1s(end) + c1s(end)^n];
+        c2s = [c2s,c2s(end) + c2s(end)^n];
+    end
+    
+    p1 = plot(c2s./(c1s+c2s),'-k'); hold on;
+    p1.Color(4) = 0.2;
+    
+end
+
+xlim([0,4000]);
+
+xlabel('Iteration','Interpreter','latex');
+ylabel('$\sigma_2 / (\sigma_1 + \sigma_2)$','Interpreter','latex');
+set(gca,'TickLabelInterpreter','latex');
+set(gca,'fontSize',18);
+
+plot([0,4000],[0.5,0.5],'-r','LineWidth',3)

### 2021-04-28 old_files/Figs/toy_model_par.m

@@ -1,0 +1,46 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 10;
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(3,1)*5+1;
+        r1s = rs(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            Q1 = c1/(c1+c2)*Q;
+            Q2 = c2/(c1+c2)*Q;
+            r1s = [r1s,r1s(end) + alpha*Q1/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q2/r2s(end).^n];
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        p1 = plot(c1s./(c1s+c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 toy-model/fivethirtyeight.m

@@ -1,0 +1,29 @@
+
+
+N = 1000;
+a = randi([0,1],N,1);
+d = randi([0,1],N,1);
+
+g = randi([0,3],N,1);
+b = randi([0,3],N,1);
+
+A = a -d + g -b;
+B = b-2*g+3*d;
+C = g-3*d;
+D = d-1/2;
+
+
+
+
+p  = linspace(0,1,100);
+figure
+for i = 1:N
+    p1 = plot(p,A(i)*p.^3+B(i)*p.^2 + C(i)*p + D(i),'-k'); hold on;
+    p1.Color(4) = 0.4;
+    
+end
+
+
+plot([0,1],[0,0],'--k')
+% axis off
+

### 2021-04-28 toy-model/newest_change.m

@@ -1,0 +1,21 @@
+
+%%
+
+theta = @(Q,r,Vcr) exp(-Q./r.^2./Vcr);
+
+p = @(thetaAoR) 4*(thetaAoR.^2 - thetaAoR.^3)+thetaAoR.^4;
+
+Q = 100;
+r = 2;
+Vcr = 8;
+fac = 0.1;
+
+
+
+for i =1:100
+    
+    
+    
+    
+end
+

### 2021-04-28 toy-model/toy_model_par.m

@@ -1,0 +1,47 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 22;
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    % subplot(3,2,n+1)
+    figure
+    
+    for i=1:20    
+        alpha = alphaS(n+1);
+        rs = rand(3,1)*5+1;
+        r1s = rs(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            Q1 = c1/(c1+c2)*Q;
+            Q2 = c2/(c1+c2)*Q;
+            r1s = [r1s,r1s(end) + alpha*Q1/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q2/r2s(end).^n];
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        p1 = plot(c1s./(c1s+c2s),'-k'); hold on;
+        % p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 toy-model/toy_model_parANDseries_clogging.m

@@ -1,0 +1,134 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+ 
+
+%      /|\
+% Pl  / | \ pr
+%     \ | /
+%      \|/
+
+Pl=10;
+Pr=1;
+N = 150 ;
+fs = 16;
+Order = @(x,n) 1/(n-1)*(n-sum(x.^2).^2./sum(x.^4));
+
+Rmin = 1;
+Rmax = 14;
+step = 0.1;
+
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+
+        rs = rand(5,1)*(Rmax-Rmin)+Rmin;
+        r1s = rs(1); r2s = rs(2);
+        r3s = rs(3); r4s = rs(4);
+        r5s = rs(5); 
+        
+        q1s = zeros(N,1);
+        q2s = zeros(N,1);
+        q3s = zeros(N,1);
+        q4s = zeros(N,1);
+        q5s = zeros(N,1);
+        
+        
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            c3 = r3s(end).^4;
+            c4 = r4s(end).^4;
+            c5 = r5s(end).^4;
+
+            
+            LHS = [-c1-c3-c4,c3;
+                   c3,-c2-c3-c5];
+            RHS = [-c1*Pl-c4*Pr;
+                   -c2*Pl-c5*Pr];
+             
+
+            
+            Ps = LHS\RHS;
+
+            P1 = Pl;
+            P4 = Pr;
+            P2 = Ps(1);
+            P3 = Ps(2);            
+            
+            
+            q1 = abs(c1*(P2-P1));
+            q2 = abs(c2*(P3-P1));
+            q3 = abs(c3*(P3-P2));
+            q4 = abs(c4*(P4-P2));
+            q5 = abs(c5*(P4-P3));            
+            
+            q1s(j) = c1*(P2-P1);
+            q2s(j) = c2*(P3-P1);
+            q3s(j) = c3*(P3-P2);
+            q4s(j) = c4*(P4-P2);
+            q5s(j) = c5*(P4-P3);            
+            
+            
+            if j==1
+                initial_q = c1*(P2-P1) + c2*(P3-P1);
+            end
+            
+            
+            
+            alpha = step./max([q1./r1s(end).^n,q2./r2s(end).^n,q3./r3s(end).^n,q4./r4s(end).^n,q5./r5s(end).^n]);
[…]

### 2021-04-28 toy-model/toy_model_par_clogging.m

@@ -1,0 +1,65 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 150 ;
+fs = 16;
+
+Rmin = 1;
+Rmax = 14;
+step = 0.1;
+minR = 0.01;
+
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+
+        rs = rand(2,1)*(Rmax-Rmin)+Rmin;
+        r1s = rs(1); r2s = rs(2);
+        
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+        
+            Q1 = c1/(c1+c2)*Q;
+            Q2 = c2/(c1+c2)*Q;
+            
+            alpha = step./max(Q1/r1s(end).^n,Q2/r2s(end).^n);
+            
+            
+            dr1 = r1s(end) - alpha*Q1/r1s(end).^n;
+            dr1Cond = dr1 > minR;              
+            dr2 = r2s(end) - alpha*Q2/r2s(end).^n;
+            dr2Cond = dr2 > minR;
+            
+            if ~dr1Cond | ~dr2Cond
+                break
+            end
+                        
+            
+            r1s = [r1s,dr1*dr1Cond + 0.1*(1-dr1Cond)];
+            r2s = [r2s,dr2*dr2Cond + 0.1*(1-dr2Cond)]; 
+            
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        p1 = plot(c1s./(c1s+c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    

### 2021-04-28 toy-model/toy_model_par_clogging_bkup.m

@@ -1,0 +1,61 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 500 ;
+fs = 10;
+
+alphaS = [1e-3,1,1,10,50,200]*1e-4;
+
+
+Rmin = 1;
+Rmax = 6;
+% maxRChange = 1-1e-1;
+minR = 0.1;
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(2,1)*(Rmax-Rmin)+Rmin;
+        r1s = rs(1); r2s = rs(2);
+        % maxR1change = min(r1s-1e-3,maxRChange);
+        % maxR2change = min(r2s-1e-3,maxRChange); 
+        
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            Q1 = c1/(c1+c2)*Q;
+            Q2 = c2/(c1+c2)*Q;
+            
+            dr1 = r1s(end) - alpha*Q1/r1s(end).^n;
+            dr1Cond = (r1s(1)-dr1(end))<maxR1change;              
+            dr2 = r2s(end) - alpha*Q2/r2s(end).^n;
+            dr2Cond = (r2s(1)-dr2(end))<maxR2change;
+            
+            r1s = [r1s,dr1*dr1Cond + r1s(end)*(1-dr1Cond)];
+            r2s = [r2s,dr2*dr2Cond + r2s(end)*(1-dr2Cond)]; 
+            
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        p1 = plot(c1s./(c1s+c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 toy-model/toy_model_par_clogging_order.m

@@ -1,0 +1,69 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 150 ;
+fs = 16;
+Order = @(x,n) 1/(n-1)*(n-sum(x.^2).^2./sum(x.^4));
+
+Rmin = 1;
+Rmax = 14;
+step = 0.1;
+minR = 0.01;
+
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+
+        rs = rand(2,1)*(Rmax-Rmin)+Rmin;
+        r1s = rs(1); r2s = rs(2);
+        
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+        
+            Q1 = c1/(c1+c2)*Q;
+            Q2 = c2/(c1+c2)*Q;
+            
+            alpha = step./max(Q1/r1s(end).^n,Q2/r2s(end).^n);
+            
+            
+            dr1 = r1s(end) - alpha*Q1/r1s(end).^n;
+            dr1Cond = dr1 > minR;              
+            dr2 = r2s(end) - alpha*Q2/r2s(end).^n;
+            dr2Cond = dr2 > minR;
+            
+            if ~dr1Cond | ~dr2Cond
+                break
+            end
+                        
+            
+            r1s = [r1s,dr1*dr1Cond + 0.1*(1-dr1Cond)];
+            r2s = [r2s,dr2*dr2Cond + 0.1*(1-dr2Cond)]; 
+            
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+        
+        q = [1./c1s; 1./c2s];
+        order = Order(q,2);
+
+        p1 = plot(order,'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$\mathcal{O}(q)$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    

### 2021-04-28 toy-model/toy_model_par_clogging_order_multiple.m

@@ -1,0 +1,65 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 150 ;
+fs = 16;
+Order = @(x,n) 1/(n-1)*(n-sum(x.^2).^2./sum(x.^4));
+
+Rmin = 1;
+Rmax = 14;
+step = 0.1;
+minR = 0.01;
+
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+
+        rs = rand(10,1)*(Rmax-Rmin)+Rmin;
+        
+        for j = 1:N
+            c = rs(:,end).^4;
+            
+            q = c./sum(c)*Q;
+            
+            
+            alpha = step./max(q./rs(:,end).^n);
+            
+            
+            dr = rs(:,end) - alpha.*q./rs(:,end).^n;
+            
+            dr = dr.*(dr>0) + 0.*(dr<=0);
+
+            drCond = dr<=0;
+            
+            if all(drCond)
+                break
+            end
+                        
+            rs = [rs,dr];
+        end    
+
+        cs = rs.^4;
+
+        q = cs./sum(cs);
+
+        order = Order(q,10);
+
+        p1 = plot(order,'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$\mathcal{O}(q)$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    

### 2021-04-28 toy-model/toy_model_par_erosion.m

@@ -1,0 +1,48 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 10;
+
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(3,1)*5+1;
+        r1s = rs(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            
+            Q1 = c1/(c1+c2)*Q;
+            Q2 = c2/(c1+c2)*Q;
+            r1s = [r1s,r1s(end) + alpha*Q1/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q2/r2s(end).^n];
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        p1 = plot(c1s./(c1s+c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 toy-model/toy_model_par_erosion_order.m

@@ -1,0 +1,52 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 10;
+Order = @(x,n) 1/(n-1)*(n-sum(x.^2).^2./sum(x.^4));
+
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(3,1)*5+1;
+        r1s = rs(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            
+            Q1 = c1/(c1+c2)*Q;
+            Q2 = c2/(c1+c2)*Q;
+            r1s = [r1s,r1s(end) + alpha*Q1/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q2/r2s(end).^n];
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+        q = [1./c1s; 1./c2s];
+        order = Order(q,2);
+
+        p1 = plot(order,'-k'); hold on;
+        
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$\mathcal{O}(q)$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 toy-model/toy_model_par_erosion_pressure.m

@@ -1,0 +1,47 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+dP = 10;
+N = 1200 ;
+fs = 10;
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(3,1)*5+1;
+        r1s = rs(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            
+            Q1 = c1*dP;
+            Q2 = c2*dP;
+            r1s = [r1s,r1s(end) + alpha*Q1/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q2/r2s(end).^n];
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        p1 = plot(c1s./(c1s+c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$Q_1 / Q$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 toy-model/toy_model_series_clogging.m

@@ -1,0 +1,65 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+dP = 10;
+N = 200 ;
+fs = 10;
+
+Rmin = 1;
+Rmax = 14;
+step = 0.1;
+minR = 0.01;
+
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        
+        rs = rand(2,1)*(Rmax-Rmin)+Rmin;
+        r1s = rs(1); r2s = rs(2);
+
+        
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            
+            ceq = c1*c2/(c1+c2);
+            Q = ceq*dP;
+            
+            alpha = step/max(Q/r1s(end).^n,Q/r2s(end).^n);
+            
+            
+            dr1 = r1s(end) - alpha*Q/r1s(end).^n;
+            dr1Cond = dr1>minR;            
+            dr2 = r2s(end) - alpha*Q/r2s(end).^n;
+            dr2Cond = dr2>minR;
+            
+            if ~dr1Cond | ~dr2Cond
+                break
+            end
+            
+            r1s = [r1s, dr1];
+            r2s = [r2s, dr2];
+
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        p1 = plot((1./c1s)./(1./c1s+1./c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$(P_m - P_l) / (P_r - P_l )$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    

### 2021-04-28 toy-model/toy_model_series_clogging_order.m

@@ -1,0 +1,69 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+dP = 10;
+N = 200 ;
+fs = 10;
+Order = @(x,n) 1/(n-1)*(n-sum(x.^2).^2./sum(x.^4));
+
+Rmin = 1;
+Rmax = 14;
+step = 0.1;
+minR = 0.01;
+
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        
+        rs = rand(2,1)*(Rmax-Rmin)+Rmin;
+        r1s = rs(1); r2s = rs(2);
+
+        
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            
+            ceq = c1*c2/(c1+c2);
+            Q = ceq*dP;
+            
+            alpha = step/max(Q/r1s(end).^n,Q/r2s(end).^n);
+            
+            
+            dr1 = r1s(end) - alpha*Q/r1s(end).^n;
+            dr1Cond = dr1>minR;            
+            dr2 = r2s(end) - alpha*Q/r2s(end).^n;
+            dr2Cond = dr2>minR;
+            
+            if ~dr1Cond | ~dr2Cond
+                break
+            end
+            
+            r1s = [r1s, dr1];
+            r2s = [r2s, dr2];
+
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+
+        q = [c1s./(c1s + c2s); c2s./(c1s + c2s)]; 
+        order = Order(q,2);
+        
+        p1 = plot(order,'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$\mathcal{O}(\Delta P) $','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    

### 2021-04-28 toy-model/toy_model_series_erosion.m

@@ -1,0 +1,49 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 10;
+
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(3,1)*5+1;
+        r1s = rs(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+
+            r1s = [r1s,r1s(end) + alpha*Q/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q/r2s(end).^n];
+            r3s = [r3s,r3s(end) + alpha*Q/r3s(end).^n];
+
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+        c3s = r3s.^4;
+
+        p1 = plot((1./c1s)./(1./c1s+1./c2s),'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$(P_m - P_l) / (P_r - P_l )$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 toy-model/toy_model_series_erosion_order.m

@@ -1,0 +1,52 @@
+
+
+close all
+figure('Position',[100,100,750,650]);
+Q = 10;
+N = 1200 ;
+fs = 10;
+Order = @(x,n) 1/(n-1)*(n-sum(x.^2).^2./sum(x.^4));
+
+
+alphaS = [0.1,1,1,10,50,200];
+
+for n = 0:5
+    
+    subplot(3,2,n+1)
+    
+    for i=1:200    
+        alpha = alphaS(n+1);
+        rs = rand(3,1)*5+1;
+        r1s = rs(1); r2s = rs(2);r3s = rs(3);
+
+        for j = 1:N
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+
+            r1s = [r1s,r1s(end) + alpha*Q/r1s(end).^n];
+            r2s = [r2s,r2s(end) + alpha*Q/r2s(end).^n];
+            r3s = [r3s,r3s(end) + alpha*Q/r3s(end).^n];
+
+        end    
+
+        c1s = r1s.^4;
+        c2s = r2s.^4;
+        c3s = r3s.^4;
+        q = [c1s./(c1s + c2s); c2s./(c1s + c2s)]; 
+        order = Order(q,2);
+        
+        p1 = plot(order,'-k'); hold on;
+        p1.Color(4) = 0.2;
+
+    end
+    drawnow
+    xlim([0,N]);
+
+    xlabel('Iteration','Interpreter','latex');
+    ylabel('$\mathcal{O}(\Delta P)$','Interpreter','latex');
+    set(gca,'TickLabelInterpreter','latex');
+    set(gca,'fontSize',fs);
+    title(sprintf('$n=%d$',n),'Interpreter','latex');
+end
+    
+% plot([0,4000],[1/3,1/3],'-r','LineWidth',3)

### 2021-04-28 toy-model/toy_par_series.m

@@ -1,0 +1,131 @@
+% toy model - par-series
+
+
+
+close all
+figure('Position',[100,100,750,650]);
+Pl = 1;
+Pr = 11;
+N = 200 ;
+
+Rmin = 1;
+Rmax = 14;
+step = 0.1;
+minR = 0.01;
+fs = 18
+Ns = 0:1:5;
+Os = zeros(size(Ns));
+plotting = true;
+
+for ij  =  1:length(Ns) % different powers of n
+    
+    n = Ns(ij);
+    
+    if plotting
+        subplot(3,2,n+1)
+    end
+    
+    
+    O_n_s = zeros(1000,1);    
+    for i=1:1000    % number of simulations
+        
+        rs = rand(5,1)*(Rmax-Rmin)+Rmin;
+        r1s = rs(1); 
+        r2s = rs(2);
+        r3s = rs(3); 
+        r4s = rs(4);
+        r5s = rs(5); 
+        Pas = [];
+        Pbs = [];
+        
+        Q14s =[];
+        order = [];
+        
+        for j = 1:N % running in steps
+
+            
+            Rs = [r1s(end);r2s(end);r3s(end);r4s(end);r5s(end)];
+            
+            c1 = r1s(end).^4;
+            c2 = r2s(end).^4;
+            c3 = r3s(end).^4;
+            c4 = r4s(end).^4;
+            c5 = r5s(end).^4;
+            
+            LHS = [-c1-c2-c3, c2; c2, -c2-c4-c5];
+            RHS = [-c1*Pl-c3*Pr; -c4*Pl-c5*Pr];
+            
+            Pm = LHS\RHS;
+           
+            Pa = Pm(1);
+            Pb = Pm(2);
+
+            Pas = [Pas,Pa];
+            Pbs = [Pbs,Pb];
+            
+            Cs = [c1;c2;c3;c4;c5];
+            dP = [Pa-Pl; Pb-Pa; Pr-Pa; Pb-Pl;Pr-Pb];
+            Q = abs(Cs.*dP);         
+            
+            order = [order, 1/4*( 5 - (sum(Q.^2)^2/sum(Q.^4)))];
+            
+            
+            
+            Q14s = [Q14s, Q(1)+Q(4)];
+            
+            alpha = step./max(Q./Rs.^n);
+            
+            
+            dr1 = r1s(end) - alpha*Q(1)/r1s(end).^n;
[…]

### 2022-03-06 review_response/Response.tex
Updates from Overleaf

%%//////////////////////////////////////////////////////////////
%%
%% P R E A M B L E
%%
%%//////////////////////////////////////////////////////////////
\documentclass{article}

%%==============================================================
%% Packages=
%%==============================================================
\usepackage[english]{babel}
\usepackage{booktabs}
\usepackage{scicite}
%\usepackage{citesort}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphics,amsfonts,amssymb,amsmath,latexsym}
\usepackage{graphicx,subfig}
\usepackage[ansinew]{inputenc}
%\usepackage{natbib}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{subfig}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{lscape}
\usepackage{authblk}
\usepackage{xr}
\usepackage{enumerate}
\usepackage{bm}
\usepackage{epstopdf}
\usepackage{float}
\setlength\parindent{0pt}
\usepackage{xr}
\usepackage{csquotes}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}

\usepackage[usenames, dvipsnames]{color}
\usepackage[dvipsnames]{xcolor}

% Color Edits
\newcommand{\add}[1]{\noindent \color{blue} #1 \normalcolor}
% \newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}
% \newcommand{\AM}[1]{\noindent \color{magenta} (AM: #1)\normalcolor}
% \newcommand{\AZ}[1]{\noindent \color{purple} (AZ: #1)\normalcolor}
% \newcommand{\PD}[1]{\noindent \color{cyan} (PD: #1)\normalcolor}

%\usepackage{scicite}
\usepackage{natbib}
\bibliographystyle{unsrt}

%%==============================================================
%% New Commands
%%==============================================================
\newcommand{\Hline}{\rule{\linewidth}{.1mm}}
%\newcommand{\RedColor}[1]{\noindent \color{red}  #1 \normalcolor}
\newcommand{\Question}[1]{\noindent \color{black}\emph{#1}\normalcolor}
\newcommand{\Answer}[1]{\noindent {\color{blue}{ #1}}\normalcolor}

\newcommand{\AnswerQ}[1]{\noindent {\footnotesize {\color{blue}{ #1}}}\normalcolor}

\renewcommand{\thepage}{R\arabic{page}}
\renewcommand{\thesection}{R\arabic{section}}
\renewcommand{\theequation}{R\arabic{equation}}
\renewcommand{\thefigure}{R\arabic{figure}}
\renewcommand{\thetable}{R\arabic{table}}
\renewcommand{\thetable}{R\arabic{table}}

\def\th{\theta}

\newcommand{\bfphi}{\boldsymbol{\phi}}%

\newcommand{\Hb}{\mathbf{\bar{H}}}

\newcommand{\revised}[1]{\noindent\color{Blue}#1\normalcolor}

\newcommand{\PD}[1]{\noindent \color{red} (PD: #1)\normalcolor}
\newcommand{\EM}[1]{\noindent \color{magenta} (EM: #1)\normalcolor}
\newcommand{\AZ}[1]{\noindent \color{purple}(AZ: #1)\normalcolor}

\def\p{\textit{p.~}}
\def\l{\textit{l.~}}
%%==============================================================
%% Setttings
%%==============================================================
\topmargin -0.5in

\setlength{\textwidth}{6in} \setlength{\textheight}{8.25in}
\setlength{\oddsidemargin}{0mm}
\setlength{\textwidth}{6.in}
\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0.25in}
\setlength{\oddsidemargin}{0.25in}
\setlength{\oddsidemargin}{0mm}

%%//////////////////////////////////////////////////////////////
%%
%% T I T L E    &    A U T H O R S
%%
%%//////////////////////////////////////////////////////////////
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{
Response to the Reviewers' comments for manuscript \\
(Tracking \#: LF18481): \\
``Temporal evolution of flow in pore-networks: From homogenization to instability"
}

\author{Ahmad Zareei, Deng Pan, and  Ariel Amir
}
\date{}

%%//////////////////////////////////////////////////////////////
%%
%% FIRST SENTENSE
%%
%%//////////////////////////////////////////////////////////////
\begin{document}
\maketitle

\noindent In the following, we address each of the Referees' comments/suggestions (\emph{in italic}). All page/paragraph/line (\textit{p.},\ \textit{par.},\ \textit{l.},\ etc.) numbers refer to the revised paper. %In addition, while using the original numbering of figures/equations/references in the manuscript (\emph{e.g.}, Fig.~1, Fig.~2,...., Eq.~(1), Eq.~(2),..., [1], [2], ...),  we add prefix ``\emph{R}'' for figures/equations/references presented in this response to the Referees' comments (\emph{e.g.}, Fig.~R1, Fig.~R2, .... Eq.~(R1), Eq.~(R2), ..., Ref.~[R1], Ref.~[R2],...).
% \centerline{(Tracking \#: LB15473 Deng)}

\vspace{5 mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ref 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
\Hline \\
\textbf{Response to Reviewer \#1} \\
\Hline
\\

% \centerline{Negative numbers are counted from the bottom of the page.}
%({\color{orange}\mbox{------}})

\Question{
This paper studies the evolution of a porous medium network model
under erosion. The basic result, which does not require any
calculation at all, is that when the wider channels are more likely to erode the flow becomes localized and when erosion is stronger in the smaller channels the flow becomes uniform. This is because in pore networks most of the flux is in the wider channels so if these are more likely to widen they will carry more and more flux, whereas more erosion in the narrow channels allows them to carry more flux and evens out the distribution.
% 
The calculations are of theoretical interest but not significant
enough for PRL. The paper could be revised to combine the
supplementary material with the main text and considered for
publication in PRE or PRFluids.
\newline}

\Answer{{We thank the reviewer for carefully reading our manuscript and providing insightful comments.}}

\vspace{0.5cm}
\textbf{Comment 1A }
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{The particular model introduced in Eq. 1 gives a local erosion rate proportional to arbitrary powers of the pressure difference and the radius, which is hard to rationalize outside of the simple case $m=1$ and $n=0$. It is probably useful to have specific models illustrating an obvious result but they are too generic to be quantitatively applicable; a justification based on a serious analysis of the erosion process would be needed. \newline}

\Answer{We thank the reviewer for encouraging us to consider more realistic models of physical erosion. To address this issue, in the revised version, we have taken different steps to make our models more realistic: (i) We identify the stability condition for the homogeneous phase starting from a rather general equation for the erosion dynamics, of which the previous power-law class is a particular case. (ii) We show that for a more realistic model of erosion -- where the erosion rate depends on the shear stresses in a nonlinear fashion, effectively incorporating both a threshold for the onset of erosion as well as saturation of the erosion rate -- our approach correctly predicts the onset of channeling and the fate of the network (which in this case may, interestingly, result in multiple channels). (iii) We further show that the model considered in the manuscript is robust to the form of the boundary conditions, in addition to the robustness to topology and the form of the disorder that was previously considered. (iv) Following previous models proposed for erosion in the literature, we consider an extension of our previous model where the onset of erosion occurs only after reaching a threshold value, while still maintaining the previously used power-law form thereafter.  We analytically show that the phase transition persists with a slightly modified condition, which we corroborate numerically. (v) Finally, we expanded our discussion of erosion models and elaborate on the connection with the existing models in literature. These results are now included both in the main text and new sections of the supplementary material. We attach the relevant excerpts from the text below.}
%
\\

\Answer{$\bullet$ (i) From \p3 and \p4 of the main text:}
%
\AnswerQ{
\begin{quote}
    ``\textit{Local Dynamics Model}-- To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Figs.~3b-c). First, assuming two cylindrical tubes with radii $r_1,r_2$ in series with a given pressure difference of $\delta p = p_r- p_l$, the radius of each tube changes as $dr_i/dt = f(q,r_i),~i=1,2$ (Fig. 3b) where $q=q_1=q_2$. Without loss of generality we assume $r_1>r_2$. Considering the pressure at the junction between tubes $\tilde p_m = (p_m-p_l)/(p_r-p_l)= C_2/(C_1+C_2)$. Time evolution of the middle pressure then follows % 
    %
    \begin{align}
        \frac{d\tilde{p}_m}{dt} = \gamma (r_1 f(q,r_2)-r_2 f(q,r_1)). 
    \end{align}
    %
    where $\gamma = \sqrt{{2\pi}/{\mu L}}{C_1^{\frac{3}{4}} C_2^{\frac{3}{4}}}/{ (C_1+C_2)^2}$. In the above equation, $r_1=r_2$ is a fixed point solution where $d\tilde p_m/dt =0$ and $p_m=1/2$. Since we assumed $r_1>r_2$, we can see that $\tilde p_m <1/2$, and if ${d\tilde{p}_m}/{dt}>0$, then $\tilde p_m \to 1/2$ and the flow homogenizes. Note that if $f(q,r) = \alpha q^m/r^n$, we find that for any $n>0$ the network homogenizes (see Fig. 3b). Contrary to tubes in series, when the tubes are in parallel (Fig. 3c), the net flow $q$ divides between the two tubes in proportion to their conductivity, i.e., $ q_1/q_2 = C_1/C_2$ which results in $q_1/q = \tilde C_1$, where $\tilde C_1 = C_1/(C_1+C_2)$. Note that the dynamics for each pipe in the parallel case can be simplified to $dr_i/dt = g(r_i)$ where $g(r_i) \equiv f(q_i, r_i)$ in which $q_i = \pi r_i^4 \Delta p / 8\mu L$. Given these dynamics, the evolution of the fluid flow ratio becomes $d(q_1/q)/dt = d \tilde C_1/dt=  \gamma (r_2 g(r_1)-r_1 g(r_2))$. Similarly, it can be seen that  $r_1=r_2$ is a fixed point, where flow is equally distributed between the edges resulting in homogenization. If $d \tilde C_1/dt <0$, then the edge with larger radius has a reduced growth rate while the smaller radius edge has an increasing growth until $r_1=r_2$ is reached. This condition results in homogenization, where both edge's radius increases until the fixed point of $r_1=r_2$ is reached. The condition of $d \tilde C_1/dt<0$ is satisfied when 
    %
    \begin{align}
        \frac{g(r_1)}{g(r_2)}<\frac{r_1}{r_2}, \quad \forall r_1>r_2>0.   \label{Eq3}
    \end{align}
    %
    Note that if $d\left(g(r)/r\right)/dr<0$, then Eq.~\eqref{Eq3} is satisfied, and homogenization would occur.
    The above homogenization condition can further be simplified as $g(r)>g'(r)r$, which can also be obtained directly using a linear stability analysis. Given the homogenization condition $g(r)>g'(r)r$, if the erosion rate is sub-linear locally near the initial radius, the network moves towards homogenization. On the other hand, if the erosion rate is super-linear, we expect the parallel tubes to move away from homogenization and channelization occurs. Applying the power law erosion model with $f(q_{i},r_i)=\alpha q_i^m/r_i^n$, it can be shown that $g(r) \propto  r^{4m-n} $, and therefore $4m-n=1$ results in no change in the flow ratio $q_1/q$ (Fig. 3c$_1$), while $4m-n<1$ results in homogenization condition (Fig.~3c$_2$), and $4m-n>1$ results in channelization (Fig. 3c$_3$). Since a complex network includes both series and parallel connections, it is plausible that the whole network structure will behave in a similar manner, with an approximate transition in the network's behavior at $ m = (n+1)/4$. This result for $m=1$ reduces to a transition at $n=3$. It is to be noted that while the flow ratio remains constant for parallel edges, the connections in series are evolving toward homogenization and that is why we find a difference between evolved network for $n=3$ and the network at $t=0$. Since series connections are always moving toward homogenization, while parallel connections show a phase transition, we expect the phase transition to be at approximately $n\approx 3$, governed by the parallel connections. This observation  is consistent with the numerical simulation results shown in Figs.~2 and 3a (for $m=1$) as well as for additional values of $m$ (Fig.~4). Note, however, that the local dynamics model is only approximate and the numerically observed value of the phase transition happens for a value slightly larger than $n=3$ in Fig.~3.''
    \end{quote}
}
\\
\newline 
\vspace{4mm}

\Answer{$\bullet$ (ii) From supplementary material, section S7:}
%
\AnswerQ{
\begin{quote}
    ``As an example of a nonlinear erosion model, we consider a shear-dependent erosion
    %
    \begin{align}
        \frac{dr}{dt} = f(\tau), 
    \end{align}
    %
    where $\tau=\tau(q,r) = 4\mu q/\pi r^3$ is the shear stress at the tube's wall assuming Poiseuille flow. It is to be noted that a shear-dependent erosion model is commonly used in studying erosion  \cite{jager2017channelization,bonelli2011micromechanical,parker2000purely} wherein such models erosion happens linearly proportional to the shear stress at the wall only after a certain threshold value $\tau_0$ (see main text for more information). Such linear models, however, ignore the maximum detachment rate of particles at the pore's boundary which would effectively limit the pore's radius maximum rate of change. To address this, we use a nonlinear erosion model
    %
    \begin{align}
        f(\tau) = \alpha \left( \tanh{\left[ \beta(\tau - \tau_0)\right]}+1\right), 
        \label{eq:sigmoidErosion}
    \end{align}
    %
    where $\beta$ determines the shear rate scale and $\alpha$ determines the erosion rate scale. Note that the erosion rate scale $\alpha$ only affects the timescale at which the final state is reached and has no effect on the pattern formation. Without loss of generality we set $\alpha = 1$. Following the local dynamics model discussion in the main text, one can find that the homogenization condition reduces to 
    %
    \begin{align}
        f(\tau)>\tau \frac{df(\tau)}{d \tau}. 
        \label{eq:sigmoidCondition}
    \end{align}
    %
    Assuming a random network (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}a), the initial values of shear stress at the walls has a  decaying distribution over a large set of values (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}b). 
    % Assuming nonlinear shear dependent erosion model (Eq. \eqref{eq:sigmoidErosion}), and the homogenization condition (Eq. \eqref{eq:sigmoidCondition}), three regions of erosion can be identified: (i) constant erosion region as $\tau\to\infty$: at this region the erosion happens at a constant rate $\lim_{\tau \to \infty} f(\tau) = 2$ and additionally the homogenization condition (Eq.~\eqref{eq:sigmoidCondition}) is satisfied (since $\lim_{\tau \to \infty} f(\tau) = 2$ and $\lim_{\tau \to \infty} f'(\tau) = 0$). The homogenization results here is similar to the constant erosion rate model or $m=0,n=0$ discussed in the main text; (ii)  the slow erosion region as $\tau\to 0$. In this region both $f(\tau)$ and $\tau f'(\tau)$ are close to 0 and erosion happens at a very slow rate; (iii) the finite erosion-rate region near $\tau = \tau_0$, where $f(\tau)$ is an increasing function. In this region $\tau f'(\tau)$ has a maximum at $\beta \tau_0$ with a bandwidth of $1/\beta$. Note that here if $\beta \tau_0 < 1$, then the maximum $\tau f'(\tau)$ does not exceed 1, and the homogenization condition holds true for any $\tau$. As the value of $\tau_0$ increases, the homogenization region moves towards larger values of $\tau$ where smaller values of $\tau$ would result in channelization.  Varying $\beta$ and $\tau_0$ can change the network behavior. 
    To test our local dynamics model, we vary $\beta$ and $\tau_0$ and run three different tests: (i) $\beta=1,\tau_0=1$: For such values of $\beta,\tau$, almost all the tubes are in the homogenization region (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}c) and the network moves toward homogenization (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}d). The final PDF of the network after erosion is further shown in (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}e). (ii) $\beta=1, \tau_0=12$: In this case, the homogenization condition is satisfied at some finite value of shear stress $\tau_0$ where $f(\tau_0) = \tau_0 f(\tau_0)$. As a result, some edges would homogenize, and some would channelize (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}f). Running the simulation over a random network, we find that a finite number of channels form (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}g). The PDF distribution of shear stress at the wall $\tau$ correspondingly becomes bimodal (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}h). (iii) $\beta=1, \tau_0=30$: In this case, almost all the edges in the network are in the channelization regime  (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}i), and performing the simulations we find that indeed one strong single channel is formed (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}j) and the PDF of shear stress $\tau$ shows a clear separation between flow in the channel versus flow in the rest of the system (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}k).''
\end{quote}
}

   \begin{figure}[htp]
     % \centering
     \centering \includegraphics[width = 0.8\textwidth]{../sigmoidDelaunay.pdf}
     \caption{\textcolor{blue}{(a) A 2D random network with $N_x=50$ and $N_y=50$ points. (b) The probability distribution function (PDF) of the shear stress for the edges of the network. (c)/(f)/(i) The PDF of the shear stress along with nonlinear erosion law $f(\tau)$ (solid red line) and $\tau f'(\tau)$ (dashed red line). The areas where the homogenization condition (i.e., $f(\tau)>\tau f'(\tau)$) is satisfied are shaded with green color, otherwise, the channelization condition is satisfied and the region is shaded with red color. (d)/(g)/(j) Snapshots of the 2D network after erosion using the nonlinear erosion law shown in the previous row until the average radius of the network is increased to twice its original size. (e)/(h)/(k) The PDF of the shear stress at the walls for the final snapshot of the network shown in the previous row. 
    }}
     \label{SIfig:fig9-sigmoidDelaunay}
 \end{figure}
 \\

 \clearpage

 \Answer{
     $\bullet$ (iii) From supplementary material, section S3:}

\AnswerQ{
\begin{quote}
In addition to the network topology and initial condition, we test the robustness of our results to changes in the boundary condition. We choose a circular domain, with the central node being the inlet and all the nodes at the outer boundary being outlets. Similar to the transition reported for the square
domain, we find a phase transition at the predicted power which shows that our analysis is independent of the geometry (Fig.~\ref{circular-S3}).
\end{quote}
}
% 
\begin{figure}[htp]
     % \centering
      \includegraphics[width = 1.0\textwidth]{../circular.pdf}
     \caption{\add{Erosion in a topologically random 3D network of tubes with a circular topology with $N = 3000 $ randomly distributed nodes and an initial uniform broad distribution of tube diameters randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$. Shown are snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$. We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$. The erosion law is based on $dr/dt = \alpha q/r^n$ where different powers of $n$ correspond to different models of erosion.}}\label{circular-S3}
 \end{figure}

 \Answer{
     $\bullet$ (iv) From supplementary material, section S4:}

\AnswerQ{     
     \begin{quote}
         ``In order to make our erosion model more realistic, we modify the model as  
        %
        \begin{align}
            \frac{dr}{dt } = \begin{cases} q^m/r^n - \beta & q^m/r^n\geq \beta\\
            0 & q^m/r^n<\beta
            \end{cases} \label{eq:thresh}
        \end{align}
        %
        where $\beta$ is the threshold for the onset of erosion. We pick $\beta = 0.25\langle q^m/r^n\rangle $ and $\beta = 0.9 \langle q^m/r^n\rangle$ corresponding to a small and a large threshold value. In both cases, we ran our simulations for different values of $m$ and $n$, and found that different behaviors of homogenization and channelization persists (see Fig. \ref{fig:figthresh1}). The result can be explained by applying the general condition for the phase transition as discussed in the main text. Following the same argument, it can be shown that the homogenization condition (Eq. 3 in the main text) is equivalent to the condition 
        %
        \begin{align}
        4m-n-1 < -\frac{\beta}{q^m/r^n}.    
        \end{align}
        %
        which can be found using $g(r) = ({\pi \Delta p}/{8\mu L})^{m} r^{m-n} - \beta $ assuming a constant pressure boundary condition. Note that the condition above depends on the value of $q^m/r^n$ which varies over the network edges. Taking the mean value of $q^m/r^n$ to find an average value for the transition condition, the transition line becomes $4m-n=0.75$ and $4m-n=0.1$ for the small and large thresholding value respectively. As a result the thresholding condition slightly shifts the intercept of the transition line while the slope remains the same. In Fig.~\ref{fig:figthresh1}, we plot the new transition lines, where the prediction for the phase boundaries matches well with the simulation results.'' 
 \end{quote}
 }

\begin{figure}[htp]
    \centering
 \includegraphics[width=0.45\textwidth]{../Fig_thres0.25.pdf}
  \includegraphics[width=0.45\textwidth]{../Fig_thresh0.9.pdf}
     \caption{\add{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq. \eqref{eq:thresh} with a small threshold value of $\beta = 0.25\langle q^m/r^n\rangle $ (left figure), and a large threshold value of $\beta = 0.9\langle q^m/r^n\rangle$ at $t=0$. The network is randomly initialized with $50\times 50$ randomly distributed pores. The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using local dynamics model, i.e., $4m-n=0.75$ (left figure), and $4m-n=0.1$ (right figure).} }\label{fig:figthresh1}% 
\end{figure}
\\

\newpage

\Answer{$\bullet$ (v) From \p2 of the main text:}
%

\AnswerQ{
\begin{quote}
    ``A general constitutive model for erosion can be written as $dr_{ij}/dt = f(q_{ij},r_{ij})$, where $f(q_{ij},r_{ij})$ represents the functional dependence of erosion on the fluid flux $q_{ij}$ and the tube radius $r_{ij}$. Erosion in saturated, granular, porous medium occurs when the shear stress  at the walls $\tau_w$ exerted by the fluid overcomes the cohesive strength of the solid matter $\tau_c$. In a class of erosion models previously studied~\cite{jager2017channelization,ristroph2012sculpting,wan2004investigation} the eroded mass per unit area is linearly proportional to the excess shear, i.e.,  $\dot{m}  = -\kappa  (\tau_w-\tau_c)$ where $\kappa$ is the linear proportionality constant. This erosion model effectively results in an increase in the radius of the edges in our network model where $\dot{r} \propto -\kappa r (|q|/r^3 - \tau_c)$. Similar models have further been used in biological models for the growth of vascular networks~\cite{chen2012haemodynamics,hacking1996shear}. In addition to local shear stress, erosion based on local fluid velocity ($v \propto |q|/r^2$) \cite{kudrolli2016evolution}, local pressure difference ($\Delta p \propto |q|/r^4$) \cite{derr2020flow,mahadevan2012flow}, and power dissipation ($P \propto q^2/r^4$ ) ~\cite{steeb2007modeling,marot2012study,sibille2015internal} have also been considered as alternative models. Here, we first focus on a class of erosion dynamics described by $f(q_{ij},r_{ij}) = \alpha |q_{ij}|^m/r_{ij}^n$ where $m,n,\alpha>0$ are constants. 
    This model unifies a diverse set of erosion and clogging dynamics as different values of $m$ and $n$ correspond to different physics of erosion. Later we will generalize the models to include other forms of nonlinearities.''
\end{quote}
}
\\

\Answer{We trust that these results illustrate the predictive power of the simplified model, and highlight the generality of our results.}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% Review # 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{10 mm}
\noindent
\Hline \\
\textbf{Response to Reviewer \#2} \\
\Hline
\\

\Question{This manuscript,``Temporal Evolution of Flow in Pore-Networks: From 
Homogenization to Instability'', presents a model for erosion in porous
media that treats the systems as an evolving flow network. In this
model a unique equation controls the dynamics of the radius of each
channel. The authors carry out a detailed study of the long time
dynamics of the model, identifying a phase transition depending on the
parameters of the model. The network evolves towards a
homogeneous/heterogeneous state as the control parameters cross the
critical line. The paper is sound and well written and I feel it
deserves to be published in one of the journals of the APS. However,
at the moment I am not convinced that the paper meets the necessary
criteria for publication in PRL, therefore I recommend publication in
PRE.\newline}

\Answer{We thank the reviewer for their thoughtful and thorough comments.}

\vspace{0.5cm}
\textbf{Comment 2A}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{This paper follows other works by some of the authors regarding porous media, e.g. references [20] and [31] in the main text. I have
not been able to find a preprint of [31] what makes it difficult to
asses the potential impact of the present work. Also, since the
authors have access to experimental setups, it would greatly improve
this work if they could provide experimental proof of the phase
transition in a real system.\newline}

\Answer{We apologize for unavailability of Ref. [31]. This reference is now published and available online. The reference has been updated with publication details. With regards to the experimental tests, all the authors of the current manuscript are theorists, and experimental studies of this work is out of our scope.}

\vspace{0.5cm}
\textbf{Comment 2B}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{My main concern regarding the phase transition is that I do not
know how general this effect is. For example, how would it change if
you change the boundary conditions? If all the input flow entered
through a node in the center of the network and all the boundary nodes
were sinks, conservation of mass would impose a decaying flow as you
get further apart from the center. Then equation (1) would probably
lead to a heterogeneous system even for $n>3$. Could you still
separate this behavior from the simple argument of equation (3) and
recover the phase transition? Would you have to redefine the order
parameter?\newline}

\Answer{We would like to thank the reviewer for their thoughtful comment. We have now included new numerical tests with the suggested boundary conditions. Particularly, we chose a circular domain, with the central node being the inlet and all the nodes at the outer boundary being outlets. Similar to the transition reported for the square domain, we find a phase transition at the predicted power which shows that our analysis is independent of the geometry. These new numerical simulations are now included in the supplementary material (supplementary material, Fig.~S5), see excerpt below.
Note that in our power-law model the transition depends on the relative values of $m$ and $n$, and not on the magnitude of the flux. Therefore even as one gets further from the inlet, the local criterion for the phase transition remains unchanged, in agreement with our numerical results.

Furthermore, in the revised version we show that our results hold for a broader class of erosion models, as we expand upon in later parts of this reply.}
%
\\

 \Answer{
     $\bullet$ (iii) From supplementary material, section S3:}

\AnswerQ{
\begin{quote}
In addition to the network topology and initial condition, we test the robustness of our results to changes in the boundary condition. We choose a circular domain, with the central node being the inlet and all the nodes at the outer boundary being outlets. Similar to the transition reported for the square
domain, we find a phase transition at the predicted power which shows that our analysis is independent of the geometry (Fig.~\ref{circular-S3-r2}).
\end{quote}
}
% 
\begin{figure}[htp]
     % \centering
      \includegraphics[width = 1.0\textwidth]{../circular.pdf}
     \caption{\add{Erosion in a topologically random 3D network of tubes with a circular topology with $N = 3000 $ randomly distributed nodes and an initial uniform broad distribution of tube diameters randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$. Shown are snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$. We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$. The erosion law is based on $dr/dt = \alpha q/r^n$ where different powers of $n$ correspond to different models of erosion.}}\label{circular-S3-r2}
 \end{figure}

%

\vspace{0.5cm}
\textbf{Comment 2C}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{Although I agree that the order parameter defined in equation (2)
provides useful information, it could mislead the reader to think that for $n=3$ the network structure stays constant (except for some rescaling: the proportion between conductivities is conserved as argued from equation (3)). I can see ``by eye'' that the $t=0$ and the
$n=3$ panels in Fig. 2 are very different. The bigger channels align
with the flow in panel $n=3$, what makes sense from equation (1). How
does one reconcile this change in the structure with the argument
about $C_1/C_2 = cte$ for $n=3$?
\newline}

\Answer{We would like to point out that for $n=3$ the network does not stay the same, since series connections are always moving toward homogenization, while parallel connections are staying in a constant proportion. This results in seeing differences between the statistics of the network at $t=0$ and the evolved network at later stages for $n=3$ (see Fig. 2 in the main text). Additionally, we expect the transition to happen at  approximate $n\approx3$ (see comment 2G for more details). We have now included this point in the main manuscript to avoid confusion.}
%
\\

\Answer{From \p4 of the main text:}
\AnswerQ{
\begin{quote}
    ``It is to be noted that while the flow ratio remains constant for parallel edges, the connection in series are evolving toward homogenization and that is why we find a difference between evolved network for $n=3$ and the network at $t=0$.''
\end{quote}
}

\vspace{0.5cm}
\textbf{Comment 2D}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{Could one collapse the dynamics of the authors' order parameter for
the different $n$ rescaling your time? And the PDF of the radii
rescaling the radius of the channels? In other words, if in Fig. 2. I
let the system evolve longer for $n=2$ and I rescaled all the radii
afterwards, could I get a plot ``equivalent'' to the $n=1$ case? It
would be very neat if one could show that the evolution of the system
for different $n$ and $m$ only translates to a rescaling of time and
mean radius. \newline}

\Answer{Following this comment we attempted to scale the distributions. We find that even if we rescale the probability distribution of diameters and fluid flux, the rescaled PDFs cannot be collapsed together, and depending on values of $m,n$ they follow different statistics (see Fig.~2 in the main text). We have now included the following sentence to the main text to emphasis this point.}
\\

\Answer{From \p3 of the main text:}
\AnswerQ{
\begin{quote}
    ``It is to be noted that the different distributions obtained for different powers of $m,n$ represent different statistics that cannot be collapsed.''
\end{quote}
%
}

\vspace{0.5cm}
\textbf{Comment 2E}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{I think the model could be much richer if it tracked the solute
being eroded (through some solute concentration). That way solute
could be deposited further along the system. In that case you would
have a competing term in equation (1) including the concentration of
solute due to erosion in other parts of the system. This would lead to
a left/right asymmetry in the system of Fig. 2, and I think the system
would not tend to a homogeneous state for $n>3$.\newline}

\Answer{We thank the reviewer for their valuable. Adding solute concentration is indeed a fascinating question and a great direction for future expansion of our work. Our current approach studies erosion models with $dr/dt=f(q,r)$, however, new fields such as solute concentration, $c$, can be added to the model, $dr/dt = f(q,r,c)$, to study erosion in systems with chemical erosion. While this extension is out of our current work's scope,  we have included this point to our conclusion for future directions.}
\\

\Answer{From \p5 of the main text:}
%
\AnswerQ{
\begin{quote}
    ``Additionally, the model studied here could become richer by tracking the solute being eroded through solute concentration using $dr/dt=f(q,r,c)$ where $c$ is the solute concentration, and also allow for solute deposition further along the porous material~[53-55].''
\end{quote}
}

\vspace{0.5cm}
\textbf{Comment 2F}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{I think the authors should be more specific in the introduction and
name a specific system where they think their model (erosion without
deposition/sedimentation or topology changes) applies. \newline}

\Answer{Erosion in saturated granular materials occurs when the shear stress at the wall exceeds the cohesive strength of the solid matter. In the revised version, we study more realistic models with these thresholding effects, including: (i) a  model where the onset of erosion occurs only after a threshold value; (ii) a nonlinear model where erosion starts slowly after a certain threshold value and eventually saturates to a maximum value which is determined by the maximum detachment rate of particles at the pore's boundary. 
 We make predictions for both models using our analysis and find that the analytical predictions agree well with the numerical simulations. These results illustrate the generality of our model and its applicability to a diverse set of physical models.

 We also expanded our introduction of the model to make a better connection with the relevant literature. In the following we attach the relevant excerpts of the main text and the supplementary material.}
 \\

% In a class of such erosion models, the eroded mass per
% unit area is linearly proportional to the excess shear, where it can be shown to be captured by an increase in the radius of the edges proportional to shear stress ($\tau \propto |q|/r^3$). In addition to local shear stress, erosion based on local fluid velocity ($v \propto |q|/r^2$), local pressure difference ($\Delta p \propto |q|/r^4$), and power dissipation ($P \propto q^2/r^4$) by flow have also been considered as alternative models. Here, we consider a general erosion dynamics $dr/dt = f(q,r)$, and identify the condition on $f(q,r)$ with which we can predict the fate of the network (homogenization or channelization). First, by focusing on a class of erosion dynamics $dr/dt = \alpha |q|^m/r^n$, which can capture various physics of erosion, we show different behaviors (channelization or homogenization) are possible to be observed. We then generalize the model to include a thresholding effect, and show, both analytically and numerically, how it only slightly affects the transition boundary. Finally, we test our analysis for a general erosion dynamics, by considering a nonlinear model of erosion law $dr/dt = \alpha \left( \tanh{\left[ \beta(\tau - \tau_0)\right]}+1\right)$ where $\beta$ is the shear rate scale and $\alpha$ is the erosion rate scale. In such models, 
\\
\vspace{4mm}

\Answer{$\bullet$ (i) From section S4 of the supplementary material:}
%

\AnswerQ{     
     \begin{quote}
         ``In order to make our erosion model more realistic, we modify the model as  
        %
        \begin{align}
            \frac{dr}{dt } = \begin{cases} q^m/r^n - \beta & q^m/r^n\geq \beta\\
            0 & q^m/r^n<\beta
            \end{cases} \label{eq:thresh-r2}
        \end{align}
        %
        where $\beta$ is the threshold for the onset of erosion. We pick $\beta = 0.25\langle q^m/r^n\rangle $ and $\beta = 0.9 \langle q^m/r^n\rangle$ corresponding to a small and a large threshold value. In both cases, we ran our simulations for different values of $m$ and $n$, and found that different behaviors of homogenization and channelization persists (see Fig. \ref{fig:figthresh1-r2}). The result can be explained by applying the general condition for the phase transition as discussed in the main text. Following the same argument, it can be shown that the homogenization condition (Eq. 3 in the main text) is equivalent to the condition 
        %
        \begin{align}
        4m-n-1 < -\frac{\beta}{q^m/r^n}.    
        \end{align}
        %
        which can be found using $g(r) = ({\pi \Delta p}/{8\mu L})^{m} r^{m-n} - \beta $ assuming a constant pressure boundary condition. Note that the condition above depends on the value of $q^m/r^n$ which varies over the network edges. Taking the mean value of $q^m/r^n$ to find an average value for the transition condition, the transition line becomes $4m-n=0.75$ and $4m-n=0.1$ for the small and large thresholding value respectively. As a result the thresholding condition slightly shifts the intercept of the transition line while the slope remains the same. In Fig.~\ref{fig:figthresh1-r2}, we plot the new transition lines, where the prediction for the phase boundaries matches well with the simulation results.'' 
 \end{quote}
 }

\begin{figure}[htp]
    \centering
 \includegraphics[width=0.45\textwidth]{../Fig_thres0.25.pdf}
  \includegraphics[width=0.45\textwidth]{../Fig_thresh0.9.pdf}
     \caption{\add{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq. \eqref{eq:thresh-r2} with a small threshold value of $\beta = 0.25\langle q^m/r^n\rangle $ (left figure), and a large threshold value of $\beta = 0.9\langle q^m/r^n\rangle$ at $t=0$. The network is randomly initialized with $50\times 50$ randomly distributed pores. The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using local dynamics model, i.e., $4m-n=0.75$ (left figure), and $4m-n=0.1$ (right figure).} }\label{fig:figthresh1-r2}% 
\end{figure}

\Answer{$\bullet$ (ii) From supplementary material, section S7:}
%

\AnswerQ{
\begin{quote}
    ``As an example of a nonlinear erosion model, we consider a shear-dependent erosion
    %
    \begin{align}
        \frac{dr}{dt} = f(\tau), 
    \end{align}
    %
    where $\tau=\tau(q,r) = 4\mu q/\pi r^3$ is the shear stress at the tube's wall assuming Poiseuille flow. It is to be noted that a shear-dependent erosion model is commonly used in studying erosion  \cite{jager2017channelization,bonelli2011micromechanical,parker2000purely} wherein such models erosion happens linearly proportional to the shear stress at the wall only after a certain threshold value $\tau_0$ (see main text for more information). Such linear models, however, ignore the maximum detachment rate of particles at the pore's boundary which would effectively limit the pore's radius maximum rate of change. To address this, we use a nonlinear erosion model
    %
    \begin{align}
        f(\tau) = \alpha \left( \tanh{\left[ \beta(\tau - \tau_0)\right]}+1\right), 
        \label{eq:sigmoidErosion-r2}
    \end{align}
    %
    where $\beta$ determines the shear rate scale and $\alpha$ determines the erosion rate scale. Note that the erosion rate scale $\alpha$ only affects the timescale at which the final state is reached and has no effect on the pattern formation. Without loss of generality we set $\alpha = 1$. Following the local dynamics model discussion in the main text, one can find that the homogenization condition reduces to 
    %
    \begin{align}
        f(\tau)>\tau \frac{df(\tau)}{d \tau}. 
        \label{eq:sigmoidCondition-r2}
    \end{align}
    %
    Assuming a random network (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}a), the initial values of shear stress at the walls has a  decaying distribution over a large set of values (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}b). 
    %Assuming nonlinear shear dependent erosion model (Eq. \eqref{eq:sigmoidErosion-r2}), and the homogenization condition (Eq. \eqref{eq:sigmoidCondition-r2}), three regions of erosion can be identified: (i) constant erosion region as $\tau\to\infty$: at this region the erosion happens at a constant rate $\lim_{\tau \to \infty} f(\tau) = 2$ and additionally the homogenization condition (Eq.~\eqref{eq:sigmoidCondition-r2}) is satisfied (since $\lim_{\tau \to \infty} f(\tau) = 2$ and $\lim_{\tau \to \infty} f'(\tau) = 0$). The homogenization results here is similar to the constant erosion rate model or $m=0,n=0$ discussed in the main text; (ii)  the slow erosion region as $\tau\to 0$. In this region both $f(\tau)$ and $\tau f'(\tau)$ are close to 0 and erosion happens at a very slow rate; (iii) the finite erosion-rate region near $\tau = \tau_0$, where $f(\tau)$ is an increasing function. In this region $\tau f'(\tau)$ has a maximum at $\beta \tau_0$ with a bandwidth of $1/\beta$. Note that here if $\beta \tau_0 < 1$, then the maximum $\tau f'(\tau)$ does not exceed 1, and the homogenization condition holds true for any $\tau$. As the value of $\tau_0$ increases, the homogenization region moves towards larger values of $\tau$ where smaller values of $\tau$ would result in channelization.  Varying $\beta$ and $\tau_0$ can change the network behavior. 
    To test our local dynamics model, we vary $\beta$ and $\tau_0$ and run three different tests: (i) $\beta=1,\tau_0=1$: For such values of $\beta,\tau$, almost all the tubes are in the homogenization region (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}c) and the network moves toward homogenization (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}d). The final PDF of the network after erosion is further shown in (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}e). (ii) $\beta=1, \tau_0=12$: In this case, the homogenization condition is satisfied at some finite value of shear stress $\tau_0$ where $f(\tau_0) = \tau_0 f(\tau_0)$. As a result, some edges would homogenize, and some would channelize (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}f). Running the simulation over a random network, we find that a finite number of channels form (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}g). The PDF distribution of shear stress at the wall $\tau$ correspondingly becomes bimodal (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}h). (iii) $\beta=1, \tau_0=30$: In this case, almost all the edges in the network are in the channelization regime  (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}i), and performing the simulations we find that indeed one strong single channel is formed (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}j) and the PDF of shear stress $\tau$ shows a clear separation between flow in the channel versus flow in the rest of the system (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r2}k).''
\end{quote}
}

   \begin{figure}[htp]
     % \centering
     \centering \includegraphics[width = 0.8\textwidth]{../sigmoidDelaunay.pdf}
     \caption{\textcolor{blue}{(a) A 2D random network with $N_x=50$ and $N_y=50$ points. (b) The probability distribution function (PDF) of the shear stress for the edges of the network. (c)/(f)/(i) The PDF of the shear stress along with nonlinear erosion law $f(\tau)$ (solid red line) and $\tau f'(\tau)$ (dashed red line). The areas where the homogenization condition (i.e., $f(\tau)>\tau f'(\tau)$) is satisfied are shaded with green color, otherwise, the channelization condition is satisfied and the region is shaded with red color. (d)/(g)/(j) Snapshots of the 2D network after erosion using the nonlinear erosion law shown in the previous row until the average radius of the network is increased to twice its original size. (e)/(h)/(k) The PDF of the shear stress at the walls for the final snapshot of the network shown in the previous row. 
    }}
     \label{SIfig:fig9-sigmoidDelaunay-r2}
 \end{figure}
 \\
 \clearpage

%
\\
\vspace{4mm}

\Answer{$\bullet$ From \p3 and \p4 of the main text:}

%
\AnswerQ{
\begin{quote}
    ``\textit{Local Dynamics Model}-- \addTo understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Figs.~3b-c). First, assuming two cylindrical tubes with radii $r_1,r_2$ in series with a given pressure difference of $\delta p = p_r- p_l$, the radius of each tube changes as $dr_i/dt = f(q,r_i),~i=1,2$ (Fig. 3b) where $q=q_1=q_2$. Without loss of generality we assume $r_1>r_2$. Considering the pressure at the junction between tubes $\tilde p_m = (p_m-p_l)/(p_r-p_l)= C_2/(C_1+C_2)$. Time evolution of the middle pressure then follows % 
    %
    \begin{align}
        \frac{d\tilde{p}_m}{dt} = \gamma (r_1 f(q,r_2)-r_2 f(q,r_1)). 
    \end{align}
    %
    where $\gamma = \sqrt{{2\pi}/{\mu L}}{C_1^{\frac{3}{4}} C_2^{\frac{3}{4}}}/{ (C_1+C_2)^2}$. In the above equation, $r_1=r_2$ is a fixed point solution where $d\tilde p_m/dt =0$ and $p_m=1/2$. Since we assumed $r_1>r_2$, we can see that $\tilde p_m <1/2$, and if ${d\tilde{p}_m}/{dt}>0$, then $\tilde p_m \to 1/2$ and the flow homogenizes. Note that if $f(q,r) = \alpha q^m/r^n$, we find that for any $n>0$ the network homogenizes (see Fig. 3b). Contrary to tubes in series, when the tubes are in parallel (Fig. 3c), the net flow $q$ divides between the two tubes in proportion to their conductivity, i.e., $ q_1/q_2 = C_1/C_2$ which results in $q_1/q = \tilde C_1$, where $\tilde C_1 = C_1/(C_1+C_2)$. Note that the dynamics for each pipe in the parallel case can be simplified to $dr_i/dt = g(r_i)$ where $g(r_i) \equiv f(q_i, r_i)$ in which $q_i = \pi r_i^4 \Delta p / 8\mu L$. Given these dynamics, the evolution of the fluid flow ratio becomes $d(q_1/q)/dt = d \tilde C_1/dt=  \gamma (r_2 g(r_1)-r_1 g(r_2))$. Similarly, it can be seen that  $r_1=r_2$ is a fixed point, where flow is equally distributed between the edges resulting in homogenization. If $d \tilde C_1/dt <0$, then the edge with larger radius has a reduced growth rate while the smaller radius edge has an increasing growth until $r_1=r_2$ is reached. This condition results in homogenization, where both edge's radius increases until the fixed point of $r_1=r_2$ is reached. The condition of $d \tilde C_1/dt<0$ is satisfied when 
    %
    \begin{align}
        \frac{g(r_1)}{g(r_2)}<\frac{r_1}{r_2}, \quad \forall r_1>r_2>0.   \label{Eq3-r2}
    \end{align}
    %
    Note that if $d\left(g(r)/r\right)/dr<0$, then Eq.~\eqref{Eq3-r2} is satisfied, and homogenization would occur.
    The above homogenization condition can further be simplified as $g(r)>g'(r)r$, which can also be obtained directly using a linear stability analysis. Given the homogenization condition $g(r)>g'(r)r$, if the erosion rate is sub-linear locally near the initial radius, the network moves towards homogenization. On the other hand, if the erosion rate is super-linear, we expect the parallel tubes to move away from homogenization and channelization occurs. Applying the power law erosion model with $f(q_{i},r_i)=\alpha q_i^m/r_i^n$, it can be shown that $g(r) \propto  r^{4m-n} $, and therefore $4m-n=1$ results in no change in the flow ratio $q_1/q$ (Fig. 3c$_1$), while $4m-n<1$ results in homogenization condition (Fig.~3c$_2$), and $4m-n>1$ results in channelization (Fig. 3c$_3$). Since a complex network includes both series and parallel connections, it is plausible that the whole network structure will behave in a similar manner, with an approximate transition in the network's behavior at $ m = (n+1)/4$. This result for $m=1$ reduces to a transition at $n=3$. It is to be noted that while the flow ratio remains constant for parallel edges, the connection in series are evolving toward homogenization and that is why we find a difference between evolved network for $n=3$ and the network at $t=0$. Since series connections are always moving toward homogenization, while parallel connections show a phase transition, we expect the phase transition to be at approximately $n\approx 3$, governed by the parallel connections. This observation  is consistent with the numerical simulation results shown in Figs.~2 and 3a (for $m=1$) as well as for additional values of $m$ (Fig.~4). Note, however, that the local dynamics model is only approximate and the numerically observed value of the phase transition happens for a value slightly larger than $n=3$ in Fig.~3. ''
    \end{quote}
}

% \Answer{We believe that the new results illustrate that the phase transition is a general effect, and our analysis using the simplified model has the predictive power of identifying the phase transition condition.}

\vspace{4mm}

\Answer{$\bullet$ From \p2 of the main text:}

%
\AnswerQ{
\begin{quote}
    ``A general constitutive model for erosion can be written as $dr_{ij}/dt = f(q_{ij},r_{ij})$, where $f(q_{ij},r_{ij})$ represents the functional dependence of erosion on the fluid flux $q_{ij}$ and the tube radius $r_{ij}$. Erosion in saturated, granular, porous medium occurs when the shear stress  at the walls $\tau_w$ exerted by the fluid overcomes the cohesive strength of the solid matter $\tau_c$. In a class of erosion models previously studied~\cite{jager2017channelization,ristroph2012sculpting,wan2004investigation} the eroded mass per unit area is linearly proportional to the excess shear, i.e.,  $\dot{m}  = -\kappa  (\tau_w-\tau_c)$ where $\kappa$ is the linear proportionality constant. This erosion model effectively results in an increase in the radius of the edges in our network model where $\dot{r} \propto -\kappa r (|q|/r^3 - \tau_c)$. Similar models have further been used in biological models for the growth of vascular networks~\cite{chen2012haemodynamics,hacking1996shear}. In addition to local shear stress, erosion based on local fluid velocity ($v \propto |q|/r^2$) \cite{kudrolli2016evolution}, local pressure difference ($\Delta p \propto |q|/r^4$) \cite{derr2020flow,mahadevan2012flow}, and power dissipation ($P \propto q^2/r^4$ ) ~\cite{steeb2007modeling,marot2012study,sibille2015internal} have also been considered as alternative models. Here, we first focus on a class of erosion dynamics described by $f(q_{ij},r_{ij}) = \alpha |q_{ij}|^m/r_{ij}^n$ where $m,n,\alpha>0$ are constants. 
    This model unifies a diverse set of erosion and clogging dynamics as different values of $m$ and $n$ correspond to different physics of erosion. Later we will generalize the models to include other forms of nonlinearities.''
\end{quote}
}

\vspace{0.5cm}
\textbf{Comment 2G}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{Minor comment: In Fig. 3 (a) lines do not cross at exactly at $n=3$, is this correct? Do the authors have any intuition for why this
happens?\newline}

%
\\
\Answer{Indeed the transition happens at a value slightly larger than $n=3$. While the parallel connections show a phase transition at $n=3$, the series connections are always moving toward homogenization. Numerically, we expect a phase transition at $n\approx 3$ governed by the parallel connections. In the simulations, we observe a  phase transition at a value slightly larger than $n=3$. We have now included this comment in the main text.} 
\\

%consistent with the homogenization effects of the series connections
\Answer{From \p4 of the main text:}
%

\AnswerQ{\begin{quote}
    ``Since series connections are always moving toward homogenization, while parallel connections show a phase transition, we expect the phase transition to be at approximately $n\approx 3$, governed by the parallel connections. This observation  is consistent with the numerical simulation results shown in Figs.~2 and 3a (for $m=1$) as well as for additional values of $m$ (Fig.~4). Note, however, that the local dynamics model is only approximate and the numerically observed value of the phase transition happens for a value slightly larger than $n=3$ in Fig.~3.''
\end{quote}}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% Review # 3 %%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage 
\vspace{10 mm}
\noindent
\Hline \\
\textbf{Response to Reviewer C} \\
\Hline
\\

\Question{This paper presents 2D and 3D pore-network models of single-phase flow through porous media, involving channel erosion. The erosion rate in a channel is modeled as a function of the flow rate through the channel and the radius of the channel.The manuscript presents an interesting transition in the behaviour of these models from a stabilizing behavior where narrow channels erode more quickly than wider ones (``homogenization'') to an unstable regime where all the flow ends up in a few pathways ``instability''). Overall I judge this to be an interesting paper that may be worth publishing in a journal such as PRFluids, but falls short of the level of impact required for PRL. I explain this below.  The manuscript has many strengths which include: - it's very clearly written and with excellent figures that clearly demonstrate the phenomena being explored; - good numerical modeling that includes 2D and 3D simulations in random and regular network topologies; - results which are universal within the class of models being considered here, being valid 2D and 3D and in regular and random networks; - a clear theory to explain the results using a local analysis,suggesting links between global and local dynamics even in quite complex systems; - links to flow in biological systems
\newline}

\Answer{We thank the reviewer for their careful reading of the manuscript and their constructive
remarks.}

\vspace{0.5cm}
\textbf{Comment 3A}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{The weaknesses in the work include: the physical relevance of the model is not clear, except for the specific biological case ... more specifics in studies of models that are closest to this one are needed, particularly also mentioning the outcomes of those studies. Some of the model's (apparent) weaknesses are being a pure power law, its scaling with pressure is unphysical: the erosion rate in all channels merely increases uniformly with applied pressure, meaning that erosion occurs even at near-zero speed/stress; there is no onset threshold.\newline}

\Answer{We appreciate the reviewers comment. The concern here is similar to comment 2F of Reviewer 2, and we repeat our reply here. Erosion in saturated granular materials occurs when the shear stress at the wall exceeds the cohesive strength of the solid matter. In the revised version, we study more realistic models including: (i) a model where the onset of erosion happens after reaching a threshold value; (ii) a model with a different (nonlinear) functional dependence on shear stress, where erosion starts after a certain threshold and eventually saturates to a maximum value which is determined by the maximal detachment rate of particles at the tube's boundary. We make predictions for both models using our analysis and find that the analytical results agree well with the numerical simulations. These results illustrate the generality of our model in relating to various physical models. (iii) Additionally, we expand our discussion before introducing the model to make a better connection with relevant studies of erosion. 
We believe that these new results illustrate that the phase transition is a general effect, and that our analysis using the local dynamics model has the predictive power of identifying the phase transition condition. In the following we attach the relevant excerpts of the main text and the supplementary material.}
\\

\vspace{4mm}

\Answer{$\bullet$ (i) From section S4 of the supplementary material:}
%

\AnswerQ{     
     \begin{quote}
         ``In order to make our erosion model more realistic, we modify the model as  
        %
        \begin{align}
            \frac{dr}{dt } = \begin{cases} q^m/r^n - \beta & q^m/r^n\geq \beta\\
            0 & q^m/r^n<\beta
            \end{cases} \label{eq:thresh-r3}
        \end{align}
        %
        where $\beta$ is the threshold for the onset of erosion. We pick $\beta = 0.25\langle q^m/r^n\rangle $ and $\beta = 0.9 \langle q^m/r^n\rangle$ corresponding to a small and a large threshold value. In both cases, we ran our simulations for different values of $m$ and $n$, and found that different behaviors of homogenization and channelization persists (see Fig. \ref{fig:figthresh1-r3}). The result can be explained by applying the general condition for the phase transition as discussed in the main text. Following the same argument, it can be shown that the homogenization condition (Eq. 3 in the main text) is equivalent to the condition 
        %
        \begin{align}
        4m-n-1 < -\frac{\beta}{q^m/r^n}.    
        \end{align}
        %
        which can be found using $g(r) = ({\pi \Delta p}/{8\mu L})^{m} r^{m-n} - \beta $ assuming a constant pressure boundary condition. Note that the condition above depends on the value of $q^m/r^n$ which varies over the network edges. Taking the mean value of $q^m/r^n$ to find an average value for the transition condition, the transition line becomes $4m-n=0.75$ and $4m-n=0.1$ for the small and large thresholding value respectively. As a result the thresholding condition slightly shifts the intercept of the transition line while the slope remains the same. In Fig.~\ref{fig:figthresh1-r3}, we plot the new transition lines, where the prediction for the phase boundaries matches well with the simulation results.'' 
 \end{quote}
 }

\begin{figure}[htp]
    \centering
 \includegraphics[width=0.45\textwidth]{../Fig_thres0.25.pdf}
  \includegraphics[width=0.45\textwidth]{../Fig_thresh0.9.pdf}
     \caption{\add{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq. \eqref{eq:thresh-r3} with a small threshold value of $\beta = 0.25\langle q^m/r^n\rangle $ (left figure), and a large threshold value of $\beta = 0.9\langle q^m/r^n\rangle$ at $t=0$. The network is randomly initialized with $50\times 50$ randomly distributed pores. The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using local dynamics model, i.e., $4m-n=0.75$ (left figure), and $4m-n=0.1$ (right figure).} }\label{fig:figthresh1-r3}% 
\end{figure}
%
\\
\vspace{4mm}

\Answer{$\bullet$ (ii) From supplementary material, section S7:}
%

\AnswerQ{
\begin{quote}
    ``As an example of a nonlinear erosion model, we consider a shear-dependent erosion
    %
    \begin{align}
        \frac{dr}{dt} = f(\tau), 
    \end{align}
    %
    where $\tau=\tau(q,r) = 4\mu q/\pi r^3$ is the shear stress at the tube's wall assuming Poiseuille flow. It is to be noted that a shear-dependent erosion model is commonly used in studying erosion  \cite{jager2017channelization,bonelli2011micromechanical,parker2000purely} wherein such models erosion happens linearly proportional to the shear stress at the wall only after a certain threshold value $\tau_0$ (see main text for more information). Such linear models, however, ignore the maximum detachment rate of particles at the pore's boundary which would effectively limit the pore's radius maximum rate of change. To address this, we use a nonlinear erosion model
    %
    \begin{align}
        f(\tau) = \alpha \left( \tanh{\left[ \beta(\tau - \tau_0)\right]}+1\right), 
        \label{eq:sigmoidErosion-r3}
    \end{align}
    %
    where $\beta$ determines the shear rate scale and $\alpha$ determines the erosion rate scale. Note that the erosion rate scale $\alpha$ only affects the timescale at which the final state is reached and has no effect on the pattern formation. Without loss of generality we set $\alpha = 1$. Following the local dynamics model discussion in the main text, one can find that the homogenization condition reduces to 
    %
    \begin{align}
        f(\tau)>\tau \frac{df(\tau)}{d \tau}. 
        \label{eq:sigmoidCondition-r3}
    \end{align}
    %
    Assuming a random network (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}a), the initial values of shear stress at the walls has a  decaying distribution over a large set of values (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}b). 
    %Assuming nonlinear shear dependent erosion model (Eq. \eqref{eq:sigmoidErosion-r2}), and the homogenization condition (Eq. \eqref{eq:sigmoidCondition-r3}), three regions of erosion can be identified: (i) constant erosion region as $\tau\to\infty$: at this region the erosion happens at a constant rate $\lim_{\tau \to \infty} f(\tau) = 2$ and additionally the homogenization condition (Eq.~\eqref{eq:sigmoidCondition-r3}) is satisfied (since $\lim_{\tau \to \infty} f(\tau) = 2$ and $\lim_{\tau \to \infty} f'(\tau) = 0$). The homogenization results here is similar to the constant erosion rate model or $m=0,n=0$ discussed in the main text; (ii)  the slow erosion region as $\tau\to 0$. In this region both $f(\tau)$ and $\tau f'(\tau)$ are close to 0 and erosion happens at a very slow rate; (iii) the finite erosion-rate region near $\tau = \tau_0$, where $f(\tau)$ is an increasing function. In this region $\tau f'(\tau)$ has a maximum at $\beta \tau_0$ with a bandwidth of $1/\beta$. Note that here if $\beta \tau_0 < 1$, then the maximum $\tau f'(\tau)$ does not exceed 1, and the homogenization condition holds true for any $\tau$. As the value of $\tau_0$ increases, the homogenization region moves towards larger values of $\tau$ where smaller values of $\tau$ would result in channelization.  Varying $\beta$ and $\tau_0$ can change the network behavior. 
    To test our local dynamics model, we vary $\beta$ and $\tau_0$ and run three different tests: (i) $\beta=1,\tau_0=1$: For such values of $\beta,\tau$, almost all the tubes are in the homogenization region (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}c) and the network moves toward homogenization (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}d). The final PDF of the network after erosion is further shown in (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}e). (ii) $\beta=1, \tau_0=12$: In this case, the homogenization condition is satisfied at some finite value of shear stress $\tau_0$ where $f(\tau_0) = \tau_0 f(\tau_0)$. As a result, some edges would homogenize, and some would channelize (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}f). Running the simulation over a random network, we find that a finite number of channels form (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}g). The PDF distribution of shear stress at the wall $\tau$ correspondingly becomes bimodal (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}h). (iii) $\beta=1, \tau_0=30$: In this case, almost all the edges in the network are in the channelization regime  (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}i), and performing the simulations we find that indeed one strong single channel is formed (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}j) and the PDF of shear stress $\tau$ shows a clear separation between flow in the channel versus flow in the rest of the system (Fig.~\ref{SIfig:fig9-sigmoidDelaunay-r3}k).''
\end{quote}
}

   \begin{figure}[htp]
     % \centering
     \centering \includegraphics[width = 0.8\textwidth]{../sigmoidDelaunay.pdf}
     \caption{\textcolor{blue}{(a) A 2D random network with $N_x=50$ and $N_y=50$ points. (b) The probability distribution function (PDF) of the shear stress for the edges of the network. (c)/(f)/(i) The PDF of the shear stress along with nonlinear erosion law $f(\tau)$ (solid red line) and $\tau f'(\tau)$ (dashed red line). The areas where the homogenization condition (i.e., $f(\tau)>\tau f'(\tau)$) is satisfied are shaded with green color, otherwise, the channelization condition is satisfied and the region is shaded with red color. (d)/(g)/(j) Snapshots of the 2D network after erosion using the nonlinear erosion law shown in the previous row until the average radius of the network is increased to twice its original size. (e)/(h)/(k) The PDF of the shear stress at the walls for the final snapshot of the network shown in the previous row. 
    }}
     \label{SIfig:fig9-sigmoidDelaunay-r3}
 \end{figure}

\clearpage

\Answer{$\bullet$ (iii) From \p2 of the main text:}

\AnswerQ{
\begin{quote}
    ``A general constitutive model for erosion can be written as $dr_{ij}/dt = f(q_{ij},r_{ij})$, where $f(q_{ij},r_{ij})$ represents the functional dependence of erosion on the fluid flux $q_{ij}$ and the tube radius $r_{ij}$. Erosion in saturated, granular, porous medium occurs when the shear stress  at the walls $\tau_w$ exerted by the fluid overcomes the cohesive strength of the solid matter $\tau_c$. In a class of erosion models previously studied~\cite{jager2017channelization,ristroph2012sculpting,wan2004investigation} the eroded mass per unit area is linearly proportional to the excess shear, i.e.,  $\dot{m}  = -\kappa  (\tau_w-\tau_c)$ where $\kappa$ is the linear proportionality constant. This erosion model effectively results in an increase in the radius of the edges in our network model where $\dot{r} \propto -\kappa r (|q|/r^3 - \tau_c)$. Similar models have further been used in biological models for the growth of vascular networks~\cite{chen2012haemodynamics,hacking1996shear}. In addition to local shear stress, erosion based on local fluid velocity ($v \propto |q|/r^2$) \cite{kudrolli2016evolution}, local pressure difference ($\Delta p \propto |q|/r^4$) \cite{derr2020flow,mahadevan2012flow}, and power dissipation ($P \propto q^2/r^4$ ) ~\cite{steeb2007modeling,marot2012study,sibille2015internal} have also been considered as alternative models. Here, we first focus on a class of erosion dynamics described by $f(q_{ij},r_{ij}) = \alpha |q_{ij}|^m/r_{ij}^n$ where $m,n,\alpha>0$ are constants. 
    This model unifies a diverse set of erosion and clogging dynamics as different values of $m$ and $n$ correspond to different physics of erosion. Later we will generalize the models to include other forms of nonlinearities.''
\end{quote}
}

% \Answer{We believe that the new results illustrate that the phase transition is a general effect, and our analysis using the simplified model has the predictive power of identifying the phase transition condition.}

% \newpage
% \vspace{0.5cm}
% \textbf{Comment 3B}
% \noindent \vspace{-0.2cm}\\ \Hline\\
% \Question{\newline}

% \Answer{To address this point, we ran new numerical simulations with thresholding effect. Particularly, we add a threshold value $\beta$ for the onset of erosion to our dynamics. We pick a small and a large value for the onset of erosion $\beta$. In both cases, we ran our experiments for different values of $m$ and $n$, and we find that the model transition line stay at $n=(m+1)/4$ and does not change (see comment 3A and Fig. \ref{fig:figthresh22}). The new threshhold model and simulations are included in the supplementary material with a reference to them in the main text. In addition to the threshold model, we consider a more realistic nonlinear model for erosion $dr/dt = \alpha \left( \tanh{\left[ \beta(\tau - \tau_0)\right]}+1\right)$ where $\beta$ determines the shear rate scale and $\alpha$ determines the erosion rate scale. In this erosion model, erosion starts slowly after a certain threshold and eventually saturates to a maximum value which is determined by the maximum detachment rate of particles at the pore's boundary. We make predictions with our analysis and find that our approach matches with the numerical simulations. These results proves the generality of our model in predicting the fate of the network for various physical models that are considered in literature. In the following we attach the relevant excerpts of the main text and the supplementary material.
% }
% \\

\vspace{0.5cm}
\textbf{Comment 3B}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{ the existence of a homogenisation regime is surely unphysical, since this regime only occurs in cases where erosion is inversely dependent on fluid velocity - the manuscript's use of flow rate rather
than velocity slightly obscures this fact.
\newline}

\Answer{We thank the reviewer for their comment. The regime corresponding to homogenization corresponds to cases with $m<(n+1)/4$, an example of which would be an erosion proportional to local fluid velocity $dr/dt \propto q/r^2$. We have rephrased the relevant sentence to make this point clear. Additionally, we would like to point out that the homogenization regime correspond to a family of models and erosion proportional to velocity is \emph{e pluribus unum}. In the revised manuscript, we have generalized our model, and found the condition for homogenization within a general class of erosion models following the dynamics $dr/dt=f(q,r)$, see the relevant excerpt from the revised main text attached below.}
\vspace{4mm}

\Answer{$\bullet$ From \p3 and \p4 of the main text:}
%

\AnswerQ{
\begin{quote}
    ``\textit{Local Dynamics Model}-- To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Figs.~3b-c). First, assuming two cylindrical tubes with radii $r_1,r_2$ in series with a given pressure difference of $\delta p = p_r- p_l$, the radius of each tube changes as $dr_i/dt = f(q,r_i),~i=1,2$ (Fig. 3b) where $q=q_1=q_2$. Without loss of generality we assume $r_1>r_2$. Considering the pressure at the junction between tubes $\tilde p_m = (p_m-p_l)/(p_r-p_l)= C_2/(C_1+C_2)$. Time evolution of the middle pressure then follows % 
    %
    \begin{align}
        \frac{d\tilde{p}_m}{dt} = \gamma (r_1 f(q,r_2)-r_2 f(q,r_1)). 
    \end{align}
    %
    where $\gamma = \sqrt{{2\pi}/{\mu L}}{C_1^{\frac{3}{4}} C_2^{\frac{3}{4}}}/{ (C_1+C_2)^2}$. In the above equation, $r_1=r_2$ is a fixed point solution where $d\tilde p_m/dt =0$ and $p_m=1/2$. Since we assumed $r_1>r_2$, we can see that $\tilde p_m <1/2$, and if ${d\tilde{p}_m}/{dt}>0$, then $\tilde p_m \to 1/2$ and the flow homogenizes. Note that if $f(q,r) = \alpha q^m/r^n$, we find that for any $n>0$ the network homogenizes (see Fig. 3b). Contrary to tubes in series, when the tubes are in parallel (Fig. 3c), the net flow $q$ divides between the two tubes in proportion to their conductivity, i.e., $ q_1/q_2 = C_1/C_2$ which results in $q_1/q = \tilde C_1$, where $\tilde C_1 = C_1/(C_1+C_2)$. Note that the dynamics for each pipe in the parallel case can be simplified to $dr_i/dt = g(r_i)$ where $g(r_i) \equiv f(q_i, r_i)$ in which $q_i = \pi r_i^4 \Delta p / 8\mu L$. Given these dynamics, the evolution of the fluid flow ratio becomes $d(q_1/q)/dt = d \tilde C_1/dt=  \gamma (r_2 g(r_1)-r_1 g(r_2))$. Similarly, it can be seen that  $r_1=r_2$ is a fixed point, where flow is equally distributed between the edges resulting in homogenization. If $d \tilde C_1/dt <0$, then the edge with larger radius has a reduced growth rate while the smaller radius edge has an increasing growth until $r_1=r_2$ is reached. This condition results in homogenization, where both edge's radius increases until the fixed point of $r_1=r_2$ is reached. The condition of $d \tilde C_1/dt<0$ is satisfied when 
    %
    \begin{align}
        \frac{g(r_1)}{g(r_2)}<\frac{r_1}{r_2}, \quad \forall r_1>r_2>0.   \label{Eq3-r3}
    \end{align}
    %
    Note that if $d\left(g(r)/r\right)/dr<0$, then Eq.~\eqref{Eq3-r3} is satisfied, and homogenization would occur.
    The above homogenization condition can further be simplified as $g(r)>g'(r)r$, which can also be obtained directly using a linear stability analysis. Given the homogenization condition $g(r)>g'(r)r$, if the erosion rate is sub-linear locally near the initial radius, the network moves towards homogenization. On the other hand, if the erosion rate is super-linear, we expect the parallel tubes to move away from homogenization and channelization occurs. Applying the power law erosion model with $f(q_{i},r_i)=\alpha q_i^m/r_i^n$, it can be shown that $g(r) \propto  r^{4m-n} $, and therefore $4m-n=1$ results in no change in the flow ratio $q_1/q$ (Fig. 3c$_1$), while $4m-n<1$ results in homogenization condition (Fig.~3c$_2$), and $4m-n>1$ results in channelization (Fig. 3c$_3$). Since a complex network includes both series and parallel connections, it is plausible that the whole network structure will behave in a similar manner, with an approximate transition in the network's behavior at $ m = (n+1)/4$. This result for $m=1$ reduces to a transition at $n=3$. It is to be noted that while the flow ratio remains constant for parallel edges, the connections in series are evolving toward homogenization and that is why we find a difference between evolved network for $n=3$ and the network at $t=0$. Since series connections are always moving toward homogenization, while parallel connections show a phase transition, we expect the phase transition to be at approximately $n\approx 3$, governed by the parallel connections. This observation  is consistent with the numerical simulation results shown in Figs.~2 and 3a (for $m=1$) as well as for additional values of $m$ (Fig.~4). Note, however, that the local dynamics model is only approximate and the numerically observed value of the phase transition happens for a value slightly larger than $n=3$ in Fig.~3.''
    \end{quote}
}

\vspace{0.5cm}
\textbf{Comment 3C}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{The model almost seems contrived to exhibit a stability transition, ... The authors appear to have chosen a model based on the ease of analysis, and uncovered a clear and rather universal transition in this model's behavior. However the model lacks fundamental aspects of erosion physics (such as an erosion-onset threshold) and yields a scaling on channel diameter that is too similar to Poiseuille's law for flow. The universal transition in the model appears to a relatively unsurprising consequence of this similarity, and one imagines that the universality would disappear if the model were changed even slightly. It is also unclear whether a homogenization regime would exist at all in any but the most contrived physical
systems.\newline}

\Answer{As mentioned above, in the revised version we have considered a general erosion law $dr/dt=f(q,r)$ and identified the stability condition for the homogeneous phase.  Additionally, as mentioned in our reply to the first comment we significantly extended our analysis to a broad range of models incoporating different forms of nonlinearities. We find that our approach correctly predicts the onset of channeling and the fate of network (see comment 3A). }
\\

\vspace{0.5cm}
\textbf{Comment 3D}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{minimal discussion of experimental results. One set of relevant
results is the transition to wormhole formation that occurs in
carbonic acid flow through limestone formations. The authors may feel
that the erosion studied here is distinct from reactive flow but the
similarities are highly significant. I advise the authors to investigate the reactive transport
literature in more depth. In terms of wormhole formation here is one
publication among many: Ott and Oedai GRL 2016 \\ 
https://doi.org/10.1002/2015GL063582.
\newline}

\Answer{We thank the reviewer for bringing this article to our attention. Since it is very relevant to our study and our model can potentially be expanded to study geologically studies, we have included it in our conclusion for future directions. The relevant part is attached in the following.}
\\

\Answer{$\bullet$ From \p5 of the main text:}
%

\AnswerQ{
\begin{quote}
    ``In the future, it would be exciting to test this and other predictions experimentally on model systems, relying on the technological advances in imaging flow profiles in porous materials, as well as extend the study to the geologically relevant case of chemical erosion \cite{edery2014origins,edery2016characterization}, and wormhole formation in geologic formations during CO$_2$ injection \cite{ott2015wormhole,szymczak2009wormhole}. Additionally, the model studied here could become richer by tracking the solute being eroded through solute concentration using $dr/dt=f(q,r,c)$ where $c$ is the solute concentration, and allow for solute deposition along the porous material~\cite{bizmark2020multiscale,jager2018clogging,jaeger2017mechanism}.''
\end{quote}

}

% \vspace{0.5cm}
% \textbf{Comment 3G}
% \noindent \vspace{-0.2cm}\\ \Hline\\
% \Question{When the strengths and weakness are considered together it is clear that this work does not have the level of impact expected for PRL, particularly when judged against the weaknesses. The work looks suitable for a different journal if there is some addressal of the weaknesses described above.
% \newline}

% \Answer{...   }

% \vspace{0.5cm}
% \textbf{Comment 3H}
% \noindent \vspace{-0.2cm}\\ \Hline\\
% \Question{The authors appear to have chosen a model based on the ease of analysis, and uncovered a clear and rather universal transition in this model's behavior. However the model lacks fundamental aspects of erosion physics (such as an erosion-onset threshold) and yields a scaling on channel diameter that is too similar to Poiseuille's law for flow. The universal transition in the model appears to a relatively unsurprising consequence of this similarity, and one imagines that the universality would disappear if the model were changed even slightly. It is also unclear whether a homogenization regime would exist at all in any but the most contrived physical
% systems..\newline}

% \Answer{In order to address this issue, we ran new numerical experiments to check for the (a) effect of different boundary conditions (see comment 2B), and also (b) adding a threshold for the onset of erosion (see comment 3C), where we observed that the transition is robust to changes in boundary condition, and also thresholding effect moreover to topology and initial disorder that we previously studied in the main manuscript. Additionally, we consider a more general model where erosion is some potentially nonlinear function of a physical quantity, i.e.,
% %
% \begin{align}
%     \frac{dr}{dt}\propto f\left(\frac{q^m}{r^n}\right)
% \end{align}
% %
% where $f(\cdot)$ represents the nonlinear function. We can further expand the right-hand-side of the above relation to find that 
% %
% \begin{align}
%     \frac{dr}{dt}\propto \alpha_1 \left(\frac{q^m}{r^n}\right) +  \alpha_2 \left(\frac{q^m}{r^n}\right)^2 + \alpha_3 \left(\frac{q^m}{r^n}\right)^3 + \cdots
% \end{align}
% %
% where $\alpha_1 q^m/r^n$ is the linear model that we considered here, and the second term shows the nonlinear relation. If all the $\alpha_i$'s are positive, we find that the transition boundary predicted by our model for each term becomes $4m-n=1$, $4m-n=1/2$, $4m-n=1/3$,  and so on. As a result, for all values of $m,n$ such that (a) $4m-n<0$ we obtain homogenization, (b) $4m-n>1$ we obtain channelization, and (c) $0<4m-n<1$ we have a transition region between the two modes. Note that since we are studying erosion, $\alpha_1>0$, while next terms could be negative. If the erosion is physical and we always keep a positive erosion, we find that the lower order terms become more prominent and the transition boundary at $4m-n=1$ holds true. We would like to point out that here we ignored the constant term in the Taylor expansion, since it would result in a constant erosion independent of our physical quantity. Such erosion corresponds to $m=0,n=0$ which in our model is predicted to move toward homogenization. As a result, our model is robust and the transition between homogenization and channelization is expected to be observed depending on different physics of erosion. 
% }

% \vspace{0.5cm}
% \textbf{Comment 3I}
% \noindent \vspace{-0.2cm}\\ \Hline\\
% \Question{The supplemental information is well written and contains a lot of
% interesting and publishable information in its own right. If this
% paper is submitted to another journal without the same page limits
% then it would be great to see the supplementary material included in
% the body of the manuscript.
% .\newline}

% \Answer{We appreciate the referee's comment.}

\vspace{0.5cm}
\textbf{Comment 3E}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{More minor comments/suggestions: the title needs to mention erosion. \newline}

\Answer{We thank the reviewer for their comment. We have now included the word ``erosion'' in the title. The revised  title is}
%
\AnswerQ{
\begin{quote}
    ``Temporal Evolution of Erosion in Pore-Networks: From Homogenization to Instability''
\end{quote}
}

\vspace{0.5cm}
\textbf{Comment 3F}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{The abstract also needs to mention erosion and perhaps emphasize
single-phase flow.\newline}

\Answer{We have now emphasised our assumption of single phase flow for erosion without sedimentation in the abstract. The revised part of abstract reads}
%

\AnswerQ{
\begin{quote}
    ``First,  we  consider  a  class  of  erosion  dynamics  for  a  single  phase  flow  with  no deposition, chemical erosion, or topology changes  assuming a constitutive law depending on flow rate, local velocities,or  shear  stress  at  the  walls.''
\end{quote}
}

\vspace{0.5cm}
\textbf{Comment 3G}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{Is the random network structure based on Poisson point processes or
something more homogeneous?\newline}

\Answer{The random network structure is indeed based on Poisson point process. We have now added this information to the main text on \p1:}
%

\AnswerQ{
\begin{quote}
    ``Initially, we consider a topologically random network of nodes constructed using uniformly distributed nodes {(i.e., a Poisson point process)} in a planar domain connected using Delaunay triangulation.''
\end{quote}
}

\vspace{0.5cm}
\textbf{Comment 3H}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{worth advertising that the simulations are both 2D and 3D (that isn't made clear until well into the manuscript)\newline}

\Answer{We thank the reviewer for their comment. We have now added an emphasis on both 2D and 3D simulations in our abstract. The relevant part of the abstract now reads:}
%
\AnswerQ{
\begin{quote}
    ``We study the dynamics of flow-networks in porous media using a two/three dimensional   pore-network  model.'' 
\end{quote}
}

% \vspace{0.5cm}
% \textbf{Comment 3M}
% \noindent \vspace{-0.2cm}\\ \Hline\\
% \Question{more specifics in studies of models that are closest to this one are needed, particularly also mentioning the outcomes of those studies.\newline}

% \Answer{??????}

\vspace{0.5cm}
\textbf{Comment 3I}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{simple models such as this are relevant for both physical erosion and chemically reactive flow, and the manuscript would benefit from some discussion of the dimensionless numbers for mass transfer in fluid mechanics such as the Peclet and Damkohler numbers.\newline}

\Answer{We would like to thank the reviewer for their thoughtful comment. The Poisoulle flow assumption in the edges requires low Reynolds regime Re$\ll$1 at all times. Additionally, we assume advection to play the major role in erosion and be much stronger than diffusion and chemical reaction. As a result, other dimensionless transport numbers such as P\'eclet number (ratio of advection to diffusion) or Damkohler number (ratio of chemical reaction rate to the transport phenomena rate) should be respectively very large and very small. We have now included this point in our manuscript.}
\\

\Answer{From supplementary material, section S1:}
%
\AnswerQ{
\begin{quote}
    ``Note that the physical assumption of low Reynolds regime Re$\ll$1 at all times ensures that the Poisoulle flow assumption remains valid. Additional dimensionless transport numbers such as the P\'eclet number (ratio of advection to diffusion) or the Damkohler number (ratio of chemical reaction rate to the transport phenomena rate) are assumed to be respectively very large and very small, resulting in advection to be much stronger than diffusion and chemical reaction.  It is to be noted that considering diffusion or chemical reactions might change the dynamics of erosion as it requires tracking a secondary concentration field that might affect the local erosion law.''
\end{quote}
%
}

\clearpage
% \bigbreak

% \bibliographystyle{unsrt}
\bibliography{ref}

\end{document}

### 2022-03-06 CL/CoverLetter.tex
Updates from Overleaf

@@
 
-\signature{\vspace{-10mm}\includegraphics[height=0.4in]{Signature.eps} \\\textbf{Ariel Amir}\\ \textit{Thomas D.
+\signature{% \vspace{-10mm}\includegraphics[height=0.4in]{Signature.eps}
+\\\textbf{Ariel Amir}\\ \textit{Thomas D.
 Cabot Associate Professor of Applied Mathematics and Applied Physics,} \\ \textit{School of Engineering and Applied Sciences,}\\ \textit{Harvard University} \\ \textit{Phone: (617) 495-5818}\\ \textit{Email: arielamir@seas.harvard.edu}}
@@
     \begin{tabular}{l l }
-        \small{Title:}  & \textbf{\small{Temporal Evolution of flow in Porous Materials: From Homogenization to Instability}} \vspace{2mm} \\ 
+        \small{Title:}  & \textbf{\small{Temporal Evolution of flow in Pore-Networks: From Homogenization to Instability}} \vspace{2mm} \\ 
         \small{Authors:}  & \small{Ahmad Zareei$^1$, Pan Deng$^1$, and Ariel Amir$^{1,2}$* (*corresponding author)} \vspace{2mm} \\
@@
 
-We are excited to submit our work, ``Temporal Evolution of flow in Porous Materials: From Homogenization to Instability'' for consideration as an article in the \emph{Physical Review Letters}.
-In this study, we demonstrate that ....
+We are excited to submit our work “Temporal Evolution of flow in Pore-Networks: From Homogenization to Instability" for consideration as an article in Physical Review Letters.
+In this manuscript, we study the temporal evolution of flow in networks under dynamic changes in the pore structure, using a combination of analytical and numerical approaches.
 
-As such, our study suggests that
+Fluid flow through porous materials undergoing a dynamical change in its network of microstructure due to erosion or material deposition is ubiquitous in nature and has numerous environmental and industrial applications.
+Understanding the dynamical change is essential to improve any of the applications.
+In light of the plethora of applications, it is surprising that the evolution of porous structures exposed to erosion and deposition has only been partially understood both theoretically and experimentally.
+
+In our work, we study a generic model of network evolution, that includes previous examples as particular cases.
+We show that depending on the erosion dynamics, the flow statistics may homogenize, stay unaffected, or become unstable and develop channels.
+We quantify the phase transition and using a simple model we identify quantitative criteria to distinguish between these regimes and as a result correctly predicting the fate of
+the network, which we corroborate numerically.
+
+Our results signify the importance of local dynamics and the nature of the feedback mechanism on the long-time global behavior of pore-networks and provide a simple route to connect local erosion dynamics to global bulk behaviors of the pore-network relevant for many environmental, biological, and industrial applications.
+We, therefore, trust that the results will be of interest to the broad readership of PRL.
+We thank you for your consideration and look forward to hearing from you.
 
@@
 
-\textbf{Karen Alim},Max Planck Institute for Dynamics and Self-Organization, G\"ottingen, Germany, \texttt{k.alim@tum.de}
+\textbf{Karen Alim}, Max Planck Institute for dynamics and self-organization, G\"ottingen, Germany, \texttt{k.alim@tum.de}
+
+\textbf{Martin Blunt}, Imperial College London, \texttt{m.blunt@imperial.ac.uk}
+
+\textbf{Harvey Scher}, Weizmann Institute of Science, \texttt{harvey.scher@weizmann.ac.il}
+
+\textbf{Martin Bazant}, Massachusetts Institute of Technology, \texttt{bazant@mit.edu}
+
+\textbf{Arshad Kudrolli}, Clark University, \texttt{akudrolli@clarku.edu}
 

### 2022-03-06 CL/CoverLetterResponse.tex
Updates from Overleaf

%
% harvard-letter.tex - an example latex file to illustrate harvardletter.cls
%
% Copyright 2019, Ahmad Zareei (ahmad@seas.harvard.edu)
%

\documentclass[11pt]{harvardletter}
\usepackage{color}
\usepackage{soul}

\newcommand{\EM}[1]{\noindent \color{cyan} (EM: #1)\normalcolor}
\newcommand{\KB}[1]{{\color{red}{Katia: #1}}}
\newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}

% \name{\includegraphics{./Signature.eps}} % used as signature, if no signature is specified

\signature{% \vspace{-10mm}\includegraphics[height=0.4in]{Signature.eps}
\\\textbf{Ariel Amir}\\ \textit{Thomas D. Cabot Associate Professor of Applied Mathematics and Applied Physics,} \\ \textit{School of Engineering and Applied Sciences,}\\ \textit{Harvard University} \\ \textit{Phone: (617) 495-5818}\\ \textit{Email: arielamir@seas.harvard.edu}}

\date{} % if no date specified, today's date is used

% \subject{This is the subject of the letter} % optional subject line

\begin{document}

\vspace{-14mm}
\begin{letter}{}
  %              {Prof. ... .... \\ 
  %              Harvard University\\ 
  %              Cambridge, MA 02148}
\vspace{-21mm}
\hfill{December 7, 2021}
\vspace{7mm}

    % \begin{tabular}{l l }
    %     \small{Title:}  & \textbf{\small{Temporal Evolution of Eroding Flow in Pore-Networks:}} \\ &  \textbf{\small{From Homogenization to Instability}} \vspace{2mm} \\ 
    %     \small{Authors:}  & \small{Ahmad Zareei$^1$, Deng Pan$^1$, and Ariel Amir$^{1,2}$* (*corresponding author)} \vspace{2mm} \\
    %     \small{Affiliations:} & \small{$^1$Harvard John A. Paulson School of Engineering and Applied Sciences, Harvard University} \\
    %     & \small{$^2$Kavli Institute, Harvard University}
    % \end{tabular}

\vspace{-7mm}

\opening{Dear Editor,}

We would like to appeal the decision to our paper and to re-submit our work ``Temporal Evolution of Erosion in Pore-Networks: From Homogenization to Instability'' for reconsideration as an article in Physical Review Letters. We would like to thank the reviewers for their insightful comments and positive feedbacks, where they found our work ``well written'', ``interesting paper worth publishing'', with ``a clear theory to explain the results'', and ``excellent figures that clearly demonstrate the phenomena being explored''. The main concern raised by the reviewers was the generality of our model and its physical relevance. We have now addressed this issue by expanding our initial model to a very general erosion law and identifying the homogenization condition for general erosion dynamics. We have further expanded the simplified model analysis, tested our analytical predictions by running numerical tests, and showed the agreement between our analysis and the network behavior. We believe the reviewers' main concerns have been addressed.

We would also like to point out that since we have posted our manuscript on the arXiv, we have received positive feedback from the community, e.g., Prof. Karen Alim, an expert in the field, has reached out to us and mentioned that she is now teaching our manuscript in one of her classes at the Technical University of Munich.

The main changes to our manuscript include:
%
\begin{itemize}
    \item Generalization of the results for an arbitrary erosion law.
    \item Identifying the transition condition between homogenization and channelization for a general erosion law.
    \item Showing the prediction power of our local dynamics model for a nonlinear erosion model.
    \item Showing robustness of the phase transition to boundary condition changes and thresholding effects.
\end{itemize}

% We are excited to re-submit our work “Temporal Evolution of Eroding Flow in Pore-Networks: From Homogenization to Instability" for consideration as an article in Physical Review Letters.

% In this manuscript, we study the temporal evolution of flow in networks under dynamic changes in the pore structure, using a combination of analytical and numerical approaches.

% Fluid flow through porous materials undergoing a dynamical change in its network of microstructure due to erosion or material deposition is ubiquitous in nature and has numerous environmental and industrial applications. Understanding the dynamical change is essential to improve any of the applications. In light of the plethora of applications, it is surprising that the evolution of porous structures exposed to erosion and deposition has only been partially understood both theoretically and experimentally.

% In our work, we study a generic model of network evolution, that includes previous examples as particular cases. We show that depending on the erosion dynamics, the flow statistics may homogenize, stay unaffected, or become unstable and develop channels. We quantify the phase transition and using a simple model we identify quantitative criteria to distinguish between these regimes and as a result correctly predicting the fate of
% the network, which we corroborate numerically.

% Our results signify the importance of local dynamics and the nature of the feedback mechanism on the long-time global behavior of pore-networks and provide a simple route to connect local erosion dynamics to global bulk behaviors of the pore-network relevant for many environmental, biological, and industrial applications. We, therefore, trust that the results will be of interest to the broad readership of PRL.  We thank you for your consideration and look forward to hearing from you.

% For reviewers, we suggest the following experts:

% \textbf{Karen Alim}, Max Planck Institute for dynamics and self-organization, G\"ottingen, Germany, \texttt{k.alim@tum.de}

% \textbf{Martin Blunt}, Imperial College London, \texttt{m.blunt@imperial.ac.uk}

% \textbf{Harvey Scher}, Weizmann Institute of Science, \texttt{harvey.scher@weizmann.ac.il}

% \textbf{Martin Bazant}, Massachusetts Institute of Technology, \texttt{bazant@mit.edu}

% \textbf{Arshad Kudrolli}, Clark University, \texttt{akudrolli@clarku.edu}

% \vspace{5mm}

% \underline{\textbf{\small{This material has not been published and is not under consideration for publication elsewhere.}}}

\vspace{5mm}

We thank you for your consideration and look forward to hearing from you.

\vspace{5mm}

\closing{Sincerely,}

% \encl{manuscript.pdf}
% \ps{Please see the enclosed file.}
% \cc{Dr. Ahmad Zareei}

\end{letter}

\end{document}
in

### 2022-03-06 backup_Sep_2_2021/paper_arxiv.tex
Updates from Overleaf

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%%
\documentclass[%
reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
% preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
 % pra,
prl,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{soul}
\usepackage{color}

\newcommand{\hlcyan}[1]{{\sethlcolor{cyan}\hl{#1}}}
\newcommand{\hlred}[1]{{\sethlcolor{red}\hl{#1}}}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}
%

\usepackage{xcolor}
\newcommand{\DP}[1]{\noindent \color{cyan} (DP: #1)\normalcolor}
\newcommand{\AZ}[1]{\noindent \color{purple} (AZ: #1)\normalcolor}
\newcommand{\add}[1]{\noindent \color{blue} #1 \normalcolor}
\newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}
\newcommand{\AM}[1]{\noindent \color{magenta} (AA: #1)\normalcolor}
\def\red{\textcolor{red}}
%
\begin{document}
%
\preprint{APS/123-QED}

\title{Temporal Evolution of Flow in Pore-Networks:\\ From Homogenization to Instability} 
% Force line breaks with \\
% \thanks{A footnote to the article title}%

\author{Ahmad Zareei}
\thanks{A.Z. and D.P. contributed equally.}
\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with 
\author{Deng Pan}%
\thanks{A.Z. and D.P. contributed equally.}
\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with
\author{Ariel Amir}%
\email{arielamir@seas.harvard.edu}
\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break  automatically or can be forced with
% need to figure out how to reference dagger

% \author{}
% \altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with \\
% \author{}%
%  \email{}
% \affiliation{% SEAS, Pierce Hall, Harvard University}%

% \collaboration{MUSO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
We study the dynamics of flow-networks in porous media using a
pore-network model. First, we consider a class of erosion dynamics
assuming a constitutive law depending on flow rate, local velocities,
or shear stress at the walls. We show that depending on the erosion
law, the flow may become uniform and homogenized or
become unstable and develop channels. By defining an order parameter
capturing these different behaviors we show that a phase transition occurs
depending on the erosion dynamics. Using a simple model, we identify
quantitative criteria to distinguish these regimes and {correctly
predict the fate of the network, and discuss the experimental relevance of our result. }
%
% Lastly, we show that the initial stages of pores clogging show analogous behaviors which depends on the clogging dynamics.

% Lastly, we show that pores clogging at the initial stages show analogous behaviors depending on clogging dynamics. % , however, due to the pore throat blockages and changes in the network connections the evolution diverges from its initial trend.

% \begin{description}
% \item[Usage] Secondary publications and information retrieval purposes.
% \item[PACS numbers] May be entered using the \verb+\pacs{#1}+ command.
% \item[Structure] You may use the \texttt{description} environment to structure your abstract; use the optional argument of the \verb+\item+ command to give the category of each item.
% \end{description}
\end{abstract}

%

% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% \tableofcontents %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% \section{Introduction} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% The fluids %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature~\cite{marbach2016pruning,alim2013random,tero2010rules,heaton2010growth} as well as in numerous environmental~\cite{schlesinger1999carbon,winkler1979pore,batzle1992seismic} and industrial applications~\cite{duduta2011semi,sun2019hierarchical,smith2017multiphase,ferguson2012nonequilibrium}.
The disordered pore structure of a porous medium results in heterogeneously distributed fluid flow between the pores.
The boundaries of the pore structure can change dynamically either through erosion or deposition/sedimentation of material. Such heterogeneous changes of the solid structure affect the pore-level fluid flow which in turn affects the dynamical changes to the pore structure. This feedback mechanism along with the initial heterogeneous fluid flow makes it difficult to understand and predict the porous media behavior. Nonetheless, an understanding of the dynamical change is essential to improve any of the porous media applications where the pore network changes over time, including groundwater remediation and precipitation of minerals in rocks~\cite{rad2013pore}, biofilm growth in water filtration, and protective filters \cite{herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous}, as well as enhanced oil recovery with polymer flooding \cite{lake2014fundamentals,parsa2020origin}, or water-driven erosion \cite{schorghofer2004spontaneous,mahadevan2012flow}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
% \section{Methods \& Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\begin{figure}[h]
    % \centering
    \includegraphics[width = 0.45\textwidth]{Fig1.pdf}
    % \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}. The scale in the bottom left shows $1$mm. The network of pores and throats is highlighted in blue. In the network model, the pores are represented with nodes and the throats between pores are approximated with tubes connecting the pores together. (b) Schematic of a topologically random network (i); and a structured diamond grid network (ii). The edge diameters in both networks are randomly distributed. The inset figure shows the conservation of mass at each node. (c) The universal probability distribution function (PDF) of fluid flux for a topologically random (in blue) or diamond network (red) with a highly disordered random network including uniform (triangles), log-normal (circles), and truncated normal (plus) distributions.}
    \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}. The scale in the bottom left shows $1$mm. The network of pores and throats is highlighted in blue. In the network model, the pores are represented with nodes and the throats between pores are approximated with tubes. (b) Schematic of a topologically random network. The edge diameters representing the pore-throats are randomly distributed. (c) A structured diamond grid network with a random distribution of edge diameters. (d) The universal probability density function (PDF) of fluid flux for a topologically random (blue) or diamond-grid (red) network of nodes (red) with a random distribution of edge diameter sampled from a uniform (triangles), log-normal (circles), or truncated normal (plus) distribution. }    
    \label{fig:fig1}
\end{figure}
%
\emph{Network approach}-- We approach this long-standing problem using a network model for the porous structure\cite{fatt1956network, blunt2013pore,stoop2019disorder,bryant1993network,blunt2013pore,dong2009pore,blunt2013pore,blunt1995pore,alim2017local}.
% Before discussing the dynamics, we briefly review the results of flow in random networks.
The network of pores inside the solid structure is connected together through pore-throats that effectively show resistance to the fluid flow between the pores (Fig.~\ref{fig:fig1}a). Network-based models have been shown to successfully capture key properties of fluid flow in a porous material such as the probability distribution of fluid flux~\cite{alim2017local}, the permeability scaling during clogging~\cite{shima2021}, or the first fluidized path in a porous structure~\cite{fraggedakis_chaparian_tammisola_2021}.  We consider low-Reynolds fluid flow through the porous network. The fluid flow rate at the edge connecting pores $i$ and $j$ is given by $ q_{ij}  = C_{ij}(p_i - p_j)$ where $p_i,p_j$ represent pressures at neighboring nodes. Poiseuille's law implies that the conductance $C_{ij} = {\pi r_{ij}^4}/{8 \mu l_{ij}}$, with $r_{ij}$ and $l_{ij}$ the edge's radius and length. Initially, we consider a topologically random network of nodes constructed using uniformly distributed nodes in a planar domain connected using Delaunay triangulation (Fig. \ref{fig:fig1}b). The pore-throats or radii of the edges are considered as independent and identically distributed random variables and fluid flow in the edges are obtained by solving for conservation of mass at all nodes given a pressure difference between the nodes on the boundaries (supplementary material S1). Independent of edge radius distribution, the probability density function (PDF) of normalized fluid flux is well described by a single exponential distribution shown in Fig. \ref{fig:fig1}d. The exponential distribution of fluid flux is similar to earlier experimental and numerical measurements~\cite{datta2013spatial,shima2021,alim2017local} and is a universal feature in random porous networks. Considering a structured diamond-grid of pores (Fig. \ref{fig:fig1}c) which significantly simplifies the geometrical complexity of the network and allows for analytical derivation, one finds that the PDF of normalized fluid flux remains unchanged for various distributions suggesting robustness to network topology (Fig.~\ref{fig:fig1}d and supplementary materials S2). In the following, we will study, analytically and numerically, how this universal distribution evolves as the network is modified based on a local constitutive law.

\textit{Network evolution}-- The degradation of the solid skeleton (i.e., erosion) or deposition of material on the pore throats (i.e., clogging) in the network of pores is modeled by the change (increase or decrease) in the radii of the edges connecting the pores which translates into changes in the flow resistance between the pores. The rate of change of the radii depends on local fluid flow parameters, however, the exact dependence is unknown. Different models have been used where erosion is assumed to be locally proportional to shear stress at the walls \cite{jager2017channelization,ristroph2012sculpting,hacking1996shear,wan2004investigation}, power dissipation by flow~\cite{steeb2007modeling,marot2012study,sibille2015internal}, or local pressure difference~\cite{derr2020flow,mahadevan2012flow}. We use a general constitutive  model which may implement a diverse set of erosion or clogging dynamics and thus allows us to study the effect of different laws in a unified way.

\begin{figure}[!h]
    % \centering
    % \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
    \includegraphics[width = 0.48\textwidth]{Fig2_.pdf}
    \caption{Erosion in a network of pipes. The initial condition is shown with the label $t=0$ in the first row. Each row afterward corresponds to the {simulation result at $t=T$ where  $\langle r_{t=T}\rangle=2r_0$ with $r_0 = \langle r_{t=0}\rangle$}. The erosion law is based on Eq. \eqref{eq:erosion-law}  {where $m=1$ and different powers of $n$ correspond to different models of erosion}. {The first, second, and third columns are snapshots of the pore network, the PDF of normalized fluid flux $q/\langle q \rangle$, and  the PDF of normalized radius $r/\langle r\rangle$ at $t=T$, respectively}.} \label{fig:fig2}
\end{figure}
%
%

In order to model erosion in porous media, we consider the abrasion in the throats leading to decrease in the tube radii. We model the dynamics as 
%
\begin{align}
   \frac{dr_{ij}}{dt} = \alpha  \frac{|q_{ij}|^m}{r_{ij}^n}, \label{eq:erosion-law}
\end{align}
%
{where $m,n,\alpha$ are constants. Different values of $m$ and $n$ along with a positive $\alpha>0$ correspond to different erosion physics (analogously, $\alpha<0$ corresponds to clogging). Particularly, the erosion when $m=1$ and  (i) $n=0$ depends on the amount of flux $q_{ij}$ passing through the edge; (ii) $n=2$ depends on the local velocities; (iii) $n=3$ depends on the shear force at the boundary of the throat.} {Additionally, $m=2$ and $n=6$ corresponds to models considered in biological transport networks where the radii changes are {proportional to the square of shear stress at the boundary walls}~\cite{hu2013adaptation,ronellenfitsch2016global}.} 
We consider a randomly initialized network with disordered diameters obtained from a uniform distribution (supplementary material S1). 
The flow inside the pores, PDF of flux in the tubes, and PDF of tube radii are shown in Fig. \ref{fig:fig2}. We assume a constant pressure difference between the left and the right boundaries. In each time step, we increase the local radii of the tubes based on the erosion law introduced in Eq. \eqref{eq:erosion-law}, assuming erosion is linear in the flux ($m=1$). Later we will consider the network behavior for other powers of $m$.
We continue the simulations until $\langle r \rangle = 2 r_0$. 
The results of the simulations for different values of $n$ are shown in Fig. \ref{fig:fig2}. When $n=1$ or $2$,  the network develops channels. In such cases, the flow is dominated by a few edges carrying most of the flow while the rest of the network carries almost no flow. This is also reflected by a bimodal radii distribution. In contrast, when $n=3$  (corresponding to erosion linear in shear), we find that despite the 
increase in tube radii and absolute flow rates, the normalized flow distribution is hardly affected, maintaining its original exponential form. Increasing $n$ to larger values, $n=4$ or $5$, we find that the flow pattern in the network moves towards homogenization. Here, the tail of the normalized fluid flux distribution retracts and the coefficient of variation reduces. Similarly, the PDF of the tube diameters becomes narrower.

{We found that similar results uphold in a 3d random tube network as well as a 2d topologically ordered (diamond grid) network, illustrating the robustness of the results to the network topology (Figs. S2 and S3). Similarly, we found that the results hold also when using an initial narrow distribution of diameters (Fig. S4), showing robustness with respect to the strength of the disorder.}

\textit{Phase transition and order parameter}-- {To quantify the transition of the network between the channeling instability and homogenization, we define an order parameter % $\mathcal{O}$ 
%
\begin{align}
\mathcal{O} = \frac{1}{N-1} \left( N - \frac{\left( \sum_{ij} q^2_{ij}\right)^2}{ \sum_{ij} q^4_{ij}}\right),
\end{align}
%
where $N$ is the number of edges.} {The order parameter defined here is inspired by the participation ratio (PR) employed to quantify the localization of an eigenstate in the analysis of Anderson localization\cite{kramer1993localization}.}  The order parameter $\mathcal{O}=0 $ when the flux through every edge is identical. On the other hand, when fluid flux becomes highly localized with only a few edges with non-zero flux, $\mathcal{O}\to 1$.  We numerically calculated the  order parameter $\mathcal{O}$ for {randomly initialized networks, averaged over 20 different realization}. 
The results are shown in Fig. \ref{fig:fig3}a for different amounts of erosion measured by the increase in the average diameter $\langle r\rangle /r_0$. As shown in 
 Fig. \ref{fig:fig3}c, at $n\approx 3$ the order parameter, remains unchanged; however for $n>3$ the order parameter moves toward zero, where the flow becomes more uniform, and for $n<3$ the order parameter goes toward unity, where channels are developed. This indicates a phase transition at $n=3$ in the long-time behavior of the network.
%

\begin{figure}[!h]
    % \centering
     \includegraphics[width = 0.45\textwidth]{Fig3.pdf}
    \caption{ (a) Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig. \ref{fig:fig2} for different powers of $n$ with $m=1$ plotted over time. (b,c) Tubes in series (b) or parallel (c) configuration. 
    The tube radius dynamically change with the erosion law (Eq. \eqref{eq:erosion-law}). When the tubes are in series, for any $m,n$, (b$_1$) the normalized pressure at the middle junction between the tubes $\tilde p_m = (p_m - p_l)/(p_r-p_l)$ approaches $1/2$ which results in a homogenized pressure distribution. 
    When the tubes are in parallel, for (c$_1$) $m=(n+1)/4$, the flow ratio between the pipes does not change over time; (c$_2$)  $m<(n+1)/4$ the flow distributes between the tubes equally and  $q_1/(q_1+q_2) \to 1$ which results in the homogenization of the network; (c$_3$) $m>(n+1)/4 $, the entire flow eventually passes through one of the tubes, and channeling occurs. }\label{fig:fig3}
\end{figure}

\textit{Simplified Model}-- {To understand the transition in network behavior during erosion for different powers of $n$, we focus on a simplified model with only two tubes in parallel or series (Figs. \ref{fig:fig3}b-c). First, assuming two cylindrical tubes with radii $r_1,r_2$ in series, the flow is the same for the two tubes $ q_1 = q_2 = q$ (Fig. \ref{fig:fig3}b). The radius of each tube then changes as $dr_i/dt = \alpha q^m /r_i^n$ where $i=1,2$. 
As a result, we find that the conductivity of each tube changes as $dC_i/dt \propto q^m C_i^{(3-n)/4}$, where each tube's conductivity increases. Considering the pressure at the junction between tubes, we find that it moves toward the average value of pressure on both sides (Fig. \ref{fig:fig3}(b$_1$)). Contrary to tubes in series, when the tubes are in parallel (Fig. \ref{fig:fig3}c), the flow divides between the two tubes in proportion to their conductivity, i.e., $q_1/q_2 = C_1/C_2$. Since each tube's radius changes as $dr_i/dt = \alpha q^m_i/r_i^n$, the evolution of the fluid flow ratio becomes 
% %% 
\begin{align}
\frac{d}{dt}\left( \frac{C_1}{C_2}\right) \propto  \frac{C_1}{C^{n/4+1}_2} \left( \left( \frac{C_1}{C_2}\right)^{m-\frac{n+1}{4}} - 1 \right). \label{eq:dyn-paral}
\end{align}
%%
When $m=(n+1)/4$ in Eq. \eqref{eq:dyn-paral}, the right-hand-side vanishes and as a result the flow ratio $C_1/C_2$ remains constant (Fig. \ref{fig:fig3}c$_1$). However, when $m \neq (n+1)/4$, we find that $C_1/C_2 = 1$ is an equilibrium point. When $m<(n+1)/4$ this equilibrium solution is stable and the flow moves toward homogenization (Fig. \ref{fig:fig3}c$_2$); however, when $m>(n+1)/4$ this equilibrium solution becomes unstable and the solution moves toward $C_1/C_2 \to 0$ or $\infty$ which means that the entire flow passes through one of the tubes (Fig. \ref{fig:fig3}c$_3$). In summary, when the tubes are in series any erosion law makes flow become more uniform; however, when the tubes are in parallel depending on the powers $m,n$ the flow in the tubes can move toward becoming more uniform ($m<(n+1)/4$), maintain the same ratio ($m=(n+1)/4$), or move toward instability and channel development ($m>(n+1)/4$). Since a complex network includes both series and parallel connections, it is plausible that the whole network structure will behave in a similar manner, with a transition in the networks behavior at $ m = (n+1)/4 $.
This observation  is consistent with the numerical simulation results shown in Figs. \ref{fig:fig2} and \ref{fig:fig3}a (for $m=1$) as well as for additional values of $m$ (Fig. \ref{fig:fig4}).}
%

\textit{Analysis of generalized model}-- So far we focused on erosion dynamics with $m=1$ (Eq. \eqref{eq:erosion-law}) since it directly corresponds to erosion laws of interest, i.e. an erosion rate with a linear dependence to fluid-flux, velocity, or shear-rate at the walls. Considering $m=2$ in Eq. \eqref{eq:erosion-law}, our model aligns with the transport optimization problem in biological networks~\cite{ronellenfitsch2016global,corson2010fluctuations,hu2013adaptation}. Previous works have suggested that in the context of biological transport networks, the network is optimized to minimize its dissipation energy with regards to some constraint (such as constant material or metabolic cost).  Interestingly, the gradient descent method utilized to find the minimal energy configurations maps to Eq. \eqref{eq:erosion-law} with $m=2$, albeit with additional regularizing terms. While under the dynamics we study here erosion will occur indefinitely, in these biological network models a minimal energy configuration exists due to these additional constraints. Nonetheless, the minimal energy configurations manifest a phase transition reminiscent of the one we observe in our model.
To test the role of the parameter $m$ in our model, we simulated the general form of erosion dynamics (Eq. \eqref{eq:erosion-law}).
The simulation results for a randomly initialized network for different powers of $m$ and $n$ are shown in Fig. \ref{fig:fig4}, where each box shows the final snapshot of the network eroded with the corresponding $m$ and $n$.  We further compare the network's simulation result with the prediction of our simplified model for the fate of the network for each pair of $m,n$. The simplified model's prediction is shown using the bounding box color (red for channelization and green for homogenization) in Fig. \ref{fig:fig4} (cf. Fig. S5 in supplementary material showing the heat map for the average change in the order parameter). Additionally, the dashed black line in Fig. \ref{fig:fig4} shows the simplified model's prediction for the boundary between network's transition to homogeneity or channelization (i.e., $m = (n+1)/4$). Although the simplified model is based on the erosion dynamics of two edges in a parallel or series configuration, it still correctly predicts the fate of the network with the complex topology for different values of $m$ and $n$, and captures the boundary separating channelization/homogenization.

\begin{figure}[!h]
    \centering
    \includegraphics[width = 0.45\textwidth]{Fig4.pdf}
    \caption{{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq. \eqref{eq:erosion-law}}. The network is randomly initialized with $50\times 50$ randomly distributed pores. The bounding box color shows the prediction of the simplified  model for the fate of the network: homogenization (blue) or channelization (red). The dashed black line shows the transition boundary between channelization instability and homogenization obtained using simplified model, i.e., $m=(n+1)/4$.}\label{fig:fig4}
\end{figure}

In the case of clogging, the initial dynamics can similarly be captured using our model, however, due to the change in the connectivity of the network, our simplified model cannot extend to large time behaviors (supplementary material S5).

%
\textit{Conclusion}-- {We analyzed the dynamics of porous networks during erosion.  We showed that depending on the form of the erosion law (namely, its dependence on flux and tube radius) the network can either move towards homogenization or towards developing a channeling instability.  We elucidated the physical origin of this phase transition and how it is achieved using a simplified model. Our results highlight the importance of local dynamics and feedback mechanisms in the network's path toward its asymptotic global behavior \cite{ronellenfitsch2016global,corson2010fluctuations,katifori2010damage,hu2013adaptation,ocko2015feedback},  and allow us to infer the local dynamics using large scale observations. As a result, our model can be used as a bulk behavior proxy for determining the local dynamics of erosion in a system~\cite{mahadevan2012flow}. Interestingly, our results indicates that an erosion model that is local and linearly dependent on shear rate cannot result in channelization (since $m=1,n=3$ and $m=(n+1)/4$). However, we note that if the dependence on the shear rate is non-linear, it will qualitatively map to our model albeit with renormalized values of $n$ and $m$: e.g., a power-law dependence on shear rate with exponent $s$ would lead to $m =s$, $n = 3 s$, implying channelization when $s>1$. In the future, it would be exciting to test this and other predictions experimentally on model systems, relying on the technological advances in imaging flow profiles in porous materials, as well as extend the study to the geologically relevant case of chemical erosion \cite{edery2014origins,edery2016characterization}. 
}

\begin{acknowledgments}
We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery,  Eleni Katifori, and Chris Rycroft
for useful discussions.
\end{acknowledgments}

\bibliography{ref.bib}
\appendix

\newpage
\onecolumngrid

\renewcommand{\thepage}{S\arabic{page}}
\setcounter{page}{1}
\renewcommand{\thesection}{S\arabic{section}}
\setcounter{section}{0}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\setcounter{equation}{0}
\def\lp{\left(}
\def\rp{\right)}
\def\lb{\left[}
\def\rb{\right]}

{\huge \textbf{Supplementary Material}}

\section{S1. Simulation algorithm}
\label{s1}
%
In our simulations, we tested two types of networks: (i) a topologically ordered (diamond-grid) network, (ii) a topologically random network (2d and 3d). 
% In the diamond-grid network, we choose 100 nodes in the horizontal direction $N_x=100$ and 50 nodes in the vertical direction $N_y=50$ which in total results in $20,000$ edges in the network (see \cite{githubrepo}). 
The 2d random network is created using uniformly distributed points with on average $N_x\times N_y$ nodes in the horizontal and vertical directions where the randomly distributed points are connected using a Delaunay triangulation. The 3d random network similarly is obtained by a uniform distribution of $N_x\times N_y \times N_z$ points in space, where the the points are connected using Voronoi cell initialization. The diameter of each edge is sampled from either a uniform distribution with $\mathcal{U}(1,14)$, log-normal distribution with $\mu=3,\sigma=0.48$, or truncated normal distribution with $\mathcal{N}(\mu=7.0,\sigma=3.6)$, where all of the distributions have a coefficient of variation close to $0.5$.  An external pressure is considered between the left-most nodes and the rightmost nodes ($p_\text{left}=10,p_\text{right}=0$). For each edge, assuming a Poiseuille flow, the fluid flux  $q$ and pressure difference $\delta P_e$ are related through $q_e = C_e \delta P_e$, where $C_e = \pi r^4_e/8\mu L_e$,  $L_e$ is the length of the tube, and $\mu$ is the viscosity of the fluid. We define $\vec{q}_e$ as the vector of fluid flux through all the edges, and as a result $\vec{q}_e = \mathbf{C} \mathbf{D}\vec{P}_n$ where $\vec{P}_n$ is the vector of pressure at all the nodes, $\mathbf{D}$ is the transpose of the network's oriented incidence matrix, and $\mathbf{C}$ is the diagonal matrix of edge conductances $\mathbf{C}_e = \text{diag} \left( C^{(1)}_e, C^{(2)}_e, \cdots,C^{(N_e)}_e\right)$. The orientation (or direction) of an edge is arbitrary selected, and it only determines the positive direction for the fluid flow in that edge. Next, we  use conservation of mass at the nodes to solve for the network pressure/flux at the nodes/edges. The conservation of mass at each node is 
%
\begin{align}
    \vec{q}_n = \mathbf{D}^\top \mathbf{C} \mathbf{D} \vec{P}_n, \label{eq:governeing}
\end{align}
%
where $\vec{q}_n$ is the vector of total incoming flow to each node. The total incoming flow to an internal node is zero inside the network due to the conservation of mass, and can only be non-zero at the boundary nodes. Without loss of generality, we renumber the boundary nodes to $1,2,\cdots, N_{B}$, where $N_B$ shows the total number of nodes at the boundary. We re-partition Eq. \eqref{eq:governeing} to obtain

\begin{align}
 \begin{bmatrix} {\mathbf{D}_{b}}^\top \mathbf{C} {\mathbf{D}_{b}}  & \vline &    {\mathbf{D}_{b}}^\top \mathbf{C} {\mathbf{D}_{n}}\\ \hline   
    {\mathbf{D}_{n}}^\top \mathbf{C} {\mathbf{D}_{b}} & \vline & {\mathbf{D}_{n}}^\top \mathbf{C} {\mathbf{D}_{n}}
    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ P_{N_B} \\  \hline  P_{N_B+1} \\ \vdots \\ P_{N_n}
    \end{bmatrix} = \begin{bmatrix} q^{BC}_1 \\ q^{BC}_2 \\ \vdots \\ q^{BC}_{N_B} \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \to 
    \begin{bmatrix} 
    \mathbf{A}_{bb} & \mathbf{A}_{bn} \\
    \mathbf{A}_{nb} & \mathbf{A}_{nn}       
    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ P^{BC}_{N_B} \\ \hline  P_{N_B+1} \\ \vdots \\ P_{N_n}
    \end{bmatrix} = \begin{bmatrix} q^{BC}_1 \\ q^{BC}_2 \\ \vdots \\ q^{BC}_{N_B}  \\ \hline  0 \\ \vdots \\ 0\end{bmatrix}, 
\end{align}
%
where $\mathbf{A}_{st} = \mathbf{D}^\top_s \mathbf{C}\mathbf{D}^\top_t$ and  $s,t\in\left\{a,b\right\}$. The first $N_B$ elements of the pressure vector (i.e., $P_1, \cdots, P_{N_B}$) represent the pressure at the boundary nodes and the rest represent the pressure for the internal nodes. In summary the above equations can be written as a combination of two set of linear equations 
%
\begin{subequations}\label{main-solve-eq}
\begin{align}
%     \begin{cases} 
  & \mathbf{A}_{bb} \vec{P}_{BC} + \mathbf{A}_{bn}  \vec{P} = \vec{q}_{BC}, \label{maina} \\
& \mathbf{A}_{nb}\vec{P}_{BC} +  \mathbf{A}_{nn} \vec{P} = 0. \label{mainb}
%     \end{cases} 
    % \\ \mathbf{A}_{nn} \ket{P_n} =- \mathbf{A}_{nb}\ket{P_{BC}} 
    % \label{eq:main-network}
 \end{align}
\end{subequations}
%
where $\vec{P}_{BC} = [P^{BC}_1, \cdots, P^{BC}_{N_B}]^\top$ is the boundary nodes pressure vector, $\vec{q}_{BC} = [q^{BC}_1, \cdots, q^{BC}_{N_B}]^\top$ is the boundary nodes incoming fluid flux vector, and $\vec{P} = [P_{N_B+1}, \cdots, P_{N_n}]^\top$ is the unknown pressure vector for the rest of the nodes. If the pressure at the boundary is given,  we can use Eq. \eqref{mainb} to solve for the internal pressure values $\vec{P}$, and then use Eq. \eqref{maina} to find the required flux at the boundary nodes $\vec{q}_{BC}$. However, if fluid flux vector at the boundary nodes is given (i.e., $\vec{q}_{BC}$ is known), we need to simultaneously solve  Eqs. \eqref{maina} and \eqref{mainb} to find the boundary pressure vector  $\vec{P}_{BC}$ and internal nodes pressure vector $\vec{P}$. In either case, solving Eq. \eqref{main-solve-eq}  results in the nodes' pressure vector and also the fluid flux vector at the boundary nodes. The fluid flux at each edge can then be calculated using  $\vec{q}_e=\mathbf{C}_e \mathbf{D} \vec{P}_n$. Next, given the flux at each edge  $q_e$, we increase (decrease) the edge radius under erosion (clogging) using 
%
\begin{align}
    \frac{dr_e}{dt} \propto \pm  \frac{q^m_e}{r_e^n},
\end{align}
%
and re-iterate the process to solve for the new fluid flux vector. We use a simple forward Euler for time integration. For each iteration, we choose the time step $dt$ so that $\max(dr_e) = 0.1 r_0$, where $r_0$ is the smallest radius among all edges. 
% Note that $r_{ij} (t+\delta t)  = r_{ij} (t)  + (\alpha \delta t)  q_{ij} (t)/ r^n_{ij} (t) $, where the coefficient $\alpha \delta t$ is chosen such that the maximum change in the radius at each time step is smaller than one-tenth  of the smallest tube's radius i.e. $\max (\Delta r_{ij}) \leq r_\text{min}/10$ of the smallest radius at the initial configuration.  
This condition guarantees that at each step a small amount of material is eroded and there is no sudden change in the network. We further test the convergence by decreasing $\max(\Delta r_{ij})$ to half and we observe that the average relative change in the flux vector is $\approx 1.2\%$, and the PDFs remain intact without any notable change. The network size for the 2d/3d networks is $N_x=100,N_y=50$/$N_x=50,N_y=12, N_z=12$ unless mentioned otherwise. In either case, the network has an order of $10^3$ edges. The code is publicly available in a GitHub repository \cite{githubrepo}.

%
% \begin{figure}[h]
%     % \centering
%     \includegraphics[width = 0.75\textwidth]{Figs/Fig2_random-low.png}
%     \caption{Ahmad's version: Erosion in a topologically random network of pipes. The first row shows the initial condition at $t=0$. Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$. The erosion law is based on Eq. (1) in the main text where different powers of $n$ correspond to different models of erosion. The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}
% \end{figure}
%

\section{S2. Analytical results for fluid flux EXP-tail PDF in a Diamond Network}
\label{s2}
%
% \label{sec:analytical}
%
As described in the main text, the PDF of flow in a topologically disordered network of tubes takes the same form  as in a  structured diamond grid. For completeness, here we repeat the derivation of Refs. \cite{liu1995force,coppersmith1996model,alim2017local} which  show that the observed exponential distribution of fluid flux can be described using a mean-field approach on a structured grid. Basically, the random distribution of the diameters along with the conservation of mass in the network are the two main ingredients resulting in an exponential tail distribution. In a diamond grid, the incoming flow to a node is redistributed among the outgoing edges (since fluid mass is conserved). Due to the randomness in the tube's diameter, the redistribution of the incoming flow to a node between the outgoing edges is random variable.  This model for the flow can be mapped one to one to the problem of force fluctuations in a bead pack \cite{liu1995force,coppersmith1996model,alim2017local} as shown in Fig. \ref{grid-result}. In a bead pack, the force at each layer is redistributed to the next layer where the total force exerted on the next layer should equal to that of the previous layer. 
%
\begin{figure}[h]
  \centering
  \includegraphics[width=.75\textwidth]{FigS1.pdf} % grid-analytica
  \caption{(a) Schematic of a  diamond grid network of tubes. The incoming flow to each node is redistributed among the outgoing edges. The thickness of the lines shows the fluid flux transferred through that edge. (b) Schematic diagram showing beads (represented with nodes) and their contacts to the neighboring sites (represented with edges). The thickness of the edges show the force transferred through that contact.} \label{grid-result}
\end{figure}
%
Given the above conditions, the flow at layer $L+1$ at node $j$ can be obtained as 
%
\begin{align}
  q(L+1,j) = \sum_i w_{ij} q(L,i) = w_{i,i+1} q(L,i+1) + w_{i,i} q(L,i), \label{total-flow}
\end{align}
%
where $w_{ij}$ shows the weights by which the flow is redistributed, and $\sum_{j} w_{ij} = 1$ since the total fluid flux is conserved. 
% Next, we assume that the weights $w_{ij}$ are drawn from a distribution $\eta(w)$. Since $\eta(w)$ is a distribution, then $\int \eta(w) dw = 1$. Furthermore, since $\sum_jw_{ij} = 1$, we can conclude that
%
%\begin{align}
%  \sum_j w_{ij}=1 \to N {E}[w_{ij}] = 1 \to E[w_{ij}] = 1/N \to {\int w\eta(w) dw = 1/N}
% \end{align}
%
Assuming a general distribution of for the weights, $\eta(w)$, we can use a mean-field approximation to find the distribution of $q$ at the layer $L$, i.e., $p_L(q)$, as 
%%
\begin{align}
  p_L (q) = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dq_j p_{L-1}(q_j)\right\} \times \delta \left( \sum_j w_j q_{j} - q \right),
\end{align}
%
% The only approximation in the above equation is that we neglect the possible correlation between the values of $q$ among ancestors. 
where $N$ is the number of outgoing edges (e.g., in our structured diamond grid $N=2$) and $\delta(\cdot)$ is the Dirac delta function. 
% The constraint that $q$'s emanating downward should add up to one is accounted for through the definition of $\eta(w)$. 
% The values of flux at each layer $q(L,i)$ are not independent for neighboring sites; however, in our mean-field approximation, we ignore such correlations.  
Taking the Laplace transform of the above equation and defining $\tilde p(s) \equiv \int_0^{\infty} p(q) e^{-qs} dq$ one obtains
%
% \begin{align}
 % \tilde P(s) & \equiv \int_0^{\infty} P(Q) e^{-Qs} dQ\\
%   \xrightarrow{\int_0^{\infty} (\cdot) e^{-Qs} dQ}  P (Q) & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp \\
%   \tilde P(s) & = \int_0^{\infty} \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp e^{-Qs}dQ \\
  %            & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j e^{-\sum w_{j}Q_{j}} P(Q_j)\right\}   \\
%              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \tilde P(s w_j) \right\} \\
%   & = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N}
% \end{align}
%
% Or in summary
%
\begin{align}
  {\tilde P_L(s) = \lp  \int_0^1 d w \eta(w) \tilde P_{L-1}(s w)  \rp^{N}}. \label{eq:main-laplace}
\end{align}
%
The above equation gives a recursive relation for the Laplace transformed of fluid flux PDF, $\tilde P_L(s)$, where it gradually converges to a distribution $\tilde P(s)$ from which the PDF of fluid flux can be obtained. Solving the above equation for a structured diamond grid network, one finds that the converged PDF of the fluid flux becomes $p(q) = 4q\exp(-2q)$ \cite{liu1995force,coppersmith1996model,alim2017local}, which is an exponential tailed distribution.

% \begin{figure}[h]
    % \centering
%     \includegraphics[width=0.75\textwidth]{Figs/randomNetworkErosion3.pdf}
%     \caption{Deng's version: Erosion in a topologically random network of pipes. The initial condition is shown with the label $t=0$ in the first row. Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius. The erosion law is based on Eq. (1) in the main text where different powers of $n$ correspond to different models of erosion. The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}% 
% \end{figure}

\newpage
\section{S3. Robustness to topology and initial condition}
\label{s3}
% 
In order to check the robustness of our result with respect to the topology of the network, we run our simulations on a three-dimensional random network with Voronoi cell initialization of nodes in space (Fig. \ref{SIfig:fig2-3d}), and also for a two dimensional topologically ordered network with a diamond grid (Fig. \ref{fig:fig2-diamond}), where  both networks are initialized with a uniform random distribution for the diameter of the tubes. We find that regardless of the topology of the network, an erosion dynamics with $n>3$ results in a homogenized network, while $n<3$ results in the channelization instability. We further check the effect of initial randomness on the fate of the network. We use a two-dimensional diamond-grid network with a narrow uniform initial distribution of tube diameters around an average diameter $d_0$ with only a very small variation ($3\%$), i.e., the tube diameters are sampled from $\mathcal{U}(d_0(1-\epsilon), d_0(1+\epsilon))$. We again find that for the networks with $n<3$ channels are formed, while for $n>3$ the network stays homogenized (Fig. \ref{SI_figs4:fig:fig2}).  
%
\begin{figure}[htp]
     % \centering
      \includegraphics[width = 1.0\textwidth]{FigS2.pdf}
     \caption{Erosion in a topologically random 3D network of tubes with $N_x=20, N_y=12, N_z=12$ points for Voronoi cell initialization and an initial uniform broad distribution of tube diameters randomly sampled from $\mathcal{U}(1,14)$. Snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$ are shown. We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$. The erosion law is based on Eq. (1) in the main text where different powers of $n$ correspond to different models of erosion.}\label{SIfig:fig2-3d}
 \end{figure}
%
\begin{figure}[htp]
    % \centering
 \includegraphics[width=0.75\textwidth]{FigS3.pdf} % Fig2-Sdiamond.pdf
     \caption{Erosion in a diamond grid network with $N_x=100, N_y=50$ randomly distributed nodes and an initially broad  distribution of tube diameter randomly sampled from $\mathcal{U}(1,14)$. The initial condition is shown with the label $t=0$ in the first row. Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius. The erosion law is based on Eq. (1) in the main text where different powers of $n$ correspond to different models of erosion. The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2-diamond}% 
\end{figure}
%
\begin{figure}[htp]
    % \centering
 \includegraphics[width=0.72\textwidth]{FigS4.pdf}
     \caption{Erosion in a structured diamond grid network with $N_x=50, N_y=50$ and an initially narrow distribution of tube diameters randomly sampled from  $\mathcal{U}\left(d_0(1-\epsilon), d_u(1+\epsilon)\right) $ where  $d_0$ is the average diameter and $\epsilon=0.03$. The initial condition is shown with the label $t=0$ in the first row. Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius. The erosion law is based on Eq. (1) in the main text where different powers of $n$ correspond to different models of erosion. The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{SI_figs4:fig:fig2}% 
\end{figure}

\newpage 
\newpage 
\newpage
\section{S4. Average Change in the  Order parameter}
\label{s4}
%
In order to quantify the network behavior shown in Fig. 4, we calculate the change in the order parameter for different $m,n$ averaged over 100 simulations with different random initial conditions, and the heat-map results are shown in Fig.~\ref{fig:fig4_SI-2}. The positive or negative change in the order parameter shows the network's change toward homogenization or channelization. The boundary between the two phases (homogenization and channelization) calculated using the simple model introduced in the main text is shown with a solid black line here, and it can be seen that it agrees well with the order parameter change. 
%
\begin{figure}[htp]
    % \centering
    \includegraphics[width = 0.70\textwidth]{FigS5.pdf}
    \caption{The heat map for the average change in the order parameter corresponding to the networks shown in Fig. 4 of the main text. The order parameter shown in the heat map here is an average of 100 different simulations with different random initialization of tube diameters. The black line shows the boundary between two phases calculated using the model introduced in the main text.}\label{fig:fig4_SI-2}
\end{figure}

\section{S5. Clogging Dynamics}
\label{s5}
% 
% \textit{}-- 
Besides erosion, another change in the network is the deposition/sedimentation of material on the boundary walls of the porous material. We refer to this dynamical change a ``clogging'' process as opposed to erosion. Contrary to erosion, the clogging behavior may cause some edges to block which effectively alters the network of connectivity and network behavior. This change in the connection between nodes through edges getting blocked can drastically alter porous structure behavior, e.g., causes a huge difference between effective and true porosity \cite{shima2021}. Despite the drastic change of network with blockages, we can still focus on the \textit{initial} change in the order parameter. The derivative of order parameter can be written as 
%
\begin{align}
    \frac{d\mathcal{O}}{dt} = \sum_{ij} \sum_{kl} \frac{\partial \mathcal{O}}{\partial q_{ij}} \frac{\partial q_{ij}}{\partial C_{kl}}  \frac{\partial C_{kl}}{\partial t} \label{eq:order-derivative}
\end{align}
%
where the last term changes sign from erosion to clogging, i.e., $\partial C_{kl}/\partial t = \pm \alpha \pi q^m_{kl} /r_{kl}^{n-3}\mu l_{kl}$ for erosion and clogging respectively. As a result, the magnitude of change in the order parameter equals that of erosion. Note that in Eq. \eqref{eq:order-derivative}, the second term depends on the network topology, and pore throat clogging results in the change of network topology at later times.
% The pore throat blockages results in the divergent of clogging results from just the negative of erosion. 
At short times, however, similar to the erosion, a phase transition exists at $n=3$. When  $n<3$ the network moves toward homogenization during the clogging process and when $n>3$ the flow moves toward the development of channeling instability. At later times, this initial trend, however, might not hold true due to the aforementioned complex changes in the connectivity network during the clogging process.

% \clearpage
% \bibliography{ref}% Produces the bibliography via BibTeX.

\end{document}

### 2022-03-06 backup_Sep_2_2021/prl_paper.tex
Updates from Overleaf

--- 2022-03-06 backup_Sep_2_2021/paper_arxiv.tex
@@
 
-Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature~\cite{marbach2016pruning,alim2013random,tero2010rules,heaton2010growth} as well as in numerous environmental~\cite{schlesinger1999carbon,winkler1979pore,batzle1992seismic} and industrial applications~\cite{duduta2011semi,sun2019hierarchical,smith2017multiphase,ferguson2012nonequilibrium}.
+Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature~\cite{marbach2016pruning,alim2013random,tero2010rules,heaton2010growth} as well as in numerous environmental~\cite{schlesinger1999carbon,winkler1979pore,batzle1992seismic,cohen2015mechanisms} and industrial applications~\cite{duduta2011semi,sun2019hierarchical,smith2017multiphase,ferguson2012nonequilibrium}.
 The disordered pore structure of a porous medium results in heterogeneously distributed fluid flow between the pores.
@@
 \bibliography{ref.bib}
+
 \appendix
 
-\newpage
-\onecolumngrid
-
-\renewcommand{\thepage}{S\arabic{page}}
-\setcounter{page}{1}
-\renewcommand{\thesection}{S\arabic{section}}
-\setcounter{section}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
-\setcounter{figure}{0}
-\renewcommand{\theequation}{S\arabic{equation}}
-\setcounter{equation}{0}
-\def\lp{\left(}
-\def\rp{\right)}
-\def\lb{\left[}
-\def\rb{\right]}
-
-{\huge \textbf{Supplementary Material}}
-
-\section{S1. Simulation algorithm}
-\label{s1}
-%
-In our simulations, we tested two types of networks: (i) a topologically ordered (diamond-grid) network, (ii) a topologically random network (2d and 3d). 
-% In the diamond-grid network, we choose 100 nodes in the horizontal direction $N_x=100$ and 50 nodes in the vertical direction $N_y=50$ which in total results in $20,000$ edges in the network (see \cite{githubrepo}).
-The 2d random network is created using uniformly distributed points with on average $N_x\times N_y$ nodes in the horizontal and vertical directions where the randomly distributed points are connected using a Delaunay triangulation.
-The 3d random network similarly is obtained by a uniform distribution of $N_x\times N_y \times N_z$ points in space, where the the points are connected using Voronoi cell initialization.
-The diameter of each edge is sampled from either a uniform distribution with $\mathcal{U}(1,14)$, log-normal distribution with $\mu=3,\sigma=0.48$, or truncated normal distribution with $\mathcal{N}(\mu=7.0,\sigma=3.6)$, where all of the distributions have a coefficient of variation close to $0.5$.
-An external pressure is considered between the left-most nodes and the rightmost nodes ($p_\text{left}=10,p_\text{right}=0$).
-For each edge, assuming a Poiseuille flow, the fluid flux  $q$ and pressure difference $\delta P_e$ are related through $q_e = C_e \delta P_e$, where $C_e = \pi r^4_e/8\mu L_e$,  $L_e$ is the length of the tube, and $\mu$ is the viscosity of the fluid.
-We define $\vec{q}_e$ as the vector of fluid flux through all the edges, and as a result $\vec{q}_e = \mathbf{C} \mathbf{D}\vec{P}_n$ where $\vec{P}_n$ is the vector of pressure at all the nodes, $\mathbf{D}$ is the transpose of the network's oriented incidence matrix, and $\mathbf{C}$ is the diagonal matrix of edge conductances $\mathbf{C}_e = \text{diag} \left( C^{(1)}_e, C^{(2)}_e, \cdots,C^{(N_e)}_e\right)$.
-The orientation (or direction) of an edge is arbitrary selected, and it only determines the positive direction for the fluid flow in that edge.
-Next, we  use conservation of mass at the nodes to solve for the network pressure/flux at the nodes/edges.
-The conservation of mass at each node is
-%
-\begin{align}
-    \vec{q}_n = \mathbf{D}^\top \mathbf{C} \mathbf{D} \vec{P}_n, \label{eq:governeing}
-\end{align}
-%
-where $\vec{q}_n$ is the vector of total incoming flow to each node.
-The total incoming flow to an internal node is zero inside the network due to the conservation of mass, and can only be non-zero at the boundary nodes.
-Without loss of generality, we renumber the boundary nodes to $1,2,\cdots, N_{B}$, where $N_B$ shows the total number of nodes at the boundary.
-We re-partition Eq.
-\eqref{eq:governeing} to obtain
-
-\begin{align}
- \begin{bmatrix} {\mathbf{D}_{b}}^\top \mathbf{C} {\mathbf{D}_{b}}  & \vline &    {\mathbf{D}_{b}}^\top \mathbf{C} {\mathbf{D}_{n}}\\ \hline   
-    {\mathbf{D}_{n}}^\top \mathbf{C} {\mathbf{D}_{b}} & \vline & {\mathbf{D}_{n}}^\top \mathbf{C} {\mathbf{D}_{n}}
-    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ P_{N_B} \\  \hline  P_{N_B+1} \\ \vdots \\ P_{N_n}
-    \end{bmatrix} = \begin{bmatrix} q^{BC}_1 \\ q^{BC}_2 \\ \vdots \\ q^{BC}_{N_B} \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \to 
-    \begin{bmatrix} 
-    \mathbf{A}_{bb} & \mathbf{A}_{bn} \\
-    \mathbf{A}_{nb} & \mathbf{A}_{nn}       
-    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ P^{BC}_{N_B} \\ \hline  P_{N_B+1} \\ \vdots \\ P_{N_n}
-    \end{bmatrix} = \begin{bmatrix} q^{BC}_1 \\ q^{BC}_2 \\ \vdots \\ q^{BC}_{N_B}  \\ \hline  0 \\ \vdots \\ 0\end{bmatrix}, 
-\end{align}
-%
-where $\mathbf{A}_{st} = \mathbf{D}^\top_s \mathbf{C}\mathbf{D}^\top_t$ and  $s,t\in\left\{a,b\right\}$.
-The first $N_B$ elements of the pressure vector (i.e., $P_1, \cdots, P_{N_B}$) represent the pressure at the boundary nodes and the rest represent the pressure for the internal nodes.
-In summary the above equations can be written as a combination of two set of linear equations
-%
-\begin{subequations}\label{main-solve-eq}
-\begin{align}
-%     \begin{cases} 
-  & \mathbf{A}_{bb} \vec{P}_{BC} + \mathbf{A}_{bn}  \vec{P} = \vec{q}_{BC}, \label{maina} \\
-& \mathbf{A}_{nb}\vec{P}_{BC} +  \mathbf{A}_{nn} \vec{P} = 0. \label{mainb}
-%     \end{cases} 
-    % \\ \mathbf{A}_{nn} \ket{P_n} =- \mathbf{A}_{nb}\ket{P_{BC}} 
-    % \label{eq:main-network}
- \end{align}
-\end{subequations}
-%
-where $\vec{P}_{BC} = [P^{BC}_1, \cdots, P^{BC}_{N_B}]^\top$ is the boundary nodes pressure vector, $\vec{q}_{BC} = [q^{BC}_1, \cdots, q^{BC}_{N_B}]^\top$ is the boundary nodes incoming fluid flux vector, and $\vec{P} = [P_{N_B+1}, \cdots, P_{N_n}]^\top$ is the unknown pressure vector for the rest of the nodes.
-If the pressure at the boundary is given,  we can use Eq.
-\eqref{mainb} to solve for the internal pressure values $\vec{P}$, and then use Eq.
-\eqref{maina} to find the required flux at the boundary nodes $\vec{q}_{BC}$.
-However, if fluid flux vector at the boundary nodes is given (i.e., $\vec{q}_{BC}$ is known), we need to simultaneously solve  Eqs.
-\eqref{maina} and \eqref{mainb} to find the boundary pressure vector  $\vec{P}_{BC}$ and internal nodes pressure vector $\vec{P}$.
-In either case, solving Eq.
-\eqref{main-solve-eq}  results in the nodes' pressure vector and also the fluid flux vector at the boundary nodes.
-The fluid flux at each edge can then be calculated using  $\vec{q}_e=\mathbf{C}_e \mathbf{D} \vec{P}_n$.
-Next, given the flux at each edge  $q_e$, we increase (decrease) the edge radius under erosion (clogging) using
-%
-\begin{align}
-    \frac{dr_e}{dt} \propto \pm  \frac{q^m_e}{r_e^n},
-\end{align}
-%
-and re-iterate the process to solve for the new fluid flux vector.
-We use a simple forward Euler for time integration.
-For each iteration, we choose the time step $dt$ so that $\max(dr_e) = 0.1 r_0$, where $r_0$ is the smallest radius among all edges.
-% Note that $r_{ij} (t+\delta t)  = r_{ij} (t)  + (\alpha \delta t)  q_{ij} (t)/ r^n_{ij} (t) $, where the coefficient $\alpha \delta t$ is chosen such that the maximum change in the radius at each time step is smaller than one-tenth  of the smallest tube's radius i.e.
-$\max (\Delta r_{ij}) \leq r_\text{min}/10$ of the smallest radius at the initial configuration.
-This condition guarantees that at each step a small amount of material is eroded and there is no sudden change in the network.
-We further test the convergence by decreasing $\max(\Delta r_{ij})$ to half and we observe that the average relative change in the flux vector is $\approx 1.2\%$, and the PDFs remain intact without any notable change.
-The network size for the 2d/3d networks is $N_x=100,N_y=50$/$N_x=50,N_y=12, N_z=12$ unless mentioned otherwise.
-In either case, the network has an order of $10^3$ edges.
-The code is publicly available in a GitHub repository \cite{githubrepo}.
-
-%
-% \begin{figure}[h]
-%     % \centering
-%     \includegraphics[width = 0.75\textwidth]{Figs/Fig2_random-low.png}
-%     \caption{Ahmad's version: Erosion in a topologically random network of pipes.
-The first row shows the initial condition at $t=0$.
-Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
-The erosion law is based on Eq.
-(1) in the main text where different powers of $n$ correspond to different models of erosion.
-The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}
-% \end{figure}
-%
-
-\section{S2. Analytical results for fluid flux EXP-tail PDF in a Diamond Network}
-\label{s2}
-%
-% \label{sec:analytical}
-%
-As described in the main text, the PDF of flow in a topologically disordered network of tubes takes the same form  as in a  structured diamond grid.
-For completeness, here we repeat the derivation of Refs.
-\cite{liu1995force,coppersmith1996model,alim2017local} which  show that the observed exponential distribution of fluid flux can be described using a mean-field approach on a structured grid.
-Basically, the random distribution of the diameters along with the conservation of mass in the network are the two main ingredients resulting in an exponential tail distribution.
-In a diamond grid, the incoming flow to a node is redistributed among the outgoing edges (since fluid mass is conserved).
-Due to the randomness in the tube's diameter, the redistribution of the incoming flow to a node between the outgoing edges is random variable.
-This model for the flow can be mapped one to one to the problem of force fluctuations in a bead pack \cite{liu1995force,coppersmith1996model,alim2017local} as shown in Fig.
-\ref{grid-result}.
-In a bead pack, the force at each layer is redistributed to the next layer where the total force exerted on the next layer should equal to that of the previous layer.
-%
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=.75\textwidth]{FigS1.pdf} % grid-analytica
-  \caption{(a) Schematic of a  diamond grid network of tubes.
-The incoming flow to each node is redistributed among the outgoing edges.
-The thickness of the lines shows the fluid flux transferred through that edge.
-(b) Schematic diagram showing beads (represented with nodes) and their contacts to the neighboring sites (represented with edges).
-The thickness of the edges show the force transferred through that contact.} \label{grid-result}
-\end{figure}
-%
-Given the above conditions, the flow at layer $L+1$ at node $j$ can be obtained as 
-%
-\begin{align}
-  q(L+1,j) = \sum_i w_{ij} q(L,i) = w_{i,i+1} q(L,i+1) + w_{i,i} q(L,i), \label{total-flow}
-\end{align}
-%
-where $w_{ij}$ shows the weights by which the flow is redistributed, and $\sum_{j} w_{ij} = 1$ since the total fluid flux is conserved. 
-% Next, we assume that the weights $w_{ij}$ are drawn from a distribution $\eta(w)$.
-Since $\eta(w)$ is a distribution, then $\int \eta(w) dw = 1$.
-Furthermore, since $\sum_jw_{ij} = 1$, we can conclude that
-%
-%\begin{align}
-%  \sum_j w_{ij}=1 \to N {E}[w_{ij}] = 1 \to E[w_{ij}] = 1/N \to {\int w\eta(w) dw = 1/N}
-% \end{align}
-%
-Assuming a general distribution of for the weights, $\eta(w)$, we can use a mean-field approximation to find the distribution of $q$ at the layer $L$, i.e., $p_L(q)$, as 
-%%
-\begin{align}
-  p_L (q) = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dq_j p_{L-1}(q_j)\right\} \times \delta \left( \sum_j w_j q_{j} - q \right),
-\end{align}
-%
-% The only approximation in the above equation is that we neglect the possible correlation between the values of $q$ among ancestors. 
-where $N$ is the number of outgoing edges (e.g., in our structured diamond grid $N=2$) and $\delta(\cdot)$ is the Dirac delta function. 
-% The constraint that $q$'s emanating downward should add up to one is accounted for through the definition of $\eta(w)$. 
-% The values of flux at each layer $q(L,i)$ are not independent for neighboring sites; however, in our mean-field approximation, we ignore such correlations.  
-Taking the Laplace transform of the above equation and defining $\tilde p(s) \equiv \int_0^{\infty} p(q) e^{-qs} dq$ one obtains
-%
-% \begin{align}
- % \tilde P(s) & \equiv \int_0^{\infty} P(Q) e^{-Qs} dQ\\
-%   \xrightarrow{\int_0^{\infty} (\cdot) e^{-Qs} dQ}  P (Q) & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp \\
-%   \tilde P(s) & = \int_0^{\infty} \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp e^{-Qs}dQ \\
-  %            & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j e^{-\sum w_{j}Q_{j}} P(Q_j)\right\}   \\
-%              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \tilde P(s w_j) \right\} \\
-%   & = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N}
-% \end{align}
-%
-% Or in summary
-%
-\begin{align}
-  {\tilde P_L(s) = \lp  \int_0^1 d w \eta(w) \tilde P_{L-1}(s w)  \rp^{N}}. \label{eq:main-laplace}
-\end{align}
-%
-The above equation gives a recursive relation for the Laplace transformed of fluid flux PDF, $\tilde P_L(s)$, where it gradually converges to a distribution $\tilde P(s)$ from which the PDF of fluid flux can be obtained.
-Solving the above equation for a structured diamond grid network, one finds that the converged PDF of the fluid flux becomes $p(q) = 4q\exp(-2q)$ \cite{liu1995force,coppersmith1996model,alim2017local}, which is an exponential tailed distribution.
-
-% \begin{figure}[h]
-    % \centering
-%     \includegraphics[width=0.75\textwidth]{Figs/randomNetworkErosion3.pdf}
-%     \caption{Deng's version: Erosion in a topologically random network of pipes.
-The initial condition is shown with the label $t=0$ in the first row.
-Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius.
-The erosion law is based on Eq.
-(1) in the main text where different powers of $n$ correspond to different models of erosion.
-The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}%
-% \end{figure}
-
-\newpage
-\section{S3. Robustness to topology and initial condition}
-\label{s3}
-% 
-In order to check the robustness of our result with respect to the topology of the network, we run our simulations on a three-dimensional random network with Voronoi cell initialization of nodes in space (Fig.
-\ref{SIfig:fig2-3d}), and also for a two dimensional topologically ordered network with a diamond grid (Fig.
-\ref{fig:fig2-diamond}), where  both networks are initialized with a uniform random distribution for the diameter of the tubes.
-We find that regardless of the topology of the network, an erosion dynamics with $n>3$ results in a homogenized network, while $n<3$ results in the channelization instability.
-We further check the effect of initial randomness on the fate of the network.
-We use a two-dimensional diamond-grid network with a narrow uniform initial distribution of tube diameters around an average diameter $d_0$ with only a very small variation ($3\%$), i.e., the tube diameters are sampled from $\mathcal{U}(d_0(1-\epsilon), d_0(1+\epsilon))$.
-We again find that for the networks with $n<3$ channels are formed, while for $n>3$ the network stays homogenized (Fig.
-\ref{SI_figs4:fig:fig2}).
-%
-\begin{figure}[htp]
-     % \centering
-      \includegraphics[width = 1.0\textwidth]{FigS2.pdf}
-     \caption{Erosion in a topologically random 3D network of tubes with $N_x=20, N_y=12, N_z=12$ points for Voronoi cell initialization and an initial uniform broad distribution of tube diameters randomly sampled from $\mathcal{U}(1,14)$.
-Snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$ are shown.
-We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
-The erosion law is based on Eq.
-(1) in the main text where different powers of $n$ correspond to different models of erosion.}\label{SIfig:fig2-3d}
- \end{figure}
-%
-\begin{figure}[htp]
-    % \centering
- \includegraphics[width=0.75\textwidth]{FigS3.pdf} % Fig2-Sdiamond.pdf
-     \caption{Erosion in a diamond grid network with $N_x=100, N_y=50$ randomly distributed nodes and an initially broad  distribution of tube diameter randomly sampled from $\mathcal{U}(1,14)$.
-The initial condition is shown with the label $t=0$ in the first row.
-Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius.
-The erosion law is based on Eq.
-(1) in the main text where different powers of $n$ correspond to different models of erosion.
-The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2-diamond}%
-\end{figure}
-%
-\begin{figure}[htp]
-    % \centering
- \includegraphics[width=0.72\textwidth]{FigS4.pdf}
-     \caption{Erosion in a structured diamond grid network with $N_x=50, N_y=50$ and an initially narrow distribution of tube diameters randomly sampled from  $\mathcal{U}\left(d_0(1-\epsilon), d_u(1+\epsilon)\right) $ where  $d_0$ is the average diameter and $\epsilon=0.03$.
-The initial condition is shown with the label $t=0$ in the first row.
-Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius.
-The erosion law is based on Eq.
-(1) in the main text where different powers of $n$ correspond to different models of erosion.
-The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{SI_figs4:fig:fig2}%
-\end{figure}
-
-\newpage 
-\newpage 
-\newpage
-\section{S4. Average Change in the  Order parameter}
-\label{s4}
-%
-In order to quantify the network behavior shown in Fig.
-4, we calculate the change in the order parameter for different $m,n$ averaged over 100 simulations with different random initial conditions, and the heat-map results are shown in Fig.~\ref{fig:fig4_SI-2}.
-The positive or negative change in the order parameter shows the network's change toward homogenization or channelization.
-The boundary between the two phases (homogenization and channelization) calculated using the simple model introduced in the main text is shown with a solid black line here, and it can be seen that it agrees well with the order parameter change.
-%
-\begin{figure}[htp]
-    % \centering
-    \includegraphics[width = 0.70\textwidth]{FigS5.pdf}
-    \caption{The heat map for the average change in the order parameter corresponding to the networks shown in Fig.
-4 of the main text.
-The order parameter shown in the heat map here is an average of 100 different simulations with different random initialization of tube diameters.
-The black line shows the boundary between two phases calculated using the model introduced in the main text.}\label{fig:fig4_SI-2}
-\end{figure}
-
-\section{S5. Clogging Dynamics}
-\label{s5}
-% 
-% \textit{}-- 
-Besides erosion, another change in the network is the deposition/sedimentation of material on the boundary walls of the porous material.
-We refer to this dynamical change a ``clogging'' process as opposed to erosion.
-Contrary to erosion, the clogging behavior may cause some edges to block which effectively alters the network of connectivity and network behavior.
-This change in the connection between nodes through edges getting blocked can drastically alter porous structure behavior, e.g., causes a huge difference between effective and true porosity \cite{shima2021}.
-Despite the drastic change of network with blockages, we can still focus on the \textit{initial} change in the order parameter.
-The derivative of order parameter can be written as
-%
-\begin{align}
-    \frac{d\mathcal{O}}{dt} = \sum_{ij} \sum_{kl} \frac{\partial \mathcal{O}}{\partial q_{ij}} \frac{\partial q_{ij}}{\partial C_{kl}}  \frac{\partial C_{kl}}{\partial t} \label{eq:order-derivative}
-\end{align}
-%
-where the last term changes sign from erosion to clogging, i.e., $\partial C_{kl}/\partial t = \pm \alpha \pi q^m_{kl} /r_{kl}^{n-3}\mu l_{kl}$ for erosion and clogging respectively.
-As a result, the magnitude of change in the order parameter equals that of erosion.
-Note that in Eq.
-\eqref{eq:order-derivative}, the second term depends on the network topology, and pore throat clogging results in the change of network topology at later times.
-% The pore throat blockages results in the divergent of clogging results from just the negative of erosion. 
-At short times, however, similar to the erosion, a phase transition exists at $n=3$.
-When  $n<3$ the network moves toward homogenization during the clogging process and when $n>3$ the flow moves toward the development of channeling instability.
-At later times, this initial trend, however, might not hold true due to the aforementioned complex changes in the connectivity network during the clogging process.
-
-% \clearpage
-% \bibliography{ref}% Produces the bibliography via BibTeX.
-
 \end{document}

### 2022-03-06 backup_Sep_2_2021/supp.tex
Updates from Overleaf

--- 2022-03-06 backup_Sep_2_2021/paper_arxiv.tex
@@
 %
-%   This file is part of the APS files in the REVTeX 4.1 distribution.
-%   Version 4.1r of REVTeX, August 2010
+%   This file is part of the APS files in the REVTeX 4.2 distribution.
+%   Version 4.2a of REVTeX, December 2014
 %
-%   Copyright (c) 2009, 2010 The American Physical Society.
+%   Copyright (c) 2014 The American Physical Society.
 %
-%   See the REVTeX 4 README file for restrictions and more information.
+%   See the REVTeX 4 README file for restrictions and more infor mation.
 %
 % TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.1
+% as well as the rest of the prerequisites for REVTeX 4.2
 %
@@
 %  4)  latex apssamp.tex
-%%
+%
 \documentclass[%
-reprint,
+%  reprint,
 %superscriptaddress,
@@
 % preprint,
-%showpacs,preprintnumbers,
+%preprintnumbers,
 %nofootinbib,
@@
  amsmath,amssymb,
- aps,
- % pra,
-prl,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-1}
+%  aps,
+%pra,
+% prb,
+% rmp,
+% prstab,
+prstper,
+% floatfix,
+]{revtex4-2}
 
-\usepackage{soul}
-\usepackage{color}
+\usepackage[usenames, dvipsnames]{color}
+% Color Edits
+\newcommand{\EM}[1]{\noindent \color{red} (AA: #1)\normalcolor}
+\newcommand{\AZ}[1]{\noindent \color{blue} (AZ: #1)\normalcolor}
 
-\newcommand{\hlcyan}[1]{{\sethlcolor{cyan}\hl{#1}}}
-\newcommand{\hlred}[1]{{\sethlcolor{red}\hl{#1}}}
-
+\usepackage{braket}
 \usepackage{graphicx}% Include figure files
 \usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-\usepackage{hyperref}% add hypertext capabilities
+\usepackage{bm}
+\usepackage[usenames, dvipsnames]{color}
+%\usepackage{hyperref}% add hypertext capabilities
 %\usepackage[mathlines]{lineno}% Enable numbering of text and display math
@@
 %]{geometry}
-%
 
-\usepackage{xcolor}
-\newcommand{\DP}[1]{\noindent \color{cyan} (DP: #1)\normalcolor}
-\newcommand{\AZ}[1]{\noindent \color{purple} (AZ: #1)\normalcolor}
-\newcommand{\add}[1]{\noindent \color{blue} #1 \normalcolor}
-\newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}
-\newcommand{\AM}[1]{\noindent \color{magenta} (AA: #1)\normalcolor}
-\def\red{\textcolor{red}}
-%
+\newcommand{\KB}[1]{\noindent \color{magenta} (KB: #1)\normalcolor}
+
+\renewcommand{\thepage}{S\arabic{page}}
+\renewcommand{\thesection}{S\arabic{section}}
+\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\theequation}{S\arabic{equation}}
+\def\lp{\left(}
+\def\rp{\right)}
+\def\lb{\left[}
+\def\rb{\right]}
 \begin{document}
-%
+
 \preprint{APS/123-QED}
 
-\title{Temporal Evolution of Flow in Pore-Networks:\\ From Homogenization to Instability} 
-% Force line breaks with \\
+\title{Temporal Evolution of Flow in Pore-Networks:\\ From Homogenization to Instability}% Force line breaks with \\
 % \thanks{A footnote to the article title}%
@@
 \author{Ahmad Zareei}
-\thanks{A.Z. and D.P. contributed equally.}
-\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with 
-\author{Deng Pan}%
-\thanks{A.Z. and D.P. contributed equally.}
-\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with
+\affiliation{ School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with \\
+\author{Pan Deng}%
+\affiliation{ School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with
 \author{Ariel Amir}%
 \email{arielamir@seas.harvard.edu}
-\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break  automatically or can be forced with
+\affiliation{ School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with
 % need to figure out how to reference dagger
-
-% \author{}
-% \altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with \\
-% \author{}%
-%  \email{}
-% \affiliation{% SEAS, Pierce Hall, Harvard University}%
 
@@
 
-\begin{abstract}
-We study the dynamics of flow-networks in porous media using a
-pore-network model. First, we consider a class of erosion dynamics
-assuming a constitutive law depending on flow rate, local velocities,
-or shear stress at the walls. We show that depending on the erosion
-law, the flow may become uniform and homogenized or
-become unstable and develop channels. By defining an order parameter
-capturing these different behaviors we show that a phase transition occurs
-depending on the erosion dynamics. Using a simple model, we identify
-quantitative criteria to distinguish these regimes and {correctly
-predict the fate of the network, and discuss the experimental relevance of our result. }
-%
-% Lastly, we show that the initial stages of pores clogging show analogous behaviors which depends on the clogging dynamics.
-
-% Lastly, we show that pores clogging at the initial stages show analogous behaviors depending on clogging dynamics.
-% , however, due to the pore throat blockages and changes in the network connections the evolution diverges from its initial trend.
-
-% \begin{description}
-% \item[Usage] Secondary publications and information retrieval purposes.
-% \item[PACS numbers] May be entered using the \verb+\pacs{#1}+ command.
-% \item[Structure] You may use the \texttt{description} environment to structure your abstract; use the optional argument of the \verb+\item+ command to give the category of each item.
-% \end{description}
-\end{abstract}
-
-%
-
-% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
 \maketitle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%% \tableofcontents %%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%% \section{Introduction} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% The fluids %%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature~\cite{marbach2016pruning,alim2013random,tero2010rules,heaton2010growth} as well as in numerous environmental~\cite{schlesinger1999carbon,winkler1979pore,batzle1992seismic} and industrial applications~\cite{duduta2011semi,sun2019hierarchical,smith2017multiphase,ferguson2012nonequilibrium}.
-The disordered pore structure of a porous medium results in heterogeneously distributed fluid flow between the pores.
-The boundaries of the pore structure can change dynamically either through erosion or deposition/sedimentation of material.
-Such heterogeneous changes of the solid structure affect the pore-level fluid flow which in turn affects the dynamical changes to the pore structure.
-This feedback mechanism along with the initial heterogeneous fluid flow makes it difficult to understand and predict the porous media behavior.
-Nonetheless, an understanding of the dynamical change is essential to improve any of the porous media applications where the pore network changes over time, including groundwater remediation and precipitation of minerals in rocks~\cite{rad2013pore}, biofilm growth in water filtration, and protective filters \cite{herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous}, as well as enhanced oil recovery with polymer flooding \cite{lake2014fundamentals,parsa2020origin}, or water-driven erosion \cite{schorghofer2004spontaneous,mahadevan2012flow}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-% \section{Methods \& Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\begin{figure}[h]
-    % \centering
-    \includegraphics[width = 0.45\textwidth]{Fig1.pdf}
-    % \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}.
-The scale in the bottom left shows $1$mm.
-The network of pores and throats is highlighted in blue.
-In the network model, the pores are represented with nodes and the throats between pores are approximated with tubes connecting the pores together.
-(b) Schematic of a topologically random network (i); and a structured diamond grid network (ii).
-The edge diameters in both networks are randomly distributed.
-The inset figure shows the conservation of mass at each node.
-(c) The universal probability distribution function (PDF) of fluid flux for a topologically random (in blue) or diamond network (red) with a highly disordered random network including uniform (triangles), log-normal (circles), and truncated normal (plus) distributions.}
-    \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}.
-The scale in the bottom left shows $1$mm.
-The network of pores and throats is highlighted in blue.
-In the network model, the pores are represented with nodes and the throats between pores are approximated with tubes.
-(b) Schematic of a topologically random network.
-The edge diameters representing the pore-throats are randomly distributed.
-(c) A structured diamond grid network with a random distribution of edge diameters.
-(d) The universal probability density function (PDF) of fluid flux for a topologically random (blue) or diamond-grid (red) network of nodes (red) with a random distribution of edge diameter sampled from a uniform (triangles), log-normal (circles), or truncated normal (plus) distribution.
-}
-    \label{fig:fig1}
-\end{figure}
-%
-\emph{Network approach}-- We approach this long-standing problem using a network model for the porous structure\cite{fatt1956network, blunt2013pore,stoop2019disorder,bryant1993network,blunt2013pore,dong2009pore,blunt2013pore,blunt1995pore,alim2017local}.
-% Before discussing the dynamics, we briefly review the results of flow in random networks.
-The network of pores inside the solid structure is connected together through pore-throats that effectively show resistance to the fluid flow between the pores (Fig.~\ref{fig:fig1}a).
-Network-based models have been shown to successfully capture key properties of fluid flow in a porous material such as the probability distribution of fluid flux~\cite{alim2017local}, the permeability scaling during clogging~\cite{shima2021}, or the first fluidized path in a porous structure~\cite{fraggedakis_chaparian_tammisola_2021}.
-We consider low-Reynolds fluid flow through the porous network.
-The fluid flow rate at the edge connecting pores $i$ and $j$ is given by $ q_{ij}  = C_{ij}(p_i - p_j)$ where $p_i,p_j$ represent pressures at neighboring nodes.
-Poiseuille's law implies that the conductance $C_{ij} = {\pi r_{ij}^4}/{8 \mu l_{ij}}$, with $r_{ij}$ and $l_{ij}$ the edge's radius and length.
-Initially, we consider a topologically random network of nodes constructed using uniformly distributed nodes in a planar domain connected using Delaunay triangulation (Fig.
-\ref{fig:fig1}b).
-The pore-throats or radii of the edges are considered as independent and identically distributed random variables and fluid flow in the edges are obtained by solving for conservation of mass at all nodes given a pressure difference between the nodes on the boundaries (supplementary material S1).
-Independent of edge radius distribution, the probability density function (PDF) of normalized fluid flux is well described by a single exponential distribution shown in Fig.
-\ref{fig:fig1}d.
-The exponential distribution of fluid flux is similar to earlier experimental and numerical measurements~\cite{datta2013spatial,shima2021,alim2017local} and is a universal feature in random porous networks.
-Considering a structured diamond-grid of pores (Fig.
-\ref{fig:fig1}c) which significantly simplifies the geometrical complexity of the network and allows for analytical derivation, one finds that the PDF of normalized fluid flux remains unchanged for various distributions suggesting robustness to network topology (Fig.~\ref{fig:fig1}d and supplementary materials S2).
-In the following, we will study, analytically and numerically, how this universal distribution evolves as the network is modified based on a local constitutive law.
-
-\textit{Network evolution}-- The degradation of the solid skeleton (i.e., erosion) or deposition of material on the pore throats (i.e., clogging) in the network of pores is modeled by the change (increase or decrease) in the radii of the edges connecting the pores which translates into changes in the flow resistance between the pores.
-The rate of change of the radii depends on local fluid flow parameters, however, the exact dependence is unknown.
-Different models have been used where erosion is assumed to be locally proportional to shear stress at the walls \cite{jager2017channelization,ristroph2012sculpting,hacking1996shear,wan2004investigation}, power dissipation by flow~\cite{steeb2007modeling,marot2012study,sibille2015internal}, or local pressure difference~\cite{derr2020flow,mahadevan2012flow}.
-We use a general constitutive  model which may implement a diverse set of erosion or clogging dynamics and thus allows us to study the effect of different laws in a unified way.
-
-\begin{figure}[!h]
-    % \centering
-    % \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
-    \includegraphics[width = 0.48\textwidth]{Fig2_.pdf}
-    \caption{Erosion in a network of pipes.
-The initial condition is shown with the label $t=0$ in the first row.
-Each row afterward corresponds to the {simulation result at $t=T$ where  $\langle r_{t=T}\rangle=2r_0$ with $r_0 = \langle r_{t=0}\rangle$}.
-The erosion law is based on Eq.
-\eqref{eq:erosion-law}  {where $m=1$ and different powers of $n$ correspond to different models of erosion}.
-{The first, second, and third columns are snapshots of the pore network, the PDF of normalized fluid flux $q/\langle q \rangle$, and  the PDF of normalized radius $r/\langle r\rangle$ at $t=T$, respectively}.} \label{fig:fig2}
-\end{figure}
-%
-%
-
-In order to model erosion in porous media, we consider the abrasion in the throats leading to decrease in the tube radii. We model the dynamics as 
-%
-\begin{align}
-   \frac{dr_{ij}}{dt} = \alpha  \frac{|q_{ij}|^m}{r_{ij}^n}, \label{eq:erosion-law}
-\end{align}
-%
-{where $m,n,\alpha$ are constants.
-Different values of $m$ and $n$ along with a positive $\alpha>0$ correspond to different erosion physics (analogously, $\alpha<0$ corresponds to clogging).
-Particularly, the erosion when $m=1$ and  (i) $n=0$ depends on the amount of flux $q_{ij}$ passing through the edge; (ii) $n=2$ depends on the local velocities; (iii) $n=3$ depends on the shear force at the boundary of the throat.} {Additionally, $m=2$ and $n=6$ corresponds to models considered in biological transport networks where the radii changes are {proportional to the square of shear stress at the boundary walls}~\cite{hu2013adaptation,ronellenfitsch2016global}.}
-We consider a randomly initialized network with disordered diameters obtained from a uniform distribution (supplementary material S1). 
-The flow inside the pores, PDF of flux in the tubes, and PDF of tube radii are shown in Fig.
-\ref{fig:fig2}.
-We assume a constant pressure difference between the left and the right boundaries.
-In each time step, we increase the local radii of the tubes based on the erosion law introduced in Eq.
-\eqref{eq:erosion-law}, assuming erosion is linear in the flux ($m=1$).
-Later we will consider the network behavior for other powers of $m$.
-We continue the simulations until $\langle r \rangle = 2 r_0$. 
-The results of the simulations for different values of $n$ are shown in Fig.
-\ref{fig:fig2}.
-When $n=1$ or $2$,  the network develops channels.
-In such cases, the flow is dominated by a few edges carrying most of the flow while the rest of the network carries almost no flow.
-This is also reflected by a bimodal radii distribution.
-In contrast, when $n=3$  (corresponding to erosion linear in shear), we find that despite the
-increase in tube radii and absolute flow rates, the normalized flow distribution is hardly affected, maintaining its original exponential form.
-Increasing $n$ to larger values, $n=4$ or $5$, we find that the flow pattern in the network moves towards homogenization.
-Here, the tail of the normalized fluid flux distribution retracts and the coefficient of variation reduces.
-Similarly, the PDF of the tube diameters becomes narrower.
-
-{We found that similar results uphold in a 3d random tube network as well as a 2d topologically ordered (diamond grid) network, illustrating the robustness of the results to the network topology (Figs.
-S2 and S3).
-Similarly, we found that the results hold also when using an initial narrow distribution of diameters (Fig.
-S4), showing robustness with respect to the strength of the disorder.}
-
-\textit{Phase transition and order parameter}-- {To quantify the transition of the network between the channeling instability and homogenization, we define an order parameter % $\mathcal{O}$ 
-%
-\begin{align}
-\mathcal{O} = \frac{1}{N-1} \left( N - \frac{\left( \sum_{ij} q^2_{ij}\right)^2}{ \sum_{ij} q^4_{ij}}\right),
-\end{align}
-%
-where $N$ is the number of edges.} {The order parameter defined here is inspired by the participation ratio (PR) employed to quantify the localization of an eigenstate in the analysis of Anderson localization\cite{kramer1993localization}.}  The order parameter $\mathcal{O}=0 $ when the flux through every edge is identical.
-On the other hand, when fluid flux becomes highly localized with only a few edges with non-zero flux, $\mathcal{O}\to 1$.
-We numerically calculated the  order parameter $\mathcal{O}$ for {randomly initialized networks, averaged over 20 different realization}.
-The results are shown in Fig. \ref{fig:fig3}a for different amounts of erosion measured by the increase in the average diameter $\langle r\rangle /r_0$. As shown in 
- Fig.
-\ref{fig:fig3}c, at $n\approx 3$ the order parameter, remains unchanged; however for $n>3$ the order parameter moves toward zero, where the flow becomes more uniform, and for $n<3$ the order parameter goes toward unity, where channels are developed.
-This indicates a phase transition at $n=3$ in the long-time behavior of the network.
-%
-
-\begin{figure}[!h]
-    % \centering
-     \includegraphics[width = 0.45\textwidth]{Fig3.pdf}
-    \caption{ (a) Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig.
-\ref{fig:fig2} for different powers of $n$ with $m=1$ plotted over time.
-(b,c) Tubes in series (b) or parallel (c) configuration.
-    The tube radius dynamically change with the erosion law (Eq.
-\eqref{eq:erosion-law}).
-When the tubes are in series, for any $m,n$, (b$_1$) the normalized pressure at the middle junction between the tubes $\tilde p_m = (p_m - p_l)/(p_r-p_l)$ approaches $1/2$ which results in a homogenized pressure distribution.
-    When the tubes are in parallel, for (c$_1$) $m=(n+1)/4$, the flow ratio between the pipes does not change over time; (c$_2$)  $m<(n+1)/4$ the flow distributes between the tubes equally and  $q_1/(q_1+q_2) \to 1$ which results in the homogenization of the network; (c$_3$) $m>(n+1)/4 $, the entire flow eventually passes through one of the tubes, and channeling occurs.
-}\label{fig:fig3}
-\end{figure}
-
-\textit{Simplified Model}-- {To understand the transition in network behavior during erosion for different powers of $n$, we focus on a simplified model with only two tubes in parallel or series (Figs.
-\ref{fig:fig3}b-c).
-First, assuming two cylindrical tubes with radii $r_1,r_2$ in series, the flow is the same for the two tubes $ q_1 = q_2 = q$ (Fig.
-\ref{fig:fig3}b).
-The radius of each tube then changes as $dr_i/dt = \alpha q^m /r_i^n$ where $i=1,2$.
-As a result, we find that the conductivity of each tube changes as $dC_i/dt \propto q^m C_i^{(3-n)/4}$, where each tube's conductivity increases.
-Considering the pressure at the junction between tubes, we find that it moves toward the average value of pressure on both sides (Fig.
-\ref{fig:fig3}(b$_1$)).
-Contrary to tubes in series, when the tubes are in parallel (Fig.
-\ref{fig:fig3}c), the flow divides between the two tubes in proportion to their conductivity, i.e., $q_1/q_2 = C_1/C_2$.
-Since each tube's radius changes as $dr_i/dt = \alpha q^m_i/r_i^n$, the evolution of the fluid flow ratio becomes
-% %% 
-\begin{align}
-\frac{d}{dt}\left( \frac{C_1}{C_2}\right) \propto  \frac{C_1}{C^{n/4+1}_2} \left( \left( \frac{C_1}{C_2}\right)^{m-\frac{n+1}{4}} - 1 \right). \label{eq:dyn-paral}
-\end{align}
-%%
-When $m=(n+1)/4$ in Eq.
-\eqref{eq:dyn-paral}, the right-hand-side vanishes and as a result the flow ratio $C_1/C_2$ remains constant (Fig.
-\ref{fig:fig3}c$_1$).
-However, when $m \neq (n+1)/4$, we find that $C_1/C_2 = 1$ is an equilibrium point.
-When $m<(n+1)/4$ this equilibrium solution is stable and the flow moves toward homogenization (Fig.
-\ref{fig:fig3}c$_2$); however, when $m>(n+1)/4$ this equilibrium solution becomes unstable and the solution moves toward $C_1/C_2 \to 0$ or $\infty$ which means that the entire flow passes through one of the tubes (Fig.
-\ref{fig:fig3}c$_3$).
-In summary, when the tubes are in series any erosion law makes flow become more uniform; however, when the tubes are in parallel depending on the powers $m,n$ the flow in the tubes can move toward becoming more uniform ($m<(n+1)/4$), maintain the same ratio ($m=(n+1)/4$), or move toward instability and channel development ($m>(n+1)/4$).
-Since a complex network includes both series and parallel connections, it is plausible that the whole network structure will behave in a similar manner, with a transition in the networks behavior at $ m = (n+1)/4 $.
-This observation  is consistent with the numerical simulation results shown in Figs. \ref{fig:fig2} and \ref{fig:fig3}a (for $m=1$) as well as for additional values of $m$ (Fig. \ref{fig:fig4}).}
-%
-
-\textit{Analysis of generalized model}-- So far we focused on erosion dynamics with $m=1$ (Eq.
-\eqref{eq:erosion-law}) since it directly corresponds to erosion laws of interest, i.e.
-an erosion rate with a linear dependence to fluid-flux, velocity, or shear-rate at the walls.
-Considering $m=2$ in Eq.
-\eqref{eq:erosion-law}, our model aligns with the transport optimization problem in biological networks~\cite{ronellenfitsch2016global,corson2010fluctuations,hu2013adaptation}.
-Previous works have suggested that in the context of biological transport networks, the network is optimized to minimize its dissipation energy with regards to some constraint (such as constant material or metabolic cost).
-Interestingly, the gradient descent method utilized to find the minimal energy configurations maps to Eq.
-\eqref{eq:erosion-law} with $m=2$, albeit with additional regularizing terms.
-While under the dynamics we study here erosion will occur indefinitely, in these biological network models a minimal energy configuration exists due to these additional constraints.
-Nonetheless, the minimal energy configurations manifest a phase transition reminiscent of the one we observe in our model.
-To test the role of the parameter $m$ in our model, we simulated the general form of erosion dynamics (Eq. \eqref{eq:erosion-law}).
-The simulation results for a randomly initialized network for different powers of $m$ and $n$ are shown in Fig.
-\ref{fig:fig4}, where each box shows the final snapshot of the network eroded with the corresponding $m$ and $n$.
-We further compare the network's simulation result with the prediction of our simplified model for the fate of the network for each pair of $m,n$.
-The simplified model's prediction is shown using the bounding box color (red for channelization and green for homogenization) in Fig.
-\ref{fig:fig4} (cf.
-Fig.
-S5 in supplementary material showing the heat map for the average change in the order parameter).
-Additionally, the dashed black line in Fig.
-\ref{fig:fig4} shows the simplified model's prediction for the boundary between network's transition to homogeneity or channelization (i.e., $m = (n+1)/4$).
-Although the simplified model is based on the erosion dynamics of two edges in a parallel or series configuration, it still correctly predicts the fate of the network with the complex topology for different values of $m$ and $n$, and captures the boundary separating channelization/homogenization.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width = 0.45\textwidth]{Fig4.pdf}
-    \caption{{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
-\eqref{eq:erosion-law}}.
-The network is randomly initialized with $50\times 50$ randomly distributed pores.
-The bounding box color shows the prediction of the simplified  model for the fate of the network: homogenization (blue) or channelization (red).
-The dashed black line shows the transition boundary between channelization instability and homogenization obtained using simplified model, i.e., $m=(n+1)/4$.}\label{fig:fig4}
-\end{figure}
-
-In the case of clogging, the initial dynamics can similarly be captured using our model, however, due to the change in the connectivity of the network, our simplified model cannot extend to large time behaviors (supplementary material S5).
-
-%
-\textit{Conclusion}-- {We analyzed the dynamics of porous networks during erosion.
-We showed that depending on the form of the erosion law (namely, its dependence on flux and tube radius) the network can either move towards homogenization or towards developing a channeling instability.
-We elucidated the physical origin of this phase transition and how it is achieved using a simplified model.
-Our results highlight the importance of local dynamics and feedback mechanisms in the network's path toward its asymptotic global behavior \cite{ronellenfitsch2016global,corson2010fluctuations,katifori2010damage,hu2013adaptation,ocko2015feedback},  and allow us to infer the local dynamics using large scale observations.
-As a result, our model can be used as a bulk behavior proxy for determining the local dynamics of erosion in a system~\cite{mahadevan2012flow}.
-Interestingly, our results indicates that an erosion model that is local and linearly dependent on shear rate cannot result in channelization (since $m=1,n=3$ and $m=(n+1)/4$).
-However, we note that if the dependence on the shear rate is non-linear, it will qualitatively map to our model albeit with renormalized values of $n$ and $m$: e.g., a power-law dependence on shear rate with exponent $s$ would lead to $m =s$, $n = 3 s$, implying channelization when $s>1$.
-In the future, it would be exciting to test this and other predictions experimentally on model systems, relying on the technological advances in imaging flow profiles in porous materials, as well as extend the study to the geologically relevant case of chemical erosion \cite{edery2014origins,edery2016characterization}.
-}
-
-\begin{acknowledgments}
-We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery,  Eleni Katifori, and Chris Rycroft
-for useful discussions.
-\end{acknowledgments}
-
-\bibliography{ref.bib}
-\appendix
-
-\newpage
-\onecolumngrid
-
-\renewcommand{\thepage}{S\arabic{page}}
-\setcounter{page}{1}
-\renewcommand{\thesection}{S\arabic{section}}
-\setcounter{section}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
-\setcounter{figure}{0}
-\renewcommand{\theequation}{S\arabic{equation}}
-\setcounter{equation}{0}
-\def\lp{\left(}
-\def\rp{\right)}
-\def\lb{\left[}
-\def\rb{\right]}
-
-{\huge \textbf{Supplementary Material}}
-
-\section{S1. Simulation algorithm}
-\label{s1}
+\section{Simulation algorithm}
 %
@@
 
-\section{S2. Analytical results for fluid flux EXP-tail PDF in a Diamond Network}
-\label{s2}
+\section{Analytical results for fluid flux EXP-tail PDF in a Diamond Network}
 %
-% \label{sec:analytical}
+\label{sec:analytical}
 %
@@
 Assuming a general distribution of for the weights, $\eta(w)$, we can use a mean-field approximation to find the distribution of $q$ at the layer $L$, i.e., $p_L(q)$, as 
-%%
+%
 \begin{align}
@@
 \newpage
-\section{S3. Robustness to topology and initial condition}
-\label{s3}
+\section{Robustness to topology and initial condition}
 % 
@@
 We use a two-dimensional diamond-grid network with a narrow uniform initial distribution of tube diameters around an average diameter $d_0$ with only a very small variation ($3\%$), i.e., the tube diameters are sampled from $\mathcal{U}(d_0(1-\epsilon), d_0(1+\epsilon))$.
-We again find that for the networks with $n<3$ channels are formed, while for $n>3$ the network stays homogenized (Fig.
-\ref{SI_figs4:fig:fig2}).
+We again find that for the networks with $n<3$ channels are formed, while for $n>3$ the network stays homogenized.
 %
@@
 (1) in the main text where different powers of $n$ correspond to different models of erosion.
-The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{SI_figs4:fig:fig2}%
+The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}%
 \end{figure}
@@
 \newpage
-\section{S4. Average Change in the  Order parameter}
-\label{s4}
+\section{Average Change in the  Order parameter}
 %
@@
 
-\section{S5. Clogging Dynamics}
-\label{s5}
+\section{Clogging Dynamics}
 % 
@@
 % \clearpage
-% \bibliography{ref}% Produces the bibliography via BibTeX.
+\bibliography{ref}% Produces the bibliography via BibTeX.
 
 \end{document}
+%
+
+%###############################################################
+%###############################################################
+%###############################################################
+%###############################################################
+%###############################################################
+%###############################################################
+%###############################################################
+
+\newpage
+\section{Clogging behavior at initial times}
+% 
+Considering a small change in the radius of edges, and as a result, the conductance of the edges $\mathbf{C}+\delta \mathbf{C}$, using Eq. \eqref{main-solve-eq} we find that 
+%
+\begin{align}
+    \ket{P'} &=  \ket{P} -  \left( \Delta_n^\top\mathbf{C} \Delta_n\right)^{-1}\left[  \left( \Delta_n^\top \delta \mathbf{C} \Delta_n\right)\ket{P} + \left( \Delta_n^\top\delta \mathbf{C} \Delta_b\right) \ket{P_{BC}}\right],
+\end{align}
+%
+where we used the fact that for an invertible matrix $\mathbf{A}$ we have 
+%
+\begin{align}
+    \left(\mathbf{A} + \delta \mathbf{A} \right)^{-1} = \mathbf{A}^{-1} - \left( \mathbf{A}^{-1} \delta \mathbf{A}\right) \mathbf{A}^{-1} + \left( \mathbf{A}^{-1}  \delta \mathbf{A}\right)^{2}\mathbf{A}^{-1}  + \cdots.
+\end{align}
+%
+Calculating for the changes in the fluid flux, we find that 
+%
+\begin{align}
+\ket{q'} & = \left( \mathbf{C}+ \delta \mathbf{C}  \right)\left( \Delta_b \ket{P_{BC}} +  \Delta_n \ket{P'} \right) \\
+& = \ket{q} + \delta\mathbf{C} \mathbf{C}^{-1}\ket{q} - \mathbf{C} \Delta_n \left( \Delta_n^\top\mathbf{C} \Delta_n\right)^{-1}\left[  \left( \Delta_n^\top \delta \mathbf{C} \Delta_n\right)\ket{P} + \left( \Delta_n^\top\delta \mathbf{C} \Delta_b\right) \ket{P_{BC}}\right].
+\end{align}
+%
+The above equation can then be used to study the evolution of order parameter in the networks.
+Note that during the blockage of pore-throats, the connectivity between the nodes changes and as a result network's connectivity matrix $\Delta$ changes and the above approximation will not hold anymore.
+
+%###############################################################
+%###############################################################
+%###############################################################
+%###############################################################
+%###############################################################
+%###############################################################
+%###############################################################
+
+% ****** End of file apssamp.tex ******
+
+ If we set
+$\eta(w) = \delta(w-1/2)$, then the flow at each node has probability of
+$1/2$ to move to either of the neighboring sites. As a result the flow at a given depth $L$ will become homogeneous as $P_L(Q) = \delta (Q-\bar{Q})$ where $\bar{Q}$
+is the average of input fluid flow. This results is the same as having the same
+diameter for all the edges which results in a singular solution in the structured grid.
+% 
+\subsection*{$P(Q)$ decays faster than $Q^{-n}$ for any $n$}
+We first show that $P(Q)$ decays faster than any power of $Q$ for any
+weight distributions. We expand the Laplace transform using a Taylor expansion as 
+%
+\begin{align}
+  \tilde P(s) = 1 + \sum_j \tilde P_{j} s^{j}.
+\end{align}
+%
+Inserting this expansion into Eq. \eqref{eq:main-laplace}, we obtain
+%
+\begin{align}
+  1 + \sum_j \tilde P_{j} s^{j}  & = \lp  \int_0^1 d w \eta(w) \lb 1 + \sum_j \tilde P_{j} (sw)^{j}\rb    \rp^{N}  = \lp  1 + \sum_j \tilde P_j \langle w^{j}\rangle  s^{j}   \rp^{N}
+\end{align}
+%
+where $\langle w^j \rangle = \int_0^1 \eta(w) w^j dw$ is the $j$-th
+moment of the weights $w$. In the above equation we can observe that
+%
+\begin{align}
+  P_j \lp N \langle w^j\rangle -1 \rp = G(P_{j-1}, P_{j-1}, \cdots, P_1)
+\end{align}
+%
+In the above equation $P_j$ can only diverge only if $N\langle w^j
+\rangle -1=0$. If $w$ can only be zero and one, then $\langle
+w^j\rangle =\langle w \rangle = 1/N$ and the coefficient can become
+zero! Other than this special distribution, when $0 \leq w \leq 1$, then
+%
+\begin{align}
+  & w\in [0,1] \rightarrow w>w^2>w^3> \cdots \\
+  & \forall k>1 \rightarrow \langle w^k \rangle < \langle w \rangle = \frac{1}{N} 
+\end{align}
+%
+which means that $N\langle w^j \rangle -1\neq 0$ and as a result
+$P_j$ is finite. $P_j$ on the other hand is the $j$-th moment or
+$\langle Q^j\rangle$ and it is finite. If $P\approx Q^{-n}$, then the
+$n$-th moment will not be finite i.e. $\langle Q^{n+1}\rangle =
+P_{n+1}$ is not finite. We can then conclude that $P(Q)$ should go to
+zero faster than any $Q^{-n}$ as $Q\to \infty$! In other words $d \log
+P(Q) / d \log Q \to -\infty$ as $Q\to \infty$.  
+% 
+\subsection*{Exponential Decay}
+%
+The main recursive governing equation for a diamond grid is  
+%
+\begin{align}
+  \tilde P(s) = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{2} \label{eq:main-recur}
+\end{align}
+%
+% In order to have an approximation for $\eta(w)$ we consider the following situation:
+At each node there are two neighboring nodes where the flux is distributed by
+$w_1$ and $w_2$ among them. Assuming that $w_1$ is uniformly distributed
+between $0$ and $1$, then $w_2 = 1-w_1$ (due to  conservation of
+mass $w_1 + w_2 = 1$). Now $\eta(w)$ can be obtained using 
+%
+\begin{align}
+  & \eta(w) = M \int_0^1 dw_1 \delta(1-w_1-w) =  M, \\
+  \text{since }& \int_0^1 \eta(w) dw = 1 \to M =1 \\
+  & \eta (w) = 1
+\end{align}
+%
+Just for completeness, if there are three neighboring connections ($N=3$), then we
+have
+%
+\begin{align}
+  \eta(w) & = M \int_0^1 dw_1 \int_0^1 dw_2 \delta(1-w_1-w_2 - w)\\
+          & = M(1-w)  \to \int_0^1\eta(w) dw = 1 \to M = \frac{1}{2} \\
+  & \eta(w) = \frac{1}{2} (1-w)
+\end{align}
+%
+As a result Eq.~\eqref{eq:main-recur} simplifies to
+%
+\begin{align}
+  \tilde P(s) = \lp  \int_0^1 d w  \tilde P(s w)  \rp^{2} 
+\end{align}
+%
+In order to solve the above equation, we assume $\tilde V (s) =
+\sqrt{\tilde{P}(s)}$.
+%
+\begin{align}
+  \tilde{V}(s) & = \int_0^1 dw \tilde V (sw) = \int_0^s \frac{du}{s}  \tilde{V}^{2}(u) \\
+  s\tilde{V}(s) & = \int_0^s du  \tilde{V}^2(u) \\
+\end{align}
+%
+Taking the differentiation with respect to $s$ yields
+%
+\begin{align}
+  \tilde{V}(s) + s \frac{d \tilde{V}(s)}{d s} = \tilde{V}^2(s) \\
+  \frac{d \tilde{V}}{\tilde{V}^2-\tilde{V}} = \frac{ds}{s}  \\
+  \log\lp \frac{1-\tilde{V}}{\tilde{V}} \rp  = \log(s)\\
+  \tilde{V}(s) = \frac{1}{1+Cs} 
+\end{align}
+%
+We set the mean to $1$ i.e.,
+%
+\begin{align}
+  \int_0^{\infty} Q P(Q) dQ = 1 \to \frac{d\tilde{P}}{ds}|_{s=0}  = -1\\
+  \frac{d \tilde{V}}{ds}  = \frac{1}{2 \sqrt{\tilde{P}(s)}} \frac{d \tilde{P}(s)}{d s}   \to \frac{d\tilde{V}(s)}{ds}|_{s=0} =\frac{-1}{2} \\
+  \frac{d\tilde{V}(s)}{ds} = \frac{-C}{(1+Cs)^{2}}|_{s=0} = -C = \frac{-1}{2}  \to C=\frac{1}{2} 
+\end{align}
+%
+As a result, we have
+%
+\begin{align}
+  \tilde{P}(s) = \lp\frac{1}{1+s/2} \rp^2 \\
+  P(Q) = 4Q e^{-2Q}
+\end{align}
+%
+We can then show that for a uniform distribution of $w$'s, the PDF of
+$Q$'s become an exponential tail. For other distribution of $w$'s, we
+similarly find a similar trend which can be seen in the numerical simulations. 
+% Actually, we showed that the PDF of $Q$ should decay faster than any power law for any distribution of
+$w$. 
+Note that in the distribution with exponential tail, the only parameter that determines the the PDF of the average fluid flow.
+This shows that why we observe the universal behaviour for the PDF of normalized fluid flux where the average of normalized fluid flux is unity.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+
+For each resistor we know that
+%
+\begin{align}
+    q_{e} = R_{e} \Delta P_{e}
+\end{align}
+%
+Assume that matrix $\mathbf{C}$ relates the pressure at nodes to the pressure difference, where 
+%
+\begin{align}
+    \ket{\Delta P_e} = \mathbf{C} \ket{P_n}, \quad \ket{q_e} = \mathbf{R} \ket{\Delta P_e}, \quad \ket{q_n} = \mathbf{C}^\top \ket{q_e} \\
+    \ket{q_n} = \mathbf{C}^\top \mathbf{R} \mathbf{C}\ket{P_n}
+\end{align}
+%
+\begin{align}
+    \mathbf{C}^\top \mathbf{R} \mathbf{C}\begin{bmatrix} P_1 \\ P_2 \\ \vdots \\ P_n
+    \end{bmatrix}
+    = \ket{q} \to \begin{bmatrix} \mathbf{C_{b}}^\top \mathbf{R} \mathbf{C_{b}}  & \vline &    \mathbf{C_{b}}^\top \mathbf{R} \mathbf{C_{n}} \\ \hline  
+    \mathbf{C_{n}}^\top \mathbf{R} \mathbf{C_{b}} & \vline & \mathbf{C_{n}}^\top \mathbf{R} \mathbf{C_{n}}
+    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ \hline  P_n \\ \vdots \\ P_{N_n}
+    \end{bmatrix} = \begin{bmatrix} q_1 \\ q_2 \\ \vdots \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \\
+    \begin{bmatrix} 
+    \mathbf{A}_{bb} & \mathbf{A}_{bn} \\
+    \mathbf{A}_{nb} & \mathbf{A}_{nn}       
+    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ \hline  P_n \\ \vdots \\ P_{N_n}
+    \end{bmatrix} = \begin{bmatrix} q_1 \\ q_2 \\ \vdots \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \to \begin{cases} 
+        \mathbf{A}_{bb} \ket{P_{BC}} + \mathbf{A}_{bn}  \ket{P_{n}} = \ket{q} \\
+    \mathbf{A}_{nb}\ket{P_{BC}} +  \mathbf{A}_{nn} \ket{P_n} = 0 
+    \end{cases} \\
+     \mathbf{A}_{nn} \ket{P_n} =- \mathbf{A}_{nb}\ket{P_{BC}} \to \mathbf{A}_{nn} \ket{P_n} = \mathbf{b}
+\end{align}
+
+In solving our problem, we have 
+%
+\begin{align}
+ \mathbf{C}_{n}^\top \mathbf{R} \mathbf{C}_{n}\ket{P} =     - \mathbf{C}_{n}^\top \mathbf{R} \mathbf{C}_{b}\ket{P}_{BC}  \to \mathbf{A}_{nn} \ket{P_n} = \mathbf{B}\ket{P}_{BC}
+\end{align}
+%
+where $\mathbf{b}$ comes from the boundary conditions.
+When the pressures are found then $\ket{q} = \mathbf{R}\mathbf{C} \ket{P}$, we can obtain the new fluxes.
+Now the question is that if $\mathbf{R} = \mathbf{R}+\delta \mathbf{R}$, then what happens to the $\ket{q}$ with respect to the first order of perturbation?
+if we set $\mathbf{R} = \mathbf{R}+\delta \mathbf{R}$ then
+%
+\begin{align}
+\mathbf{C}_{n}^\top \left( \mathbf{R} + \delta \mathbf{R} \right) \mathbf{C}_{n}\ket{P'} &= - \mathbf{C}_{n}^\top \left( \mathbf{R} + \delta \mathbf{R} \right) \mathbf{C}_{b}\ket{P}_{BC} \\
+(\mathbf{A} + \delta \mathbf{A}) \ket{P'} &= (\mathbf{B} + \delta \mathbf{B})\ket{P_{BC}} \\
+\ket{P'} &=(\mathbf{A} + \delta \mathbf{A})^{-1} (\mathbf{B} + \delta \mathbf{B})\ket{P_{BC}}  \\
+\ket{P'} &= \left( \mathbf{A}^{-1} - \left( \mathbf{A}^{-1} \delta \mathbf{A}\right) \mathbf{A}^{-1}\right) (\mathbf{B} + \delta \mathbf{B})\ket{P_{BC}} \\
+\ket{P'} &= \mathbf{A}^{-1} \mathbf{B} \ket{P_{BC}} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} - \mathbf{A}^{-1} \delta \mathbf{A} \mathbf{A}^{-1} \mathbf{B} \ket{P_{BC}} \\
+\ket{P'} &= \ket{P} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} - \mathbf{A}^{-1} \delta \mathbf{A} \ket{P}
+\end{align}
+%
+where we used the fact that 
+%
+\begin{align}
+    \left(\mathbf{A} + \delta \mathbf{A} \right)^{-1} = \mathbf{A}^{-1} - \left( \mathbf{A}^{-1} \delta \mathbf{A}\right) \mathbf{A}^{-1} + \left( \mathbf{A}^{-1}  \delta \mathbf{A}\right)^{2}\mathbf{A}^{-1}  + \cdots
+\end{align}
+%
+The fluid flow can then be obtained 
+%
+\begin{align}
+    \ket{q'} = \left( \mathbf{R}+ \delta \mathbf{R}\right) \mathbf{C} \ket{P'}    \\
+    \text{where} \quad \mathbf{A} = \mathbf{C}^\top\mathbf{R} \mathbf{C},\quad \delta \mathbf{A} = \mathbf{C}^\top \delta \mathbf{R} \mathbf{C}
+\end{align}
+%
+Upto the first order, we find that
+%
+\begin{align}
+    \ket{P'} &= \ket{P} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} - \mathbf{A}^{-1} \delta \mathbf{A} \ket{P} \\
+    & = \left(\mathbf{I} - \mathbf{A}^{-1} \delta \mathbf{A}  \right) \ket{P} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} \\
+    & = \left( \mathbf{I} - \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1} \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\right)\ket{P} -  \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1} \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}} \\
+    & = \ket{P} -  \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right]
+\end{align}
+%
+Calculating the fluid flow, we obtain
+%
+\begin{align}
+\ket{q'} & = \left( \mathbf{R}+ \delta \mathbf{R}  \right)\left( \mathbf{C}_b \ket{P_{BC}} +  \mathbf{C}_n \ket{P'} \right) \\
+& = \left( \mathbf{R}+ \delta \mathbf{R}  \right)\left( \mathbf{C}_b \ket{P_{BC}} + \mathbf{C}_n \left\{ \ket{P} -  \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right] \right\} \right) \\
+& = \mathbf{R}\left( \mathbf{C}_b \ket{P_{BC}} +  \mathbf{C}_n \ket{P} \right) + \delta \mathbf{R}\left( \mathbf{C}_b \ket{P_{BC}} +  \mathbf{C}_n \ket{P} \right) - \mathbf{R} \mathbf{C}_n \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right]  \\
+& = \ket{q} + \delta\mathbf{R} \mathbf{R}^{-1}\ket{q} - \mathbf{R} \mathbf{C}_n \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right]
+\end{align}
+
+\newpage
+\section{Example}
+%
+
+\begin{figure}
+    \vspace{5mm}
+    \centering
+    \includegraphics[width=0.2\textwidth]{./Figs/fig1}
+    \caption{An example of network structure for a network of pipes}
+    \label{Fig:fig1}
+\end{figure}
+%
+%
+\begin{align}
+    \ket{\Delta P_\text{e}} = \mathbf{C} \ket{P_n}, \quad  \ket{q_e} = \mathbf{R} \ket{\Delta P_e}, \quad \ket{q_n} = \mathbf{C}^\top \ket{q_e} \\
+    \begin{bmatrix} \Delta p_e^1 \\ \Delta p_e^2 \\\Delta p_e^3 \\\Delta p_e^4 \\\Delta p_e^5 \\ \Delta p_e^6
+    \end{bmatrix} = \begin{bmatrix} 
+    -1 & 1 & 0 & 0 \\
+     0 & -1 & 1 & 0 \\
+     0 & 0 & -1 & 1 \\
+    -1 & 0 & 0 & 1 \\
+    -1 & 0 & 1 & 0 \\
+     0 & -1 & 0 & 1
+    \end{bmatrix}\begin{bmatrix} P_n^1 \\ P_n^2 \\  P_n^3 \\P_n^4\end{bmatrix}, \quad 
+    \begin{bmatrix}
+    q_e^1\\    q_e^2\\    q_e^3\\    q_e^4\\    q_e^5\\    q_e^6\\
+    \end{bmatrix} = \begin{bmatrix}
+    R_1 & 0 & 0 & 0 & 0 & 0 \\
+    0 & R_2 & 0 & 0 & 0 & 0 \\
+    0 & 0 & R_3 & 0 & 0 & 0 \\
+    0 & 0 & 0 & R_4 & 0 & 0 \\
+    0 & 0 & 0 & 0 & R_5 & 0 \\
+    0 & 0 & 0 & 0 & 0 & R_6 
+    \end{bmatrix}
+    \begin{bmatrix} \Delta p_e^1 \\ \Delta p_e^2 \\\Delta p_e^3 \\\Delta p_e^4 \\\Delta p_e^5 \\ \Delta p_e^6
+    \end{bmatrix} \\
+    \begin{bmatrix}
+    q_n^1 \\    q_n^2 \\    q_n^3 \\    q_n^4 \\
+    \end{bmatrix}= \begin{bmatrix} 
+    -1 & 0 & 0 & -1 & -1 & 0 \\
+    1 & -1 & 0 & 0 & 0 & -1 \\
+    0 & 1 & -1 & 1 & 0 & 0  \\
+    0 & 0 & 1 & 1 & 0 & 1
+    \end{bmatrix}\begin{bmatrix}
+    q_e^1\\    q_e^2\\    q_e^3\\    q_e^4\\    q_e^5\\    q_e^6\\
+    \end{bmatrix}
+\end{align}

### 2022-03-06 old_files/june14/paper.tex
Updates from Overleaf

--- 2022-03-06 backup_Sep_2_2021/prl_paper.tex
@@
 
-Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature~\cite{marbach2016pruning,alim2013random,tero2010rules,heaton2010growth} as well as in numerous environmental~\cite{schlesinger1999carbon,winkler1979pore,batzle1992seismic,cohen2015mechanisms} and industrial applications~\cite{duduta2011semi,sun2019hierarchical,smith2017multiphase,ferguson2012nonequilibrium}.
+Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature as well as in numerous environmental and industrial applications~\cite{fraggedakis2015flow,sahimi2011flow,schlesinger1999carbon,duduta2011semi,sun2019hierarchical,marbach2016pruning,tero2010rules,alim2013random,heaton2010growth,smith2017multiphase,ferguson2012nonequilibrium}.
 The disordered pore structure of a porous medium results in heterogeneously distributed fluid flow between the pores.
@@
     % \centering
-    \includegraphics[width = 0.45\textwidth]{Fig1.pdf}
+    \includegraphics[width = 0.45\textwidth]{./Fig1.pdf}
     % \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}.
@@
     % \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
-    \includegraphics[width = 0.48\textwidth]{Fig2_.pdf}
+    \includegraphics[width = 0.48\textwidth]{./Fig2.pdf}
     \caption{Erosion in a network of pipes.
@@
     % \centering
-     \includegraphics[width = 0.45\textwidth]{Fig3.pdf}
+     \includegraphics[width = 0.45\textwidth]{./Fig3.pdf}
     \caption{ (a) Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig.
@@
 
-\textit{Analysis of generalized model}-- So far we focused on erosion dynamics with $m=1$ (Eq.
+\textit{Analysis of generalized Model}-- So far we focused on erosion dynamics with $m=1$ (Eq.
 \eqref{eq:erosion-law}) since it directly corresponds to erosion laws of interest, i.e.
@@
     \centering
-    \includegraphics[width = 0.45\textwidth]{Fig4.pdf}
+    \includegraphics[width = 0.45\textwidth]{./Fig4.pdf}
     \caption{{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
@@
 \begin{acknowledgments}
-We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery,  Eleni Katifori, and Chris Rycroft
-for useful discussions.
+We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery and Eleni Katifori for useful discussions.
 \end{acknowledgments}
 
-\bibliography{ref.bib}
+% \bibliography{ref.bib}
+% \appendix
 
-\appendix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{48}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Fraggedakis}\ \emph {et~al.}(2015)\citenamefont
+  {Fraggedakis}, \citenamefont {Kouris}, \citenamefont {Dimakopoulos},\ and\
+  \citenamefont {Tsamopoulos}}]{fraggedakis2015flow}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Fraggedakis}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Kouris}},
+  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Dimakopoulos}}, \ and\
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Tsamopoulos}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physics of
+  Fluids}\ }\textbf {\bibinfo {volume} {27}},\ \bibinfo {pages} {082102}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sahimi}(2011)}]{sahimi2011flow}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Sahimi}},\ }\href@noop {} {\emph {\bibinfo {title} {Flow and transport in
+  porous media and fractured rock: from classical methods to modern
+  approaches}}}\ (\bibinfo  {publisher} {John Wiley \& Sons},\ \bibinfo {year}
+  {2011})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schlesinger}(1999)}]{schlesinger1999carbon}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~H.}\ \bibnamefont
+  {Schlesinger}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Science}\ }\textbf {\bibinfo {volume} {284}},\ \bibinfo {pages} {2095}
+  (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Duduta}\ \emph {et~al.}(2011)\citenamefont {Duduta},
+  \citenamefont {Ho}, \citenamefont {Wood}, \citenamefont {Limthongkul},
+  \citenamefont {Brunini}, \citenamefont {Carter},\ and\ \citenamefont
+  {Chiang}}]{duduta2011semi}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Duduta}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Ho}}, \bibinfo
+  {author} {\bibfnamefont {V.~C.}\ \bibnamefont {Wood}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Limthongkul}}, \bibinfo {author}
+  {\bibfnamefont {V.~E.}\ \bibnamefont {Brunini}}, \bibinfo {author}
+  {\bibfnamefont {W.~C.}\ \bibnamefont {Carter}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Y.-M.}\ \bibnamefont {Chiang}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Advanced Energy Materials}\ }\textbf
+  {\bibinfo {volume} {1}},\ \bibinfo {pages} {511} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2019)\citenamefont {Sun},
+  \citenamefont {Zhu}, \citenamefont {Baumann}, \citenamefont {Peng},
+  \citenamefont {Xu}, \citenamefont {Shakir}, \citenamefont {Huang},\ and\
+  \citenamefont {Duan}}]{sun2019hierarchical}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Sun}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhu}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Baumann}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Peng}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Xu}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Shakir}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Huang}}, \
+  and\ \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Duan}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Reviews Materials}\
+  }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {45} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Marbach}\ \emph {et~al.}(2016)\citenamefont
+  {Marbach}, \citenamefont {Alim}, \citenamefont {Andrew}, \citenamefont
+  {Pringle},\ and\ \citenamefont {Brenner}}]{marbach2016pruning}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Marbach}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Alim}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Andrew}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {117}},\ \bibinfo {pages} {178103} (\bibinfo
+  {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tero}\ \emph {et~al.}(2010)\citenamefont {Tero},
+  \citenamefont {Takagi}, \citenamefont {Saigusa}, \citenamefont {Ito},
+  \citenamefont {Bebber}, \citenamefont {Fricker}, \citenamefont {Yumiki},
+  \citenamefont {Kobayashi},\ and\ \citenamefont {Nakagaki}}]{tero2010rules}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Tero}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Takagi}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Saigusa}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Ito}}, \bibinfo {author}
+  {\bibfnamefont {D.~P.}\ \bibnamefont {Bebber}}, \bibinfo {author}
+  {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \bibinfo {author}
+  {\bibfnamefont {K.}~\bibnamefont {Yumiki}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Kobayashi}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Nakagaki}},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {327}},\ \bibinfo
+  {pages} {439} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2013)\citenamefont {Alim},
+  \citenamefont {Amselem}, \citenamefont {Peaudecerf}, \citenamefont
+  {Brenner},\ and\ \citenamefont {Pringle}}]{alim2013random}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Alim}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Amselem}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Peaudecerf}}, \bibinfo
+  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
+  Academy of Sciences}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages}
+  {13306} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Heaton}\ \emph {et~al.}(2010)\citenamefont {Heaton},
+  \citenamefont {L{\'o}pez}, \citenamefont {Maini}, \citenamefont {Fricker},\
+  and\ \citenamefont {Jones}}]{heaton2010growth}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~L.}\ \bibnamefont
+  {Heaton}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {L{\'o}pez}},
+  \bibinfo {author} {\bibfnamefont {P.~K.}\ \bibnamefont {Maini}}, \bibinfo
+  {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {N.~S.}\ \bibnamefont {Jones}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the Royal Society
+  B: Biological Sciences}\ }\textbf {\bibinfo {volume} {277}},\ \bibinfo
+  {pages} {3265} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Smith}\ and\ \citenamefont
+  {Bazant}(2017)}]{smith2017multiphase}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~B.}\ \bibnamefont
+  {Smith}}\ and\ \bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
+  {Bazant}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of The Electrochemical Society}\ }\textbf {\bibinfo {volume}
+  {164}},\ \bibinfo {pages} {E3291} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Ferguson}\ and\ \citenamefont
+  {Bazant}(2012)}]{ferguson2012nonequilibrium}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~R.}\ \bibnamefont
+  {Ferguson}}\ and\ \bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
+  {Bazant}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of The Electrochemical Society}\ }\textbf {\bibinfo {volume}
+  {159}},\ \bibinfo {pages} {A1967} (\bibinfo {year} {2012})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Rad}\ \emph {et~al.}(2013)\citenamefont {Rad},
+  \citenamefont {Shokri},\ and\ \citenamefont {Sahimi}}]{rad2013pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~N.}\ \bibnamefont
+  {Rad}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Shokri}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Sahimi}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review E}\ }\textbf
+  {\bibinfo {volume} {88}},\ \bibinfo {pages} {032404} (\bibinfo {year}
+  {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Herzig}\ \emph {et~al.}(1970)\citenamefont {Herzig},
+  \citenamefont {Leclerc},\ and\ \citenamefont {Goff}}]{herzig1970flow}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Herzig}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Leclerc}}, \
+  and\ \bibinfo {author} {\bibfnamefont {P.~L.}\ \bibnamefont {Goff}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Industrial \&
+  Engineering Chemistry}\ }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages}
+  {8} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tien}\ and\ \citenamefont
+  {Payatakes}(1979)}]{tien1979advances}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Tien}}\ and\ \bibinfo {author} {\bibfnamefont {A.~C.}\ \bibnamefont
+  {Payatakes}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {AIChE Journal}\ }\textbf {\bibinfo {volume} {25}},\ \bibinfo {pages} {737}
+  (\bibinfo {year} {1979})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jaisi}\ \emph {et~al.}(2008)\citenamefont {Jaisi},
+  \citenamefont {Saleh}, \citenamefont {Blake},\ and\ \citenamefont
+  {Elimelech}}]{jaisi2008transport}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
+  {Jaisi}}, \bibinfo {author} {\bibfnamefont {N.~B.}\ \bibnamefont {Saleh}},
+  \bibinfo {author} {\bibfnamefont {R.~E.}\ \bibnamefont {Blake}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Elimelech}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Environmental Science \&
+  Technology}\ }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages} {8317}
+  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carrel}\ \emph {et~al.}(2018)\citenamefont {Carrel},
+  \citenamefont {Morales}, \citenamefont {Beltran}, \citenamefont {Derlon},
+  \citenamefont {Kaufmann}, \citenamefont {Morgenroth},\ and\ \citenamefont
+  {Holzner}}]{carrel2018biofilms}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Carrel}}, \bibinfo {author} {\bibfnamefont {V.~L.}\ \bibnamefont {Morales}},
+  \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Beltran}}, \bibinfo
+  {author} {\bibfnamefont {N.}~\bibnamefont {Derlon}}, \bibinfo {author}
+  {\bibfnamefont {R.}~\bibnamefont {Kaufmann}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Morgenroth}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Holzner}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Water Research}\ }\textbf {\bibinfo {volume}
+  {134}},\ \bibinfo {pages} {280} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Seymour}\ \emph {et~al.}(2004)\citenamefont
+  {Seymour}, \citenamefont {Gage}, \citenamefont {Codd},\ and\ \citenamefont
+  {Gerlach}}]{seymour2004anomalous}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
+  {Seymour}}, \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Gage}},
+  \bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont {Codd}}, \ and\
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Gerlach}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {93}},\ \bibinfo {pages} {198103} (\bibinfo
+  {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lake}\ \emph {et~al.}(2014)\citenamefont {Lake},
+  \citenamefont {Johns}, \citenamefont {Rossen}, \citenamefont {Pope} \emph
+  {et~al.}}]{lake2014fundamentals}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
+  {Lake}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Johns}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Rossen}}, \bibinfo
+  {author} {\bibfnamefont {G.~A.}\ \bibnamefont {Pope}},  \emph {et~al.},\
+  }\bibfield  {booktitle} {\emph {\bibinfo {booktitle} {Fundamentals of
+  Enhanced Oil Recovery}},\ }\href@noop {} {\  (\bibinfo {year}
+  {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parsa}\ \emph {et~al.}(2020)\citenamefont {Parsa},
+  \citenamefont {Santanach-Carreras}, \citenamefont {Xiao},\ and\ \citenamefont
+  {Weitz}}]{parsa2020origin}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Parsa}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Santanach-Carreras}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Xiao}}, \ and\ \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+  {Weitz}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Fluids}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages}
+  {022001} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schorghofer}\ \emph {et~al.}(2004)\citenamefont
+  {Schorghofer}, \citenamefont {Jensen}, \citenamefont {Kudrolli},\ and\
+  \citenamefont {Rothman}}]{schorghofer2004spontaneous}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Schorghofer}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Jensen}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kudrolli}}, \ and\
+  \bibinfo {author} {\bibfnamefont {D.~H.}\ \bibnamefont {Rothman}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of Fluid
+  Mechanics}\ }\textbf {\bibinfo {volume} {503}},\ \bibinfo {pages} {357}
+  (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mahadevan}\ \emph {et~al.}(2012)\citenamefont
+  {Mahadevan}, \citenamefont {Orpe}, \citenamefont {Kudrolli},\ and\
+  \citenamefont {Mahadevan}}]{mahadevan2012flow}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Mahadevan}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Orpe}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kudrolli}}, \ and\
+  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Mahadevan}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf
+  {\bibinfo {volume} {98}},\ \bibinfo {pages} {58003} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Akanji}\ and\ \citenamefont
+  {Matthai}(2010)}]{akanji2010finite}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~T.}\ \bibnamefont
+  {Akanji}}\ and\ \bibinfo {author} {\bibfnamefont {S.~K.}\ \bibnamefont
+  {Matthai}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Transport in Porous Media}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo
+  {pages} {241} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fatt}\ \emph {et~al.}(1956)\citenamefont {Fatt} \emph
+  {et~al.}}]{fatt1956network}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Fatt}} \emph {et~al.},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Transactions of the AIME}\ }\textbf {\bibinfo {volume} {207}},\
+  \bibinfo {pages} {144} (\bibinfo {year} {1956})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Blunt}\ \emph {et~al.}(2013)\citenamefont {Blunt},
+  \citenamefont {Bijeljic}, \citenamefont {Dong}, \citenamefont {Gharbi},
+  \citenamefont {Iglauer}, \citenamefont {Mostaghimi}, \citenamefont
+  {Paluszny},\ and\ \citenamefont {Pentland}}]{blunt2013pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+  {Blunt}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Bijeljic}},
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Dong}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Gharbi}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Iglauer}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Mostaghimi}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Paluszny}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Pentland}},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Advances in Water resources}\ }\textbf {\bibinfo
+  {volume} {51}},\ \bibinfo {pages} {197} (\bibinfo {year} {2013})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Stoop}\ \emph {et~al.}(2019)\citenamefont {Stoop},
+  \citenamefont {Waisbord}, \citenamefont {Kantsler}, \citenamefont {Heinonen},
+  \citenamefont {Guasto},\ and\ \citenamefont {Dunkel}}]{stoop2019disorder}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Stoop}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Waisbord}},
+  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Kantsler}}, \bibinfo
+  {author} {\bibfnamefont {V.}~\bibnamefont {Heinonen}}, \bibinfo {author}
+  {\bibfnamefont {J.~S.}\ \bibnamefont {Guasto}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Dunkel}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Non-Newtonian Fluid Mechanics}\
+  }\textbf {\bibinfo {volume} {268}},\ \bibinfo {pages} {66} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bryant}\ \emph {et~al.}(1993)\citenamefont {Bryant},
+  \citenamefont {King},\ and\ \citenamefont {Mellor}}]{bryant1993network}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
+  {Bryant}}, \bibinfo {author} {\bibfnamefont {P.~R.}\ \bibnamefont {King}}, \
+  and\ \bibinfo {author} {\bibfnamefont {D.~W.}\ \bibnamefont {Mellor}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Transport in
+  porous media}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages} {53}
+  (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dong}\ and\ \citenamefont
+  {Blunt}(2009)}]{dong2009pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Dong}}\ and\ \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+  {Blunt}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review E}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages}
+  {036307} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Blunt}\ and\ \citenamefont
+  {Scher}(1995)}]{blunt1995pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+  {Blunt}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Scher}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  E}\ }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {6387} (\bibinfo
+  {year} {1995})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2017)\citenamefont {Alim},
+  \citenamefont {Parsa}, \citenamefont {Weitz},\ and\ \citenamefont
+  {Brenner}}]{alim2017local}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Alim}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Parsa}},
+  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Letters}\ }\textbf {\bibinfo {volume} {119}},\ \bibinfo {pages} {144501}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parsa}\ \emph {et~al.}(2021)\citenamefont {Parsa},
+  \citenamefont {Zareei}, \citenamefont {Santanach-Carreras}, \citenamefont
+  {Morris}, \citenamefont {Amir}, \citenamefont {Xiao},\ and\ \citenamefont
+  {Weitz}}]{shima2021}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Parsa}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zareei}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Santanach-Carreras}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Morris}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Amir}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Xiao}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {submitted}\ } (\bibinfo {year}
+  {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fraggedakis}\ \emph {et~al.}(2021)\citenamefont
+  {Fraggedakis}, \citenamefont {Chaparian},\ and\ \citenamefont
+  {Tammisola}}]{fraggedakis_chaparian_tammisola_2021}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Fraggedakis}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Chaparian}}, \ and\ \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+  {Tammisola}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of Fluid Mechanics}\ }\textbf {\bibinfo {volume} {911}},\ \bibinfo
+  {pages} {A58} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Datta}\ \emph {et~al.}(2013)\citenamefont {Datta},
+  \citenamefont {Chiang}, \citenamefont {Ramakrishnan},\ and\ \citenamefont
+  {Weitz}}]{datta2013spatial}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
+  {Datta}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Chiang}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ramakrishnan}}, \ and\
+  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {111}},\ \bibinfo {pages} {064501} (\bibinfo
+  {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {J{\"a}ger}\ \emph {et~al.}(2017)\citenamefont
+  {J{\"a}ger}, \citenamefont {Mendoza},\ and\ \citenamefont
+  {Herrmann}}]{jager2017channelization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {J{\"a}ger}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Mendoza}},
+  \ and\ \bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont {Herrmann}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  E}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages} {013110} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ristroph}\ \emph {et~al.}(2012)\citenamefont
+  {Ristroph}, \citenamefont {Moore}, \citenamefont {Childress}, \citenamefont
+  {Shelley},\ and\ \citenamefont {Zhang}}]{ristroph2012sculpting}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Ristroph}}, \bibinfo {author} {\bibfnamefont {M.~N.}\ \bibnamefont {Moore}},
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Childress}}, \bibinfo
+  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Shelley}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Zhang}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
+  Academy of Sciences}\ }\textbf {\bibinfo {volume} {109}},\ \bibinfo {pages}
+  {19606} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hacking}\ \emph {et~al.}(1996)\citenamefont
+  {Hacking}, \citenamefont {VanBavel},\ and\ \citenamefont
+  {Spaan}}]{hacking1996shear}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Hacking}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {VanBavel}}, \
+  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Spaan}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {American Journal
+  of Physiology-Heart and Circulatory Physiology}\ }\textbf {\bibinfo {volume}
+  {270}},\ \bibinfo {pages} {H364} (\bibinfo {year} {1996})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Wan}\ and\ \citenamefont
+  {Fell}(2004)}]{wan2004investigation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+  {Wan}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Fell}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of
+  Geotechnical and Geoenvironmental Engineering}\ }\textbf {\bibinfo {volume}
+  {130}},\ \bibinfo {pages} {373} (\bibinfo {year} {2004})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Steeb}\ \emph {et~al.}()\citenamefont {Steeb},
+  \citenamefont {Diebels},\ and\ \citenamefont
+  {Vardoulakis}}]{steeb2007modeling}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Steeb}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Diebels}}, \
+  and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Vardoulakis}},\
+  }\enquote {\bibinfo {title} {Modeling internal erosion in porous media},}\
+  in\ \href@noop {} {\emph {\bibinfo {booktitle} {Computer Applications In
+  Geotechnical Engineering}}},\ pp.\ \bibinfo {pages} {1--10}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Marot}\ \emph {et~al.}(2012)\citenamefont {Marot},
+  \citenamefont {Le}, \citenamefont {Garnier}, \citenamefont {Thorel},\ and\
+  \citenamefont {Audrain}}]{marot2012study}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Marot}}, \bibinfo {author} {\bibfnamefont {V.~D.}\ \bibnamefont {Le}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Garnier}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Thorel}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Audrain}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {European Journal of Environmental and Civil
+  Engineering}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {1}
+  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sibille}\ \emph {et~al.}(2015)\citenamefont
+  {Sibille}, \citenamefont {Lomin{\'e}}, \citenamefont {Poullain},
+  \citenamefont {Sail},\ and\ \citenamefont {Marot}}]{sibille2015internal}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Sibille}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Lomin{\'e}}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Poullain}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Sail}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Marot}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Hydrological Processes}\ }\textbf {\bibinfo
+  {volume} {29}},\ \bibinfo {pages} {2149} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Derr}\ \emph {et~al.}(2020)\citenamefont {Derr},
+  \citenamefont {Fronk}, \citenamefont {Weber}, \citenamefont {Mahadevan},
+  \citenamefont {Rycroft},\ and\ \citenamefont {Mahadevan}}]{derr2020flow}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~J.}\ \bibnamefont
+  {Derr}}, \bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont {Fronk}},
+  \bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont {Weber}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Mahadevan}}, \bibinfo {author}
+  {\bibfnamefont {C.~H.}\ \bibnamefont {Rycroft}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Mahadevan}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo
+  {volume} {125}},\ \bibinfo {pages} {158002} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hu}\ and\ \citenamefont
+  {Cai}(2013)}]{hu2013adaptation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Hu}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Cai}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Letters}\ }\textbf {\bibinfo {volume} {111}},\ \bibinfo {pages} {138701}
+  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ronellenfitsch}\ and\ \citenamefont
+  {Katifori}(2016)}]{ronellenfitsch2016global}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Ronellenfitsch}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Katifori}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Letters}\ }\textbf {\bibinfo {volume} {117}},\ \bibinfo
+  {pages} {138301} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kramer}\ and\ \citenamefont
+  {MacKinnon}(1993)}]{kramer1993localization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Kramer}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {MacKinnon}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Reports on Progress in Physics}\ }\textbf {\bibinfo {volume} {56}},\
+  \bibinfo {pages} {1469} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Corson}(2010)}]{corson2010fluctuations}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Corson}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Letters}\ }\textbf {\bibinfo {volume} {104}},\ \bibinfo
+  {pages} {048703} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Katifori}\ \emph {et~al.}(2010)\citenamefont
+  {Katifori}, \citenamefont {Sz{\"o}ll{\H{o}}si},\ and\ \citenamefont
+  {Magnasco}}]{katifori2010damage}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Katifori}}, \bibinfo {author} {\bibfnamefont {G.~J.}\ \bibnamefont
+  {Sz{\"o}ll{\H{o}}si}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~O.}\
+  \bibnamefont {Magnasco}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Physical review letters}\ }\textbf {\bibinfo {volume} {104}},\
+  \bibinfo {pages} {048704} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ocko}\ and\ \citenamefont
+  {Mahadevan}(2015)}]{ocko2015feedback}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
+  {Ocko}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Mahadevan}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Letters}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo
+  {pages} {134501} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Edery}\ \emph {et~al.}(2014)\citenamefont {Edery},
+  \citenamefont {Guadagnini}, \citenamefont {Scher},\ and\ \citenamefont
+  {Berkowitz}}]{edery2014origins}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Edery}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Guadagnini}},
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Scher}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Berkowitz}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Water Resources Research}\
+  }\textbf {\bibinfo {volume} {50}},\ \bibinfo {pages} {1490} (\bibinfo {year}
+  {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Edery}\ \emph {et~al.}(2016)\citenamefont {Edery},
+  \citenamefont {Porta}, \citenamefont {Guadagnini}, \citenamefont {Scher},\
+  and\ \citenamefont {Berkowitz}}]{edery2016characterization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Edery}}, \bibinfo {author} {\bibfnamefont {G.~M.}\ \bibnamefont {Porta}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Guadagnini}}, \bibinfo
+  {author} {\bibfnamefont {H.}~\bibnamefont {Scher}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Berkowitz}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Transport in Porous Media}\ }\textbf
+  {\bibinfo {volume} {115}},\ \bibinfo {pages} {291} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\end{thebibliography}%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-03-06 old_files/june14/supp.tex
Updates from Overleaf

--- 2022-03-06 backup_Sep_2_2021/supp.tex
@@
 This condition guarantees that at each step a small amount of material is eroded and there is no sudden change in the network.
-We further test the convergence by decreasing $\max(\Delta r_{ij})$ to half and we observe that the average relative change in the flux vector is $\approx 1.2\%$, and the PDFs remain intact without any notable change.
+We further test the convergence by decreasing $\max(\Delta r_{ij})$ to half and we observe that the average relative change in the flux vector is $\aprrox 1.2\%$, and the PDFs remain intact without any notable change.
 The network size for the 2d/3d networks is $N_x=100,N_y=50$/$N_x=50,N_y=12, N_z=12$ unless mentioned otherwise.
@@
   \centering
-  \includegraphics[width=.75\textwidth]{FigS1.pdf} % grid-analytica
+  \includegraphics[width=.75\textwidth]{./FigS1.pdf} % grid-analytica
   \caption{(a) Schematic of a  diamond grid network of tubes.
@@
 % The values of flux at each layer $q(L,i)$ are not independent for neighboring sites; however, in our mean-field approximation, we ignore such correlations.  
-Taking the Laplace transform of the above equation and defining $\tilde p(s)  \equiv \int_0^{\infty} p(q) e^{-qs} dq$ one obtains
+Taking the Laplace transform of the above equation and defining $\tilde p(s) & \equiv \int_0^{\infty} p(q) e^{-qs} dq$ one obtains
 %
@@
      % \centering
-      \includegraphics[width = 1.0\textwidth]{FigS2.pdf}
+      \includegraphics[width = 1.0\textwidth]{./FigS2.pdf}
      \caption{Erosion in a topologically random 3D network of tubes with $N_x=20, N_y=12, N_z=12$ points for Voronoi cell initialization and an initial uniform broad distribution of tube diameters randomly sampled from $\mathcal{U}(1,14)$.
@@
     % \centering
- \includegraphics[width=0.75\textwidth]{FigS3.pdf} % Fig2-Sdiamond.pdf
+ \includegraphics[width=0.75\textwidth]{./FigS3.pdf} % Fig2-Sdiamond.pdf
      \caption{Erosion in a diamond grid network with $N_x=100, N_y=50$ randomly distributed nodes and an initially broad  distribution of tube diameter randomly sampled from $\mathcal{U}(1,14)$.
@@
     % \centering
- \includegraphics[width=0.72\textwidth]{FigS4.pdf}
+ \includegraphics[width=0.72\textwidth]{./FigS4.pdf}
      \caption{Erosion in a structured diamond grid network with $N_x=50, N_y=50$ and an initially narrow distribution of tube diameters randomly sampled from  $\mathcal{U}\left(d_0(1-\epsilon), d_u(1+\epsilon)\right) $ where  $d_0$ is the average diameter and $\epsilon=0.03$.
@@
     % \centering
-    \includegraphics[width = 0.70\textwidth]{FigS5.pdf}
+    \includegraphics[width = 0.70\textwidth]{./FigS5.pdf}
     \caption{The heat map for the average change in the order parameter corresponding to the networks shown in Fig.
@@
 % \clearpage
-\bibliography{ref}% Produces the bibliography via BibTeX.
-
+% \bibliography{ref}% Produces the bibliography via BibTeX.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{5}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{https://doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{git(2021)}]{githubrepo}%
+  \BibitemOpen
+  \href@noop {} {\bibinfo {title} {Network instability}},\ \bibinfo
+  {howpublished} {\url{https://github.com/ahmadzareei/networkInstability}}
+  (\bibinfo {year} {2021})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Liu}\ \emph {et~al.}(1995)\citenamefont {Liu},
+  \citenamefont {Nagel}, \citenamefont {Schecter}, \citenamefont {Coppersmith},
+  \citenamefont {Majumdar}, \citenamefont {Narayan},\ and\ \citenamefont
+  {Witten}}]{liu1995force}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.-h.}\ \bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont {Nagel}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Schecter}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Coppersmith}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Majumdar}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Narayan}},\ and\ \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Witten}},\ }\bibfield  {title} {\bibinfo
+  {title} {Force fluctuations in bead packs},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
+  {269}},\ \bibinfo {pages} {513} (\bibinfo {year} {1995})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Coppersmith}\ \emph {et~al.}(1996)\citenamefont
+  {Coppersmith}, \citenamefont {Liu}, \citenamefont {Majumdar}, \citenamefont
+  {Narayan},\ and\ \citenamefont {Witten}}]{coppersmith1996model}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Coppersmith}}, \bibinfo {author} {\bibfnamefont {C.-h.}\ \bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Majumdar}},
+  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Narayan}},\ and\ \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {Witten}},\ }\bibfield  {title}
+  {\bibinfo {title} {Model for force fluctuations in bead packs},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review E}\ }\textbf
+  {\bibinfo {volume} {53}},\ \bibinfo {pages} {4673} (\bibinfo {year}
+  {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2017)\citenamefont {Alim},
+  \citenamefont {Parsa}, \citenamefont {Weitz},\ and\ \citenamefont
+  {Brenner}}]{alim2017local}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Alim}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Parsa}},
+  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\
+  }\bibfield  {title} {\bibinfo {title} {Local pore size correlations determine
+  flow distributions in porous media},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
+  {119}},\ \bibinfo {pages} {144501} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Parsa}\ \emph {et~al.}(2021)\citenamefont {Parsa},
+  \citenamefont {Zareei}, \citenamefont {Santanach-Carreras}, \citenamefont
+  {Morris}, \citenamefont {Amir}, \citenamefont {Xiao},\ and\ \citenamefont
+  {Weitz}}]{shima2021}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Parsa}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zareei}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Santanach-Carreras}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Morris}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Amir}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Xiao}},\ and\ \bibinfo {author}
+  {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ }\bibfield  {title} {\bibinfo
+  {title} {Unexpected scaling of interstitial velocities with permeability due
+  to polymer retention in porous media},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {submitted}\ } (\bibinfo {year} {2021})}\BibitemShut
+  {NoStop}%
+\end{thebibliography}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}
 %
-
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-
-\newpage
-\section{Clogging behavior at initial times}
-% 
-Considering a small change in the radius of edges, and as a result, the conductance of the edges $\mathbf{C}+\delta \mathbf{C}$, using Eq. \eqref{main-solve-eq} we find that 
-%
-\begin{align}
-    \ket{P'} &=  \ket{P} -  \left( \Delta_n^\top\mathbf{C} \Delta_n\right)^{-1}\left[  \left( \Delta_n^\top \delta \mathbf{C} \Delta_n\right)\ket{P} + \left( \Delta_n^\top\delta \mathbf{C} \Delta_b\right) \ket{P_{BC}}\right],
-\end{align}
-%
-where we used the fact that for an invertible matrix $\mathbf{A}$ we have 
-%
-\begin{align}
-    \left(\mathbf{A} + \delta \mathbf{A} \right)^{-1} = \mathbf{A}^{-1} - \left( \mathbf{A}^{-1} \delta \mathbf{A}\right) \mathbf{A}^{-1} + \left( \mathbf{A}^{-1}  \delta \mathbf{A}\right)^{2}\mathbf{A}^{-1}  + \cdots.
-\end{align}
-%
-Calculating for the changes in the fluid flux, we find that 
-%
-\begin{align}
-\ket{q'} & = \left( \mathbf{C}+ \delta \mathbf{C}  \right)\left( \Delta_b \ket{P_{BC}} +  \Delta_n \ket{P'} \right) \\
-& = \ket{q} + \delta\mathbf{C} \mathbf{C}^{-1}\ket{q} - \mathbf{C} \Delta_n \left( \Delta_n^\top\mathbf{C} \Delta_n\right)^{-1}\left[  \left( \Delta_n^\top \delta \mathbf{C} \Delta_n\right)\ket{P} + \left( \Delta_n^\top\delta \mathbf{C} \Delta_b\right) \ket{P_{BC}}\right].
-\end{align}
-%
-The above equation can then be used to study the evolution of order parameter in the networks.
-Note that during the blockage of pore-throats, the connectivity between the nodes changes and as a result network's connectivity matrix $\Delta$ changes and the above approximation will not hold anymore.
-
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-
-% ****** End of file apssamp.tex ******
-
- If we set
-$\eta(w) = \delta(w-1/2)$, then the flow at each node has probability of
-$1/2$ to move to either of the neighboring sites. As a result the flow at a given depth $L$ will become homogeneous as $P_L(Q) = \delta (Q-\bar{Q})$ where $\bar{Q}$
-is the average of input fluid flow. This results is the same as having the same
-diameter for all the edges which results in a singular solution in the structured grid.
-% 
-\subsection*{$P(Q)$ decays faster than $Q^{-n}$ for any $n$}
-We first show that $P(Q)$ decays faster than any power of $Q$ for any
-weight distributions. We expand the Laplace transform using a Taylor expansion as 
-%
-\begin{align}
-  \tilde P(s) = 1 + \sum_j \tilde P_{j} s^{j}.
-\end{align}
-%
-Inserting this expansion into Eq. \eqref{eq:main-laplace}, we obtain
-%
-\begin{align}
-  1 + \sum_j \tilde P_{j} s^{j}  & = \lp  \int_0^1 d w \eta(w) \lb 1 + \sum_j \tilde P_{j} (sw)^{j}\rb    \rp^{N}  = \lp  1 + \sum_j \tilde P_j \langle w^{j}\rangle  s^{j}   \rp^{N}
-\end{align}
-%
-where $\langle w^j \rangle = \int_0^1 \eta(w) w^j dw$ is the $j$-th
-moment of the weights $w$. In the above equation we can observe that
-%
-\begin{align}
-  P_j \lp N \langle w^j\rangle -1 \rp = G(P_{j-1}, P_{j-1}, \cdots, P_1)
-\end{align}
-%
-In the above equation $P_j$ can only diverge only if $N\langle w^j
-\rangle -1=0$. If $w$ can only be zero and one, then $\langle
-w^j\rangle =\langle w \rangle = 1/N$ and the coefficient can become
-zero! Other than this special distribution, when $0 \leq w \leq 1$, then
-%
-\begin{align}
-  & w\in [0,1] \rightarrow w>w^2>w^3> \cdots \\
-  & \forall k>1 \rightarrow \langle w^k \rangle < \langle w \rangle = \frac{1}{N} 
-\end{align}
-%
-which means that $N\langle w^j \rangle -1\neq 0$ and as a result
-$P_j$ is finite. $P_j$ on the other hand is the $j$-th moment or
-$\langle Q^j\rangle$ and it is finite. If $P\approx Q^{-n}$, then the
-$n$-th moment will not be finite i.e. $\langle Q^{n+1}\rangle =
-P_{n+1}$ is not finite. We can then conclude that $P(Q)$ should go to
-zero faster than any $Q^{-n}$ as $Q\to \infty$! In other words $d \log
-P(Q) / d \log Q \to -\infty$ as $Q\to \infty$.  
-% 
-\subsection*{Exponential Decay}
-%
-The main recursive governing equation for a diamond grid is  
-%
-\begin{align}
-  \tilde P(s) = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{2} \label{eq:main-recur}
-\end{align}
-%
-% In order to have an approximation for $\eta(w)$ we consider the following situation:
-At each node there are two neighboring nodes where the flux is distributed by
-$w_1$ and $w_2$ among them. Assuming that $w_1$ is uniformly distributed
-between $0$ and $1$, then $w_2 = 1-w_1$ (due to  conservation of
-mass $w_1 + w_2 = 1$). Now $\eta(w)$ can be obtained using 
-%
-\begin{align}
-  & \eta(w) = M \int_0^1 dw_1 \delta(1-w_1-w) =  M, \\
-  \text{since }& \int_0^1 \eta(w) dw = 1 \to M =1 \\
-  & \eta (w) = 1
-\end{align}
-%
-Just for completeness, if there are three neighboring connections ($N=3$), then we
-have
-%
-\begin{align}
-  \eta(w) & = M \int_0^1 dw_1 \int_0^1 dw_2 \delta(1-w_1-w_2 - w)\\
-          & = M(1-w)  \to \int_0^1\eta(w) dw = 1 \to M = \frac{1}{2} \\
-  & \eta(w) = \frac{1}{2} (1-w)
-\end{align}
-%
-As a result Eq.~\eqref{eq:main-recur} simplifies to
-%
-\begin{align}
-  \tilde P(s) = \lp  \int_0^1 d w  \tilde P(s w)  \rp^{2} 
-\end{align}
-%
-In order to solve the above equation, we assume $\tilde V (s) =
-\sqrt{\tilde{P}(s)}$.
-%
-\begin{align}
-  \tilde{V}(s) & = \int_0^1 dw \tilde V (sw) = \int_0^s \frac{du}{s}  \tilde{V}^{2}(u) \\
-  s\tilde{V}(s) & = \int_0^s du  \tilde{V}^2(u) \\
-\end{align}
-%
-Taking the differentiation with respect to $s$ yields
-%
-\begin{align}
-  \tilde{V}(s) + s \frac{d \tilde{V}(s)}{d s} = \tilde{V}^2(s) \\
-  \frac{d \tilde{V}}{\tilde{V}^2-\tilde{V}} = \frac{ds}{s}  \\
-  \log\lp \frac{1-\tilde{V}}{\tilde{V}} \rp  = \log(s)\\
-  \tilde{V}(s) = \frac{1}{1+Cs} 
-\end{align}
-%
-We set the mean to $1$ i.e.,
-%
-\begin{align}
-  \int_0^{\infty} Q P(Q) dQ = 1 \to \frac{d\tilde{P}}{ds}|_{s=0}  = -1\\
-  \frac{d \tilde{V}}{ds}  = \frac{1}{2 \sqrt{\tilde{P}(s)}} \frac{d \tilde{P}(s)}{d s}   \to \frac{d\tilde{V}(s)}{ds}|_{s=0} =\frac{-1}{2} \\
-  \frac{d\tilde{V}(s)}{ds} = \frac{-C}{(1+Cs)^{2}}|_{s=0} = -C = \frac{-1}{2}  \to C=\frac{1}{2} 
-\end{align}
-%
-As a result, we have
-%
-\begin{align}
-  \tilde{P}(s) = \lp\frac{1}{1+s/2} \rp^2 \\
-  P(Q) = 4Q e^{-2Q}
-\end{align}
-%
-We can then show that for a uniform distribution of $w$'s, the PDF of
-$Q$'s become an exponential tail. For other distribution of $w$'s, we
-similarly find a similar trend which can be seen in the numerical simulations. 
-% Actually, we showed that the PDF of $Q$ should decay faster than any power law for any distribution of
-$w$. 
-Note that in the distribution with exponential tail, the only parameter that determines the the PDF of the average fluid flow.
-This shows that why we observe the universal behaviour for the PDF of normalized fluid flux where the average of normalized fluid flux is unity.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-
-For each resistor we know that
-%
-\begin{align}
-    q_{e} = R_{e} \Delta P_{e}
-\end{align}
-%
-Assume that matrix $\mathbf{C}$ relates the pressure at nodes to the pressure difference, where 
-%
-\begin{align}
-    \ket{\Delta P_e} = \mathbf{C} \ket{P_n}, \quad \ket{q_e} = \mathbf{R} \ket{\Delta P_e}, \quad \ket{q_n} = \mathbf{C}^\top \ket{q_e} \\
-    \ket{q_n} = \mathbf{C}^\top \mathbf{R} \mathbf{C}\ket{P_n}
-\end{align}
-%
-\begin{align}
-    \mathbf{C}^\top \mathbf{R} \mathbf{C}\begin{bmatrix} P_1 \\ P_2 \\ \vdots \\ P_n
-    \end{bmatrix}
-    = \ket{q} \to \begin{bmatrix} \mathbf{C_{b}}^\top \mathbf{R} \mathbf{C_{b}}  & \vline &    \mathbf{C_{b}}^\top \mathbf{R} \mathbf{C_{n}} \\ \hline  
-    \mathbf{C_{n}}^\top \mathbf{R} \mathbf{C_{b}} & \vline & \mathbf{C_{n}}^\top \mathbf{R} \mathbf{C_{n}}
-    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ \hline  P_n \\ \vdots \\ P_{N_n}
-    \end{bmatrix} = \begin{bmatrix} q_1 \\ q_2 \\ \vdots \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \\
-    \begin{bmatrix} 
-    \mathbf{A}_{bb} & \mathbf{A}_{bn} \\
-    \mathbf{A}_{nb} & \mathbf{A}_{nn}       
-    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ \hline  P_n \\ \vdots \\ P_{N_n}
-    \end{bmatrix} = \begin{bmatrix} q_1 \\ q_2 \\ \vdots \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \to \begin{cases} 
-        \mathbf{A}_{bb} \ket{P_{BC}} + \mathbf{A}_{bn}  \ket{P_{n}} = \ket{q} \\
-    \mathbf{A}_{nb}\ket{P_{BC}} +  \mathbf{A}_{nn} \ket{P_n} = 0 
-    \end{cases} \\
-     \mathbf{A}_{nn} \ket{P_n} =- \mathbf{A}_{nb}\ket{P_{BC}} \to \mathbf{A}_{nn} \ket{P_n} = \mathbf{b}
-\end{align}
-
-In solving our problem, we have 
-%
-\begin{align}
- \mathbf{C}_{n}^\top \mathbf{R} \mathbf{C}_{n}\ket{P} =     - \mathbf{C}_{n}^\top \mathbf{R} \mathbf{C}_{b}\ket{P}_{BC}  \to \mathbf{A}_{nn} \ket{P_n} = \mathbf{B}\ket{P}_{BC}
-\end{align}
-%
-where $\mathbf{b}$ comes from the boundary conditions.
-When the pressures are found then $\ket{q} = \mathbf{R}\mathbf{C} \ket{P}$, we can obtain the new fluxes.
-Now the question is that if $\mathbf{R} = \mathbf{R}+\delta \mathbf{R}$, then what happens to the $\ket{q}$ with respect to the first order of perturbation?
-if we set $\mathbf{R} = \mathbf{R}+\delta \mathbf{R}$ then
-%
-\begin{align}
-\mathbf{C}_{n}^\top \left( \mathbf{R} + \delta \mathbf{R} \right) \mathbf{C}_{n}\ket{P'} &= - \mathbf{C}_{n}^\top \left( \mathbf{R} + \delta \mathbf{R} \right) \mathbf{C}_{b}\ket{P}_{BC} \\
-(\mathbf{A} + \delta \mathbf{A}) \ket{P'} &= (\mathbf{B} + \delta \mathbf{B})\ket{P_{BC}} \\
-\ket{P'} &=(\mathbf{A} + \delta \mathbf{A})^{-1} (\mathbf{B} + \delta \mathbf{B})\ket{P_{BC}}  \\
-\ket{P'} &= \left( \mathbf{A}^{-1} - \left( \mathbf{A}^{-1} \delta \mathbf{A}\right) \mathbf{A}^{-1}\right) (\mathbf{B} + \delta \mathbf{B})\ket{P_{BC}} \\
-\ket{P'} &= \mathbf{A}^{-1} \mathbf{B} \ket{P_{BC}} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} - \mathbf{A}^{-1} \delta \mathbf{A} \mathbf{A}^{-1} \mathbf{B} \ket{P_{BC}} \\
-\ket{P'} &= \ket{P} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} - \mathbf{A}^{-1} \delta \mathbf{A} \ket{P}
-\end{align}
-%
-where we used the fact that 
-%
-\begin{align}
-    \left(\mathbf{A} + \delta \mathbf{A} \right)^{-1} = \mathbf{A}^{-1} - \left( \mathbf{A}^{-1} \delta \mathbf{A}\right) \mathbf{A}^{-1} + \left( \mathbf{A}^{-1}  \delta \mathbf{A}\right)^{2}\mathbf{A}^{-1}  + \cdots
-\end{align}
-%
-The fluid flow can then be obtained 
-%
-\begin{align}
-    \ket{q'} = \left( \mathbf{R}+ \delta \mathbf{R}\right) \mathbf{C} \ket{P'}    \\
-    \text{where} \quad \mathbf{A} = \mathbf{C}^\top\mathbf{R} \mathbf{C},\quad \delta \mathbf{A} = \mathbf{C}^\top \delta \mathbf{R} \mathbf{C}
-\end{align}
-%
-Upto the first order, we find that
-%
-\begin{align}
-    \ket{P'} &= \ket{P} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} - \mathbf{A}^{-1} \delta \mathbf{A} \ket{P} \\
-    & = \left(\mathbf{I} - \mathbf{A}^{-1} \delta \mathbf{A}  \right) \ket{P} + \mathbf{A}^{-1}\delta \mathbf{B}\ket{P_{BC}} \\
-    & = \left( \mathbf{I} - \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1} \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\right)\ket{P} -  \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1} \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}} \\
-    & = \ket{P} -  \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right]
-\end{align}
-%
-Calculating the fluid flow, we obtain
-%
-\begin{align}
-\ket{q'} & = \left( \mathbf{R}+ \delta \mathbf{R}  \right)\left( \mathbf{C}_b \ket{P_{BC}} +  \mathbf{C}_n \ket{P'} \right) \\
-& = \left( \mathbf{R}+ \delta \mathbf{R}  \right)\left( \mathbf{C}_b \ket{P_{BC}} + \mathbf{C}_n \left\{ \ket{P} -  \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right] \right\} \right) \\
-& = \mathbf{R}\left( \mathbf{C}_b \ket{P_{BC}} +  \mathbf{C}_n \ket{P} \right) + \delta \mathbf{R}\left( \mathbf{C}_b \ket{P_{BC}} +  \mathbf{C}_n \ket{P} \right) - \mathbf{R} \mathbf{C}_n \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right]  \\
-& = \ket{q} + \delta\mathbf{R} \mathbf{R}^{-1}\ket{q} - \mathbf{R} \mathbf{C}_n \left( \mathbf{C}_n^\top\mathbf{R} \mathbf{C}_n\right)^{-1}\left[  \left( \mathbf{C}_n^\top \delta \mathbf{R} \mathbf{C}_n\right)\ket{P} + \left( \mathbf{C}_n^\top\delta \mathbf{R} \mathbf{C}_b\right) \ket{P_{BC}}\right]
-\end{align}
-
-\newpage
-\section{Example}
-%
-
-\begin{figure}
-    \vspace{5mm}
-    \centering
-    \includegraphics[width=0.2\textwidth]{./Figs/fig1}
-    \caption{An example of network structure for a network of pipes}
-    \label{Fig:fig1}
-\end{figure}
-%
-%
-\begin{align}
-    \ket{\Delta P_\text{e}} = \mathbf{C} \ket{P_n}, \quad  \ket{q_e} = \mathbf{R} \ket{\Delta P_e}, \quad \ket{q_n} = \mathbf{C}^\top \ket{q_e} \\
-    \begin{bmatrix} \Delta p_e^1 \\ \Delta p_e^2 \\\Delta p_e^3 \\\Delta p_e^4 \\\Delta p_e^5 \\ \Delta p_e^6
-    \end{bmatrix} = \begin{bmatrix} 
-    -1 & 1 & 0 & 0 \\
-     0 & -1 & 1 & 0 \\
-     0 & 0 & -1 & 1 \\
-    -1 & 0 & 0 & 1 \\
-    -1 & 0 & 1 & 0 \\
-     0 & -1 & 0 & 1
-    \end{bmatrix}\begin{bmatrix} P_n^1 \\ P_n^2 \\  P_n^3 \\P_n^4\end{bmatrix}, \quad 
-    \begin{bmatrix}
-    q_e^1\\    q_e^2\\    q_e^3\\    q_e^4\\    q_e^5\\    q_e^6\\
-    \end{bmatrix} = \begin{bmatrix}
-    R_1 & 0 & 0 & 0 & 0 & 0 \\
-    0 & R_2 & 0 & 0 & 0 & 0 \\
-    0 & 0 & R_3 & 0 & 0 & 0 \\
-    0 & 0 & 0 & R_4 & 0 & 0 \\
-    0 & 0 & 0 & 0 & R_5 & 0 \\
-    0 & 0 & 0 & 0 & 0 & R_6 
-    \end{bmatrix}
-    \begin{bmatrix} \Delta p_e^1 \\ \Delta p_e^2 \\\Delta p_e^3 \\\Delta p_e^4 \\\Delta p_e^5 \\ \Delta p_e^6
-    \end{bmatrix} \\
-    \begin{bmatrix}
-    q_n^1 \\    q_n^2 \\    q_n^3 \\    q_n^4 \\
-    \end{bmatrix}= \begin{bmatrix} 
-    -1 & 0 & 0 & -1 & -1 & 0 \\
-    1 & -1 & 0 & 0 & 0 & -1 \\
-    0 & 1 & -1 & 1 & 0 & 0  \\
-    0 & 0 & 1 & 1 & 0 & 1
-    \end{bmatrix}\begin{bmatrix}
-    q_e^1\\    q_e^2\\    q_e^3\\    q_e^4\\    q_e^5\\    q_e^6\\
-    \end{bmatrix}
-\end{align}

### 2022-03-06 old_files/submission-arxiv/paper_arxiv.tex
Updates from Overleaf

--- 2022-03-06 old_files/june14/paper.tex
@@
 
-Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature as well as in numerous environmental and industrial applications~\cite{fraggedakis2015flow,sahimi2011flow,schlesinger1999carbon,duduta2011semi,sun2019hierarchical,marbach2016pruning,tero2010rules,alim2013random,heaton2010growth,smith2017multiphase,ferguson2012nonequilibrium}.
+Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature~\cite{marbach2016pruning,alim2013random,tero2010rules,heaton2010growth} as well as in numerous environmental~\cite{schlesinger1999carbon,winkler1979pore,batzle1992seismic} and industrial applications~\cite{duduta2011semi,sun2019hierarchical,smith2017multiphase,ferguson2012nonequilibrium}.
 The disordered pore structure of a porous medium results in heterogeneously distributed fluid flow between the pores.
@@
     % \centering
-    \includegraphics[width = 0.45\textwidth]{./Fig1.pdf}
+    \includegraphics[width = 0.45\textwidth]{Fig1.pdf}
     % \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}.
@@
     % \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
-    \includegraphics[width = 0.48\textwidth]{./Fig2.pdf}
+    \includegraphics[width = 0.48\textwidth]{Fig2_.pdf}
     \caption{Erosion in a network of pipes.
@@
     % \centering
-     \includegraphics[width = 0.45\textwidth]{./Fig3.pdf}
+     \includegraphics[width = 0.45\textwidth]{Fig3.pdf}
     \caption{ (a) Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig.
@@
 
-\textit{Analysis of generalized Model}-- So far we focused on erosion dynamics with $m=1$ (Eq.
+\textit{Analysis of generalized model}-- So far we focused on erosion dynamics with $m=1$ (Eq.
 \eqref{eq:erosion-law}) since it directly corresponds to erosion laws of interest, i.e.
@@
     \centering
-    \includegraphics[width = 0.45\textwidth]{./Fig4.pdf}
+    \includegraphics[width = 0.45\textwidth]{Fig4.pdf}
     \caption{{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
@@
 \begin{acknowledgments}
-We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery and Eleni Katifori for useful discussions.
+We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery,  Eleni Katifori, and Chris Rycroft
+for useful discussions.
 \end{acknowledgments}
@@
 % \bibliography{ref.bib}
-% \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{48}%
+\begin{thebibliography}{51}%
 \makeatletter
@@
 %</preamble>
-\bibitem [{\citenamefont {Fraggedakis}\ \emph {et~al.}(2015)\citenamefont
-  {Fraggedakis}, \citenamefont {Kouris}, \citenamefont {Dimakopoulos},\ and\
-  \citenamefont {Tsamopoulos}}]{fraggedakis2015flow}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Fraggedakis}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Kouris}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Dimakopoulos}}, \ and\
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Tsamopoulos}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physics of
-  Fluids}\ }\textbf {\bibinfo {volume} {27}},\ \bibinfo {pages} {082102}
-  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sahimi}(2011)}]{sahimi2011flow}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Sahimi}},\ }\href@noop {} {\emph {\bibinfo {title} {Flow and transport in
-  porous media and fractured rock: from classical methods to modern
-  approaches}}}\ (\bibinfo  {publisher} {John Wiley \& Sons},\ \bibinfo {year}
-  {2011})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Marbach}\ \emph {et~al.}(2016)\citenamefont
+  {Marbach}, \citenamefont {Alim}, \citenamefont {Andrew}, \citenamefont
+  {Pringle},\ and\ \citenamefont {Brenner}}]{marbach2016pruning}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Marbach}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Alim}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Andrew}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {117}},\ \bibinfo {pages} {178103} (\bibinfo
+  {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2013)\citenamefont {Alim},
+  \citenamefont {Amselem}, \citenamefont {Peaudecerf}, \citenamefont
+  {Brenner},\ and\ \citenamefont {Pringle}}]{alim2013random}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Alim}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Amselem}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Peaudecerf}}, \bibinfo
+  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
+  Academy of Sciences}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages}
+  {13306} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tero}\ \emph {et~al.}(2010)\citenamefont {Tero},
+  \citenamefont {Takagi}, \citenamefont {Saigusa}, \citenamefont {Ito},
+  \citenamefont {Bebber}, \citenamefont {Fricker}, \citenamefont {Yumiki},
+  \citenamefont {Kobayashi},\ and\ \citenamefont {Nakagaki}}]{tero2010rules}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Tero}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Takagi}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Saigusa}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Ito}}, \bibinfo {author}
+  {\bibfnamefont {D.~P.}\ \bibnamefont {Bebber}}, \bibinfo {author}
+  {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \bibinfo {author}
+  {\bibfnamefont {K.}~\bibnamefont {Yumiki}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Kobayashi}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Nakagaki}},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {327}},\ \bibinfo
+  {pages} {439} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Heaton}\ \emph {et~al.}(2010)\citenamefont {Heaton},
+  \citenamefont {L{\'o}pez}, \citenamefont {Maini}, \citenamefont {Fricker},\
+  and\ \citenamefont {Jones}}]{heaton2010growth}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~L.}\ \bibnamefont
+  {Heaton}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {L{\'o}pez}},
+  \bibinfo {author} {\bibfnamefont {P.~K.}\ \bibnamefont {Maini}}, \bibinfo
+  {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {N.~S.}\ \bibnamefont {Jones}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the Royal Society
+  B: Biological Sciences}\ }\textbf {\bibinfo {volume} {277}},\ \bibinfo
+  {pages} {3265} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Schlesinger}(1999)}]{schlesinger1999carbon}%
@@
   (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Winkler}\ and\ \citenamefont
+  {Nur}(1979)}]{winkler1979pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Winkler}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Nur}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Geophysical
+  Research Letters}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {1}
+  (\bibinfo {year} {1979})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Batzle}\ and\ \citenamefont
+  {Wang}(1992)}]{batzle1992seismic}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Batzle}}\ and\ \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Geophysics}\
+  }\textbf {\bibinfo {volume} {57}},\ \bibinfo {pages} {1396} (\bibinfo {year}
+  {1992})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Duduta}\ \emph {et~al.}(2011)\citenamefont {Duduta},
@@
   {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Marbach}\ \emph {et~al.}(2016)\citenamefont
-  {Marbach}, \citenamefont {Alim}, \citenamefont {Andrew}, \citenamefont
-  {Pringle},\ and\ \citenamefont {Brenner}}]{marbach2016pruning}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Marbach}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Alim}},
-  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Andrew}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
-  }\textbf {\bibinfo {volume} {117}},\ \bibinfo {pages} {178103} (\bibinfo
-  {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Tero}\ \emph {et~al.}(2010)\citenamefont {Tero},
-  \citenamefont {Takagi}, \citenamefont {Saigusa}, \citenamefont {Ito},
-  \citenamefont {Bebber}, \citenamefont {Fricker}, \citenamefont {Yumiki},
-  \citenamefont {Kobayashi},\ and\ \citenamefont {Nakagaki}}]{tero2010rules}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Tero}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Takagi}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Saigusa}}, \bibinfo
-  {author} {\bibfnamefont {K.}~\bibnamefont {Ito}}, \bibinfo {author}
-  {\bibfnamefont {D.~P.}\ \bibnamefont {Bebber}}, \bibinfo {author}
-  {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \bibinfo {author}
-  {\bibfnamefont {K.}~\bibnamefont {Yumiki}}, \bibinfo {author} {\bibfnamefont
-  {R.}~\bibnamefont {Kobayashi}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Nakagaki}},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {327}},\ \bibinfo
-  {pages} {439} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2013)\citenamefont {Alim},
-  \citenamefont {Amselem}, \citenamefont {Peaudecerf}, \citenamefont
-  {Brenner},\ and\ \citenamefont {Pringle}}]{alim2013random}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Alim}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Amselem}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Peaudecerf}}, \bibinfo
-  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
-  Academy of Sciences}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages}
-  {13306} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Heaton}\ \emph {et~al.}(2010)\citenamefont {Heaton},
-  \citenamefont {L{\'o}pez}, \citenamefont {Maini}, \citenamefont {Fricker},\
-  and\ \citenamefont {Jones}}]{heaton2010growth}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~L.}\ \bibnamefont
-  {Heaton}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {L{\'o}pez}},
-  \bibinfo {author} {\bibfnamefont {P.~K.}\ \bibnamefont {Maini}}, \bibinfo
-  {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {N.~S.}\ \bibnamefont {Jones}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the Royal Society
-  B: Biological Sciences}\ }\textbf {\bibinfo {volume} {277}},\ \bibinfo
-  {pages} {3265} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Smith}\ and\ \citenamefont
@@
   {2016})}\BibitemShut {NoStop}%
+\bibitem [{git(2021)}]{githubrepo}%
+  \BibitemOpen
+  \href@noop {} {\enquote {\bibinfo {title} {Network instability},}\ }\bibinfo
+  {howpublished} {\url{https://github.com/ahmadzareei/networkInstability}}
+  (\bibinfo {year} {2021})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Liu}\ \emph {et~al.}(1995)\citenamefont {Liu},
+  \citenamefont {Nagel}, \citenamefont {Schecter}, \citenamefont {Coppersmith},
+  \citenamefont {Majumdar}, \citenamefont {Narayan},\ and\ \citenamefont
+  {Witten}}]{liu1995force}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.-h.}\ \bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont {Nagel}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Schecter}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Coppersmith}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Majumdar}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Narayan}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Witten}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
+  {269}},\ \bibinfo {pages} {513} (\bibinfo {year} {1995})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Coppersmith}\ \emph {et~al.}(1996)\citenamefont
+  {Coppersmith}, \citenamefont {Liu}, \citenamefont {Majumdar}, \citenamefont
+  {Narayan},\ and\ \citenamefont {Witten}}]{coppersmith1996model}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Coppersmith}}, \bibinfo {author} {\bibfnamefont {C.-h.}\ \bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Majumdar}},
+  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Narayan}}, \ and\
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Witten}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review E}\ }\textbf
+  {\bibinfo {volume} {53}},\ \bibinfo {pages} {4673} (\bibinfo {year}
+  {1996})}\BibitemShut {NoStop}%
 \end{thebibliography}%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+\newpage
+\onecolumngrid
+
+\renewcommand{\thepage}{S\arabic{page}}
+\setcounter{page}{1}
+\renewcommand{\thesection}{S\arabic{section}}
+\setcounter{section}{0}
+\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\setcounter{figure}{0}
+\renewcommand{\theequation}{S\arabic{equation}}
+\setcounter{equation}{0}
+\def\lp{\left(}
+\def\rp{\right)}
+\def\lb{\left[}
+\def\rb{\right]}
+
+{\huge \textbf{Supplementary Material}}
+
+\section{S1. Simulation algorithm}
+\label{s1}
+%
+In our simulations, we tested two types of networks: (i) a topologically ordered (diamond-grid) network, (ii) a topologically random network (2d and 3d). 
+% In the diamond-grid network, we choose 100 nodes in the horizontal direction $N_x=100$ and 50 nodes in the vertical direction $N_y=50$ which in total results in $20,000$ edges in the network (see \cite{githubrepo}).
+The 2d random network is created using uniformly distributed points with on average $N_x\times N_y$ nodes in the horizontal and vertical directions where the randomly distributed points are connected using a Delaunay triangulation.
+The 3d random network similarly is obtained by a uniform distribution of $N_x\times N_y \times N_z$ points in space, where the the points are connected using Voronoi cell initialization.
+The diameter of each edge is sampled from either a uniform distribution with $\mathcal{U}(1,14)$, log-normal distribution with $\mu=3,\sigma=0.48$, or truncated normal distribution with $\mathcal{N}(\mu=7.0,\sigma=3.6)$, where all of the distributions have a coefficient of variation close to $0.5$.
+An external pressure is considered between the left-most nodes and the rightmost nodes ($p_\text{left}=10,p_\text{right}=0$).
+For each edge, assuming a Poiseuille flow, the fluid flux  $q$ and pressure difference $\delta P_e$ are related through $q_e = C_e \delta P_e$, where $C_e = \pi r^4_e/8\mu L_e$,  $L_e$ is the length of the tube, and $\mu$ is the viscosity of the fluid.
+We define $\vec{q}_e$ as the vector of fluid flux through all the edges, and as a result $\vec{q}_e = \mathbf{C} \mathbf{D}\vec{P}_n$ where $\vec{P}_n$ is the vector of pressure at all the nodes, $\mathbf{D}$ is the transpose of the network's oriented incidence matrix, and $\mathbf{C}$ is the diagonal matrix of edge conductances $\mathbf{C}_e = \text{diag} \left( C^{(1)}_e, C^{(2)}_e, \cdots,C^{(N_e)}_e\right)$.
+The orientation (or direction) of an edge is arbitrary selected, and it only determines the positive direction for the fluid flow in that edge.
+Next, we  use conservation of mass at the nodes to solve for the network pressure/flux at the nodes/edges.
+The conservation of mass at each node is
+%
+\begin{align}
+    \vec{q}_n = \mathbf{D}^\top \mathbf{C} \mathbf{D} \vec{P}_n, \label{eq:governeing}
+\end{align}
+%
+where $\vec{q}_n$ is the vector of total incoming flow to each node.
+The total incoming flow to an internal node is zero inside the network due to the conservation of mass, and can only be non-zero at the boundary nodes.
+Without loss of generality, we renumber the boundary nodes to $1,2,\cdots, N_{B}$, where $N_B$ shows the total number of nodes at the boundary.
+We re-partition Eq.
+\eqref{eq:governeing} to obtain
+
+\begin{align}
+ \begin{bmatrix} {\mathbf{D}_{b}}^\top \mathbf{C} {\mathbf{D}_{b}}  & \vline &    {\mathbf{D}_{b}}^\top \mathbf{C} {\mathbf{D}_{n}}\\ \hline   
+    {\mathbf{D}_{n}}^\top \mathbf{C} {\mathbf{D}_{b}} & \vline & {\mathbf{D}_{n}}^\top \mathbf{C} {\mathbf{D}_{n}}
+    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ P_{N_B} \\  \hline  P_{N_B+1} \\ \vdots \\ P_{N_n}
+    \end{bmatrix} = \begin{bmatrix} q^{BC}_1 \\ q^{BC}_2 \\ \vdots \\ q^{BC}_{N_B} \\ \hline  0 \\ \vdots \\ 0\end{bmatrix} \to 
+    \begin{bmatrix} 
+    \mathbf{A}_{bb} & \mathbf{A}_{bn} \\
+    \mathbf{A}_{nb} & \mathbf{A}_{nn}       
+    \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ P^{BC}_{N_B} \\ \hline  P_{N_B+1} \\ \vdots \\ P_{N_n}
+    \end{bmatrix} = \begin{bmatrix} q^{BC}_1 \\ q^{BC}_2 \\ \vdots \\ q^{BC}_{N_B}  \\ \hline  0 \\ \vdots \\ 0\end{bmatrix}, 
+\end{align}
+%
+where $\mathbf{A}_{st} = \mathbf{D}^\top_s \mathbf{C}\mathbf{D}^\top_t$ and  $s,t\in\left\{a,b\right\}$.
+The first $N_B$ elements of the pressure vector (i.e., $P_1, \cdots, P_{N_B}$) represent the pressure at the boundary nodes and the rest represent the pressure for the internal nodes.
+In summary the above equations can be written as a combination of two set of linear equations
+%
+\begin{subequations}\label{main-solve-eq}
+\begin{align}
+%     \begin{cases} 
+  & \mathbf{A}_{bb} \vec{P}_{BC} + \mathbf{A}_{bn}  \vec{P} = \vec{q}_{BC}, \label{maina} \\
+& \mathbf{A}_{nb}\vec{P}_{BC} +  \mathbf{A}_{nn} \vec{P} = 0. \label{mainb}
+%     \end{cases} 
+    % \\ \mathbf{A}_{nn} \ket{P_n} =- \mathbf{A}_{nb}\ket{P_{BC}} 
+    % \label{eq:main-network}
+ \end{align}
+\end{subequations}
+%
+where $\vec{P}_{BC} = [P^{BC}_1, \cdots, P^{BC}_{N_B}]^\top$ is the boundary nodes pressure vector, $\vec{q}_{BC} = [q^{BC}_1, \cdots, q^{BC}_{N_B}]^\top$ is the boundary nodes incoming fluid flux vector, and $\vec{P} = [P_{N_B+1}, \cdots, P_{N_n}]^\top$ is the unknown pressure vector for the rest of the nodes.
+If the pressure at the boundary is given,  we can use Eq.
+\eqref{mainb} to solve for the internal pressure values $\vec{P}$, and then use Eq.
+\eqref{maina} to find the required flux at the boundary nodes $\vec{q}_{BC}$.
+However, if fluid flux vector at the boundary nodes is given (i.e., $\vec{q}_{BC}$ is known), we need to simultaneously solve  Eqs.
+\eqref{maina} and \eqref{mainb} to find the boundary pressure vector  $\vec{P}_{BC}$ and internal nodes pressure vector $\vec{P}$.
+In either case, solving Eq.
+\eqref{main-solve-eq}  results in the nodes' pressure vector and also the fluid flux vector at the boundary nodes.
+The fluid flux at each edge can then be calculated using  $\vec{q}_e=\mathbf{C}_e \mathbf{D} \vec{P}_n$.
+Next, given the flux at each edge  $q_e$, we increase (decrease) the edge radius under erosion (clogging) using
+%
+\begin{align}
+    \frac{dr_e}{dt} \propto \pm  \frac{q^m_e}{r_e^n},
+\end{align}
+%
+and re-iterate the process to solve for the new fluid flux vector.
+We use a simple forward Euler for time integration.
+For each iteration, we choose the time step $dt$ so that $\max(dr_e) = 0.1 r_0$, where $r_0$ is the smallest radius among all edges.
+% Note that $r_{ij} (t+\delta t)  = r_{ij} (t)  + (\alpha \delta t)  q_{ij} (t)/ r^n_{ij} (t) $, where the coefficient $\alpha \delta t$ is chosen such that the maximum change in the radius at each time step is smaller than one-tenth  of the smallest tube's radius i.e.
+$\max (\Delta r_{ij}) \leq r_\text{min}/10$ of the smallest radius at the initial configuration.
+This condition guarantees that at each step a small amount of material is eroded and there is no sudden change in the network.
+We further test the convergence by decreasing $\max(\Delta r_{ij})$ to half and we observe that the average relative change in the flux vector is $\approx 1.2\%$, and the PDFs remain intact without any notable change.
+The network size for the 2d/3d networks is $N_x=100,N_y=50$/$N_x=50,N_y=12, N_z=12$ unless mentioned otherwise.
+In either case, the network has an order of $10^3$ edges.
+The code is publicly available in a GitHub repository \cite{githubrepo}.
+
+%
+% \begin{figure}[h]
+%     % \centering
+%     \includegraphics[width = 0.75\textwidth]{Figs/Fig2_random-low.png}
+%     \caption{Ahmad's version: Erosion in a topologically random network of pipes.
+The first row shows the initial condition at $t=0$.
+Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
+The erosion law is based on Eq.
+(1) in the main text where different powers of $n$ correspond to different models of erosion.
+The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}
+% \end{figure}
+%
+
+\section{S2. Analytical results for fluid flux EXP-tail PDF in a diamond network}
+\label{s2}
+%
+% \label{sec:analytical}
+%
+As described in the main text, the PDF of flow in a topologically disordered network of tubes takes the same form  as in a  structured diamond grid.
+For completeness, here we repeat the derivation of Refs.
+\cite{liu1995force,coppersmith1996model,alim2017local} which  show that the observed exponential distribution of fluid flux can be described using a mean-field approach on a structured grid.
+Basically, the random distribution of the diameters along with the conservation of mass in the network are the two main ingredients resulting in an exponential tail distribution.
+In a diamond grid, the incoming flow to a node is redistributed among the outgoing edges (since fluid mass is conserved).
+Due to the randomness in the tube's diameter, the redistribution of the incoming flow to a node between the outgoing edges is random variable.
+This model for the flow can be mapped one to one to the problem of force fluctuations in a bead pack \cite{liu1995force,coppersmith1996model,alim2017local} as shown in Fig.
+\ref{grid-result}.
+In a bead pack, the force at each layer is redistributed to the next layer where the total force exerted on the next layer should equal to that of the previous layer.
+%
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=.75\textwidth]{FigS1.pdf} % grid-analytica
+  \caption{(a) Schematic of a  diamond grid network of tubes.
+The incoming flow to each node is redistributed among the outgoing edges.
+The thickness of the lines shows the fluid flux transferred through that edge.
+(b) Schematic diagram showing beads (represented with nodes) and their contacts to the neighboring sites (represented with edges).
+The thickness of the edges show the force transferred through that contact.} \label{grid-result}
+\end{figure}
+%
+Given the above conditions, the flow at layer $L+1$ at node $j$ can be obtained as 
+%
+\begin{align}
+  q(L+1,j) = \sum_i w_{ij} q(L,i) = w_{i,i+1} q(L,i+1) + w_{i,i} q(L,i), \label{total-flow}
+\end{align}
+%
+where $w_{ij}$ shows the weights by which the flow is redistributed, and $\sum_{j} w_{ij} = 1$ since the total fluid flux is conserved. 
+% Next, we assume that the weights $w_{ij}$ are drawn from a distribution $\eta(w)$.
+Since $\eta(w)$ is a distribution, then $\int \eta(w) dw = 1$.
+Furthermore, since $\sum_jw_{ij} = 1$, we can conclude that
+%
+%\begin{align}
+%  \sum_j w_{ij}=1 \to N {E}[w_{ij}] = 1 \to E[w_{ij}] = 1/N \to {\int w\eta(w) dw = 1/N}
+% \end{align}
+%
+Assuming a general distribution of for the weights, $\eta(w)$, we can use a mean-field approximation to find the distribution of $q$ at the layer $L$, i.e., $p_L(q)$, as 
+%%
+\begin{align}
+  p_L (q) = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dq_j p_{L-1}(q_j)\right\} \times \delta \left( \sum_j w_j q_{j} - q \right),
+\end{align}
+%
+% The only approximation in the above equation is that we neglect the possible correlation between the values of $q$ among ancestors. 
+where $N$ is the number of outgoing edges (e.g., in our structured diamond grid $N=2$) and $\delta(\cdot)$ is the Dirac delta function. 
+% The constraint that $q$'s emanating downward should add up to one is accounted for through the definition of $\eta(w)$. 
+% The values of flux at each layer $q(L,i)$ are not independent for neighboring sites; however, in our mean-field approximation, we ignore such correlations.  
+Taking the Laplace transform of the above equation and defining $\tilde p(s) \equiv \int_0^{\infty} p(q) e^{-qs} dq$ one obtains
+%
+% \begin{align}
+ % \tilde P(s) & \equiv \int_0^{\infty} P(Q) e^{-Qs} dQ\\
+%   \xrightarrow{\int_0^{\infty} (\cdot) e^{-Qs} dQ}  P (Q) & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp \\
+%   \tilde P(s) & = \int_0^{\infty} \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j P(Q_j)\right\} \times \delta \lp \sum_j w_j Q_{j} - Q \rp e^{-Qs}dQ \\
+  %            & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \int_0^{\infty} dQ_j e^{-\sum w_{j}Q_{j}} P(Q_j)\right\}   \\
+%              & = \prod_{j=1}^N \left\{ \int_0^1 d w_j \eta(w_j) \tilde P(s w_j) \right\} \\
+%   & = \lp  \int_0^1 d w \eta(w) \tilde P(s w)  \rp^{N}
+% \end{align}
+%
+% Or in summary
+%
+\begin{align}
+  {\tilde P_L(s) = \lp  \int_0^1 d w \eta(w) \tilde P_{L-1}(s w)  \rp^{N}}. \label{eq:main-laplace}
+\end{align}
+%
+The above equation gives a recursive relation for the Laplace transformed of fluid flux PDF, $\tilde P_L(s)$, where it gradually converges to a distribution $\tilde P(s)$ from which the PDF of fluid flux can be obtained.
+Solving the above equation for a structured diamond grid network, one finds that the converged PDF of the fluid flux becomes $p(q) = 4q\exp(-2q)$ \cite{liu1995force,coppersmith1996model,alim2017local}, which is an exponential tailed distribution.
+
+% \begin{figure}[h]
+    % \centering
+%     \includegraphics[width=0.75\textwidth]{Figs/randomNetworkErosion3.pdf}
+%     \caption{Deng's version: Erosion in a topologically random network of pipes.
+The initial condition is shown with the label $t=0$ in the first row.
+Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius.
+The erosion law is based on Eq.
+(1) in the main text where different powers of $n$ correspond to different models of erosion.
+The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}%
+% \end{figure}
+
+\newpage
+\section{S3. Robustness to topology and initial condition}
+\label{s3}
+% 
+In order to check the robustness of our result with respect to the topology of the network, we run our simulations on a three-dimensional random network with Voronoi cell initialization of nodes in space (Fig.
+\ref{SIfig:fig2-3d}), and also for a two dimensional topologically ordered network with a diamond grid (Fig.
+\ref{fig:fig2-diamond}), where  both networks are initialized with a uniform random distribution for the diameter of the tubes.
+We find that regardless of the topology of the network, an erosion dynamics with $n>3$ results in a homogenized network, while $n<3$ results in the channelization instability.
+We further check the effect of initial randomness on the fate of the network.
+We use a two-dimensional diamond-grid network with a narrow uniform initial distribution of tube diameters around an average diameter $d_0$ with only a very small variation ($3\%$), i.e., the tube diameters are sampled from $\mathcal{U}(d_0(1-\epsilon), d_0(1+\epsilon))$.
+We again find that for the networks with $n<3$ channels are formed, while for $n>3$ the network stays homogenized (Fig.
+\ref{SI_figs4:fig:fig2}).
+%
+\begin{figure}[htp]
+     % \centering
+      \includegraphics[width = 1.0\textwidth]{FigS2.pdf}
+     \caption{Erosion in a topologically random 3D network of tubes with $N_x=20, N_y=12, N_z=12$ points for Voronoi cell initialization and an initial uniform broad distribution of tube diameters randomly sampled from $\mathcal{U}(1,14)$.
+Snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$ are shown.
+We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
+The erosion law is based on Eq.
+(1) in the main text where different powers of $n$ correspond to different models of erosion.}\label{SIfig:fig2-3d}
+ \end{figure}
+%
+\begin{figure}[htp]
+    % \centering
+ \includegraphics[width=0.75\textwidth]{FigS3.pdf} % Fig2-Sdiamond.pdf
+     \caption{Erosion in a diamond grid network with $N_x=100, N_y=50$ randomly distributed nodes and an initially broad  distribution of tube diameter randomly sampled from $\mathcal{U}(1,14)$.
+The initial condition is shown with the label $t=0$ in the first row.
+Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius.
+The erosion law is based on Eq.
+(1) in the main text where different powers of $n$ correspond to different models of erosion.
+The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2-diamond}%
+\end{figure}
+%
+\begin{figure}[htp]
+    % \centering
+ \includegraphics[width=0.72\textwidth]{FigS4.pdf}
+     \caption{Erosion in a structured diamond grid network with $N_x=50, N_y=50$ and an initially narrow distribution of tube diameters randomly sampled from  $\mathcal{U}\left(d_0(1-\epsilon), d_u(1+\epsilon)\right) $ where  $d_0$ is the average diameter and $\epsilon=0.03$.
+The initial condition is shown with the label $t=0$ in the first row.
+Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius.
+The erosion law is based on Eq.
+(1) in the main text where different powers of $n$ correspond to different models of erosion.
+The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{SI_figs4:fig:fig2}%
+\end{figure}
+
+\newpage 
+\newpage 
+\newpage
+\section{S4. Average Change in the  order parameter}
+\label{s4}
+%
+In order to quantify the network behavior shown in Fig.
+4, we calculate the change in the order parameter for different $m,n$ averaged over 100 simulations with different random initial conditions, and the heat-map results are shown in Fig.~\ref{fig:fig4_SI-2}.
+The positive or negative change in the order parameter shows the network's change toward homogenization or channelization.
+The boundary between the two phases (homogenization and channelization) calculated using the simple model introduced in the main text is shown with a solid black line here, and it can be seen that it agrees well with the order parameter change.
+%
+\begin{figure}[htp]
+    % \centering
+    \includegraphics[width = 0.70\textwidth]{FigS5.pdf}
+    \caption{The heat map for the average change in the order parameter corresponding to the networks shown in Fig.
+4 of the main text.
+The order parameter shown in the heat map here is an average of 100 different simulations with different random initialization of tube diameters.
+The black line shows the boundary between two phases calculated using the model introduced in the main text.}\label{fig:fig4_SI-2}
+\end{figure}
+
+\section{S5. Clogging dynamics}
+\label{s5}
+% 
+% \textit{}-- 
+Besides erosion, another change in the network is the deposition/sedimentation of material on the boundary walls of the porous material.
+We refer to this dynamical change a ``clogging'' process as opposed to erosion.
+Contrary to erosion, the clogging behavior may cause some edges to block which effectively alters the network of connectivity and network behavior.
+This change in the connection between nodes through edges getting blocked can drastically alter porous structure behavior, e.g., causes a huge difference between effective and true porosity \cite{shima2021}.
+Despite the drastic change of network with blockages, we can still focus on the \textit{initial} change in the order parameter.
+The derivative of order parameter can be written as
+%
+\begin{align}
+    \frac{d\mathcal{O}}{dt} = \sum_{ij} \sum_{kl} \frac{\partial \mathcal{O}}{\partial q_{ij}} \frac{\partial q_{ij}}{\partial C_{kl}}  \frac{\partial C_{kl}}{\partial t} \label{eq:order-derivative}
+\end{align}
+%
+where the last term changes sign from erosion to clogging, i.e., $\partial C_{kl}/\partial t = \pm \alpha \pi q^m_{kl} /r_{kl}^{n-3}\mu l_{kl}$ for erosion and clogging respectively.
+As a result, the magnitude of change in the order parameter equals that of erosion.
+Note that in Eq.
+\eqref{eq:order-derivative}, the second term depends on the network topology, and pore throat clogging results in the change of network topology at later times.
+% The pore throat blockages results in the divergent of clogging results from just the negative of erosion. 
+At short times, however, similar to the erosion, a phase transition exists at $n=3$.
+When  $n<3$ the network moves toward homogenization during the clogging process and when $n>3$ the flow moves toward the development of channeling instability.
+At later times, this initial trend, however, might not hold true due to the aforementioned complex changes in the connectivity network during the clogging process.
+
+% \clearpage
+% \bibliography{ref}% Produces the bibliography via BibTeX.
 

### 2022-03-06 old_files/submission-prl/submit_file/prl_paper.tex
Updates from Overleaf

--- 2022-03-06 old_files/june14/paper.tex
@@
 
-Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature as well as in numerous environmental and industrial applications~\cite{fraggedakis2015flow,sahimi2011flow,schlesinger1999carbon,duduta2011semi,sun2019hierarchical,marbach2016pruning,tero2010rules,alim2013random,heaton2010growth,smith2017multiphase,ferguson2012nonequilibrium}.
+Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature~\cite{marbach2016pruning,alim2013random,tero2010rules,heaton2010growth} as well as in numerous environmental~\cite{schlesinger1999carbon,winkler1979pore,batzle1992seismic,cohen2015mechanisms} and industrial applications~\cite{duduta2011semi,sun2019hierarchical,smith2017multiphase,ferguson2012nonequilibrium}.
 The disordered pore structure of a porous medium results in heterogeneously distributed fluid flow between the pores.
@@
 % \bibliography{ref.bib}
-% \appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{48}%
+\begin{thebibliography}{49}%
 \makeatletter
@@
 %</preamble>
-\bibitem [{\citenamefont {Fraggedakis}\ \emph {et~al.}(2015)\citenamefont
-  {Fraggedakis}, \citenamefont {Kouris}, \citenamefont {Dimakopoulos},\ and\
-  \citenamefont {Tsamopoulos}}]{fraggedakis2015flow}%
+\bibitem [{\citenamefont {Marbach}\ \emph {et~al.}(2016)\citenamefont
+  {Marbach}, \citenamefont {Alim}, \citenamefont {Andrew}, \citenamefont
+  {Pringle},\ and\ \citenamefont {Brenner}}]{marbach2016pruning}%
   \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Fraggedakis}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Kouris}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Dimakopoulos}}, \ and\
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Tsamopoulos}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physics of
-  Fluids}\ }\textbf {\bibinfo {volume} {27}},\ \bibinfo {pages} {082102}
-  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sahimi}(2011)}]{sahimi2011flow}%
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Marbach}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Alim}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Andrew}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {117}},\ \bibinfo {pages} {178103} (\bibinfo
+  {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2013)\citenamefont {Alim},
+  \citenamefont {Amselem}, \citenamefont {Peaudecerf}, \citenamefont
+  {Brenner},\ and\ \citenamefont {Pringle}}]{alim2013random}%
   \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Sahimi}},\ }\href@noop {} {\emph {\bibinfo {title} {Flow and transport in
-  porous media and fractured rock: from classical methods to modern
-  approaches}}}\ (\bibinfo  {publisher} {John Wiley \& Sons},\ \bibinfo {year}
-  {2011})\BibitemShut {NoStop}%
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Alim}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Amselem}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Peaudecerf}}, \bibinfo
+  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
+  Academy of Sciences}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages}
+  {13306} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tero}\ \emph {et~al.}(2010)\citenamefont {Tero},
+  \citenamefont {Takagi}, \citenamefont {Saigusa}, \citenamefont {Ito},
+  \citenamefont {Bebber}, \citenamefont {Fricker}, \citenamefont {Yumiki},
+  \citenamefont {Kobayashi},\ and\ \citenamefont {Nakagaki}}]{tero2010rules}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Tero}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Takagi}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Saigusa}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Ito}}, \bibinfo {author}
+  {\bibfnamefont {D.~P.}\ \bibnamefont {Bebber}}, \bibinfo {author}
+  {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \bibinfo {author}
+  {\bibfnamefont {K.}~\bibnamefont {Yumiki}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Kobayashi}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Nakagaki}},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {327}},\ \bibinfo
+  {pages} {439} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Heaton}\ \emph {et~al.}(2010)\citenamefont {Heaton},
+  \citenamefont {L{\'o}pez}, \citenamefont {Maini}, \citenamefont {Fricker},\
+  and\ \citenamefont {Jones}}]{heaton2010growth}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~L.}\ \bibnamefont
+  {Heaton}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {L{\'o}pez}},
+  \bibinfo {author} {\bibfnamefont {P.~K.}\ \bibnamefont {Maini}}, \bibinfo
+  {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {N.~S.}\ \bibnamefont {Jones}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the Royal Society
+  B: Biological Sciences}\ }\textbf {\bibinfo {volume} {277}},\ \bibinfo
+  {pages} {3265} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Schlesinger}(1999)}]{schlesinger1999carbon}%
@@
   (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Winkler}\ and\ \citenamefont
+  {Nur}(1979)}]{winkler1979pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Winkler}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Nur}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Geophysical
+  Research Letters}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {1}
+  (\bibinfo {year} {1979})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Batzle}\ and\ \citenamefont
+  {Wang}(1992)}]{batzle1992seismic}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Batzle}}\ and\ \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Geophysics}\
+  }\textbf {\bibinfo {volume} {57}},\ \bibinfo {pages} {1396} (\bibinfo {year}
+  {1992})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cohen}\ and\ \citenamefont
+  {Rothman}(2015)}]{cohen2015mechanisms}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Cohen}}\ and\ \bibinfo {author} {\bibfnamefont {D.~H.}\ \bibnamefont
+  {Rothman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Proceedings of the Royal Society A: Mathematical, Physical and Engineering
+  Sciences}\ }\textbf {\bibinfo {volume} {471}},\ \bibinfo {pages} {20140853}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Duduta}\ \emph {et~al.}(2011)\citenamefont {Duduta},
@@
 \end{thebibliography}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
 

### 2022-03-06 prl_paper.tex
Updates from Overleaf

@@
 %frontmatterverbose,
-%preprint,
+% preprint,
 %showpacs,preprintnumbers,
@@
  aps,
-%pra,
-%prb,
+ % pra,
+prl,
 %rmp,
@@
 ]{revtex4-1}
+
+\usepackage{soul}
+\usepackage{color}
+
+\newcommand{\hlcyan}[1]{{\sethlcolor{cyan}\hl{#1}}}
+\newcommand{\hlred}[1]{{\sethlcolor{red}\hl{#1}}}
 
@@
 %
+\def\blue{\textcolor{blue}}
+
 \begin{document}
@@
 
-\title{Temporal Evolution of flow in Pore-Networks:\\ From Homogenization to Instability} 
+\title{Temporal Evolution of Erosion in Pore-Networks:\\ From Homogenization to Instability} 
 % Force line breaks with \\
@@
 \author{Ahmad Zareei}
-\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with \\
+\thanks{A.Z. and D.P. contributed equally.}
+\affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with 
 \author{Deng Pan}%
+\thanks{A.Z. and D.P. contributed equally.}
 \affiliation{School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with
@@
 \begin{abstract}
-We study the dynamics of flow-networks in porous media using a pore-network model.
-First, we consider a class of erosion dynamics assuming a constitutive law depending on flow rate, local velocities, or shear stress at the walls.
-We show that depending on the erosion law, the flow may become uniform and homogenize, stay as it is, or become unstable and develop channels.
-By defining an order parameter capturing different behaviors we show that a phase transition occurs depending on the erosion dynamics.
-Using a simple model, we identify quantitative criteria to distinguish these regimes.
-Lastly, we show that pores clogging at the initial stages show analogous behaviors depending on clogging dynamics.
+We study the dynamics of flow-networks in porous media using a two/three dimensional
+pore-network model. We consider a class of erosion dynamics
+for a single phase flow with no deposition, chemical reactions, or topology changes assuming a constitutive law depending on flow rate, local velocities, or shear stress at the walls.
+We show that depending on the erosion law, the flow may become uniform and homogenized or become unstable and develop channels.
+By defining an order parameter capturing these different behaviors we show that a phase transition occurs depending on the erosion dynamics.
+Using a simple model, we identify quantitative criteria to distinguish these regimes and {correctly predict the fate of the network, and discuss the experimental relevance of our result.
+}
+%
+% Lastly, we show that the initial stages of pores clogging show analogous behaviors which depends on the clogging dynamics.
+
+% Lastly, we show that pores clogging at the initial stages show analogous behaviors depending on clogging dynamics.
 % , however, due to the pore throat blockages and changes in the network connections the evolution diverges from its initial trend.
@@
 \end{abstract}
+
+%
 
@@
 
-Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is a challenging problem and has many environmental and industrial applications~\cite{fraggedakis2015flow,sahimi2011flow,schlesinger1999carbon,herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous,duduta2011semi,sun2019hierarchical,marbach2016pruning,tero2010rules,alim2013random,heaton2010growth}.
-% , such as oil recovery~\cite{fraggedakis2015flow,sahimi2011flow}, CO$_2$ sequestration~\cite{schlesinger1999carbon}, water filtration/separation~\cite{herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous}, energy storage~\cite{duduta2011semi,sun2019hierarchical}, or biological applications \cite{marbach2016pruning,tero2010rules,alim2013random,heaton2010growth}.
-The disordered pore structure of a porous medium results in a heterogeneously distributed fluid flow between the pores.
-% Fluid flow in a porous medium is often heterogeneously distributed between the pores as a result of a highly disordered pore structure.
-Due to the fluid flow, the pore structure can further change dynamically either through the erosion of pore boundary walls or deposition/sedimentation of material on the boundary of the pores.
-Such heterogeneous and dynamical changes of the solid structure affect the pore-level fluid flow which in turn affects the dynamical changes to the pore structure.
-This feedback mechanism along with the initial heterogeneous fluid flow complicates the dynamical process and makes it difficult to understand and predict the porous media behavior.
-Nonetheless, an understanding of the dynamical change is essential to improve any of the porous media applications where the pore network changes over time, applications such as groundwater remediation and precipitation of minerals in rocks~\cite{rad2013pore}, biofilm growth in water filtration, and protective filters \cite{herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous}, as well as enhanced oil recovery with polymer flooding \cite{lake2014fundamentals,parsa2020origin}, or water-driven erosion \cite{schorghofer2004spontaneous,mahadevan2012flow}.
-
-% to the pore structure affects local fluid flow as well as bulk properties of the medium. 
-% Understanding flow behavior is important to improve any of the the applications where the pore structure changes dynamically either by erosion of the boundary wall or deposition/sedimentation of material on the boundary.
-Changes in the micro-structure and solid boundaries affect local fluid flow as well as the bulk properties.
-The  erosion or deposition process in a porous media plays an essential role in many environmental and industrial applications such as groundwater remediation and precipitation of minerals in rocks, bio-film growth in water filtration and the design of protective filters,  as well as enhanced oil recovery with polymer flooding, water-driven erosion.
-The structures of such porous media are usually highly disordered with a heterogeneous distribution of pore-level flow velocities.
-%%
-
-% Albeit there is an abundance of applications in understanding 
-% Despite the importance of understanding flow evolution in porous structures exposed to erosion and deposition,it 
-% \footnote{It can be shown that the rate of change in tube's radius in \cite{reddi2000permeability} assuming a dilute solution becomes proportional to local fluid velocity},
-
-In light of the plethora of applications, it is surprising that the evolution of porous structures exposed to erosion and deposition has only been partially understood both theoretically and experimentally.
-In order to model erosion in porous materials, different models have been used where erosion is assumed to be locally proportional to different flow parameters.
-Some studies have focused on the erosion of the pore structure proportional to the shear stress at the walls \cite{jager2017channelization,ristroph2012sculpting,hacking1996shear,wan2004investigation}, or proportional to the power dissipated by the flow~\cite{steeb2007modeling,marot2012study,sibille2015internal}.
-More recently it has been shown that using a coarse-grained model with an erosion rate depending on the local pressure gradient, different branching instability can be reached in a porous material~\cite{derr2020flow,mahadevan2012flow}.
-Similarly, in clogging, deposition rate based on local fluid flux, velocity, or even at a constant rate independent of any flow parameters has been used~\cite{yang2017pore,reddi2000permeability,boccardo2014microscale}.
-In order to unify the different approaches, we use a general continuous model which allows us to study the effect of different erosion or clogging dynamics with a single constitutive law.
-Additionally, we use a network approach~\cite{alim2017local,fatt1956network, blunt2013pore,stoop2019disorder,bryant1993network} to study the flow dynamics in the porous media.
-The network approach has the advantage of not requiring coarse-grained homogenization and is computationally simple allowing us to simulate larger domains.
-
-% (which is the same as shear at the walls),
-% to capture the flow dynamics
-
-% Despite all of the different models, a consensus on the dynamics of erosion or clogging is missing.\red{focus more on the network model} The adventage versatile law network approach -> does not need homogenization or meanfield assumption
-
-% Since the dynamics of erosion in a porous material is not well understood,
-
-% A phenomenological discrete network-based model~\cite{alim2017local,fatt1956network, blunt2013pore,stoop2019disorder,bryant1993network} is used to model the hydrodynamically driven erosion or clogging in a porous material.
-% In the network model, the pores are represented by spherical nodes connected with edges represented by cylindrical tubes.
-
-The network of pores inside the solid structure is connected together through pore-throats that effectively show resistance to the fluid flow between the pores (Fig.~\ref{fig:fig1}a).
-In a network model, the pores/voids of the porous medium are represented by a two- or three-dimensional lattice of nodes.
-The edges between the nodes of the network represent the pore-throats between the pores and are modeled using cylindrical tubes characterized by their radius and length.
-Network-based models have successfully shown to capture key properties of fluid flow in a porous material such as the probability distribution of fluid flux~\cite{alim2017local}, the permeability scaling during clogging~\cite{shima2021}, or the first fluidized path in a porous structure~\cite{fraggedakis_chaparian_tammisola_2021}.
-% Using such network models, it has been shown that the probability distribution of fluid flux in a porous material is universal when the porous material is random enough.
-Furthermore, during the clogging process, the usage of Kozeny-Carman fails to correctly predict the porosity since all the length scales are not eroding at the same time (the erosion only happens at the corss sections and not along the length of a porous material).
-New relation based on the variation in porosity has been proposed that can successfully find the relation between porosity and permeability variation using such models which is verified experimentally.
-The degradation of the solid skeleton (i.e., erosion) or deposition of material on the pore throats (i.e., clogging) in such networks is modeled by the change (increase or decrease) in the radius of the edges connecting the pores which ultimately translates in the changes in the flow resistance between the pores.
-Using a general local erosion law that can model different dynamics, we show a variety of behaviors are possible.
-The network can either move toward stability and homogenization, stay as it is with no significant change in network statistics, or become unstable and develop channels.
-Using numerical solutions with an erosion model on a random network we show the emergence of two behaviors and morphologies are possible through selective erosion and subsequent flow enhancement.
-Using a simplified model we capture the underlying physics and furthermore show a phase transition occurs depending on the parameters of the model.
-% Here, based on the porous network model, we link various erosion laws with different large-scale behaviors and show a variety of behaviors that can be observe
-% In order to better understand the effect of different erosion dynamics in a porous based on local parameters, 
-% network model has been successful in predicting the first open channeel \cite{fraggedakis_chaparian_tammisola_2021} and capturing the fluid flow distribution \cite{alim2017local}
-% \cite{fatt1956network} 
-% \cite{blunt2013pore}
-% \cite{stoop2019disorder}
-% Consequently, clogging effects are excluded from these assumptions. Thus, the eroded fines can be transported through the porous material within these statistically homogeneous distributed channels
-% Albeit there is an abundance of applications, the evolution of structures exposed to erosion and deposition is in general not easily predictable and usually requires the use of numerical techniques.
-% However, this process is difficult to model due to diverse processes that may arise, including particle advection through the pore space by fluid flow, adsorption and deposition onto the solid matrix, and erosion or resuspension.
-% \begin{itemize}
-% \item Importance of porous media
-% \item importance of dynamics in porous media
-% \item we study evolution with a network model
-% \end{itemize}
+Fluid flow through a porous medium undergoing a dynamical change in its network of micro-structure is ubiquitous in nature~\cite{marbach2016pruning,alim2013random,tero2010rules,heaton2010growth} as well as in numerous environmental~\cite{schlesinger1999carbon,winkler1979pore,batzle1992seismic,cohen2015mechanisms} and industrial applications~\cite{duduta2011semi,sun2019hierarchical,smith2017multiphase,ferguson2012nonequilibrium}.
+The disordered pore structure of a porous medium results in heterogeneously distributed fluid flow between the pores.
+The boundaries of the pore structure can change dynamically either through erosion or deposition/sedimentation of material.
+Such heterogeneous changes of the solid structure affect the pore-level fluid flow which in turn affects the dynamical changes to the pore structure.
+This feedback mechanism along with the initial heterogeneous fluid flow makes it difficult to understand and predict the porous media behavior.
+Nonetheless, an understanding of the dynamical change is essential to improve any of the porous media applications where the pore network changes over time, including groundwater remediation and precipitation of minerals in rocks~\cite{rad2013pore}, biofilm growth in water filtration, and protective filters \cite{herzig1970flow,tien1979advances,jaisi2008transport,carrel2018biofilms,seymour2004anomalous}, as well as enhanced oil recovery with polymer flooding \cite{lake2014fundamentals,parsa2020origin}, or water-driven erosion \cite{schorghofer2004spontaneous,mahadevan2012flow}.
 
@@
     % \centering
-    \includegraphics[width = 0.45\textwidth]{Figs/Fig1_pppp.eps}
-    \caption{(a) Cross section of a porous media obtained using  computerized tomography (CT) scan of a sandstone sample (CT image taken from \cite{akanji2010finite}).
+    \includegraphics[width = 0.45\textwidth]{Fig1.pdf}
+    % \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}.
 The scale in the bottom left shows $1$mm.
@@
 The inset figure shows the conservation of mass at each node.
-(c) The universal probability distribution function (PDF) of fluid flux for a topologically random (in blue) or diamond network (red) with a highly disordered random net including uniform (triangles), log-normal (circles), and truncated normal (plus) distributions.
-The distribution parameters are chosen such that the coefficient of variation (the ratio of the standard deviation to the mean) becomes $0.5$ which results in a highly disordered pore throat distribution.
-Generally, in a highly disordered random network, the PDF of normalized fluid flux becomes independent of the network and follows a universal distribution with an exponential tail.
-}\label{fig:fig1}
+(c) The universal probability distribution function (PDF) of fluid flux for a topologically random (in blue) or diamond network (red) with a highly disordered random network including uniform (triangles), log-normal (circles), and truncated normal (plus) distributions.}
+    \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}.
+The scale in the bottom left shows $1$mm.
+The network of pores and throats is highlighted in blue.
+In the network model, the pores are represented with nodes and the throats between pores are approximated with tubes.
+(b) Schematic of a topologically random network.
+The edge diameters representing the pore-throats are randomly distributed.
+(c) A structured diamond grid network with a random distribution of edge diameters.
+(d) The universal probability density function (PDF) of fluid flux for a topologically random (blue) or diamond-grid (red) network of nodes (red) with a random distribution of edge diameter sampled from a uniform (triangles), log-normal (circles), or truncated normal (plus) distribution.
+}
+    \label{fig:fig1}
 \end{figure}
 %
-% \AZ{Things are not topoligically random }
-% \AZ{random end }
-% \AZ{structured allows for mean field theory}
-% \AZ{the edges are the same - exponential where it is coming from}
-% \AZ{boundary between phases, where the mean fields hold}
+\emph{Network approach}-- We approach this long-standing problem using a network model for the porous structure~\cite{fatt1956network, blunt2013pore,stoop2019disorder,bryant1993network,blunt2013pore,dong2009pore,blunt2013pore,blunt1995pore,alim2017local}.
+% Before discussing the dynamics, we briefly review the results of flow in random networks.
+The network of pores inside the solid structure is connected together through pore-throats that effectively show resistance to the fluid flow between the pores (Fig.~\ref{fig:fig1}a).
+Network-based models have been shown to successfully capture key properties of fluid flow in a porous material such as the probability distribution of fluid flux~\cite{alim2017local}, the permeability scaling during clogging~\cite{shima2021}, or the first fluidized path in a porous structure~\cite{fraggedakis_chaparian_tammisola_2021}.
+We consider low-Reynolds fluid flow through the porous network.
+The fluid flow rate at the edge connecting pores $i$ and $j$ is given by $ q_{ij}  = C_{ij}(p_i - p_j)$ where $p_i,p_j$ represent pressures at neighboring nodes.
+Poiseuille's law implies that the conductance $C_{ij} = {\pi r_{ij}^4}/{8 \mu l_{ij}}$, with $r_{ij}$ and $l_{ij}$ the edge's radius and length.
+Initially, we consider a topologically random network of nodes constructed using uniformly distributed nodes (i.e., a Poisson point process) in a planar domain connected using Delaunay triangulation (Fig.
+\ref{fig:fig1}b).
+The pore-throats or radii of the edges are considered as independent and identically distributed random variables and fluid flow in the edges are obtained by solving for conservation of mass at all nodes given a pressure difference between the nodes on the boundaries (supplementary material, SM, \S1).
+Independent of edge radius distribution, the probability density function (PDF) of normalized fluid flux is well described by a single exponential distribution shown in Fig.
+\ref{fig:fig1}d.
+The exponential distribution of fluid flux is similar to earlier experimental and numerical measurements~\cite{datta2013spatial,shima2021,alim2017local} and is a universal feature in random porous networks.
+Considering a structured diamond-grid of pores (Fig.
+\ref{fig:fig1}c) which significantly simplifies the geometrical complexity of the network and allows for analytical tractability, one finds that the PDF of normalized fluid flux remains unchanged for various distributions suggesting robustness to network topology (Fig.~\ref{fig:fig1}d and SM \S2).
+In the following, we will study, analytically and numerically, how this universal distribution evolves as the network is modified based on a local constitutive law.
 
-  % Flow through pores and throats of a porous medium can be modeled using a pore network model \cite{alim2017local,fatt1956network, blunt2013pore,stoop2019disorder}.
-In a network model, the pores/voids of porous medium are represented by a two- or three-dimensional lattice of nodes.
-The edges between the nodes of the network represent the pore-throat between the pores and are modeled using cylindrical tubes characterized by their radius and length (see Fig.
-\ref{fig:fig1}(a)).
-The pore-network model is well suited for the simulation of low-Reynolds fluid flow and has proved to capture the flow dynamics of porous media \cite{alim2017local} and also the first fluidized path \cite{fraggedakis_chaparian_tammisola_2021}.
-We use a structured/unstructured network with randomly distributed nodes and edge length.
-% It has been shown that flow through such network correctly captures the exponential tail for distribution of fluid velocities through a porous medium.
-
-\textit{Methods and Results}-- We consider low-Reynolds fluid flow through the porous network, i.e.,  $\rho u r/\mu \ll 1$ where $\rho$ is the fluid density and $\mu$ is the kinematic viscosity, $u$ and $r$ are characteristic fluid velocity and pore radius.
-In such conditions, the fluid flow in each tube follows the Poiseuille law
- $ p_i - p_j  = ({8 \mu l_{ij}}/{\pi r_{ij}^4}) q_{ij}$ where $p_i,p_j$ represents pressures at neighboring nodes $i$, $j$, and $r_{ij}, l_{ij}, q_{ij}$ are respectively the radius, length, and fluid flow rate at the edge connecting pores $i$ and $j$.
-The coefficient ${\pi r_{ij}^4}/{8 \mu l_{ij}}$ which relates the fluid flux to the pressure difference can be considered as the conductance $C_{ij}$ of the edge $ij$ in the pore-network.
-In addition to Poiseuille flow at the edges,  the total incoming flow at a node should be equal to the total outgoing flow in order to conserve mass.
-The conservation of mass at pore $i$ can be written as $\sum_{j\in \mathcal{N}(i)} q_{ij} =0$ where $\mathcal{N}(i)$ represents all the neighboring nodes of node $i$.
-First, we consider a topologically random network of nodes constructed using a uniform distribution of $N_x\times N_y$ nodes in a planar domain $\left[0,L_x\right]\times \left[0,L_y\right]$ where the nodes connectivity are obtained using Delaunay triangulation (see Fig.
-\ref{fig:fig1}b(i) for a part of such network).
-The radius of the edges is considered as independent and identically distributed random variables sampled from a probability distribution that can be either uniform, log-normal, or a truncated normal distribution (see supplementary material S1 for more details).
-Assuming a pressure difference between the boundary nodes at the left and the right boundary, the pressure at the nodes, and the fluid flow rate at the tubes can be obtained by solving the corresponding set of linear equations.
-We find that for large enough randomness in the edge radii (i.e., $\text{std}(r_{ij})/\text{mean}(r_{ij})\geq 0.5$), the PDF is well described by a single exponential distribution as shown in Fig.
-\ref{fig:fig1}c.
-The exponential form of the PDF reflects the relatively small number of edges with extremely large fluid fluxes.
-The exponential distribution of fluid flux obtained here is similar to the earlier experimental or numerical measurements~\cite{datta2013spatial,shima2021,alim2017local}.
-Next, we consider a structured diamond-grid of pores (Fig.
-\ref{fig:fig1}b(ii)) which significantly simplifies the geometrical complexity of the network.
-First, we find that the PDF of normalized fluid flux remains unchanged in such networks for various distributions and in fact matches with an unstructured random network (Fig.
-\ref{fig:fig1}c).
-The diamond grid allows us to analytically track the propagation of fluid into the network and calculate the distribution of fluid flux using a mean-field approximation (see supplementary material S3).
-Using a similar idea proposed for the force distribution in granular materials~\cite{liu1995force,coppersmith1996model,alim2017local}, it can be shown that the PDF of normalized fluid flux inside a highly disordered porous material converges to a universal distribution with an exponential form, i.e., $p(\hat{q}) \propto e^{-\alpha \hat{q}}$ for large $\hat{q}$ where $\hat{q}$ is the normalized fluid flux $\hat{q} = {q}/\langle q \rangle$ (see supplementary materials S3).
-This result indicates that the diamond grid network of pores where cylindrical edges between the pores have a highly disordered distribution is sufficient to capture the statistics of a heterogeneous fluid flow inside a porous material.
-
- % In the following parts we show the results of a diamond grid, and the results for a random-graph is presented in the supplementary material.
-
-%  independent of the pore structure, becomes exponentially distributed. 
-%  Considering a random \AZ{needs explicit definition} or structured network with a random distribution of tube's radius/length (i.e., effectively their flow resistance) and a 
-%  For a large enough randomness in the edge resistances between the pores $R_{ij}$, the probability distribution of flux in the tubes normalized by the average flux follows a universal curve with an exponential tail, i.e., $P(\hat{q}) \propto e^{-\alpha \hat{q}}$ for large $\hat{q}$ where $\hat{q}$ is the normalized fluid flux $\hat{q} = {q}/\langle q \rangle$ (See Fig.
-\ref{fig:fig1}c and supplementary material for more details).
-This PDF of fluid flux $q$ has been shown to correctly captures the exponential tail for the fluid flux in a porous medium \cite{alim2017local,shima2021}.
+\textit{Network evolution model}-- The degradation of the solid skeleton (i.e., erosion) or deposition of material on the pore throats (i.e., clogging) in the network of pores is modeled by the change (increase or decrease) in the radii of the edges connecting the pores which translates into changes in the flow resistance between the pores.
+The rate of change of the radii depends on local fluid flow parameters (i.e., $q, r$), however, the exact dependence is unknown.
+A general constitutive model for erosion can be written as $dr_{ij}/dt = f(q_{ij},r_{ij})$, where $f(q_{ij},r_{ij})$ represents the functional dependence of erosion on the fluid flux $q_{ij}$ and the tube radius $r_{ij}$.
+Erosion in saturated, granular, porous medium occurs when the shear stress  at the walls $\tau_w$ exerted by the fluid overcomes the cohesive strength of the solid matter $\tau_c$.
+In a class of erosion models previously studied~\cite{jager2017channelization,ristroph2012sculpting,wan2004investigation} the eroded mass per unit area is linearly proportional to the excess shear, i.e.,  $\dot{m}  = -\kappa  (\tau_w-\tau_c)$ where $\kappa$ is the linear proportionality constant.
+This erosion model effectively results in an increase in the radius of the edges in our network model where \add{$\dot{r} \propto \kappa/r (|q|/r^3 - \tau_c)$ , where $1/r$ factor comes from the eroded mass $dm =2\pi\rho r l dr$ for a cylindrical pipe and $|q|/r^3$ comes from the known result of shear stress of laminar flow in pipes \cite{white2006viscous}}.
+Similar models have further been used in biological models for the growth of vascular networks~\cite{chen2012haemodynamics,hacking1996shear}.
+In addition to local shear stress, erosion based on local fluid velocity ($v \propto |q|/r^2$) \cite{kudrolli2016evolution}, local pressure difference ($\Delta p \propto |q|/r^4$) \cite{derr2020flow,mahadevan2012flow}, and power dissipation ($P \propto q^2/r^4$ ) ~\cite{steeb2007modeling,marot2012study,sibille2015internal} have also been considered as alternative models.
+Here, we first focus on a class of erosion dynamics described by $f(q_{ij},r_{ij}) = \alpha |q_{ij}|^m/r_{ij}^n$ where $m,n,\alpha>0$ are constants.
+This model unifies a diverse set of erosion and clogging dynamics as different values of $m$ and $n$ correspond to different physics of erosion.
+Later we will generalize the models to include other forms of nonlinearities.
+% We use a general constitutive  model which may implement a diverse set of erosion or clogging dynamics and thus allows us to study the effect of different laws in a unified way.
 %
-
-% Note that the flux $q_ij$ depends on the pressure gradient between nodes i.e. $(p_i-p_j)/l_{ij}$. On the other hand 
-% We first start with a numerical model, where we assume a network of $200\times 100$ tubes in the horizontal and vertical direction on a diamond lattice \AZ{better motivation: explain and discuss the meanfield picture behind figure 1c} (similar results for a general \AZ{needs definition} random network is presented in the supplemental materials).
 \begin{figure}[!h]
     % \centering
-    \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
+    % \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
+    \includegraphics[width = 0.48\textwidth]{Fig2_.pdf}
     \caption{Erosion in a network of pipes.
 The initial condition is shown with the label $t=0$ in the first row.
-Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
-The erosion law is based on Eq.
-\eqref{eq:erosion-law} where different powers of $n$ correspond to different models of erosion.
-The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}
+Each row afterward corresponds to the {simulation result at $t=T$ where  $\langle r_{t=T}\rangle=2r_0$ with $r_0 = \langle r_{t=0}\rangle$}.
+The erosion law is based on $f(|q|,r) = |q|/r^n$  with different powers of $n$ correspond to different models of erosion.
+The first, second, and third columns are snapshots of the pore network, the PDF of normalized fluid flux $q/\langle q \rangle$, and  the PDF of normalized radius $r/\langle r\rangle$ at $t=T$, respectively.} \label{fig:fig2}
 \end{figure}
 %
-
-In order to model erosion in porous media, we consider the abrasion in the throats which correspond to the change in the radius of the edges in the network.
-We model the dynamics of the change in the radius as
 % 
-\begin{align}
-   \frac{dr_{ij}}{dt} = \alpha  \frac{|q_{ij}|^m}{r_{ij}^n} \label{eq:erosion-law}
-\end{align}
+% \begin{figure*}[htp]
+%      % \centering
+%       \includegraphics[width = 1.0\textwidth]{FigS2.pdf}
+%      \caption{\add{Erosion in a topologically random 3D network of tubes with $N_x=20, N_y=12, N_z=12$ points for Voronoi cell initialization and an initial uniform broad distribution of tube diameters randomly sampled from $\mathcal{U}(1,14)$.
+Snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$ are shown.
+We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
+The erosion law is based on Eq.
+(1) \del{in the main text} where different powers of $n$ correspond to different models of erosion.}}\label{SIfig:fig2-3d}
+%  \end{figure*}
 %
-\add{where $m,n,\alpha$ are constants.
-Different powers of $m$ and $n$ correspond to different physics in the erosion.
-Particularly, when $m=1$ and (i) $n=0$ the erosion depends on the amount of flux $q_{ij}$ passing through the edge; (ii) $n=2$ the erosion depends on the local velocities; (iii) $n=3$ the erosion depends on the shear force at the boundary of the throat.} \add{Additionally, $m=2$ and $n=6$ corresponds to the models considered in biological transport networks where the there the radius change has a quadratic dependence on wall shear stress~\cite{hu2013adaptation,ronellenfitsch2016global}.} We consider network of randomly distributed pores with  $N_x\times N_y$ pores in the horizontal and vertical directions.
-The randomly distributed points are connected using Delaunay triangulation.
-We initialize the network with a uniform random distribution of diameters within $[r_\text{min}, r_\text{max}]$ range with a large coefficient of variation such that  $\sigma_r/r_0\approx 0.5$ where $\sigma_r$ is the standard deviation, and $r_0 = \langle r \rangle$~\cite{alim2017local}.
+% In order to model erosion in porous media, we consider the abrasion in the throats leading to decrease in the tube radii. We model the dynamics as 
+%
+% \begin{align}
+%   \frac{dr_{ij}}{dt} = \alpha  \frac{|q_{ij}|^m}{r_{ij}^n}, \label{eq:erosion-law}
+% \end{align}
+%
+% where $m,n,\alpha$ are constants. Different values of $m$ and $n$ along with a positive $\alpha>0$ correspond to different erosion physics (analogously, $\alpha<0$ corresponds to clogging).
+Particularly, the erosion when $m=1$ and  (i) $n=0$ depends on the amount of flux $q_{ij}$ passing through the edge; (ii) $n=2$ depends on the local velocities  \cite{kudrolli2016evolution}; (iii) $n=3$ depends on the shear force at the boundary of the throat~ \cite{bonelli2011micromechanical,parker2000purely,jager2017channelization}.
+{Additionally, $m=2$ and $n=6$ corresponds to models considered in biological transport networks where the radii changes are {proportional to the square of shear stress at the boundary walls}~\cite{hu2013adaptation,ronellenfitsch2016global}.}  We later address the effect of incorporating the threshold discussed above into our model.
+We consider a randomly initialized network with disordered diameters obtained from a uniform distribution (SM S1). 
 The flow inside the pores, PDF of flux in the tubes, and PDF of tube radii are shown in Fig.
@@
 We assume a constant pressure difference between the left and the right boundaries.
-In each time step, we increase the local radius of the tubes based on the erosion law introduced in Eq.
-\eqref{eq:erosion-law}.
-Note that $r_{ij} (t+\delta t)  = r_{ij} (t)  + (\alpha \delta t)  q_{ij} (t)/ r^n_{ij} (t) $, where the coefficient $\alpha \delta t$ is chosen such that the maximum change in the radius at each time step is smaller than one-tenth  of the smallest tube's radius i.e.
-$\max (\Delta r_{ij}) \leq r_\text{min}/10$ of the smallest radius at the initial configuration.
-This condition guarantees that at each step a small amount of material is eroded and there's no sudden change in the network.
-We further test the convergence by decreasing $\max(\Delta r_{ij})$ to half and we observe that the average relative change in the flux vector becomes $\aprrox 1.2\%$, and the PDFs remain intact without any change.
+In each time step, we increase the local radii of the tubes based on the erosion law $dr_{ij}/dt = \alpha q_{ij}^m/r_{ij}^n$, assuming erosion is linear in the flux ($m=1$).
+Later we will consider the network behavior for other powers of $m$.
 We continue the simulations until $\langle r \rangle = 2 r_0$. 
-%
-The results of the simulations for different $n$ are shown in Fig.
+The results of the simulations for different values of $n$ are shown in Fig.
 \ref{fig:fig2}.
@@
 In such cases, the flow is dominated by a few edges carrying most of the flow while the rest of the network carries almost no flow.
-This can be seen in the PDF of the normalized radius which becomes bimodal.
-Furthermore, the PDF of the normalized fluid flux contains a small number of edges with very large flux values while the majority of the edges carry small flux.
-Contrary to $n=1,2$, when $n=3$ and the erosion depends on shear at the throats' boundary walls, we find that the flow patterns stay very close to the initial shape, however, with larger and exacerbated flux values.
-Although the maximum fluid flux increases, the PDF of normalized fluid fluxes remains almost exponential, and the PDF of diameters moves toward larger values.
-Increasing $n$ to larger values, $n=4$ or $5$, we find that the flow pattern in the network moves toward homogenization.
-Here, the tail of the normalized fluid flux distribution retracts and the distribution moves toward the average value.
-We further find that the PDF of the diameters moves toward the average and the coefficient of variation reduces.
-Running the simulations for longer times, we observe that the flow becomes completely uniform where only a single radius appears to carry the flow with the same fluid flux (i.e., the average value) for all the tubes in the network.
-In summary, we have observed a transition in the network behavior during erosion which happens at $n=3$: when $n<3$ the network moves toward developing channels, and when $n>3$ the erosion results in the homogenization of the flow.
+This is also reflected by a bimodal radii distribution.
+In contrast, when $n=3$  (corresponding to erosion linear in shear), we find that despite the
+increase in tube radii and absolute flow rates, the normalized flow distribution is hardly affected, maintaining its original exponential form.
+Increasing $n$ to larger values, $n=4$ or $5$, we find that the flow pattern in the network moves towards homogenization.
+Here, the tail of the normalized fluid flux distribution retracts and the coefficient of variation reduces.
+Similarly, the PDF of the tube diameters becomes narrower.
+It is to be noted that the different distributions obtained for different powers of $m,n$ represent different statistics that cannot be collapsed.
+
+We found that similar results uphold in a 3d random tube network  (see SM, Fig.~S2) as well as a 2d topologically ordered (diamond grid) network, illustrating the robustness of the results to the network topology (SM, Fig.~S3).
+Similarly, we found that the results hold also when using an initial narrow distribution of diameters (SM, Fig.~S4), showing robustness with respect to the strength of the disorder.
+We further changed the boundary conditions, using a circular random network with the inlet at the center and outlet at the outer edges and we find that similar results uphold~(SM, Fig.~S5).
+
+\textit{Phase transition and order parameter}-- {To quantify the transition of the network between the channeling instability and homogenization, we define an order parameter % $\mathcal{O}$ 
+%
+\begin{align}
+\mathcal{O} = \frac{1}{N-1} \left( N - \frac{\left( \sum_{ij} q^2_{ij}\right)^2}{ \sum_{ij} q^4_{ij}}\right),
+\end{align}
+%
+where $N$ is the number of edges.} {The order parameter defined here is inspired by the participation ratio (PR) employed to quantify the localization of an eigenstate in the analysis of Anderson localization~\cite{kramer1993localization}.}  The order parameter $\mathcal{O}=0 $ when the flux through every edge is identical.
+On the other hand, when fluid flux becomes highly localized with only a few edges with non-zero flux, $\mathcal{O}\to 1$.
+We numerically calculated the  order parameter $\mathcal{O}$ for {randomly initialized networks, averaged over 20 different realization}.
+The results are shown in Fig. \ref{fig:fig3}a for different amounts of erosion measured by the increase in the average diameter $\langle r\rangle /r_0$. As shown in 
+ Fig.
+\ref{fig:fig3}c, at $n\approx 3$ the order parameter, remains unchanged; however for $n>3$ the order parameter moves toward zero, where the flow becomes more uniform, and for $n<3$ the order parameter goes toward unity, where channels are developed.
+This indicates a phase transition at $n=3$ in the long-time behavior of the network.
+%
 
@@
     % \centering
-    \includegraphics[width = 0.45\textwidth]{Figs/Fig3_new.png}
-    \caption{Two tubes in (a) series  or (b) parallel configuration.
-When the tubes are in series configuration, the tubes have the same fluid flow rate $q$.
-The tube radius dynamically change with the erosion law $\dot{r_i}\propto q/r_i^n$.
-For any $n$, the normalized pressure at the junction between the tubes $\tilde p_m = (p_m - p_l)/(p_r-p_l)$ approaches $1/2$ which results in a homogenized pressure distribution  shown in (a$_2$).
-When the pipes are in parallel, however, the flow is distributed among the tubes based on their flow conductivity $C_1,C_2$.
-The local fluid flow rate then affects the erosion of the tub $\dot{r}_i\propto q_i/r_i^n$.
-When $n<3$ in the erosion law, the fluid flow eventually passes through a single tube, and channeling occurs; (b$_2$) when $n=3$, the flow ratio between the pipes does not change; and (b$_3$) when $n>3$ the flow ratio approaches $1/2$ which is the homogenization.(c) Order parameter $\mathcal{O}$ for different powers of $n$ plotted over time as the network structure is eroded and average edge radius is increasing $\langle r\rangle/r_0$.
-When $n<3$ the order parameter increases ($\mathcal{O}\to 1$) while the network is developing channels, and when $n>3$ the order parameter decreases ($\mathcal{O}\to 0$) while the network moves toward homogenization, and when $n=3$ the order parameter stays as it while the network statistics remains unchanged.}\label{fig:fig3}
+     \includegraphics[width = 0.45\textwidth]{Fig3.pdf}
+    \caption{ (a) Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig.
+\ref{fig:fig2} for different powers of $n$ with $m=1$ plotted over time.
+(b,c) Tubes in series (b) or parallel (c) configuration.
+    The tube radius dynamically change with the erosion law, i.e., $f(q,r) = \alpha |q|^m/r^n$.
+When the tubes are in series, for any $m,n$, (b$_1$) the normalized pressure at the middle junction between the tubes $\tilde p_m = (p_m - p_l)/(p_r-p_l)$ approaches $1/2$ which results in a homogenized pressure distribution.
+    When the tubes are in parallel, for (c$_1$) $m=(n+1)/4$, the flow ratio between the pipes does not change over time; (c$_2$)  $m<(n+1)/4$ the flow distributes between the tubes equally and  $q_1/(q_1+q_2) \to 1$ which results in the homogenization of the network; (c$_3$) $m>(n+1)/4 $, the entire flow eventually passes through one of the tubes, and channeling occurs.
+}\label{fig:fig3}
 \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section{Simplified Model}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-%
-
-\textit{Simplified Model}-- In order to understand the underlying reason behind the transition in network behavior during erosion for different powers of $n$, we focus on a simplified model with only two tubes in parallel or series (see Fig.
-\ref{fig:fig3}a,b).
-First, assuming two cylindrical tubes with radii $r_1,r_2$ in series and connected back to back, the flow is the same for the two tubes $ q_1 = q_2 = q$ (Fig.
-\ref{fig:fig3}a).
-The radius of each tube then changes with $dr_i/dt = \alpha q/r_i^n$ where $i=1,2$.
-Each tube can be considered as a resistor where its conductivity  $C_i =\pi r_i^4/8\mu l_i$ changes over time.
-In similarity with resistor networks, the pressure difference $\Delta P_i$ acts analogous to the voltage difference and the fluid flux $q_i$ is analogous to the current where we have $q_i = C_i \Delta P_i$.
-When the cylindrical tubes are in series, we find that the conductivity of each tube changes as $dC_i/dt \propto C_i^{(n-3)/4}$.
-As a result, each tube's conductivity increases with a rate depending on $n$, i.e.
-the larger the $n$ the faster it moves toward larger values.
-If we consider the pressure at the junction between tubes, we find that this middle point pressure moves toward the average value of pressure on both sides (see Fig.
-\ref{fig:fig3}(a$_1$)).
-As a result, when the tubes are in series, the erosion results in a homogenized distribution of pressure.
-Contrary to tubes in series, when the tubes are in parallel (Fig.
-\ref{fig:fig3}b), the flow divides between the two tubes based on their conductivity i.e.
-$q_1/q_2 = C_1/C_2$.
-Since each tube's radius changes as $dr_i/dt = \alpha q_i/r_i^n$, the evolution of the fluid flow ratio becomes
-% %% 
-\begin{align}
- \frac{d}{dt}\left( \frac{C_1}{C_2}\right) \propto  \frac{C_1}{C^{(n+1)/4}_2} \left( \left( \frac{C_1}{C_2}\right)^{\frac{n-3}{4}} - 1 \right). \label{eq:dyn-paral}
-\end{align}
-%a
-When $n=3$ in Eq.
-\eqref{eq:dyn-paral}, the right-hand-side becomes zero and as a result the flow ratio $C_1/C_2$ remains constant and does not change.
-However, when $n\neq 3$, we find that $C_1/C_2 = 1$ is an equilibrium point.
-When $n>3$ this equilibrium solution is stable and the flow moves toward homogenization; however, when $n<3$ this equilibrium solution becomes unstable and the solution moves toward $C_1/C_2 \to 0$ or $\infty$ which means that the whole flow passes through one of the tubes.
-To summarize, when the tubes are in series any erosion law makes flow become more uniform; however, when the tubes are in parallel depending on the power $n$ the flow in the tubes can move toward becoming more uniform ($n>3$), stay the same ($n=3$), or move toward instability and channel development ($n<3$).
-Since a complex network includes both series and parallel connections, we expect that the whole network structure behaves in a similar manner and we observe a network transition between becoming uniform ($n<3$) to developing channels ($n>3$).
-This observation here is consistent with the numerical simulation results shown in Fig.
-\ref{fig:fig2}.
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section{Phase transition}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% From instability to homogenization
-%
-
-\textit{Phase transition}--  order to quantify the transition of the network between channeling instability and homogenization, we define an order parameter $\mathcal{O}$ that moves toward $0$ or $1$ if the network moves toward channeling or homogenization respectively.
-The order parameter is defined as
+\textit{Local Dynamics Model}--  To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes \add{of the same length $L$} in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Figs.
+\ref{fig:fig3}b-c).
+First, assuming two cylindrical tubes with radii $r_1,r_2$ in series with a given pressure difference of $\delta p = p_r- p_l$, the radius of each tube changes as $dr_i/dt = f(q,r_i),~i=1,2$ (Fig.
+\ref{fig:fig3}b) where $q=q_1=q_2$.
+Without loss of generality we assume $r_1>r_2$.
+Considering the pressure at the junction between tubes $\tilde p_m = (p_m-p_l)/(p_r-p_l)= C_2/(C_1+C_2)$.
+Time evolution of the middle pressure then follows %
 %
 \begin{align}
-    \mathcal{O} = \frac{1}{N-1} \left( N - \frac{\left( \sum_{ij} q^2_{ij}\right)^2}{ \sum_{ij} q^4_{ij}}\right)
+    \frac{d\tilde{p}_m}{dt} = \gamma (r_1 f(q,r_2)-r_2 f(q,r_1)).
 \end{align}
 %
-where $N$ is the number of edges.
-The order parameter $\mathcal{O}=0 $ when the flux in all the edges become the same $q_{ij} = \bar{q}$.
-On the other hand, when fluid flux becomes highly localized with only a few edges with non-zero flux, $\mathcal{O}\to 1$.
-We numerically calculated the order parameter $\mathcal{O}$ for the diamond-grid network during the erosion process.
-The results are shown in Fig.
-\ref{fig:fig3}c for different amounts of erosion measured by the increase in the average diameter $\langle r\rangle /r_0$.
-As shown in
- Fig.
-\ref{fig:fig3}c, at $n\approx 3$ the order parameter, remains unchanged; however for $n>3$ the order parameter moves toward zero, where the flow becomes more uniform, and for $n<3$ the order parameter goes toward unity, where channels are developed.
-The transition in the order parameter indicates a phase transition at $n=3$ in the long-time behavior of the network which is in agreement with the toy model prediction and simulation results of Fig.
-\ref{fig:fig2}.
+where $\gamma = \sqrt{{2\pi}/{\mu L}}{C_1^{\frac{3}{4}} C_2^{\frac{3}{4}}}/{ (C_1+C_2)^2}$.
+In the above equation, $r_1=r_2$ is a fixed point solution where $d\tilde p_m/dt =0$ and $p_m=1/2$.
+Since we assumed $r_1>r_2$, we can see that $\tilde p_m <1/2$, and if ${d\tilde{p}_m}/{dt}>0$, then $\tilde p_m \to 1/2$ and the flow homogenizes.
+Note that if $f(q,r) = \alpha q^m/r^n$, we find that for any $n>0$ the network homogenizes (see Fig.
+\ref{fig:fig3}b).
+Contrary to tubes in series, when the tubes are in parallel (Fig.
+\ref{fig:fig3}c), the net flow $q$ divides between the two tubes in proportion to their conductivity, i.e., $ q_1/q_2 = C_1/C_2$ which results in $q_1/q = \tilde C_1$, where $\tilde C_1 = C_1/(C_1+C_2)$.
+Note that the dynamics for each pipe in the parallel case can be simplified to $dr_i/dt = g(r_i)$ where $g(r_i) \equiv f(q_i, r_i)$ in which $q_i = \pi r_i^4 \Delta p / 8\mu L$.
+Given these dynamics, the evolution of the fluid flow ratio becomes $d(q_1/q)/dt = d \tilde C_1/dt= \sqrt{{2\pi}/{\mu L}} \gamma (r_2 g(r_1)-r_1 g(r_2))$.
+Similarly, it can be seen that  $r_1=r_2$ is a fixed point, where flow is equally distributed between the edges resulting in homogenization.
+If $d \tilde C_1/dt <0$, then the edge with larger radius has a reduced growth rate while the smaller radius edge has an increasing growth until $r_1=r_2$ is reached.
+This condition results in homogenization, where both edge's radius increases until the fixed point of $r_1=r_2$ is reached.
+The condition of $d \tilde C_1/dt<0$ is satisfied when
 %
+\begin{align}
+    \frac{g(r_1)}{g(r_2)}<\frac{r_1}{r_2}, \quad \forall r_1>r_2>0. \label{eq:condition}
+\end{align}
+%
+\add{In fact, this condition will hold for nonlaminar flow as long as $C \propto r^k (k>0).$ The power law dependence of conductance with respect to radius leads to the scale-free criteria $r_1/r_2$.}
+Note that if $d\left(g(r)/r\right)/dr<0$, then Eq.~\eqref{eq:condition} is satisfied, and homogenization would occur. 
+The above homogenization condition can further be simplified as $g(r)>g'(r)r$, which can also be obtained directly using a linear stability analysis.
+Given the homogenization condition $g(r)>g'(r)r$, if the erosion rate is sub-linear locally near the initial radius, the network moves towards homogenization.
+On the other hand, if the erosion rate is super-linear, we expect the parallel tubes to move away from homogenization and channelization occurs.
+Applying the power law erosion model with $f(q_{i},r_i)=\alpha q_i^m/r_i^n$, it can be shown that $g(r) \propto  r^{4m-n} $, and therefore $4m-n=1$ results in no change in the flow ratio $q_1/q$ (Fig.
+\ref{fig:fig3}c$_1$), while $4m-n<1$ results in homogenization condition (Fig.~\ref{fig:fig3}c$_2$), and $4m-n>1$ results in channelization (Fig.
+\ref{fig:fig3}c$_3$).
+Since a complex network includes both series and parallel connections, it is plausible that the whole network structure will behave in a similar manner, with an approximate transition in the network's behavior at $ m = (n+1)/4$.
+This result for $m=1$ reduces to a transition at $n=3$.
+It is to be noted that while the flow ratio remains constant for parallel edges, the connections in series are evolving toward homogenization and that is why we find a difference between evolved network for $n=3$ and the network at $t=0$.
+Since series connections are always moving toward homogenization, while parallel connections show a phase transition, we expect the phase transition to be at approximately $n\approx 3$, governed by the parallel connections.
+This observation  is consistent with the numerical simulation results shown in Figs.~\ref{fig:fig2} and \ref{fig:fig3}a (for $m=1$) as well as for additional values of $m$ (Fig.~\ref{fig:fig4}).
+Note, however, that the local dynamics model is only approximate and the numerically observed value of the phase transition happens for a value slightly larger than $n=3$ in Fig.
+\ref{fig:fig3}.
+% consistent with the homogenizing effect of the series connections. }
+% Although the result is derived under the constant pressure difference assumption, it holds validity for homogenization cases, where the pressure difference is going towards homogenization as well.
 
-\begin{figure}[!h]
+% \textit{Simplified Model}-- {To understand the transition in network behavior during erosion for different powers of $n$, we focus on a simplified model with only two tubes in parallel or series (Figs.
+\ref{fig:fig3}b-c).
+First, assuming two cylindrical tubes with radii $r_1,r_2$ in series, the flow is the same for the two tubes $ q_1 = q_2 = q$ (Fig.
+\ref{fig:fig3}b).
+The radius of each tube then changes as $dr_i/dt = \alpha q^m /r_i^n$ where $i=1,2$.
+% As a result, we find that the conductivity of each tube changes as $dC_i/dt \propto q^m C_i^{(3-n)/4}$, where each tube's conductivity increases.
+Considering the pressure at the junction between tubes, we find that it moves toward the average value of pressure on both sides (Fig.
+\ref{fig:fig3}(b$_1$)).
+Contrary to tubes in series, when the tubes are in parallel (Fig.
+\ref{fig:fig3}c), the flow divides between the two tubes in proportion to their conductivity, i.e., $q_1/q_2 = C_1/C_2$.
+Since each tube's radius changes as $dr_i/dt = \alpha q^m_i/r_i^n$, the evolution of the fluid flow ratio becomes
+% % %% 
+% \begin{align}
+% \frac{d}{dt}\left( \frac{C_1}{C_2}\right) \propto  \frac{C_1}{C^{n/4+1}_2} \left( \left( \frac{C_1}{C_2}\right)^{m-\frac{n+1}{4}} - 1 \right). \label{eq:dyn-paral}
+% \end{align}
+% %%
+% When $m=(n+1)/4$ in Eq.
+\eqref{eq:dyn-paral}, the right-hand-side vanishes and as a result the flow ratio $C_1/C_2$ remains constant \add{while the radius keeps changing} (Fig.~\ref{fig:fig3}c$_1$).
+However, when $m \neq (n+1)/4$, we find that $C_1/C_2 = 1$ is an equilibrium point.
+When $m<(n+1)/4$ this equilibrium solution is stable and the flow moves toward homogenization (Fig.
+\ref{fig:fig3}c$_2$); however, when $m>(n+1)/4$ this equilibrium solution becomes unstable and the solution moves toward $C_1/C_2 \to 0$ or $\infty$ which means that the entire flow passes through one of the tubes (Fig.
+\ref{fig:fig3}c$_3$).
+In summary, when the tubes are in series any erosion law makes flow become more uniform; however, when the tubes are in parallel depending on the powers $m,n$ the flow in the tubes can move toward becoming more uniform ($m<(n+1)/4$), maintain the same ratio ($m=(n+1)/4$), or move toward instability and channel development ($m>(n+1)/4$).
+{Since a complex network includes both series and parallel connections, it is plausible that the whole network structure will behave in a similar manner, with \add{an approximate} transition in the networks behavior at $ m = (n+1)/4$}.
+\add{It is to be noted that the series connection are always moving toward homogenization, while only parallel connections showing a phase transition.
+As a result, we expect the phase transition to be happening close at approximately $n\approx 3$, where the parallel connections reflect this transition.} This observation  is consistent with the numerical simulation results shown in Figs.~\ref{fig:fig2} and \ref{fig:fig3}a (for $m=1$) as well as for additional values of $m$ (Fig.~\ref{fig:fig4}).} \add{Note that the true phase transition happens for a value slightly smaller than $n=3$ in Fig.
+\ref{fig:fig3} and the the order parameter for $n=3$ slightly moves toward homogenization.
+This is due to the fact that the series connections are homogenizing while the parallel connections grow in proportion.}
+% %
+% %
+
+\textit{Analysis of generalized model}--  So far we focused on erosion dynamics with $m=1$ in $f(|q_{ij}|,r_{ij})=\alpha |q_{ij}|^m/r_{ij}^n$ since it directly corresponds to erosion laws of interest, i.e.
+an erosion rate with a linear dependence on fluid-flux, velocity, or shear-rate at the walls.
+Considering $m=2$, our model aligns with the transport optimization problem in biological networks~\cite{ronellenfitsch2016global,corson2010fluctuations,hu2013adaptation}.
+% Previous works have suggested that in the context of biological transport networks, the network is optimized to minimize its dissipation energy with regards to some constraint (such as constant material or metabolic cost).
+Interestingly, the gradient descent method utilized to find the minimal energy configurations maps to Eq.
+\eqref{eq:erosion-law} with $m=2$, albeit with additional regularizing terms.
+While under the dynamics we study here erosion will occur indefinitely, in these biological network models a minimal energy configuration exists due to these additional constraints.
+Nonetheless, the minimal energy configurations manifest a phase transition reminiscent of the one we observe in our model.
+To test the role of the parameter $m$ in our model, we simulated the general form of erosion dynamics with $f(|q_{ij}|,r_{ij}) = \alpha |q_{ij}|^m/r_{ij}^n$.
+The simulation results for a randomly initialized network for different powers of $m$ and $n$ are shown in Fig.
+\ref{fig:fig4}, where each box shows the final snapshot of the network eroded with the corresponding $m$ and $n$.
+% We further compare the network's simulation result with the simplified model's prediction.
+for the fate of the network for each pair of $m,n$.
+Additionally, the prediction of the local dynamics model is shown using the bounding box color (red for channelization and green for homogenization) in Fig.
+\ref{fig:fig4} (cf., Fig.~S8 in SM showing the heat map for the average change in the order parameter).
+The dashed black line in Fig.
+\ref{fig:fig4} shows the  the local dynamics model's prediction for the boundary between network's transition to homogeneity or channelization (i.e., $m = (n+1)/4$).
+% Although the simplified model is based on the erosion dynamics of two edges in a parallel or series configuration, it still 
+We find that the local dynamics model correctly predicts the fate of the network with the complex topology for different values of $m$ and $n$, and captures the boundary separating channelization/homogenization.
+We further consider a model where the onset of erosion happens only after  a certain threshold (see SM \S4 and Figs.
+S6 and S7) and find that the transition remains unchanged at $m=(n+1)/4$, showing robustness to thresholding effects.
+Additionally, to further test the generality of the local dynamics model, we used a nonlinear function of shear rate as $dr/dt = h(\tau)$ where $\tau=q/r^3$.
+We found that the prediction of the local dynamics model matches with the direct simulations (see SM \S7 and Figs.
+S9 and S10) where it can be used to predict the fate of a network given a general erosion law.
+
+\begin{figure}[!ht]
     \centering
-    \includegraphics[width = 0.45\textwidth]{Figs/Fig4_new33.png}
-    \caption{Evolution of a randomly initialized network for various $m$ and $n$ until $\cdots$.
-The network is randomly initialized with $N_x=$ and $N_y=$.
-The red box and the blue box shows the prediction of the simplified  model for the fate of network either homogenization (blue) or channelization (red).
-It is seen that the toy model prediction matches with the simulation of the network.
-}\label{fig:fig4}
+    \includegraphics[width = 0.45\textwidth]{Fig4.pdf}
+    \caption{Evolution of a randomly initialized network for various powers of $m$ and $n$ in $f(|q|,r) = \alpha |q|^m/r^n$.
+The network is randomly initialized with $50\times 50$ randomly distributed pores.
+The bounding box color shows the prediction of the local dynamics model for the fate of the network: homogenization (blue) or channelization (red).
+The dashed black line shows the transition boundary between channelization instability and homogenization obtained using local dynamics model, i.e., $m=(n+1)/4$.}\label{fig:fig4}
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In the case of clogging, the initial dynamics can similarly be captured using our model, however, due to the change in the connectivity of the network, our local dynamics model cannot extend to large time behaviors (SM, \S5).
 
-\add{Next, we test our simplified model for additional values of $m$.
-We compare simulation of a randomly initiated network using general erosion dynamics given in Eq.
-\eqref{eq:erosion-law} and compare the network's simulation result with the prediction of simplified model (see Fig.
-\ref{fig:fig4}).
-Each box in Fig.
-\ref{fig:4} shows the final snapshot of a network simulation for a given $n$ and $m$.
-The simplified model prediction for each box is shown using the color of the bounding box (red for channelization and green for homogenization).
-It is seen that although the simplified model is based on the erosion dynamics of two edges in parallel or series configuration, it still can correctly predict the fate of the network for different values of $m$ and $n$ and capture the line separating channelinzation/homogenization (see the black line in Fig.
-\ref{fig:fig4} in the fate of the network}
-
- \add{In this manuscript, we mainly considered the case of $m=1$, since it directly corresponds to different physics of erosion in a network with different assumptions of erosion with a linear constant, fluid-flux, velocity, or shear rate dependence.
-.
-Considering $m=2$ in Eq.
-\eqref{eq:erosion-law}, the model aligns with the transport optimization in biological networks \cite{ronellenfitsch2016global,corson2010fluctuations,hu2013adaptation}.
-In addition to our erosion dynamics, in such biological transport networks, there is an extra constraint where the network is optimized to minimize its total cost function.
-Adding the additional constraints results in global/local minimum point in the network which can be found numerically.
-In addition to the constraints, the boundary condiitons are alos different, where in biological transport networks each node consumes a part of the incoming flow, however, in the erosion considered here there is no minimum point and the flow continually moves toward more and more erosion without any bounds.
-A similar transition given all the differences is observed in biological network modes.
-The simplified model introduced here captures the evolutional process toward either channelization or homogenization and can be used to determine the fate of the network.
+%
+\textit{Conclusion}-- {We analyzed the dynamics of porous networks during erosion.
+We showed that depending on the form of the erosion law (namely, its dependence on flux and tube radius) the network can either move towards homogenization or towards developing a channeling instability.
+We elucidated the physical origin of this phase transition and how it is achieved using a simplified model.
+Our results highlight the importance of local dynamics and feedback mechanisms in the network's path toward its asymptotic global behavior \cite{ronellenfitsch2016global,corson2010fluctuations,katifori2010damage,hu2013adaptation,ocko2015feedback},  and allow us to infer the local dynamics using large scale observations.
+As a result, our model can be used as a bulk behavior proxy for determining the local dynamics of erosion in a system~\cite{mahadevan2012flow}.
+Interestingly, our results indicates that an erosion model that is local and linearly dependent on shear rate cannot result in channelization (since $m=1,n=3$ and $m=(n+1)/4$).
+However, we note that if the dependence on the shear rate is non-linear, it will qualitatively map to our model albeit with renormalized values of $n$ and $m$: e.g., a power-law dependence on shear rate with exponent $s$ would lead to $m =s$, $n = 3 s$, implying channelization when $s>1$.
+In the future, it would be exciting to test this and other predictions experimentally on model systems, relying on the technological advances in imaging flow profiles in porous materials, as well as extend the study to the geologically relevant case of chemical erosion \cite{edery2014origins,edery2016characterization}, and wormhole formation in geologic formations during CO$_2$ injection \cite{ott2015wormhole,szymczak2009wormhole}.
+Additionally, the model studied here could become richer by tracking the solute
+being eroded through solute concentration using $dr/dt=f(q,r,c)$ where $c$ is the solute concentration, and allow for solute deposition along the porous material~\cite{bizmark2020multiscale,jager2018clogging,jaeger2017mechanism}.
 }
 
-%%%
-%\begin{figure}[h]
-%    \centering
-%    \includegraphics[width = 0.4\textwidth]{Figs/Fig4_clogging}
-%    \caption{Phase transition at the power}
-%    \label{fig:fig4-clogging}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section{Clogging Dynamics}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5 
-%
-\textit{Clogging Dynamics}-- Besides erosion, another change in the network is the deposition/sedimentation of material on the boundary walls of the porous material.
-We name this dynamical change a ``clogging'' process as opposed to erosion.
-Contrary to erosion, the clogging behavior may cause some edges to block which effectively alters the network of connectivity and network behavior.
-This change in the connection between nodes through edges getting blocked can drastically alter porous structure behavior, e.g., causes a huge difference between effective and true porosity \cite{shima2021}.
-Despite the drastic change of network with blockages, we can still focus on the \textit{initial} change in the order parameter.
-The derivative of order parameter can be written as
-%
-\begin{align}
-    \frac{d\mathcal{O}}{dt} = \sum_{ij} \sum_{kl} \frac{\partial \mathcal{O}}{\partial q_{ij}} \frac{\partial q_{ij}}{\partial C_{kl}}  \frac{\partial C_{kl}}{\partial t} \label{eq:order-derivative}
-\end{align}
-%
-where the last term changes sign from erosion to clogging, i.e., $\partial C_{kl}/\partial t = \pm \alpha \pi q_{kl} /r_{kl}^{n-3}\mu l_{kl}$ for erosion and clogging respectively.
-As a result, the magnitude of change in the order parameter equals that of erosion.
-Note that in Eq.
-\eqref{eq:order-derivative}, the second term depends on the network topology, and pore throat clogging results in the change of network topology at later times.
-% The pore throat blockages results in the divergent of clogging results from just the negative of erosion. 
-In short times, however, similar to the erosion, a phase transition exists at $n=3$.
-When  $n<3$ the network moves toward homogenization during the clogging process and when $n>3$ the flow moves toward the development of channeling instability.
-At later times, this initial trend, however, might not hold true due to the aforementioned complex changes in the connectivity network during the clogging process.
+\begin{acknowledgments}
+We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery,  Eleni Katifori, and Chris Rycroft
+for useful discussions.
+\end{acknowledgments}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-% \section{Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-\textit{Conclusion}-- In summary, we analyzed the dynamics of the porous networks during erosion.
-We showed that depending on different erosion laws various network behaviors are observable.
-We used simple erosion laws, inspired by previously proposed models, and showed that depending on the rate of erosion the network can either move toward homogenization or toward developing a channeling instability.
-Next, we propose an order parameter to capture the phase transition behavior, and using a simplified model of two tubes we elucidated the physical origin of the phase transition behavior.
-In the case of clogging, since the network connectivity can vary significantly our approach does not hold at large times, however, the initial variation can be captured using our model where the results similarly show a behavior change at $n=3$.
-Our results signify the importance of local dynamics and feedback mechanism in long-time global behavior and complement similar feedback-induced studies for active conducting mediums~\cite{ocko2015feedback}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{58}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Marbach}\ \emph {et~al.}(2016)\citenamefont
+  {Marbach}, \citenamefont {Alim}, \citenamefont {Andrew}, \citenamefont
+  {Pringle},\ and\ \citenamefont {Brenner}}]{marbach2016pruning}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Marbach}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Alim}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Andrew}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {117}},\ \bibinfo {pages} {178103} (\bibinfo
+  {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2013)\citenamefont {Alim},
+  \citenamefont {Amselem}, \citenamefont {Peaudecerf}, \citenamefont
+  {Brenner},\ and\ \citenamefont {Pringle}}]{alim2013random}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Alim}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Amselem}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Peaudecerf}}, \bibinfo
+  {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Pringle}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
+  Academy of Sciences}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages}
+  {13306} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tero}\ \emph {et~al.}(2010)\citenamefont {Tero},
+  \citenamefont {Takagi}, \citenamefont {Saigusa}, \citenamefont {Ito},
+  \citenamefont {Bebber}, \citenamefont {Fricker}, \citenamefont {Yumiki},
+  \citenamefont {Kobayashi},\ and\ \citenamefont {Nakagaki}}]{tero2010rules}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Tero}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Takagi}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Saigusa}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Ito}}, \bibinfo {author}
+  {\bibfnamefont {D.~P.}\ \bibnamefont {Bebber}}, \bibinfo {author}
+  {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \bibinfo {author}
+  {\bibfnamefont {K.}~\bibnamefont {Yumiki}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Kobayashi}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {T.}~\bibnamefont {Nakagaki}},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {327}},\ \bibinfo
+  {pages} {439} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Heaton}\ \emph {et~al.}(2010)\citenamefont {Heaton},
+  \citenamefont {L{\'o}pez}, \citenamefont {Maini}, \citenamefont {Fricker},\
+  and\ \citenamefont {Jones}}]{heaton2010growth}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~L.}\ \bibnamefont
+  {Heaton}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {L{\'o}pez}},
+  \bibinfo {author} {\bibfnamefont {P.~K.}\ \bibnamefont {Maini}}, \bibinfo
+  {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Fricker}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {N.~S.}\ \bibnamefont {Jones}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the Royal Society
+  B: Biological Sciences}\ }\textbf {\bibinfo {volume} {277}},\ \bibinfo
+  {pages} {3265} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schlesinger}(1999)}]{schlesinger1999carbon}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~H.}\ \bibnamefont
+  {Schlesinger}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Science}\ }\textbf {\bibinfo {volume} {284}},\ \bibinfo {pages} {2095}
+  (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Winkler}\ and\ \citenamefont
+  {Nur}(1979)}]{winkler1979pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Winkler}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Nur}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Geophysical
+  Research Letters}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {1}
+  (\bibinfo {year} {1979})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Batzle}\ and\ \citenamefont
+  {Wang}(1992)}]{batzle1992seismic}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Batzle}}\ and\ \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Geophysics}\
+  }\textbf {\bibinfo {volume} {57}},\ \bibinfo {pages} {1396} (\bibinfo {year}
+  {1992})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cohen}\ and\ \citenamefont
+  {Rothman}(2015)}]{cohen2015mechanisms}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Cohen}}\ and\ \bibinfo {author} {\bibfnamefont {D.~H.}\ \bibnamefont
+  {Rothman}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Proceedings of the Royal Society A: Mathematical, Physical and Engineering
+  Sciences}\ }\textbf {\bibinfo {volume} {471}},\ \bibinfo {pages} {20140853}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Duduta}\ \emph {et~al.}(2011)\citenamefont {Duduta},
+  \citenamefont {Ho}, \citenamefont {Wood}, \citenamefont {Limthongkul},
+  \citenamefont {Brunini}, \citenamefont {Carter},\ and\ \citenamefont
+  {Chiang}}]{duduta2011semi}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Duduta}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Ho}}, \bibinfo
+  {author} {\bibfnamefont {V.~C.}\ \bibnamefont {Wood}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Limthongkul}}, \bibinfo {author}
+  {\bibfnamefont {V.~E.}\ \bibnamefont {Brunini}}, \bibinfo {author}
+  {\bibfnamefont {W.~C.}\ \bibnamefont {Carter}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Y.-M.}\ \bibnamefont {Chiang}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Advanced Energy Materials}\ }\textbf
+  {\bibinfo {volume} {1}},\ \bibinfo {pages} {511} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2019)\citenamefont {Sun},
+  \citenamefont {Zhu}, \citenamefont {Baumann}, \citenamefont {Peng},
+  \citenamefont {Xu}, \citenamefont {Shakir}, \citenamefont {Huang},\ and\
+  \citenamefont {Duan}}]{sun2019hierarchical}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Sun}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhu}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Baumann}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Peng}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Xu}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Shakir}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Huang}}, \
+  and\ \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Duan}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Reviews Materials}\
+  }\textbf {\bibinfo {volume} {4}},\ \bibinfo {pages} {45} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Smith}\ and\ \citenamefont
+  {Bazant}(2017)}]{smith2017multiphase}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~B.}\ \bibnamefont
+  {Smith}}\ and\ \bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
+  {Bazant}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of The Electrochemical Society}\ }\textbf {\bibinfo {volume}
+  {164}},\ \bibinfo {pages} {E3291} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Ferguson}\ and\ \citenamefont
+  {Bazant}(2012)}]{ferguson2012nonequilibrium}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~R.}\ \bibnamefont
+  {Ferguson}}\ and\ \bibinfo {author} {\bibfnamefont {M.~Z.}\ \bibnamefont
+  {Bazant}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of The Electrochemical Society}\ }\textbf {\bibinfo {volume}
+  {159}},\ \bibinfo {pages} {A1967} (\bibinfo {year} {2012})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Rad}\ \emph {et~al.}(2013)\citenamefont {Rad},
+  \citenamefont {Shokri},\ and\ \citenamefont {Sahimi}}]{rad2013pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~N.}\ \bibnamefont
+  {Rad}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Shokri}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Sahimi}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review E}\ }\textbf
+  {\bibinfo {volume} {88}},\ \bibinfo {pages} {032404} (\bibinfo {year}
+  {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Herzig}\ \emph {et~al.}(1970)\citenamefont {Herzig},
+  \citenamefont {Leclerc},\ and\ \citenamefont {Goff}}]{herzig1970flow}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Herzig}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Leclerc}}, \
+  and\ \bibinfo {author} {\bibfnamefont {P.~L.}\ \bibnamefont {Goff}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Industrial \&
+  Engineering Chemistry}\ }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages}
+  {8} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tien}\ and\ \citenamefont
+  {Payatakes}(1979)}]{tien1979advances}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Tien}}\ and\ \bibinfo {author} {\bibfnamefont {A.~C.}\ \bibnamefont
+  {Payatakes}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {AIChE Journal}\ }\textbf {\bibinfo {volume} {25}},\ \bibinfo {pages} {737}
+  (\bibinfo {year} {1979})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jaisi}\ \emph {et~al.}(2008)\citenamefont {Jaisi},
+  \citenamefont {Saleh}, \citenamefont {Blake},\ and\ \citenamefont
+  {Elimelech}}]{jaisi2008transport}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
+  {Jaisi}}, \bibinfo {author} {\bibfnamefont {N.~B.}\ \bibnamefont {Saleh}},
+  \bibinfo {author} {\bibfnamefont {R.~E.}\ \bibnamefont {Blake}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Elimelech}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Environmental Science \&
+  Technology}\ }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages} {8317}
+  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carrel}\ \emph {et~al.}(2018)\citenamefont {Carrel},
+  \citenamefont {Morales}, \citenamefont {Beltran}, \citenamefont {Derlon},
+  \citenamefont {Kaufmann}, \citenamefont {Morgenroth},\ and\ \citenamefont
+  {Holzner}}]{carrel2018biofilms}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Carrel}}, \bibinfo {author} {\bibfnamefont {V.~L.}\ \bibnamefont {Morales}},
+  \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Beltran}}, \bibinfo
+  {author} {\bibfnamefont {N.}~\bibnamefont {Derlon}}, \bibinfo {author}
+  {\bibfnamefont {R.}~\bibnamefont {Kaufmann}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Morgenroth}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Holzner}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Water Research}\ }\textbf {\bibinfo {volume}
+  {134}},\ \bibinfo {pages} {280} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Seymour}\ \emph {et~al.}(2004)\citenamefont
+  {Seymour}, \citenamefont {Gage}, \citenamefont {Codd},\ and\ \citenamefont
+  {Gerlach}}]{seymour2004anomalous}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
+  {Seymour}}, \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Gage}},
+  \bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont {Codd}}, \ and\
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Gerlach}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {93}},\ \bibinfo {pages} {198103} (\bibinfo
+  {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lake}\ \emph {et~al.}(2014)\citenamefont {Lake},
+  \citenamefont {Johns}, \citenamefont {Rossen}, \citenamefont {Pope} \emph
+  {et~al.}}]{lake2014fundamentals}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~W.}\ \bibnamefont
+  {Lake}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Johns}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Rossen}}, \bibinfo
+  {author} {\bibfnamefont {G.~A.}\ \bibnamefont {Pope}},  \emph {et~al.},\
+  }\bibfield  {booktitle} {\emph {\bibinfo {booktitle} {Fundamentals of
+  Enhanced Oil Recovery}},\ }\href@noop {} {\  (\bibinfo {year}
+  {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parsa}\ \emph {et~al.}(2020)\citenamefont {Parsa},
+  \citenamefont {Santanach-Carreras}, \citenamefont {Xiao},\ and\ \citenamefont
+  {Weitz}}]{parsa2020origin}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Parsa}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Santanach-Carreras}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Xiao}}, \ and\ \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+  {Weitz}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Fluids}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages}
+  {022001} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schorghofer}\ \emph {et~al.}(2004)\citenamefont
+  {Schorghofer}, \citenamefont {Jensen}, \citenamefont {Kudrolli},\ and\
+  \citenamefont {Rothman}}]{schorghofer2004spontaneous}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Schorghofer}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Jensen}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kudrolli}}, \ and\
+  \bibinfo {author} {\bibfnamefont {D.~H.}\ \bibnamefont {Rothman}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of Fluid
+  Mechanics}\ }\textbf {\bibinfo {volume} {503}},\ \bibinfo {pages} {357}
+  (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mahadevan}\ \emph {et~al.}(2012)\citenamefont
+  {Mahadevan}, \citenamefont {Orpe}, \citenamefont {Kudrolli},\ and\
+  \citenamefont {Mahadevan}}]{mahadevan2012flow}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Mahadevan}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Orpe}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kudrolli}}, \ and\
+  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Mahadevan}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf
+  {\bibinfo {volume} {98}},\ \bibinfo {pages} {58003} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Akanji}\ and\ \citenamefont
+  {Matthai}(2010)}]{akanji2010finite}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~T.}\ \bibnamefont
+  {Akanji}}\ and\ \bibinfo {author} {\bibfnamefont {S.~K.}\ \bibnamefont
+  {Matthai}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Transport in Porous Media}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo
+  {pages} {241} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fatt}\ \emph {et~al.}(1956)\citenamefont {Fatt} \emph
+  {et~al.}}]{fatt1956network}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Fatt}} \emph {et~al.},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Transactions of the AIME}\ }\textbf {\bibinfo {volume} {207}},\
+  \bibinfo {pages} {144} (\bibinfo {year} {1956})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Blunt}\ \emph {et~al.}(2013)\citenamefont {Blunt},
+  \citenamefont {Bijeljic}, \citenamefont {Dong}, \citenamefont {Gharbi},
+  \citenamefont {Iglauer}, \citenamefont {Mostaghimi}, \citenamefont
+  {Paluszny},\ and\ \citenamefont {Pentland}}]{blunt2013pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+  {Blunt}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Bijeljic}},
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Dong}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Gharbi}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Iglauer}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Mostaghimi}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Paluszny}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Pentland}},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Advances in Water Resources}\ }\textbf {\bibinfo
+  {volume} {51}},\ \bibinfo {pages} {197} (\bibinfo {year} {2013})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Stoop}\ \emph {et~al.}(2019)\citenamefont {Stoop},
+  \citenamefont {Waisbord}, \citenamefont {Kantsler}, \citenamefont {Heinonen},
+  \citenamefont {Guasto},\ and\ \citenamefont {Dunkel}}]{stoop2019disorder}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Stoop}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Waisbord}},
+  \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Kantsler}}, \bibinfo
+  {author} {\bibfnamefont {V.}~\bibnamefont {Heinonen}}, \bibinfo {author}
+  {\bibfnamefont {J.~S.}\ \bibnamefont {Guasto}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Dunkel}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Non-Newtonian Fluid Mechanics}\
+  }\textbf {\bibinfo {volume} {268}},\ \bibinfo {pages} {66} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bryant}\ \emph {et~al.}(1993)\citenamefont {Bryant},
+  \citenamefont {King},\ and\ \citenamefont {Mellor}}]{bryant1993network}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
+  {Bryant}}, \bibinfo {author} {\bibfnamefont {P.~R.}\ \bibnamefont {King}}, \
+  and\ \bibinfo {author} {\bibfnamefont {D.~W.}\ \bibnamefont {Mellor}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Transport in
+  Porous Media}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages} {53}
+  (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dong}\ and\ \citenamefont
+  {Blunt}(2009)}]{dong2009pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Dong}}\ and\ \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+  {Blunt}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review E}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages}
+  {036307} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Blunt}\ and\ \citenamefont
+  {Scher}(1995)}]{blunt1995pore}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+  {Blunt}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Scher}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  E}\ }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {6387} (\bibinfo
+  {year} {1995})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2017)\citenamefont {Alim},
+  \citenamefont {Parsa}, \citenamefont {Weitz},\ and\ \citenamefont
+  {Brenner}}]{alim2017local}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Alim}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Parsa}},
+  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Letters}\ }\textbf {\bibinfo {volume} {119}},\ \bibinfo {pages} {144501}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parsa}\ \emph {et~al.}(2021)\citenamefont {Parsa},
+  \citenamefont {Zareei}, \citenamefont {Santanach-Carreras}, \citenamefont
+  {Morris}, \citenamefont {Amir}, \citenamefont {Xiao},\ and\ \citenamefont
+  {Weitz}}]{shima2021}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Parsa}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zareei}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Santanach-Carreras}},
+  \bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont {Morris}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Amir}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Xiao}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Physical Review Fluids}\ }\textbf {\bibinfo
+  {volume} {6}},\ \bibinfo {pages} {L082302} (\bibinfo {year}
+  {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fraggedakis}\ \emph {et~al.}(2021)\citenamefont
+  {Fraggedakis}, \citenamefont {Chaparian},\ and\ \citenamefont
+  {Tammisola}}]{fraggedakis_chaparian_tammisola_2021}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Fraggedakis}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Chaparian}}, \ and\ \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+  {Tammisola}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of Fluid Mechanics}\ }\textbf {\bibinfo {volume} {911}},\ \bibinfo
+  {pages} {A58} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Datta}\ \emph {et~al.}(2013)\citenamefont {Datta},
+  \citenamefont {Chiang}, \citenamefont {Ramakrishnan},\ and\ \citenamefont
+  {Weitz}}]{datta2013spatial}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
+  {Datta}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Chiang}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ramakrishnan}}, \ and\
+  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review Letters}\
+  }\textbf {\bibinfo {volume} {111}},\ \bibinfo {pages} {064501} (\bibinfo
+  {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {J{\"a}ger}\ \emph {et~al.}(2017)\citenamefont
+  {J{\"a}ger}, \citenamefont {Mendoza},\ and\ \citenamefont
+  {Herrmann}}]{jager2017channelization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {J{\"a}ger}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Mendoza}},
+  \ and\ \bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont {Herrmann}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  E}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages} {013110} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ristroph}\ \emph {et~al.}(2012)\citenamefont
+  {Ristroph}, \citenamefont {Moore}, \citenamefont {Childress}, \citenamefont
+  {Shelley},\ and\ \citenamefont {Zhang}}]{ristroph2012sculpting}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Ristroph}}, \bibinfo {author} {\bibfnamefont {M.~N.}\ \bibnamefont {Moore}},
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Childress}}, \bibinfo
+  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Shelley}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Zhang}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
+  Academy of Sciences}\ }\textbf {\bibinfo {volume} {109}},\ \bibinfo {pages}
+  {19606} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wan}\ and\ \citenamefont
+  {Fell}(2004)}]{wan2004investigation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+  {Wan}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Fell}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of
+  Geotechnical and Geoenvironmental Engineering}\ }\textbf {\bibinfo {volume}
+  {130}},\ \bibinfo {pages} {373} (\bibinfo {year} {2004})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2012)\citenamefont {Chen},
+  \citenamefont {Jiang}, \citenamefont {Li}, \citenamefont {Hu}, \citenamefont
+  {Bu}, \citenamefont {Cai},\ and\ \citenamefont {Du}}]{chen2012haemodynamics}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont
+  {Chen}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Jiang}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Li}}, \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Hu}}, \bibinfo {author} {\bibfnamefont
+  {J.-w.}\ \bibnamefont {Bu}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Cai}}, \ and\ \bibinfo {author} {\bibfnamefont {J.-l.}\
+  \bibnamefont {Du}},\ }\href@noop {} {\  (\bibinfo {year} {2012})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Hacking}\ \emph {et~al.}(1996)\citenamefont
+  {Hacking}, \citenamefont {VanBavel},\ and\ \citenamefont
+  {Spaan}}]{hacking1996shear}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Hacking}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {VanBavel}}, \
+  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Spaan}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {American Journal
+  of Physiology-Heart and Circulatory Physiology}\ }\textbf {\bibinfo {volume}
+  {270}},\ \bibinfo {pages} {H364} (\bibinfo {year} {1996})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Kudrolli}\ and\ \citenamefont
+  {Clotet}(2016)}]{kudrolli2016evolution}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Kudrolli}}\ and\ \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
+  {Clotet}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Letters}\ }\textbf {\bibinfo {volume} {117}},\ \bibinfo
+  {pages} {028001} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Derr}\ \emph {et~al.}(2020)\citenamefont {Derr},
+  \citenamefont {Fronk}, \citenamefont {Weber}, \citenamefont {Mahadevan},
+  \citenamefont {Rycroft},\ and\ \citenamefont {Mahadevan}}]{derr2020flow}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~J.}\ \bibnamefont
+  {Derr}}, \bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont {Fronk}},
+  \bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont {Weber}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Mahadevan}}, \bibinfo {author}
+  {\bibfnamefont {C.~H.}\ \bibnamefont {Rycroft}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Mahadevan}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo
+  {volume} {125}},\ \bibinfo {pages} {158002} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Steeb}\ \emph {et~al.}()\citenamefont {Steeb},
+  \citenamefont {Diebels},\ and\ \citenamefont
+  {Vardoulakis}}]{steeb2007modeling}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Steeb}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Diebels}}, \
+  and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Vardoulakis}},\
+  }\enquote {\bibinfo {title} {Modeling internal erosion in porous media},}\
+  in\ \href@noop {} {\emph {\bibinfo {booktitle} {Computer Applications In
+  Geotechnical Engineering}}},\ pp.\ \bibinfo {pages} {1--10}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Marot}\ \emph {et~al.}(2012)\citenamefont {Marot},
+  \citenamefont {Le}, \citenamefont {Garnier}, \citenamefont {Thorel},\ and\
+  \citenamefont {Audrain}}]{marot2012study}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Marot}}, \bibinfo {author} {\bibfnamefont {V.~D.}\ \bibnamefont {Le}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Garnier}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Thorel}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Audrain}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {European Journal of Environmental and Civil
+  Engineering}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {1}
+  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sibille}\ \emph {et~al.}(2015)\citenamefont
+  {Sibille}, \citenamefont {Lomin{\'e}}, \citenamefont {Poullain},
+  \citenamefont {Sail},\ and\ \citenamefont {Marot}}]{sibille2015internal}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Sibille}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Lomin{\'e}}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Poullain}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Sail}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Marot}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Hydrological Processes}\ }\textbf {\bibinfo
+  {volume} {29}},\ \bibinfo {pages} {2149} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bonelli}\ and\ \citenamefont
+  {Marot}(2011)}]{bonelli2011micromechanical}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Bonelli}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Marot}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {European Journal of Environmental and Civil Engineering}\ }\textbf {\bibinfo
+  {volume} {15}},\ \bibinfo {pages} {1207} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parker}\ and\ \citenamefont
+  {Izumi}(2000)}]{parker2000purely}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Parker}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Izumi}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of Fluid
+  Mechanics}\ }\textbf {\bibinfo {volume} {419}},\ \bibinfo {pages} {203}
+  (\bibinfo {year} {2000})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hu}\ and\ \citenamefont
+  {Cai}(2013)}]{hu2013adaptation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Hu}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Cai}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Letters}\ }\textbf {\bibinfo {volume} {111}},\ \bibinfo {pages} {138701}
+  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ronellenfitsch}\ and\ \citenamefont
+  {Katifori}(2016)}]{ronellenfitsch2016global}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Ronellenfitsch}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Katifori}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Letters}\ }\textbf {\bibinfo {volume} {117}},\ \bibinfo
+  {pages} {138301} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kramer}\ and\ \citenamefont
+  {MacKinnon}(1993)}]{kramer1993localization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Kramer}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {MacKinnon}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Reports on Progress in Physics}\ }\textbf {\bibinfo {volume} {56}},\
+  \bibinfo {pages} {1469} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Corson}(2010)}]{corson2010fluctuations}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Corson}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Letters}\ }\textbf {\bibinfo {volume} {104}},\ \bibinfo
+  {pages} {048703} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Katifori}\ \emph {et~al.}(2010)\citenamefont
+  {Katifori}, \citenamefont {Sz{\"o}ll{\H{o}}si},\ and\ \citenamefont
+  {Magnasco}}]{katifori2010damage}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Katifori}}, \bibinfo {author} {\bibfnamefont {G.~J.}\ \bibnamefont
+  {Sz{\"o}ll{\H{o}}si}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~O.}\
+  \bibnamefont {Magnasco}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume} {104}},\
+  \bibinfo {pages} {048704} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ocko}\ and\ \citenamefont
+  {Mahadevan}(2015)}]{ocko2015feedback}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
+  {Ocko}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Mahadevan}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review Letters}\ }\textbf {\bibinfo {volume} {114}},\ \bibinfo
+  {pages} {134501} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Edery}\ \emph {et~al.}(2014)\citenamefont {Edery},
+  \citenamefont {Guadagnini}, \citenamefont {Scher},\ and\ \citenamefont
+  {Berkowitz}}]{edery2014origins}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Edery}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Guadagnini}},
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Scher}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Berkowitz}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Water Resources Research}\
+  }\textbf {\bibinfo {volume} {50}},\ \bibinfo {pages} {1490} (\bibinfo {year}
+  {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Edery}\ \emph {et~al.}(2016)\citenamefont {Edery},
+  \citenamefont {Porta}, \citenamefont {Guadagnini}, \citenamefont {Scher},\
+  and\ \citenamefont {Berkowitz}}]{edery2016characterization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Edery}}, \bibinfo {author} {\bibfnamefont {G.~M.}\ \bibnamefont {Porta}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Guadagnini}}, \bibinfo
+  {author} {\bibfnamefont {H.}~\bibnamefont {Scher}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Berkowitz}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Transport in Porous Media}\ }\textbf
+  {\bibinfo {volume} {115}},\ \bibinfo {pages} {291} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ott}\ and\ \citenamefont
+  {Oedai}(2015)}]{ott2015wormhole}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Ott}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Oedai}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Geophysical
+  Research Letters}\ }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages}
+  {2270} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Szymczak}\ and\ \citenamefont
+  {Ladd}(2009)}]{szymczak2009wormhole}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Szymczak}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Ladd}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal
+  of Geophysical Research: Solid Earth}\ }\textbf {\bibinfo {volume} {114}}
+  (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bizmark}\ \emph {et~al.}(2020)\citenamefont
+  {Bizmark}, \citenamefont {Schneider}, \citenamefont {Priestley},\ and\
+  \citenamefont {Datta}}]{bizmark2020multiscale}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Bizmark}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Schneider}},
+  \bibinfo {author} {\bibfnamefont {R.~D.}\ \bibnamefont {Priestley}}, \ and\
+  \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont {Datta}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Science Advances}\ }\textbf
+  {\bibinfo {volume} {6}},\ \bibinfo {pages} {eabc2530} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {J{\"a}ger}\ \emph {et~al.}(2018)\citenamefont
+  {J{\"a}ger}, \citenamefont {Mendoza},\ and\ \citenamefont
+  {Herrmann}}]{jager2018clogging}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {J{\"a}ger}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Mendoza}},
+  \ and\ \bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont {Herrmann}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Fluids}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {074302}
+  (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jaeger}\ \emph {et~al.}(2017)\citenamefont {Jaeger},
+  \citenamefont {Mendoza},\ and\ \citenamefont
+  {Herrmann}}]{jaeger2017mechanism}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Jaeger}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Mendoza}}, \
+  and\ \bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont {Herrmann}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Letters}\ }\textbf {\bibinfo {volume} {119}},\ \bibinfo {pages} {124501}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\end{thebibliography}%
 
-% \add{phase transition from channeling to full blocking in active porous structures \cite{ocko2015feedback}}
-
-\textit{Acknowledgments}-- We would like to acknowledge Kavli Institute for the fruitful discussions and also MRSEC  DMR-2011754 and DMR-1420570 for the support.
-
-% \begin{figure}[h]
-    % \centering
-%     \includegraphics[width = 0.48\textwidth]{Figs/Fig2p_clogging.png}
-%    \caption{Clogging in a network of pipes.
-The initial condition is shown with the label $t=0$ in the first row.
-Each row afterward corresponds to the simulation result after $N$ steps such that $\langle R_{t=N}\rangle=0.5 R_0$ where $R_0 = \langle R_{t=0}\rangle$; in other words the same amount of material is eroded in all cases.
-The erosion laws used here is $dR/dt = \alpha Q/R^n$ where $n$ varies for each row.
-The constant $\alpha$ in all cases are $1$ and time step $dt$ is chosen such that the maximum amount of increase in $R$ at each step is smaller than $0.01 R_0$.
-}\label{fig:fig2}
-% \end{figure}
-
-% \begin{itemize}
-%    \item second order phase transition
-%     \item intro
-%    \item fig 4 for random network
-%    \item clogging? 
-% \end{itemize}
-
-\bibliography{ref.bib}
+%\bibliography{ref.bib}
 

### 2022-03-06 response_submission/prl_paper.tex
Updates from Overleaf

--- 2022-03-06 prl_paper.tex
@@
 
-\title{Temporal Evolution of Erosion in Pore-Networks:\\ From Homogenization to Instability} 
+\title{Temporal Evolution of \add{Erosion} in Pore-Networks:\\ From Homogenization to Instability} 
 % Force line breaks with \\
@@
 \begin{abstract}
-We study the dynamics of flow-networks in porous media using a two/three dimensional
-pore-network model. We consider a class of erosion dynamics
-for a single phase flow with no deposition, chemical reactions, or topology changes assuming a constitutive law depending on flow rate, local velocities, or shear stress at the walls.
+We study the dynamics of flow-networks in porous media using a \add{two/three dimensional}
+pore-network model. First, we consider a class of erosion dynamics
+\add{for a single phase flow with no deposition, chemical reactions, or topology changes} assuming a constitutive law depending on flow rate, local velocities, or shear stress at the walls.
 We show that depending on the erosion law, the flow may become uniform and homogenized or become unstable and develop channels.
@@
 Poiseuille's law implies that the conductance $C_{ij} = {\pi r_{ij}^4}/{8 \mu l_{ij}}$, with $r_{ij}$ and $l_{ij}$ the edge's radius and length.
-Initially, we consider a topologically random network of nodes constructed using uniformly distributed nodes (i.e., a Poisson point process) in a planar domain connected using Delaunay triangulation (Fig.
+Initially, we consider a topologically random network of nodes constructed using uniformly distributed nodes \add{(i.e., a Poisson point process)} in a planar domain connected using Delaunay triangulation (Fig.
 \ref{fig:fig1}b).
@@
 \textit{Network evolution model}-- The degradation of the solid skeleton (i.e., erosion) or deposition of material on the pore throats (i.e., clogging) in the network of pores is modeled by the change (increase or decrease) in the radii of the edges connecting the pores which translates into changes in the flow resistance between the pores.
-The rate of change of the radii depends on local fluid flow parameters (i.e., $q, r$), however, the exact dependence is unknown.
-A general constitutive model for erosion can be written as $dr_{ij}/dt = f(q_{ij},r_{ij})$, where $f(q_{ij},r_{ij})$ represents the functional dependence of erosion on the fluid flux $q_{ij}$ and the tube radius $r_{ij}$.
-Erosion in saturated, granular, porous medium occurs when the shear stress  at the walls $\tau_w$ exerted by the fluid overcomes the cohesive strength of the solid matter $\tau_c$.
+The rate of change of the radii depends on local fluid flow parameters \add{(i.e., $q, r$),} however, the exact dependence is unknown.
+\add{A general constitutive model for erosion can be written as $dr_{ij}/dt = f(q_{ij},r_{ij})$, where $f(q_{ij},r_{ij})$ represents the functional dependence of erosion on the fluid flux $q_{ij}$ and the tube radius $r_{ij}$.} \add{Erosion in saturated, granular, porous medium occurs when the shear stress  at the walls $\tau_w$ exerted by the fluid overcomes the cohesive strength of the solid matter $\tau_c$.
 In a class of erosion models previously studied~\cite{jager2017channelization,ristroph2012sculpting,wan2004investigation} the eroded mass per unit area is linearly proportional to the excess shear, i.e.,  $\dot{m}  = -\kappa  (\tau_w-\tau_c)$ where $\kappa$ is the linear proportionality constant.
-This erosion model effectively results in an increase in the radius of the edges in our network model where \add{$\dot{r} \propto \kappa/r (|q|/r^3 - \tau_c)$ , where $1/r$ factor comes from the eroded mass $dm =2\pi\rho r l dr$ for a cylindrical pipe and $|q|/r^3$ comes from the known result of shear stress of laminar flow in pipes \cite{white2006viscous}}.
+This erosion model effectively results in an increase in the radius of the edges in our network model where $\dot{r} \propto -\kappa r (|q|/r^3 - \tau_c)$.
 Similar models have further been used in biological models for the growth of vascular networks~\cite{chen2012haemodynamics,hacking1996shear}.
-In addition to local shear stress, erosion based on local fluid velocity ($v \propto |q|/r^2$) \cite{kudrolli2016evolution}, local pressure difference ($\Delta p \propto |q|/r^4$) \cite{derr2020flow,mahadevan2012flow}, and power dissipation ($P \propto q^2/r^4$ ) ~\cite{steeb2007modeling,marot2012study,sibille2015internal} have also been considered as alternative models.
-Here, we first focus on a class of erosion dynamics described by $f(q_{ij},r_{ij}) = \alpha |q_{ij}|^m/r_{ij}^n$ where $m,n,\alpha>0$ are constants.
+In addition to local shear stress, erosion based on local fluid velocity ($v \propto |q|/r^2$) \cite{kudrolli2016evolution}, local pressure difference ($\Delta p \propto |q|/r^4$) \cite{derr2020flow,mahadevan2012flow}, and power dissipation ($P \propto q^2/r^4$ ) ~\cite{steeb2007modeling,marot2012study,sibille2015internal} have also been considered as alternative models.} \add{Here, we first focus on a class of erosion dynamics described by $f(q_{ij},r_{ij}) = \alpha |q_{ij}|^m/r_{ij}^n$ where $m,n,\alpha>0$ are constants.
 This model unifies a diverse set of erosion and clogging dynamics as different values of $m$ and $n$ correspond to different physics of erosion.
-Later we will generalize the models to include other forms of nonlinearities.
-% We use a general constitutive  model which may implement a diverse set of erosion or clogging dynamics and thus allows us to study the effect of different laws in a unified way.
+Later we will generalize the models to include other forms of nonlinearities.} % We use a general constitutive  model which may implement a diverse set of erosion or clogging dynamics and thus allows us to study the effect of different laws in a unified way.
 %
@@
 % where $m,n,\alpha$ are constants. Different values of $m$ and $n$ along with a positive $\alpha>0$ correspond to different erosion physics (analogously, $\alpha<0$ corresponds to clogging).
-Particularly, the erosion when $m=1$ and  (i) $n=0$ depends on the amount of flux $q_{ij}$ passing through the edge; (ii) $n=2$ depends on the local velocities  \cite{kudrolli2016evolution}; (iii) $n=3$ depends on the shear force at the boundary of the throat~ \cite{bonelli2011micromechanical,parker2000purely,jager2017channelization}.
-{Additionally, $m=2$ and $n=6$ corresponds to models considered in biological transport networks where the radii changes are {proportional to the square of shear stress at the boundary walls}~\cite{hu2013adaptation,ronellenfitsch2016global}.}  We later address the effect of incorporating the threshold discussed above into our model.
+Particularly, the erosion when $m=1$ and  (i) $n=0$ depends on the amount of flux $q_{ij}$ passing through the edge; (ii) $n=2$ depends on the local velocities \add{\cite{kudrolli2016evolution};} (iii) $n=3$ depends on the shear force at the boundary of the throat~\add{\cite{bonelli2011micromechanical,parker2000purely,jager2017channelization}}.
+{Additionally, $m=2$ and $n=6$ corresponds to models considered in biological transport networks where the radii changes are {proportional to the square of shear stress at the boundary walls}~\cite{hu2013adaptation,ronellenfitsch2016global}.} \add{We later address the effect of incorporating the threshold discussed above into our model.}
 We consider a randomly initialized network with disordered diameters obtained from a uniform distribution (SM S1). 
@@
 Similarly, the PDF of the tube diameters becomes narrower.
-It is to be noted that the different distributions obtained for different powers of $m,n$ represent different statistics that cannot be collapsed.
-
-We found that similar results uphold in a 3d random tube network  (see SM, Fig.~S2) as well as a 2d topologically ordered (diamond grid) network, illustrating the robustness of the results to the network topology (SM, Fig.~S3).
+\add{It is to be noted that the different distributions obtained for different powers of $m,n$ represent different statistics that cannot be collapsed.}
+
+We found that similar results uphold in a 3d random tube network \add{(see SM, Fig.~S2)} as well as a 2d topologically ordered (diamond grid) network, illustrating the robustness of the results to the network topology (SM, Fig.~S3).
 Similarly, we found that the results hold also when using an initial narrow distribution of diameters (SM, Fig.~S4), showing robustness with respect to the strength of the disorder.
-We further changed the boundary conditions, using a circular random network with the inlet at the center and outlet at the outer edges and we find that similar results uphold~(SM, Fig.~S5).
+\add{We further changed the boundary conditions, using a circular random network with the inlet at the center and outlet at the outer edges and we find that similar results uphold~(SM, Fig.~S5).
+}
 
@@
 
-\textit{Local Dynamics Model}--  To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes \add{of the same length $L$} in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Figs.
+\textit{Local Dynamics Model}-- \add{To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Figs.
 \ref{fig:fig3}b-c).
@@
 %
-\add{In fact, this condition will hold for nonlaminar flow as long as $C \propto r^k (k>0).$ The power law dependence of conductance with respect to radius leads to the scale-free criteria $r_1/r_2$.}
 Note that if $d\left(g(r)/r\right)/dr<0$, then Eq.~\eqref{eq:condition} is satisfied, and homogenization would occur.
@@
 Note, however, that the local dynamics model is only approximate and the numerically observed value of the phase transition happens for a value slightly larger than $n=3$ in Fig.
-\ref{fig:fig3}.
+\ref{fig:fig3}.}
 % consistent with the homogenizing effect of the series connections. }
@@
 
-\textit{Analysis of generalized model}--  So far we focused on erosion dynamics with $m=1$ in $f(|q_{ij}|,r_{ij})=\alpha |q_{ij}|^m/r_{ij}^n$ since it directly corresponds to erosion laws of interest, i.e.
+\textit{Analysis of generalized model}-- \add{So far we focused on erosion dynamics with $m=1$ in $f(|q_{ij}|,r_{ij})=\alpha |q_{ij}|^m/r_{ij}^n$ since it directly corresponds to erosion laws of interest, i.e.
 an erosion rate with a linear dependence on fluid-flux, velocity, or shear-rate at the walls.
@@
 % Although the simplified model is based on the erosion dynamics of two edges in a parallel or series configuration, it still 
-We find that the local dynamics model correctly predicts the fate of the network with the complex topology for different values of $m$ and $n$, and captures the boundary separating channelization/homogenization.
-We further consider a model where the onset of erosion happens only after  a certain threshold (see SM \S4 and Figs.
-S6 and S7) and find that the transition remains unchanged at $m=(n+1)/4$, showing robustness to thresholding effects.
-Additionally, to further test the generality of the local dynamics model, we used a nonlinear function of shear rate as $dr/dt = h(\tau)$ where $\tau=q/r^3$.
+We find that the local dynamics model correctly predicts the fate of the network with the complex topology for different values of $m$ and $n$, and captures the boundary separating channelization/homogenization.} \add{We further consider a model where the onset of erosion happens only after  a certain threshold (see SM \S4 and Figs.
+S6 and S7) and find that the transition remains unchanged at $m=(n+1)/4$, showing robustness to thresholding effects.} \add{Additionally, to further test the generality of the local dynamics model, we used a nonlinear function of shear rate as $dr/dt = h(\tau)$ where $\tau=q/r^3$.
 We found that the prediction of the local dynamics model matches with the direct simulations (see SM \S7 and Figs.
-S9 and S10) where it can be used to predict the fate of a network given a general erosion law.
+S9 and S10) where it can be used to predict the fate of a network given a general erosion law.}
 
@@
 However, we note that if the dependence on the shear rate is non-linear, it will qualitatively map to our model albeit with renormalized values of $n$ and $m$: e.g., a power-law dependence on shear rate with exponent $s$ would lead to $m =s$, $n = 3 s$, implying channelization when $s>1$.
-In the future, it would be exciting to test this and other predictions experimentally on model systems, relying on the technological advances in imaging flow profiles in porous materials, as well as extend the study to the geologically relevant case of chemical erosion \cite{edery2014origins,edery2016characterization}, and wormhole formation in geologic formations during CO$_2$ injection \cite{ott2015wormhole,szymczak2009wormhole}.
-Additionally, the model studied here could become richer by tracking the solute
+In the future, it would be exciting to test this and other predictions experimentally on model systems, relying on the technological advances in imaging flow profiles in porous materials, as well as extend the study to the geologically relevant case of chemical erosion \cite{edery2014origins,edery2016characterization}, \add{and wormhole formation in geologic formations during CO$_2$ injection \cite{ott2015wormhole,szymczak2009wormhole}.} \add{Additionally, the model studied here could become richer by tracking the solute
 being eroded through solute concentration using $dr/dt=f(q,r,c)$ where $c$ is the solute concentration, and allow for solute deposition along the porous material~\cite{bizmark2020multiscale,jager2018clogging,jaeger2017mechanism}.
+}
 }

### 2022-03-06 response_submission/supp.tex
Updates from Overleaf

--- 2022-03-06 backup_Sep_2_2021/supp.tex
@@
 % Color Edits
-\newcommand{\EM}[1]{\noindent \color{red} (AA: #1)\normalcolor}
-\newcommand{\AZ}[1]{\noindent \color{blue} (AZ: #1)\normalcolor}
 
@@
 \usepackage[usenames, dvipsnames]{color}
+\usepackage{subfig}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 
+\usepackage{xcolor}
+\newcommand{\DP}[1]{\noindent \color{cyan} (DP: #1)\normalcolor}
+% \newcommand{\AZ}[1]{\noindent \color{purple} (AZ: #1)\normalcolor}
+\newcommand{\add}[1]{\noindent \color{blue} #1 \normalcolor}
+\newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}
+\newcommand{\AZ}[1]{\noindent \color{magenta} (AZ: #1)\normalcolor}
 \renewcommand{\thepage}{S\arabic{page}}
@@
 
-\title{Temporal Evolution of Flow in Pore-Networks:\\ From Homogenization to Instability}% Force line breaks with \\
+\title{Temporal Evolution of Erosion in Pore-Networks:\\ From Homogenization to Instability}% Force line breaks with \\
 % \thanks{A footnote to the article title}%
@@
 \affiliation{ School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with \\
-\author{Pan Deng}%
+\author{Deng Pan}%
 \affiliation{ School of Engineering and Applied Sciences, Harvard University, Cambridge, MA, 02148}%\altaffiliation[]{SEAS, Pierce Hall}%Lines break automatically or can be forced with
@@
 In either case, the network has an order of $10^3$ edges.
-The code is publicly available in a GitHub repository \cite{githubrepo}.
+\add{Note that the physical assumption of low Reynolds regime Re$\ll$1 at all times ensures that the Poisoulle flow assumption remains valid.
+Additional dimensionless transport numbers such as the P\'eclet number (ratio of advection to diffusion) or the Damkohler number (ratio of chemical reaction rate to the transport phenomena rate) are assumed to be respectively very large and very small, resulting in advection to be much stronger than diffusion and chemical reaction.
+It is to be noted that considering diffusion or chemical reactions might change the dynamics of erosion as it requires tracking a secondary concentration field that might affect the local erosion law.} The code is publicly available in a GitHub repository \cite{githubrepo}.
 
@@
 %
-
+\newpage
 \section{Analytical results for fluid flux EXP-tail PDF in a Diamond Network}
@@
 \newpage
-\section{Robustness to topology and initial condition}
+\section{Robustness to topology, initial condition, and boundary condition}
 % 
-In order to check the robustness of our result with respect to the topology of the network, we run our simulations on a three-dimensional random network with Voronoi cell initialization of nodes in space (Fig.
+In order to check the robustness of our results with respect to the topology of the network, we run our simulations on a three-dimensional random network with Voronoi cell initialization of nodes in space (Fig.
 \ref{SIfig:fig2-3d}), and also for a two dimensional topologically ordered network with a diamond grid (Fig.
@@
 We further check the effect of initial randomness on the fate of the network.
-We use a two-dimensional diamond-grid network with a narrow uniform initial distribution of tube diameters around an average diameter $d_0$ with only a very small variation ($3\%$), i.e., the tube diameters are sampled from $\mathcal{U}(d_0(1-\epsilon), d_0(1+\epsilon))$.
+We use a two-dimensional diamond-grid network with a narrow uniform initial distribution of tube diameters around an average diameter $d_0$ with only a very small variation ($3\%$), i.e., the tube diameters are sampled from a uniform distribution with $\mathcal{U}(d_0(1-\epsilon), d_0(1+\epsilon))$.
 We again find that for the networks with $n<3$ channels are formed, while for $n>3$ the network stays homogenized.
+\add{In addition to the network topology and initial condition, we test the robustness of our results to changes in the boundary condition.
+We choose a circular domain, with the central node being the inlet and all the nodes at the outer boundary being outlets.
+Similar to the transition reported for the square
+domain, we find a phase transition at the predicted power which shows that our analysis is independent of the geometry (Fig.~\ref{SIfig:fig2-3d_circular}). }
 %
@@
       \includegraphics[width = 1.0\textwidth]{FigS2.pdf}
-     \caption{Erosion in a topologically random 3D network of tubes with $N_x=20, N_y=12, N_z=12$ points for Voronoi cell initialization and an initial uniform broad distribution of tube diameters randomly sampled from $\mathcal{U}(1,14)$.
+     \caption{Erosion in a topologically random 3D network of tubes with $N_x=20, N_y=12, N_z=12$ points for Voronoi cell initialization and an initial uniform broad distribution of tube diameters randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$.
 Snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$ are shown.
 We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
-The erosion law is based on Eq.
-(1) in the main text where different powers of $n$ correspond to different models of erosion.}\label{SIfig:fig2-3d}
+The erosion law is based on $dr/dt = \alpha q/r^n$ where different powers of $n$ correspond to different models of erosion.}\label{SIfig:fig2-3d}
  \end{figure}
@@
  \includegraphics[width=0.75\textwidth]{FigS3.pdf} % Fig2-Sdiamond.pdf
-     \caption{Erosion in a diamond grid network with $N_x=100, N_y=50$ randomly distributed nodes and an initially broad  distribution of tube diameter randomly sampled from $\mathcal{U}(1,14)$.
+     \caption{Erosion in a diamond grid network with $N_x=100, N_y=50$ randomly distributed nodes and an initially broad  distribution of tube diameter randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$.
 The initial condition is shown with the label $t=0$ in the first row.
@@
  \includegraphics[width=0.72\textwidth]{FigS4.pdf}
-     \caption{Erosion in a structured diamond grid network with $N_x=50, N_y=50$ and an initially narrow distribution of tube diameters randomly sampled from  $\mathcal{U}\left(d_0(1-\epsilon), d_u(1+\epsilon)\right) $ where  $d_0$ is the average diameter and $\epsilon=0.03$.
+     \caption{Erosion in a structured diamond grid network with $N_x=50, N_y=50$ and an initially narrow distribution of tube diameters randomly sampled from a uniform distribution with  $\mathcal{U}\left(d_0(1-\epsilon), d_u(1+\epsilon)\right) $ where  $d_0$ is the average diameter and $\epsilon=0.03$.
 The initial condition is shown with the label $t=0$ in the first row.
@@
 \end{figure}
+%
+\begin{figure}[htp]
+     % \centering
+      \includegraphics[width = 0.70\textwidth]{./circular3.pdf}
+     \caption{\textcolor{blue}{Erosion in a topologically random 3D network of tubes with a circular topology with $N = 3000 $ randomly distributed nodes and an initial uniform broad distribution of tube diameters randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$.
+Shown are snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$.
+We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
+The erosion law is based on Eq.
+(1) in the main text where different powers of $n$ correspond to different models of erosion.}}\label{SIfig:fig2-3d_circular}
+ \end{figure}
+%
+
+\clearpage
+\section{Erosion with a threshold}
+%
+\add{In order to make our erosion model more realistic, we modify the model as  
+%
+\begin{align}
+    \frac{dr}{dt } = \begin{cases} q^m/r^n - \beta & q^m/r^n\geq \beta\\
+    0 & q^m/r^n<\beta
+    \end{cases} \label{eq:thresh}
+\end{align}
+%
+where $\beta$ is the threshold for the onset of erosion.
+We pick $\beta = 0.25\langle q^m/r^n\rangle $ and $\beta = 0.9 \langle q^m/r^n\rangle$ corresponding to a small and a large threshold value.
+In both cases, we ran our simulations for different values of $m$ and $n$, and found that different behaviors of homogenization and channelization persists (see Fig.
+\ref{fig:figthresh1}).
+The result can be explained by applying the general condition for the phase transition as discussed in the main text.
+Following the same argument, it can be shown that the homogenization condition (Eq.
+3 in the main text) is equivalent to the condition
+%
+\begin{align}
+4m-n-1 < -\frac{\beta}{q^m/r^n}.    
+\end{align}
+%
+which can be found using $g(r) = ({\pi \Delta p}/{8\mu L})^{m} r^{m-n} - \beta $ assuming a constant pressure boundary condition.
+Note that the condition above depends on the value of $q^m/r^n$ which varies over the network edges.
+Taking the mean value of $q^m/r^n$ to find an average value for the transition condition, the transition line becomes $4m-n=0.75$ and $4m-n=0.1$ for the small and large thresholding value respectively.
+As a result the thresholding condition slightly shifts the intercept of the transition line while the slope remains the same.
+In Fig.~\ref{fig:figthresh1}, we plot the new transition lines, where the prediction for the phase boundaries matches well with the simulation results.}
+
+\begin{figure}[htp]
+    \centering
+ \includegraphics[width=0.45\textwidth]{./Fig_thres0.25.pdf}
+  \includegraphics[width=0.45\textwidth]{./Fig_thresh0.9.pdf}
+     \caption{\add{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
+\eqref{eq:thresh} with a small threshold value of $\beta = 0.25\langle q^m/r^n\rangle $ (left figure), and a large threshold value of $\beta = 0.9\langle q^m/r^n\rangle$ at $t=0$.
+The network is randomly initialized with $50\times 50$ randomly distributed pores.
+The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using local dynamics model, i.e., $4m-n=0.75$ (left figure), and $4m-n=0.1$ (right figure).} }\label{fig:figthresh1}%
+\end{figure}
+
+% \begin{figure}[htp]
+%     % \centering
+%  \includegraphics[width=0.72\textwidth]{Fig_thres0.25.pdf}
+%      \caption{\textcolor{blue}{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
+\eqref{eq:thresh} with a small thresholding value of $\beta = 0.25\langle q^m/r^n\rangle $ at $t=0$.
+The network is randomly initialized with $50\times 50$ randomly distributed pores.
+The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using simplified model, i.e., $m=(n+1)/4$.} }\label{fig:figthresh1}%
+% \end{figure}
+
+% \begin{figure}[htp]
+%     % \centering
+%  \includegraphics[width=0.72\textwidth]{Fig_thresh0.9.pdf}
+%      \caption{\textcolor{blue}{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
+\eqref{eq:thresh} with a large thresholding value of $\beta = 0.9\langle q^m/r^n\rangle $ at $t=0$.
+The network is randomly initialized with $50\times 50$ randomly distributed pores.
+The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using simplified model, i.e., $m=(n+1)/4$.}}\label{fig:figthresh2}%
+% \end{figure}
 
@@
 
-% \clearpage
-\bibliography{ref}% Produces the bibliography via BibTeX.
+% \section{Generalization of the toy model}
+% %
+% A general erosion in the edges of a network can be written as 
+% %
+% \begin{align}
+%     \frac{dr}{dt} = f(q,r), \label{eq:general}
+% \end{align}
+% %
+% where $q$, and $r$ are the fluid flux and the radius of an edge, and $f(\cdot)$ represents the function that determines the physics of erosion.
+Note that if $f(q,r)>0$ the edge is eroding, and if $f(q,r)<0$, the edge is clogging.
+In this section, we study the fate of our toy model, given such general erosion law.
+
+% \textbf{Parallel Tubes: }
+% %
+% We first consider parallel edges with an arbitrary erosion function, i.e., Eq.~\eqref{eq:general}.
+In the parallel case, both tubes experiencing the same pressure difference $\delta p$, and using Darcy's law the flux in each tube $q_i = \beta r_i^4 \delta p$, where $\beta = \pi/8\mu L$, $L$ being the length of the tube, $\mu$ the viscosity of the fluid, and $i=1,2$ correspond to the edges.
+We define $g(r_i) = f(q_i, r_i)$ and as a result the erosion dynamics can be written as $dr_i/dt = g(r_i)$.
+Without loss of generality we assume $r_1>r_2$.
+The fluid flux in the tubes can be obtained using $q_i/q = \tilde C_i $, where $q$ is the total flux, and $\tidle C_i = C_i/(C_1+C_2)$ is the relative conductivity, and $C_i = \pi r_i^4/8\mu L $ is the tubes conductance.
+In order to find the evolution of the fluid flux, we find the time derivative of relative conductivity,
+% %
+% \begin{align}
+%     \frac{d\tilde{C}_1}{dt} = \frac{4C_1^{\frac{3}{4}} C_2^{\frac{3}{4}}}{(C_1+C_2)^2}(r_2 g(r_1)-r_1 g(r_2)).
+% \end{align}
+% %
+% We find that $r_1=r_2$ is a fixed point, where flow is equally distributed between the edges resulting in homogenization.
+If $d \tilde C_1/dt <0$, then the edge with larger radius has a reduced growth the smaller radius edge has an increasing growth until $r_1=r_2$ is reached.
+This condition results in the homogenization where both edge's radius increases until the fixed point of $r_1=r_2$ is reached.
+The condition of $d \tilde C_1/dt<0$ is satisfied when
+% %
+% \begin{align}
+%     \frac{g(r_1)}{g(r_2)}<\frac{r_1}{r_2}, \forall r_1>r_2>0.
+% \end{align}
+% %
+% The above result can further be simplified as if $d\left(g(r)/r\right)/dr<0$ which ultimately results in homogenization of the parallel edges.
+Lastly, we can also study the perturbation of tube's radius around the fixed point as $r_1=r_0_\delta r$ and $r_2 = r_0$.
+Using Taylor series expansion, we can show that stability condition reduces to $g(r_0)>g'(r_0) r_0$.
+Therefore, if the erosion rate is sub-linear locally near the initial radius, the network moves towards homogenization in short time, while the long term behavior is less predictable.
+On the other hand, if the erosion rate is sup-linear, we expect the parallel tubes to move away from homogenization (i.e., channelization) in short times.
+Applying the power law erosion model with $f(q,r)=\alpha q^m/r^n$, it can be shown that $g(r) \propto  r^{4m-n} $, and therefore homogenization condition becomes $4m-n<1$ as seen in simulations.
+Although the result is derived under the constant pressure difference assumption, it holds validity for homogenization cases, where the pressure difference is going towards homogenization as well.
+However, for channelization cases, the pressure difference can be varied vastly inside the network, thus once the channelization happens, negative feedback effect of erosion rate might not be able to reverse that.
+
+% \textbf{Series Tubes: }
+% %
+% In the series toy model, we have $q_1=q_2 = q = \frac{C_1 C_2}{C_1+C_2}\delta p$ and similar results can be derived so that the condition for homogenization becomes
+% %
+% \begin{align}
+%     \frac{f(q,r_1)}{f(q,r_2)}<\frac{r_1}{r_2}, \forall r_1>r_2>0.
+% \end{align}
+% %
+% Note that if the dependence of $f$ on $q$ is non-homogeneous, then this condition might be valid for some $q$'s but not the others.
+Applying the power law erosion model with $f(q,r)=\alpha q^m/r^n$, it can be shown that homogenization condition is $n>0$ as it has been seen in simulations.
+
+\add{\section{General shear dependent erosion model}}
+\add{
+As an example of a nonlinear erosion model, we consider a shear-dependent erosion
+%
+\begin{align}
+    \frac{dr}{dt} = f(\tau),
+\end{align}
+%
+where $\tau=\tau(q,r) = 4\mu q/\pi r^3$ is the shear stress at the tube's wall assuming Poiseuille flow.
+It is to be noted that a shear-dependent erosion model is commonly used in studying erosion  \cite{jager2017channelization,bonelli2011micromechanical,parker2000purely} wherein such models erosion happens linearly proportional to the shear stress at the wall only after a certain threshold value $\tau_0$ (see main text for more information).
+Such linear models, however, ignore the maximum detachment rate of particles at the pore's boundary which would effectively limit the pore's radius maximum rate of change.
+To address this, we use a nonlinear erosion model
+%
+\begin{align}
+    f(\tau) = \alpha \left( \tanh{\left[ \beta(\tau - \tau_0)\right]}+1\right),
+    \label{eq:sigmoidErosion}
+\end{align}
+%
+where $\beta$ determines the shear rate scale and $\alpha$ determines the erosion rate scale.
+Note that the erosion rate scale $\alpha$ only affects the timescale at which the final state is reached and has no effect on the pattern formation.
+Without loss of generality we set $\alpha = 1$.
+Following the local dynamics model discussion in the main text, one can find that the homogenization condition reduces to
+%
+\begin{align}
+    f(\tau)>\tau \frac{df(\tau)}{d \tau}.
+    \label{eq:sigmoidCondition}
+\end{align}
+%
+Assuming a random network (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}a), the initial values of shear stress at the walls have a  decaying distribution over a large set of values (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}b).
+%Assuming nonlinear shear dependent erosion model (Eq.
+\eqref{eq:sigmoidErosion}) three regions of erosion can be identified: (i) The constant erosion region as $\tau\to\infty$.
+In this region the erosion happens at a constant rate $\lim_{\tau \to \infty} f(\tau) = 2$ and additionally the homogenization condition (Eq.~\eqref{eq:sigmoidCondition}) is satisfied (since $\lim_{\tau \to \infty} f(\tau) = 2$ and $\lim_{\tau \to \infty} f'(\tau) = 0$).
+It is to be noted that the homogenization effect for the constant erosion rate is similar to $m=0,n=0$ case for the erosion model discussed in the main text; (ii)  The slow-erosion region as $\tau\to 0$.
+In this region both $f(\tau)$ and $\tau f'(\tau)$ are close to 0 and since $f(\tau)$ is bounded in-between 0 and 2, erosion in the edges at this region happens at a very slower rate compared to other edges with nonzero shear-rate; (iii) The finite erosion-rate region near $\tau = \tau_0$, where $f(\tau)$ is an increasing function.
+In this region $\tau f'(\tau)$ has a maximum at $\beta \tau_0$ with a bandwidth of $1/\beta$.
+If $\beta \tau_0 < 1$, then the maximum $\tau f'(\tau)$ does not exceed 1, and the homogenization condition holds true for any $\tau$.
+As the value of $\tau_0$ increases, the homogenization region moves towards larger values of $\tau$ where edges with smaller values of $\tau$ would result in channelization.
+It can be seen that varying $\beta$ and $\tau_0$ changes the network behavior.
+To test our local dynamics model, we vary $\beta$ and $\tau_0$ and run three different tests: (i) $\beta=1,\tau_0=1$: For such values of $\beta,\tau$, almost all the tubes are in the homogenization region corresponding to Eq.~\eqref{eq:sigmoidCondition} (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}c) and the network moves toward homogenization (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}d).
+The final PDF of the network after erosion is further shown in (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}e).
+(ii) $\beta=1, \tau_0=12$: In this case, the homogenization condition is satisfied at some finite value of shear stress $\tau_0$ where $f(\tau_0) = \tau_0 f(\tau_0)$.
+As a result, some edges would homogenize, and some would channelize (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}f).
+Running the simulation over a random network, we find that a finite number of channels form (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}g).
+The PDF distribution of shear stress at the wall $\tau$ correspondingly becomes bimodal (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}h).
+(iii) $\beta=1, \tau_0=30$: In this case, almost all the edges in the network are in the channelization regime  (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}i), and performing the simulations we find that indeed one strong single channel is formed (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}j) and the PDF of shear stress $\tau$ shows a clear separation between flow in the channel versus flow in the rest of the system (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}k).
+}
+   \begin{figure}[htp]
+     % \centering
+      \includegraphics[width = 0.8\textwidth]{sigmoidDelaunay.pdf}
+     \caption{\textcolor{blue}{(a) A 2D random network with $N_x=50$ and $N_y=50$ points.
+(b) The probability distribution function (PDF) of the shear stress for the edges of the network.
+(c)/(f)/(i) The PDF of the shear stress along with nonlinear erosion law $f(\tau)$ (solid red line) and $\tau f'(\tau)$ (dashed red line).
+The areas where the homogenization condition (i.e., $f(\tau)>\tau f'(\tau)$) is satisfied are shaded with green color, otherwise, the channelization condition is satisfied and the region is shaded with red color.
+(d)/(g)/(j) Snapshots of the 2D network after erosion using the nonlinear erosion law shown in the previous row until the average radius of the network is increased to twice its original size.
+(e)/(h)/(k) The PDF of the shear stress at the walls for the final snapshot of the network shown in the previous row.
+    }}
+     \label{SIfig:fig9-sigmoidDelaunay}
+ \end{figure}
+
+%  \begin{figure}[htp]
+%      % \centering
+%       \includegraphics[width = 1.0\textwidth]{sigmoidDelaunay_rev1.pdf}
+%      \caption{\add{Nonlionear erosion in a 2D random network of tubes with $N_x=50$ and $N_y=50$, where edge radii are sampled from a uniform distribution with $\mathcal{U}[1,14]$.
+Snapshots of the network after for different erosion rate $\beta$ and threshold values $\tau_0$ are shown after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle = 7.5$.
+The erosion law is based on Eq.
+\eqref{eq:sigmoidErosion}.
+As shown above, increasing $\tau_0$ results in a stronger channelization, while changing $\beta$ has a much smaller effect.
+Note that increasing $\tau_0$, increases the number of tubes in the channelization region, while increasing $\beta$ slightly shifts the region and has a much smaller effect.} }
+%      \label{SIfig:fig10-sigmoidDelaunay}
+%  \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{align}
+%     \frac{dr_i}{dt} = f(|q_i|,r_i),
+% \end{align}
+% %
+% where $i = 1$ and $2$ correspond to pipe 1 and pipe 2 respectively and $f(q,r)$ can be negative thus it allows clogging.
+In the toy model case $q_i = C p r_i^4$ where $p$ is the pressure difference between two terminals of the pipes.
+Therefore the erosion rate only depends on $r_i$
+% \begin{align}
+%     f(|q_i|,r_i) = g(r_i).
+% \end{align}
+% The time derivative of relative conductivity $\tilde{C}_1 = C_1/(C_1+C_2)$ can be written as
+% \begin{align}
+%     \frac{d\tilde{C}_1}{dt} = \frac{4C_1^{\frac{3}{4}} C_2^{\frac{3}{4}}}{(C_1+C_2)^2}(r_2 g(r_1)-r_1 g(r_2)).
+% \end{align}
+% It is obvious that in the toy model, $r_1=r_2$ is a fixed point, while its stability depends on the form of $f(q,r)$, or equivalently $g(r)$ in the parallel case.
+It can be shown that the condition for homogenization is
+% \begin{align}
+%     \frac{g(r_1)}{g(r_2)}<\frac{r_1}{r_2}, \forall r_1>r_2>0.
+% \end{align}
+% This is a strong constraint to $g(r)$, and in reality it might not hold true for arbitrary $r$'s when negative feedback over erosion rate is introduced.
+One generalization we can make is to expand the function near the value we are interested in.
+Let $r_0 = r_2$ be the initial value, and $r_1 = r_0 + \delta r$ to be the perturbation in one pipe.
+With Taylor series expansion the above condition can be written as
+% \begin{align}
+%     g(r_0)>g'(r_0) r_0.
+% \end{align}
+% Therefore, if the erosion rate is sub-linear locally near the initial radius, we can say it will drive the network towards homogenization in short time, while the long term behavior is less predictable.
+On the other hand, if the erosion rate is sup-linear, we expect to see channelization to some extent.
+
+% Applying the power law erosion model with $f(q,r)=C q^m/r^n$, it can be shown that $g(r) = C p r^(4m-n) $ and therefore homogenization condition is $4m-n<1$ as seen in simulations.
+
+% Although the result is derived under the constant pressure difference assumption, it holds validity for homogenization cases, where the pressure difference is going towards homogenization as well.
+However, for channelization cases, the pressure difference can be varied vastly inside the network, thus once the channelization happens, negative feedback effect of erosion rate might not be able to reverse that.
+
+% In the series toy model, we have $q_1=q_2 = q = p \frac{C_1 C_2}{C_1+C_2}$ and similar results can be derived so that the condition for homogenization is
+% \begin{align}
+%     \frac{f(q,r_1)}{f(q,r_2)}<\frac{r_1}{r_2}, \forall r_1>r_2>0.
+% \end{align}
+% Note that if the dependence of $f$ on $q$ is non-homogeneous, then this condition might be valid for some $q$'s but not the others.
+
+% Applying the power law erosion model with $f(q,r)=C q^m/r^n$, it can be shown that homogenization condition is $n>0$ as seen in simulations.
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \bibliography{ref}% Produces the bibliography via BibTeX.
+%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{8}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{https://doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{git(2021)}]{githubrepo}%
+  \BibitemOpen
+  \href@noop {} {\bibinfo {title} {Network instability}},\ \bibinfo
+  {howpublished} {\url{https://github.com/ahmadzareei/networkInstability}}
+  (\bibinfo {year} {2021})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Liu}\ \emph {et~al.}(1995)\citenamefont {Liu},
+  \citenamefont {Nagel}, \citenamefont {Schecter}, \citenamefont {Coppersmith},
+  \citenamefont {Majumdar}, \citenamefont {Narayan},\ and\ \citenamefont
+  {Witten}}]{liu1995force}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.-h.}\ \bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont {Nagel}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Schecter}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Coppersmith}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Majumdar}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Narayan}},\ and\ \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Witten}},\ }\bibfield  {title} {\bibinfo
+  {title} {Force fluctuations in bead packs},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
+  {269}},\ \bibinfo {pages} {513} (\bibinfo {year} {1995})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Coppersmith}\ \emph {et~al.}(1996)\citenamefont
+  {Coppersmith}, \citenamefont {Liu}, \citenamefont {Majumdar}, \citenamefont
+  {Narayan},\ and\ \citenamefont {Witten}}]{coppersmith1996model}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Coppersmith}}, \bibinfo {author} {\bibfnamefont {C.-h.}\ \bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Majumdar}},
+  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Narayan}},\ and\ \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {Witten}},\ }\bibfield  {title}
+  {\bibinfo {title} {Model for force fluctuations in bead packs},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review E}\ }\textbf
+  {\bibinfo {volume} {53}},\ \bibinfo {pages} {4673} (\bibinfo {year}
+  {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2017)\citenamefont {Alim},
+  \citenamefont {Parsa}, \citenamefont {Weitz},\ and\ \citenamefont
+  {Brenner}}]{alim2017local}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Alim}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Parsa}},
+  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\
+  }\bibfield  {title} {\bibinfo {title} {Local pore size correlations determine
+  flow distributions in porous media},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
+  {119}},\ \bibinfo {pages} {144501} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Parsa}\ \emph {et~al.}(2021)\citenamefont {Parsa},
+  \citenamefont {Zareei}, \citenamefont {Santanach-Carreras}, \citenamefont
+  {Morris}, \citenamefont {Amir}, \citenamefont {Xiao},\ and\ \citenamefont
+  {Weitz}}]{shima2021}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Parsa}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zareei}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Santanach-Carreras}},
+  \bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont {Morris}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Amir}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Xiao}},\ and\ \bibinfo {author}
+  {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ }\bibfield  {title} {\bibinfo
+  {title} {Unexpected scaling of interstitial velocities with permeability due
+  to polymer retention in porous media},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review Fluids}\ }\textbf {\bibinfo {volume}
+  {6}},\ \bibinfo {pages} {L082302} (\bibinfo {year} {2021})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {J{\"a}ger}\ \emph {et~al.}(2017)\citenamefont
+  {J{\"a}ger}, \citenamefont {Mendoza},\ and\ \citenamefont
+  {Herrmann}}]{jager2017channelization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {J{\"a}ger}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Mendoza}},\
+  and\ \bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont {Herrmann}},\
+  }\bibfield  {title} {\bibinfo {title} {Channelization in porous media driven
+  by erosion and deposition},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Physical Review E}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo
+  {pages} {013110} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bonelli}\ and\ \citenamefont
+  {Marot}(2011)}]{bonelli2011micromechanical}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Bonelli}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Marot}},\ }\bibfield  {title} {\bibinfo {title} {Micromechanical modeling of
+  internal erosion},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {European Journal of Environmental and Civil Engineering}\ }\textbf {\bibinfo
+  {volume} {15}},\ \bibinfo {pages} {1207} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parker}\ and\ \citenamefont
+  {Izumi}(2000)}]{parker2000purely}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Parker}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Izumi}},\
+  }\bibfield  {title} {\bibinfo {title} {Purely erosional cyclic and solitary
+  steps created by flow over a cohesive bed},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Fluid Mechanics}\ }\textbf
+  {\bibinfo {volume} {419}},\ \bibinfo {pages} {203} (\bibinfo {year}
+  {2000})}\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2022-03-06 review_response/Response2.tex
Updates from Overleaf

%%//////////////////////////////////////////////////////////////
%%
%% P R E A M B L E
%%
%%//////////////////////////////////////////////////////////////
\documentclass{article}

%%==============================================================
%% Packages=
%%==============================================================
\usepackage[english]{babel}
\usepackage{booktabs}
\usepackage{scicite}
%\usepackage{citesort}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphics,amsfonts,amssymb,amsmath,latexsym}
\usepackage{graphicx,subfig}
\usepackage[ansinew]{inputenc}
%\usepackage{natbib}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{subfig}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{lscape}
\usepackage{authblk}
\usepackage{xr}
\usepackage{enumerate}
\usepackage{bm}
\usepackage{epstopdf}
\usepackage{float}
\setlength\parindent{0pt}
\usepackage{xr}
\usepackage{csquotes}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}

\usepackage[usenames, dvipsnames]{color}
\usepackage[dvipsnames]{xcolor}

% Color Edits
\newcommand{\add}[1]{\noindent \color{blue} #1 \normalcolor}
% \newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}
% \newcommand{\AM}[1]{\noindent \color{magenta} (AM: #1)\normalcolor}
% \newcommand{\AZ}[1]{\noindent \color{purple} (AZ: #1)\normalcolor}
% \newcommand{\PD}[1]{\noindent \color{cyan} (PD: #1)\normalcolor}

%\usepackage{scicite}
\usepackage{natbib}
\bibliographystyle{unsrt}

%%==============================================================
%% New Commands
%%==============================================================
\newcommand{\Hline}{\rule{\linewidth}{.1mm}}
%\newcommand{\RedColor}[1]{\noindent \color{red}  #1 \normalcolor}
\newcommand{\Question}[1]{\noindent \color{black}\emph{#1}\normalcolor}
\newcommand{\Answer}[1]{\noindent {\color{blue}{ #1}}\normalcolor}

\newcommand{\AnswerQ}[1]{\noindent {\footnotesize {\color{blue}{ #1}}}\normalcolor}

\renewcommand{\thepage}{R\arabic{page}}
\renewcommand{\thesection}{R\arabic{section}}
\renewcommand{\theequation}{R\arabic{equation}}
\renewcommand{\thefigure}{R\arabic{figure}}
\renewcommand{\thetable}{R\arabic{table}}
\renewcommand{\thetable}{R\arabic{table}}

\def\th{\theta}

\newcommand{\bfphi}{\boldsymbol{\phi}}%

\newcommand{\Hb}{\mathbf{\bar{H}}}

\newcommand{\revised}[1]{\noindent\color{Blue}#1\normalcolor}

\newcommand{\PD}[1]{\noindent \color{red} (PD: #1)\normalcolor}
\newcommand{\EM}[1]{\noindent \color{magenta} (EM: #1)\normalcolor}
\newcommand{\AZ}[1]{\noindent \color{purple}(AZ: #1)\normalcolor}

\def\p{\textit{p.~}}
\def\l{\textit{l.~}}
%%==============================================================
%% Setttings
%%==============================================================
\topmargin -0.5in

\setlength{\textwidth}{6in} \setlength{\textheight}{8.25in}
\setlength{\oddsidemargin}{0mm}
\setlength{\textwidth}{6.in}
\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0.25in}
\setlength{\oddsidemargin}{0.25in}
\setlength{\oddsidemargin}{0mm}

%%//////////////////////////////////////////////////////////////
%%
%% T I T L E    &    A U T H O R S
%%
%%//////////////////////////////////////////////////////////////
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{
Response to the Reviewers' comments for manuscript \\
(Tracking \#: LF18481): \\
``Temporal evolution of flow in pore-networks: From homogenization to instability"
}

\author{Ahmad Zareei, Deng Pan, and  Ariel Amir
}
\date{}

%%//////////////////////////////////////////////////////////////
%%
%% FIRST SENTENSE
%%
%%//////////////////////////////////////////////////////////////
\begin{document}
\maketitle

\noindent In the following, we address each of the Referees' comments/suggestions (\emph{in italic}). All page/paragraph/line (\textit{p.},\ \textit{par.},\ \textit{l.},\ etc.) numbers refer to the revised paper. %In addition, while using the original numbering of figures/equations/references in the manuscript (\emph{e.g.}, Fig.~1, Fig.~2,...., Eq.~(1), Eq.~(2),..., [1], [2], ...),  we add prefix ``\emph{R}'' for figures/equations/references presented in this response to the Referees' comments (\emph{e.g.}, Fig.~R1, Fig.~R2, .... Eq.~(R1), Eq.~(R2), ..., Ref.~[R1], Ref.~[R2],...).
% \centerline{(Tracking \#: LB15473 Deng)}

\vspace{5 mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ref 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
\Hline \\
\textbf{Response to Reviewer B} \\
\Hline
\\

% \centerline{Negative numbers are counted from the bottom of the page.}
%({\color{orange}\mbox{------}})

\Question{
The only answer that I do not find completely satisfying is to this
point: ``…since the authors have access to experimental setups, it
would greatly improve this work if they could provide experimental
proof of the phase transition in a real system." To what the authors
answered: `` With regards to the experimental tests, all the authors of
the current manuscript are theorists, and experimental studies of this
work is out of our scope." 2/3 of the authors of this manuscript are coauthors of Reference [31],
which presents experiments related to the results of the current
manuscript. Actually, one of the co-first authors of this manuscript
is also co-first author in [31]. I do not think that all publications
in PRL should include experimental results, but in this particular
case it is striking that the authors do not try to validate their
theory having (apparently) all the experimental tools at hand.
\newline
To summarize, the main and unanimous criticism from the first round of
review was if the paper was physically grounded. On the one hand, I
think the authors have greatly improved the manuscript including more
realistic models of physical erosion. However, on the other hand, I
think the authors have missed the opportunity of including at least
some preliminary experimental results that support their theory or at
least to discuss in their answer why this was not possible.
\newline
Finally, whereas I do not strongly support publication in PRL, I do
not oppose to it either, I leave the final decision to the editors.
\newline}

\Answer{We thank the referee for appreciating the more realistic physical
models utilized in the revised version and the extended theoretical
framework we used.
With regards to the question about the potential experimental tests of
the theory:
We completely agree with the referee that performing experiments to
test our theory is important. Unfortunately performing them is
currently unfeasible for us, since the Amir group is a theory group
and has no lab space.
We would like to make some clarifications with regards to Ref. [31].
In this work Dr. Shima Parsa, then a postdoc in the Weitz lab, had
empirical observations relating the mean velocity and permeability as
flow in a porous material is clogged with a polymer. Dr. Ahmad Zareii,
working under the guidance of Prof. Ariel Amir, set out to explain the
observed scaling using a combination of numerical simulations and
analytical work, which led to a joint publication (Ref. [31] mentioned
by the referee). Note that the experiments were performed by Dr. Parsa
over the course of several years while she was at Harvard. Dr. Parsa
has recently started as faculty at the Rochester Institute of
Technology, and therefore the experimental system associated with Ref.
[31] is no longer active at Harvard. We also resonated with the
comments of Referee D: "Experiments are notoriously hard to perform
and can not be produced easily, especially when the parameter space
that needs to be explored is as wide as in this study (without
considering the 3D and polar simulations in the supplementary). I
believe that the results are convincing, and requiring an experiment
is somewhat unrealistic for the scope of this study. In many ways,
this study can trigger the community to search for this ordering
parameter in existing experimental setups, which will advance the
field further by exploring the role of flow rate to shear rate or mean
pore size." Indeed, we hope that as Referee D mentioned our
theoretical study will trigger further experimental work in the
future.}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% Review # 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{10 mm}
\noindent
\Hline \\
\textbf{Response to Reviewer C} \\
\Hline
\\

\Question{The work is greatly improved after revision, and many of the issues
raised by the reviewers have been effectively addressed. In particular
the consideration of nonlinear erosion models and the derivation of a
more general local stability criterion address many of the concerns
about generality and applicability, expressed by all referees.
\newline
For me, the modified work now achieves the level of significance that
it can be published PRL and my suggestions for further changes are
relatively minor. However, there would be significant advantages in
publishing in PRE or PRFluids where the excellent Supplementary
Material could be included in the body of the article.\newline}

\Answer{We thank the reviewer for their thoughtful and thorough comments.}

\vspace{0.5cm}
\textbf{Comment C1}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{Having said that, the work does have a significant weakness in that
the primary model studied is a power law and therefore scale-free. The
scale-free nature is the primary reason why the local dynamics set the
behavior of the entire network. The majority of interesting real-world
cases will have a scale associated with them (e.g. a non-trivial
dependence on flow-rate). In the more general case we will find that
Eq. (3) and the condition described just after it will hold for some
flow rates but not all. This dependence on flow rate (or applied
pressure drop) is not well explained in the manuscript. Also, the new
investigation of a tanh profile shows that intermediate states are
possible - i.e. states that lie somewhere between homogenization and
instability. It would be good for the manuscript to acknowledge some
of these limitations of their result - which remains interesting.\newline}

\Answer{We thank the reviewer for the valuable comment. Indeed our model has limitations. We have now expanded our conclusion to include such limitations as mentioned by the reviewer.

admit scale free after Eq. 3

If not parallel, g(r) can be more complex

acknowledge inbetween cases in the main text ...
}

\vspace{0.5cm}
\textbf{Comment C2}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{In the abstract `First' in line 2 is a bit confusing as it isn't
followed up with a `second' or similar.\newline}

\Answer{We would like to thank the reviewer for carefully reading our manuscript. We removed `First' in the abstract to avoid any confusion.}
%
\\

%

\vspace{0.5cm}
\textbf{Comment C3}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{On page 2 column 1, in the shear model, it's unclear to me why
moving from $\dot{m}$ to $\dot{r}$ would introduce an $r$ factor ($-\kappa$
becomes $-\kappa r$). Also it would be nice to add a reference for the
shear stress being proportional to $q/r^3$ - this is a standard result
but it would improve readability for the PRL audience.
\newline}

\Answer{We would like to point out that for $n=3$ the network does not stay the same, since series connections are always moving toward homogenization, while parallel connections are staying in a constant proportion. This results in seeing differences between the statistics of the network at $t=0$ and the evolved network at later stages for $n=3$ (see Fig. 2 in the main text). Additionally, we expect the transition to happen at  approximate $n\approx3$ (see comment 2G for more details). We have now included this point in the main manuscript to avoid confusion.}
%
\\

\Answer{From \p4 of the main text:}
\AnswerQ{
\begin{quote}
    ``It is to be noted that while the flow ratio remains constant for parallel edges, the connection in series are evolving toward homogenization and that is why we find a difference between evolved network for $n=3$ and the network at $t=0$.''
\end{quote}
}

\vspace{0.5cm}
\textbf{Comment C3}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{Last line of page 3 - the parameter $L$ looks to be used without
definition.}
\\

\Answer{We thank the reviewer for their careful comment. We have now included the definition in the main text.}%

\AnswerQ{
\begin{quote}
    ``To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes \add{of the same length $L$} in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Figs. \ref{fig:fig3}b-c)''   
\end{quote}
}

\vspace{0.5cm}
\textbf{Comment C4}
\noindent \vspace{-0.2cm}\\ \Hline\\

\Question{It would be great to briefly explain the physical origin of the
$r_1/r_2$ factor in equation 3 as this is such a significant part of the
result. My interpretation is that it is because stability depends on
the fractional change in conductance associated with a change in
radius, and that the fractional change will be inversely proportional
to the radius.\newline}

\Answer{We thank the reviewer for their valuable recommendations. The physical origin the scale-free criteria $r_1/r_2$ turns out to be the result of power law dependence of conductance with respect to radius, meaning that our homogenization condition can be generalized to nonlaminar flow as well. The relevant part is attached. }
\AnswerQ{
\begin{quote}
    ``In fact, this condition will hold for nonlaminar flow as long as $C\propto r^k (k > 0)$. The power law dependence of conductance with respect to radius leads to the scale-free criteria $r_1/r_2$. ''   
\end{quote}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% Review # 3 %%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage 
\vspace{10 mm}
\noindent
\Hline \\
\textbf{Response to Reviewer D} \\
\Hline
\\

\Question{This paper presents 2D and 3D pore-network models of single-phase flow through porous media, involving channel erosion. The erosion rate in a channel is modeled as a function of the flow rate through the channel and the radius of the channel.The manuscript presents an interesting transition in the behaviour of these models from a stabilizing behavior where narrow channels erode more quickly than wider ones (``homogenization'') to an unstable regime where all the flow ends up in a few pathways ``instability''). Overall I judge this to be an interesting paper that may be worth publishing in a journal such as PRFluids, but falls short of the level of impact required for PRL. I explain this below.  The manuscript has many strengths which include: - it's very clearly written and with excellent figures that clearly demonstrate the phenomena being explored; - good numerical modeling that includes 2D and 3D simulations in random and regular network topologies; - results which are universal within the class of models being considered here, being valid 2D and 3D and in regular and random networks; - a clear theory to explain the results using a local analysis,suggesting links between global and local dynamics even in quite complex systems; - links to flow in biological systems
\newline}

\Answer{We thank the reviewer for their careful reading of the manuscript and their constructive
remarks.}

\vspace{0.5cm}
\textbf{Comment 3A}
\noindent \vspace{-0.2cm}\\ \Hline\\
\Question{The weaknesses in the work include: the physical relevance of the model is not clear, except for the specific biological case ... more specifics in studies of models that are closest to this one are needed, particularly also mentioning the outcomes of those studies. Some of the model's (apparent) weaknesses are being a pure power law, its scaling with pressure is unphysical: the erosion rate in all channels merely increases uniformly with applied pressure, meaning that erosion occurs even at near-zero speed/stress; there is no onset threshold.\newline}

\Answer{We appreciate the reviewers comment. The concern here is similar to comment 2F of Reviewer 2, and we repeat our reply here. Erosion in saturated granular materials occurs when the shear stress at the wall exceeds the cohesive strength of the solid matter. In the revised version, we study more realistic models including: (i) a model where the onset of erosion happens after reaching a threshold value; (ii) a model with a different (nonlinear) functional dependence on shear stress, where erosion starts after a certain threshold and eventually saturates to a maximum value which is determined by the maximal detachment rate of particles at the tube's boundary. We make predictions for both models using our analysis and find that the analytical results agree well with the numerical simulations. These results illustrate the generality of our model in relating to various physical models. (iii) Additionally, we expand our discussion before introducing the model to make a better connection with relevant studies of erosion. 
We believe that these new results illustrate that the phase transition is a general effect, and that our analysis using the local dynamics model has the predictive power of identifying the phase transition condition. In the following we attach the relevant excerpts of the main text and the supplementary material.}

\clearpage
% \bigbreak

% \bibliographystyle{unsrt}
% \bibliography{ref}

\end{document}

### 2022-03-06 supp.tex
Updates from Overleaf

@@
 %
-%   See the REVTeX 4 README file for restrictions and more information.
+%   See the REVTeX 4 README file for restrictions and more infor mation.
 %
@@
 
-\title{Temporal Evolution in the Networks of Porous Materials:\\ From Homogenization to Instability}% Force line breaks with \\
+\title{Temporal Evolution of Erosion in Pore-Networks:\\ From Homogenization to Instability}% Force line breaks with \\
 % \thanks{A footnote to the article title}%
@@
 %
-In our simulations, we tested two types of network: a (i) diamond-grid network, and a (ii) topologically random network.
-In the diamond-grid network, we choose $N_x=200$ edges in the horizontal direction and $N_y=100$ edges in the vertical direction.
-The random network is created using uniformly distributed points with on average $N_x\times N_y$ edges in the horizontal and vertical directions.
-Note that the randomly distributed points are connected using a Delaunay triangulation.
-The diameter of each edge is sampled from either a uniform distribution in $r\in[1,14]$, log-normal distribution with $\mu=3,\sigma=0.48$, or truncated normal distribution with $\mathcal{N}(\mu=7.0,\sigma=3.6)$.
-The external flow pressure is applied horizontally from left to right.
-An external pressure is then considered between the left-most nodes and the rightmost nodes ($p_\text{left}=10,p_\text{right}=0$).
-Assuming a Poiseuille flow in each edge, the fluid flow $q$ and pressure difference $\delta P_e$ in each edge is related through $q_e = C_e \delta P_e$, where $C_e = \pi r^4_e/8\mu L_e$,  $L_e$ is the length of the tube, and $\mu$ is the viscosity of the fluid.
-Let $\Delta$ be the transpose of the network's oriented incidence matrix.
-Note that the orientation of each edge is arbitrary since it only determines the positive direction of flow in that edge.
-Define $\ket{q_e}$ as the vector of flow through all the edges, then we have $\ket{q_e} = C_e\Delta \ket{P_n}$ where $\ket{P_n}$ is the vector of pressure at all the nodes.
-With a given boundary condition, we solve the equation through a modified nodal analysis as follows.
-The conservation of mass at each node can be written as
+In our simulations, we tested two types of networks: (i) a topologically ordered (diamond-grid) network, (ii) a topologically random network (2d and 3d). 
+% In the diamond-grid network, we choose 100 nodes in the horizontal direction $N_x=100$ and 50 nodes in the vertical direction $N_y=50$ which in total results in $20,000$ edges in the network (see \cite{githubrepo}).
+The 2d random network is created using uniformly distributed points with on average $N_x\times N_y$ nodes in the horizontal and vertical directions where the randomly distributed points are connected using a Delaunay triangulation.
+The 3d random network similarly is obtained by a uniform distribution of $N_x\times N_y \times N_z$ points in space, where the the points are connected using Voronoi cell initialization.
+The diameter of each edge is sampled from either a uniform distribution with $\mathcal{U}(1,14)$, log-normal distribution with $\mu=3,\sigma=0.48$, or truncated normal distribution with $\mathcal{N}(\mu=7.0,\sigma=3.6)$, where all of the distributions have a coefficient of variation close to $0.5$.
+An external pressure is considered between the left-most nodes and the rightmost nodes ($p_\text{left}=10,p_\text{right}=0$).
+For each edge, assuming a Poiseuille flow, the fluid flux  $q$ and pressure difference $\delta P_e$ are related through $q_e = C_e \delta P_e$, where $C_e = \pi r^4_e/8\mu L_e$,  $L_e$ is the length of the tube, and $\mu$ is the viscosity of the fluid.
+We define $\vec{q}_e$ as the vector of fluid flux through all the edges, and as a result $\vec{q}_e = \mathbf{C} \mathbf{D}\vec{P}_n$ where $\vec{P}_n$ is the vector of pressure at all the nodes, $\mathbf{D}$ is the transpose of the network's oriented incidence matrix, and $\mathbf{C}$ is the diagonal matrix of edge conductances $\mathbf{C}_e = \text{diag} \left( C^{(1)}_e, C^{(2)}_e, \cdots,C^{(N_e)}_e\right)$.
+The orientation (or direction) of an edge is arbitrary selected, and it only determines the positive direction for the fluid flow in that edge.
+Next, we  use conservation of mass at the nodes to solve for the network pressure/flux at the nodes/edges.
+The conservation of mass at each node is
 %
-
 \begin{align}
-    \ket{q_n} = \Delta^\top \mathbf{C} \Delta \ket{P_n}, \label{eq:governeing}
+    \vec{q}_n = \mathbf{D}^\top \mathbf{C} \mathbf{D} \vec{P}_n, \label{eq:governeing}
 \end{align}
 %
-where $\mathbf{C} = \text{diag}\left( C^{(1)}_e, C^{(2)}_e, \cdots,C^{(N_e)}_e\right)$ is a diagonal matrix of edge conductances, and $\ket{q_n}$ is the vector of total incoming flow to each node.
-Note that total incoming flow to an internal node is zero inside the network due to the conservation of mass, and is only non-zero at the boundary nodes.
-Renumbering the boundary nodes to $1,2,\cdots, N_{B}$, we can partition Eq.
+where $\vec{q}_n$ is the vector of total incoming flow to each node.
+The total incoming flow to an internal node is zero inside the network due to the conservation of mass, and can only be non-zero at the boundary nodes.
+Without loss of generality, we renumber the boundary nodes to $1,2,\cdots, N_{B}$, where $N_B$ shows the total number of nodes at the boundary.
+We re-partition Eq.
 \eqref{eq:governeing} to obtain
@@
 \begin{align}
- \begin{bmatrix} {\Delta_{b}}^\top \mathbf{C} {\Delta_{b}}  & \vline &    {\Delta_{b}}^\top \mathbf{C} {\Delta_{n}} \\ \hline  
-    {\Delta_{n}}^\top \mathbf{C} {\Delta_{b}} & \vline & {\Delta_{n}}^\top \mathbf{C} {\Delta_{n}}
+ \begin{bmatrix} {\mathbf{D}_{b}}^\top \mathbf{C} {\mathbf{D}_{b}}  & \vline &    {\mathbf{D}_{b}}^\top \mathbf{C} {\mathbf{D}_{n}}\\ \hline   
+    {\mathbf{D}_{n}}^\top \mathbf{C} {\mathbf{D}_{b}} & \vline & {\mathbf{D}_{n}}^\top \mathbf{C} {\mathbf{D}_{n}}
     \end{bmatrix} \begin{bmatrix} P^{BC}_1 \\ P^{BC}_2 \\ \vdots \\ P_{N_B} \\  \hline  P_{N_B+1} \\ \vdots \\ P_{N_n}
@@
 %
-where $\mathbf{A}_{st} = \Delta^\top_s \mathbf{C}\Delta^\top_t$ and  $s,t\in\left\{a,b\right\}$. In summary the above equations simplifies to 
+where $\mathbf{A}_{st} = \mathbf{D}^\top_s \mathbf{C}\mathbf{D}^\top_t$ and  $s,t\in\left\{a,b\right\}$.
+The first $N_B$ elements of the pressure vector (i.e., $P_1, \cdots, P_{N_B}$) represent the pressure at the boundary nodes and the rest represent the pressure for the internal nodes.
+In summary the above equations can be written as a combination of two set of linear equations
+%
+\begin{subequations}\label{main-solve-eq}
+\begin{align}
+%     \begin{cases} 
+  & \mathbf{A}_{bb} \vec{P}_{BC} + \mathbf{A}_{bn}  \vec{P} = \vec{q}_{BC}, \label{maina} \\
+& \mathbf{A}_{nb}\vec{P}_{BC} +  \mathbf{A}_{nn} \vec{P} = 0. \label{mainb}
+%     \end{cases} 
+    % \\ \mathbf{A}_{nn} \ket{P_n} =- \mathbf{A}_{nb}\ket{P_{BC}} 
+    % \label{eq:main-network}
+ \end{align}
+\end{subequations}
+%
+where $\vec{P}_{BC} = [P^{BC}_1, \cdots, P^{BC}_{N_B}]^\top$ is the boundary nodes pressure vector, $\vec{q}_{BC} = [q^{BC}_1, \cdots, q^{BC}_{N_B}]^\top$ is the boundary nodes incoming fluid flux vector, and $\vec{P} = [P_{N_B+1}, \cdots, P_{N_n}]^\top$ is the unknown pressure vector for the rest of the nodes.
+If the pressure at the boundary is given,  we can use Eq.
+\eqref{mainb} to solve for the internal pressure values $\vec{P}$, and then use Eq.
+\eqref{maina} to find the required flux at the boundary nodes $\vec{q}_{BC}$.
+However, if fluid flux vector at the boundary nodes is given (i.e., $\vec{q}_{BC}$ is known), we need to simultaneously solve  Eqs.
+\eqref{maina} and \eqref{mainb} to find the boundary pressure vector  $\vec{P}_{BC}$ and internal nodes pressure vector $\vec{P}$.
+In either case, solving Eq.
+\eqref{main-solve-eq}  results in the nodes' pressure vector and also the fluid flux vector at the boundary nodes.
+The fluid flux at each edge can then be calculated using  $\vec{q}_e=\mathbf{C}_e \mathbf{D} \vec{P}_n$.
+Next, given the flux at each edge  $q_e$, we increase (decrease) the edge radius under erosion (clogging) using
 %
 \begin{align}
-    \begin{cases} 
-        \mathbf{A}_{bb} \ket{P_{BC}} + \mathbf{A}_{bn}  \ket{P} = \ket{q_{BC}}, \\
-    \mathbf{A}_{nb}\ket{P_{BC}} +  \mathbf{A}_{nn} \ket{P} = 0. 
-    \end{cases} 
-    % \\ \mathbf{A}_{nn} \ket{P_n} =- \mathbf{A}_{nb}\ket{P_{BC}} 
-    \label{eq:main-network}
+    \frac{dr_e}{dt} \propto \pm  \frac{q^m_e}{r_e^n},
 \end{align}
 %
-Solving the above equations results in the nodes' pressure and also the fluid flux at the boundary nodes.
-With the flux at each edge, $q_e$, the increase (decrease) of tube radius under erosion (clogging) is obtained as
+and re-iterate the process to solve for the new fluid flux vector.
+We use a simple forward Euler for time integration.
+For each iteration, we choose the time step $dt$ so that $\max(dr_e) = 0.1 r_0$, where $r_0$ is the smallest radius among all edges.
+% Note that $r_{ij} (t+\delta t)  = r_{ij} (t)  + (\alpha \delta t)  q_{ij} (t)/ r^n_{ij} (t) $, where the coefficient $\alpha \delta t$ is chosen such that the maximum change in the radius at each time step is smaller than one-tenth  of the smallest tube's radius i.e.
+$\max (\Delta r_{ij}) \leq r_\text{min}/10$ of the smallest radius at the initial configuration.
+This condition guarantees that at each step a small amount of material is eroded and there is no sudden change in the network.
+We further test the convergence by decreasing $\max(\Delta r_{ij})$ to half and we observe that the average relative change in the flux vector is $\approx 1.2\%$, and the PDFs remain intact without any notable change.
+The network size for the 2d/3d networks is $N_x=100,N_y=50$/$N_x=50,N_y=12, N_z=12$ unless mentioned otherwise.
+In either case, the network has an order of $10^3$ edges.
+\add{Note that the physical assumption of low Reynolds regime Re$\ll$1 at all times ensures that the Poisoulle flow assumption remains valid.
+Additional dimensionless transport numbers such as the P\'eclet number (ratio of advection to diffusion) or the Damkohler number (ratio of chemical reaction rate to the transport phenomena rate) are assumed to be respectively very large and very small, resulting in advection to be much stronger than diffusion and chemical reaction.
+It is to be noted that considering diffusion or chemical reactions might change the dynamics of erosion as it requires tracking a secondary concentration field that might affect the local erosion law.} The code is publicly available in a GitHub repository \cite{githubrepo}.
+
 %
-\begin{align}
-    \frac{dr_e}{dt} \propto \pm  \frac{q_e}{r_e^n}.
-\end{align}
-%
-We use simple forward Euler for time integration. For each iteration, we choose the time step $dt$ so that $\max(dr_e) = 0.1 r_0$, where $r_0$ is the smallest radius among all edges.
-
-\newpage
-\section{Additional Numerical Result}
-%
-\begin{figure}[h]
-    % \centering
-    \includegraphics[width = 0.75\textwidth]{Figs/Fig2_random-low.png}
-    \caption{Ahmad's version: Erosion in a topologically random network of pipes.
+% \begin{figure}[h]
+%     % \centering
+%     \includegraphics[width = 0.75\textwidth]{Figs/Fig2_random-low.png}
+%     \caption{Ahmad's version: Erosion in a topologically random network of pipes.
 The first row shows the initial condition at $t=0$.
@@
 The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}
-\end{figure}
+% \end{figure}
 %
-
 \newpage
-\section{Analytical results}
+\section{Analytical results for fluid flux EXP-tail PDF in a Diamond Network}
 %
@@
 %
-As described in the main text, the PDF of flow in a topologically disordered network of tubes is the same as a structured diamond grid when the radius of the tubes is highly disordered.
-In this section, we show that the observed exponential distribution of fluid flux can be described using a mean-field approach on a structured grid.
+As described in the main text, the PDF of flow in a topologically disordered network of tubes takes the same form  as in a  structured diamond grid.
+For completeness, here we repeat the derivation of Refs.
+\cite{liu1995force,coppersmith1996model,alim2017local} which  show that the observed exponential distribution of fluid flux can be described using a mean-field approach on a structured grid.
 Basically, the random distribution of the diameters along with the conservation of mass in the network are the two main ingredients resulting in an exponential tail distribution.
 In a diamond grid, the incoming flow to a node is redistributed among the outgoing edges (since fluid mass is conserved).
-Due to the randomness in the tube's diameter, one can imagine that the redistribution of the incoming flow to a node between the outgoing edges is random variable.
-The only condition required to be hold here is that the incoming flux should be equal to the outgoing flux.
+Due to the randomness in the tube's diameter, the redistribution of the incoming flow to a node between the outgoing edges is random variable.
 This model for the flow can be mapped one to one to the problem of force fluctuations in a bead pack \cite{liu1995force,coppersmith1996model,alim2017local} as shown in Fig.
@@
   \centering
-  \includegraphics[width=.75\textwidth]{./Figs/grid-analytica.eps}
-  \caption{(a) Schematic of diamond grid network of tubes.
+  \includegraphics[width=.75\textwidth]{FigS1.pdf} % grid-analytica
+  \caption{(a) Schematic of a  diamond grid network of tubes.
 The incoming flow to each node is redistributed among the outgoing edges.
-The thickness of the lines shows the fluid flux transferred in that edge.
+The thickness of the lines shows the fluid flux transferred through that edge.
 (b) Schematic diagram showing beads (represented with nodes) and their contacts to the neighboring sites (represented with edges).
-The thickness of the edges show the weight transferred through that contact.} \label{grid-result}
+The thickness of the edges show the force transferred through that contact.} \label{grid-result}
 \end{figure}
@@
 %
-where $w_{ij}$ shows the weights by which the flow is redistributed. Note that since the total fluid flux is conserved, then  $\sum_{j} w_{ij} = 1$. 
+where $w_{ij}$ shows the weights by which the flow is redistributed, and $\sum_{j} w_{ij} = 1$ since the total fluid flux is conserved. 
 % Next, we assume that the weights $w_{ij}$ are drawn from a distribution $\eta(w)$.
@@
 %
-Assuming a general distribution of $\eta(w)$, we can use the mean-field approximation to find the distribution of $q$ at the layer $L$, i.e., $p_L(q)$.
-The values of $q(L,i)$ are not independent for neighboring
-sites; however, in our mean-field approximation we ignore such
-correlations. We find
+Assuming a general distribution of for the weights, $\eta(w)$, we can use a mean-field approximation to find the distribution of $q$ at the layer $L$, i.e., $p_L(q)$, as 
 %
@@
 % The only approximation in the above equation is that we neglect the possible correlation between the values of $q$ among ancestors. 
-where $N$ is the number of outgoing edges (e.g., in our structured diamond grid $N=2$) and $\delta(\cdot)$ is the Kronecker delta function.
-Note that the constraint that $q$'s emanating downward should add up to one is in the definition of $\eta(w)$.
-Taking the Laplace transform of the above equation and defining $\tilde p(s) & \equiv \int_0^{\infty} p(q) e^{-qs} dq$ we obtain
+where $N$ is the number of outgoing edges (e.g., in our structured diamond grid $N=2$) and $\delta(\cdot)$ is the Dirac delta function. 
+% The constraint that $q$'s emanating downward should add up to one is accounted for through the definition of $\eta(w)$. 
+% The values of flux at each layer $q(L,i)$ are not independent for neighboring sites; however, in our mean-field approximation, we ignore such correlations.  
+Taking the Laplace transform of the above equation and defining $\tilde p(s)  \equiv \int_0^{\infty} p(q) e^{-qs} dq$ one obtains
 %
@@
 %
-The probability distribution at the layers converges to a distribution $\tilde P(s)$.
-The final solution for a structured diamond grid with two neighboring sites becomes $p(q) = 4q\exp(-2q)$ \cite{liu1995force,coppersmith1996model,alim2017local}, which is a distribution with an exponential tail.
+The above equation gives a recursive relation for the Laplace transformed of fluid flux PDF, $\tilde P_L(s)$, where it gradually converges to a distribution $\tilde P(s)$ from which the PDF of fluid flux can be obtained.
+Solving the above equation for a structured diamond grid network, one finds that the converged PDF of the fluid flux becomes $p(q) = 4q\exp(-2q)$ \cite{liu1995force,coppersmith1996model,alim2017local}, which is an exponential tailed distribution.
 
-\newpage
-
-\begin{figure}[h]
+% \begin{figure}[h]
     % \centering
-    \includegraphics[width=0.75\textwidth]{Figs/randomNetworkErosion3.pdf}
-    \caption{Deng's version: Erosion in a topologically random network of pipes.
+%     \includegraphics[width=0.75\textwidth]{Figs/randomNetworkErosion3.pdf}
+%     \caption{Deng's version: Erosion in a topologically random network of pipes.
 The initial condition is shown with the label $t=0$ in the first row.
@@
 (1) in the main text where different powers of $n$ correspond to different models of erosion.
-The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}
+The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}%
+% \end{figure}
+
+\newpage
+\section{Robustness to topology, initial condition, and boundary condition}
+% 
+In order to check the robustness of our results with respect to the topology of the network, we run our simulations on a three-dimensional random network with Voronoi cell initialization of nodes in space (Fig.
+\ref{SIfig:fig2-3d}), and also for a two dimensional topologically ordered network with a diamond grid (Fig.
+\ref{fig:fig2-diamond}), where  both networks are initialized with a uniform random distribution for the diameter of the tubes.
+We find that regardless of the topology of the network, an erosion dynamics with $n>3$ results in a homogenized network, while $n<3$ results in the channelization instability.
+We further check the effect of initial randomness on the fate of the network.
+We use a two-dimensional diamond-grid network with a narrow uniform initial distribution of tube diameters around an average diameter $d_0$ with only a very small variation ($3\%$), i.e., the tube diameters are sampled from a uniform distribution with $\mathcal{U}(d_0(1-\epsilon), d_0(1+\epsilon))$.
+We again find that for the networks with $n<3$ channels are formed, while for $n>3$ the network stays homogenized.
+\add{In addition to the network topology and initial condition, we test the robustness of our results to changes in the boundary condition.
+We choose a circular domain, with the central node being the inlet and all the nodes at the outer boundary being outlets.
+Similar to the transition reported for the square
+domain, we find a phase transition at the predicted power which shows that our analysis is independent of the geometry (Fig.~\ref{SIfig:fig2-3d_circular}). }
+%
+\begin{figure}[htp]
+     % \centering
+      \includegraphics[width = 1.0\textwidth]{FigS2.pdf}
+     \caption{Erosion in a topologically random 3D network of tubes with $N_x=20, N_y=12, N_z=12$ points for Voronoi cell initialization and an initial uniform broad distribution of tube diameters randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$.
+Snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$ are shown.
+We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
+The erosion law is based on $dr/dt = \alpha q/r^n$ where different powers of $n$ correspond to different models of erosion.}\label{SIfig:fig2-3d}
+ \end{figure}
+%
+\begin{figure}[htp]
+    % \centering
+ \includegraphics[width=0.75\textwidth]{FigS3.pdf} % Fig2-Sdiamond.pdf
+     \caption{Erosion in a diamond grid network with $N_x=100, N_y=50$ randomly distributed nodes and an initially broad  distribution of tube diameter randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$.
+The initial condition is shown with the label $t=0$ in the first row.
+Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius.
+The erosion law is based on Eq.
+(1) in the main text where different powers of $n$ correspond to different models of erosion.
+The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2-diamond}%
+\end{figure}
+%
+\begin{figure}[htp]
+    % \centering
+ \includegraphics[width=0.72\textwidth]{FigS4.pdf}
+     \caption{Erosion in a structured diamond grid network with $N_x=50, N_y=50$ and an initially narrow distribution of tube diameters randomly sampled from a uniform distribution with  $\mathcal{U}\left(d_0(1-\epsilon), d_u(1+\epsilon)\right) $ where  $d_0$ is the average diameter and $\epsilon=0.03$.
+The initial condition is shown with the label $t=0$ in the first row.
+Each row afterward corresponds to the simulation result after $N$ steps such that $\langle r_{t=N}\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$ or twice the initial average radius.
+The erosion law is based on Eq.
+(1) in the main text where different powers of $n$ correspond to different models of erosion.
+The first column is a snapshot of the pore network, the second column is the PDF of normalized fluid flux $q/\langle q \rangle$, and the last column is the PDF of normalized radius $r/\langle r\rangle$.}\label{fig:fig2}%
+\end{figure}
+%
+\begin{figure}[htp]
+     % \centering
+      \includegraphics[width = 0.70\textwidth]{./circular3.pdf}
+     \caption{\textcolor{blue}{Erosion in a topologically random 3D network of tubes with a circular topology with $N = 3000 $ randomly distributed nodes and an initial uniform broad distribution of tube diameters randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$.
+Shown are snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$.
+We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
+The erosion law is based on Eq.
+(1) in the main text where different powers of $n$ correspond to different models of erosion.}}\label{SIfig:fig2-3d_circular}
+ \end{figure}
+%
+
+\clearpage
+\section{Erosion with a threshold}
+%
+\add{In order to make our erosion model more realistic, we modify the model as  
+%
+\begin{align}
+    \frac{dr}{dt } = \begin{cases} q^m/r^n - \beta & q^m/r^n\geq \beta\\
+    0 & q^m/r^n<\beta
+    \end{cases} \label{eq:thresh}
+\end{align}
+%
+where $\beta$ is the threshold for the onset of erosion.
+We pick $\beta = 0.25\langle q^m/r^n\rangle $ and $\beta = 0.9 \langle q^m/r^n\rangle$ corresponding to a small and a large threshold value.
+In both cases, we ran our simulations for different values of $m$ and $n$, and found that different behaviors of homogenization and channelization persists (see Fig.
+\ref{fig:figthresh1}).
+The result can be explained by applying the general condition for the phase transition as discussed in the main text.
+Following the same argument, it can be shown that the homogenization condition (Eq.
+3 in the main text) is equivalent to the condition
+%
+\begin{align}
+4m-n-1 < -\frac{\beta}{q^m/r^n}.    
+\end{align}
+%
+which can be found using $g(r) = ({\pi \Delta p}/{8\mu L})^{m} r^{m-n} - \beta $ assuming a constant pressure boundary condition.
+Note that the condition above depends on the value of $q^m/r^n$ which varies over the network edges.
+Taking the mean value of $q^m/r^n$ to find an average value for the transition condition, the transition line becomes $4m-n=0.75$ and $4m-n=0.1$ for the small and large thresholding value respectively.
+As a result the thresholding condition slightly shifts the intercept of the transition line while the slope remains the same.
+In Fig.~\ref{fig:figthresh1}, we plot the new transition lines, where the prediction for the phase boundaries matches well with the simulation results.}
+
+\begin{figure}[htp]
+    \centering
+ \includegraphics[width=0.45\textwidth]{./Fig_thres0.25.pdf}
+  \includegraphics[width=0.45\textwidth]{./Fig_thresh0.9.pdf}
+     \caption{\add{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
+\eqref{eq:thresh} with a small threshold value of $\beta = 0.25\langle q^m/r^n\rangle $ (left figure), and a large threshold value of $\beta = 0.9\langle q^m/r^n\rangle$ at $t=0$.
+The network is randomly initialized with $50\times 50$ randomly distributed pores.
+The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using local dynamics model, i.e., $4m-n=0.75$ (left figure), and $4m-n=0.1$ (right figure).} }\label{fig:figthresh1}%
 \end{figure}
 
-% \clearpage
-% \newpage
-\bibliography{ref}% Produces the bibliography via BibTeX.
+% \begin{figure}[htp]
+%     % \centering
+%  \includegraphics[width=0.72\textwidth]{Fig_thres0.25.pdf}
+%      \caption{\textcolor{blue}{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
+\eqref{eq:thresh} with a small thresholding value of $\beta = 0.25\langle q^m/r^n\rangle $ at $t=0$.
+The network is randomly initialized with $50\times 50$ randomly distributed pores.
+The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using simplified model, i.e., $m=(n+1)/4$.} }\label{fig:figthresh1}%
+% \end{figure}
+
+% \begin{figure}[htp]
+%     % \centering
+%  \includegraphics[width=0.72\textwidth]{Fig_thresh0.9.pdf}
+%      \caption{\textcolor{blue}{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
+\eqref{eq:thresh} with a large thresholding value of $\beta = 0.9\langle q^m/r^n\rangle $ at $t=0$.
+The network is randomly initialized with $50\times 50$ randomly distributed pores.
+The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using simplified model, i.e., $m=(n+1)/4$.}}\label{fig:figthresh2}%
+% \end{figure}
+
+\newpage 
+\newpage 
+\newpage
+\section{Average Change in the  Order parameter}
+%
+In order to quantify the network behavior shown in Fig.
+4, we calculate the change in the order parameter for different $m,n$ averaged over 100 simulations with different random initial conditions, and the heat-map results are shown in Fig.~\ref{fig:fig4_SI-2}.
+The positive or negative change in the order parameter shows the network's change toward homogenization or channelization.
+The boundary between the two phases (homogenization and channelization) calculated using the simple model introduced in the main text is shown with a solid black line here, and it can be seen that it agrees well with the order parameter change.
+%
+\begin{figure}[htp]
+    % \centering
+    \includegraphics[width = 0.70\textwidth]{FigS5.pdf}
+    \caption{The heat map for the average change in the order parameter corresponding to the networks shown in Fig.
+4 of the main text.
+The order parameter shown in the heat map here is an average of 100 different simulations with different random initialization of tube diameters.
+The black line shows the boundary between two phases calculated using the model introduced in the main text.}\label{fig:fig4_SI-2}
+\end{figure}
+
+\section{Clogging Dynamics}
+% 
+% \textit{}-- 
+Besides erosion, another change in the network is the deposition/sedimentation of material on the boundary walls of the porous material.
+We refer to this dynamical change a ``clogging'' process as opposed to erosion.
+Contrary to erosion, the clogging behavior may cause some edges to block which effectively alters the network of connectivity and network behavior.
+This change in the connection between nodes through edges getting blocked can drastically alter porous structure behavior, e.g., causes a huge difference between effective and true porosity \cite{shima2021}.
+Despite the drastic change of network with blockages, we can still focus on the \textit{initial} change in the order parameter.
+The derivative of order parameter can be written as
+%
+\begin{align}
+    \frac{d\mathcal{O}}{dt} = \sum_{ij} \sum_{kl} \frac{\partial \mathcal{O}}{\partial q_{ij}} \frac{\partial q_{ij}}{\partial C_{kl}}  \frac{\partial C_{kl}}{\partial t} \label{eq:order-derivative}
+\end{align}
+%
+where the last term changes sign from erosion to clogging, i.e., $\partial C_{kl}/\partial t = \pm \alpha \pi q^m_{kl} /r_{kl}^{n-3}\mu l_{kl}$ for erosion and clogging respectively.
+As a result, the magnitude of change in the order parameter equals that of erosion.
+Note that in Eq.
+\eqref{eq:order-derivative}, the second term depends on the network topology, and pore throat clogging results in the change of network topology at later times.
+% The pore throat blockages results in the divergent of clogging results from just the negative of erosion. 
+At short times, however, similar to the erosion, a phase transition exists at $n=3$.
+When  $n<3$ the network moves toward homogenization during the clogging process and when $n>3$ the flow moves toward the development of channeling instability.
+At later times, this initial trend, however, might not hold true due to the aforementioned complex changes in the connectivity network during the clogging process.
+
+% \section{Generalization of the toy model}
+% %
+% A general erosion in the edges of a network can be written as 
+% %
+% \begin{align}
+%     \frac{dr}{dt} = f(q,r), \label{eq:general}
+% \end{align}
+% %
+% where $q$, and $r$ are the fluid flux and the radius of an edge, and $f(\cdot)$ represents the function that determines the physics of erosion.
+Note that if $f(q,r)>0$ the edge is eroding, and if $f(q,r)<0$, the edge is clogging.
+In this section, we study the fate of our toy model, given such general erosion law.
+
+% \textbf{Parallel Tubes: }
+% %
+% We first consider parallel edges with an arbitrary erosion function, i.e., Eq.~\eqref{eq:general}.
+In the parallel case, both tubes experiencing the same pressure difference $\delta p$, and using Darcy's law the flux in each tube $q_i = \beta r_i^4 \delta p$, where $\beta = \pi/8\mu L$, $L$ being the length of the tube, $\mu$ the viscosity of the fluid, and $i=1,2$ correspond to the edges.
+We define $g(r_i) = f(q_i, r_i)$ and as a result the erosion dynamics can be written as $dr_i/dt = g(r_i)$.
+Without loss of generality we assume $r_1>r_2$.
+The fluid flux in the tubes can be obtained using $q_i/q = \tilde C_i $, where $q$ is the total flux, and $\tidle C_i = C_i/(C_1+C_2)$ is the relative conductivity, and $C_i = \pi r_i^4/8\mu L $ is the tubes conductance.
+In order to find the evolution of the fluid flux, we find the time derivative of relative conductivity,
+% %
+% \begin{align}
+%     \frac{d\tilde{C}_1}{dt} = \frac{4C_1^{\frac{3}{4}} C_2^{\frac{3}{4}}}{(C_1+C_2)^2}(r_2 g(r_1)-r_1 g(r_2)).
+% \end{align}
+% %
+% We find that $r_1=r_2$ is a fixed point, where flow is equally distributed between the edges resulting in homogenization.
+If $d \tilde C_1/dt <0$, then the edge with larger radius has a reduced growth the smaller radius edge has an increasing growth until $r_1=r_2$ is reached.
+This condition results in the homogenization where both edge's radius increases until the fixed point of $r_1=r_2$ is reached.
+The condition of $d \tilde C_1/dt<0$ is satisfied when
+% %
+% \begin{align}
+%     \frac{g(r_1)}{g(r_2)}<\frac{r_1}{r_2}, \forall r_1>r_2>0.
+% \end{align}
+% %
+% The above result can further be simplified as if $d\left(g(r)/r\right)/dr<0$ which ultimately results in homogenization of the parallel edges.
+Lastly, we can also study the perturbation of tube's radius around the fixed point as $r_1=r_0_\delta r$ and $r_2 = r_0$.
+Using Taylor series expansion, we can show that stability condition reduces to $g(r_0)>g'(r_0) r_0$.
+Therefore, if the erosion rate is sub-linear locally near the initial radius, the network moves towards homogenization in short time, while the long term behavior is less predictable.
+On the other hand, if the erosion rate is sup-linear, we expect the parallel tubes to move away from homogenization (i.e., channelization) in short times.
+Applying the power law erosion model with $f(q,r)=\alpha q^m/r^n$, it can be shown that $g(r) \propto  r^{4m-n} $, and therefore homogenization condition becomes $4m-n<1$ as seen in simulations.
+Although the result is derived under the constant pressure difference assumption, it holds validity for homogenization cases, where the pressure difference is going towards homogenization as well.
+However, for channelization cases, the pressure difference can be varied vastly inside the network, thus once the channelization happens, negative feedback effect of erosion rate might not be able to reverse that.
+
+% \textbf{Series Tubes: }
+% %
+% In the series toy model, we have $q_1=q_2 = q = \frac{C_1 C_2}{C_1+C_2}\delta p$ and similar results can be derived so that the condition for homogenization becomes
+% %
+% \begin{align}
+%     \frac{f(q,r_1)}{f(q,r_2)}<\frac{r_1}{r_2}, \forall r_1>r_2>0.
+% \end{align}
+% %
+% Note that if the dependence of $f$ on $q$ is non-homogeneous, then this condition might be valid for some $q$'s but not the others.
+Applying the power law erosion model with $f(q,r)=\alpha q^m/r^n$, it can be shown that homogenization condition is $n>0$ as it has been seen in simulations.
+
+\add{\section{General shear dependent erosion model}}
+\add{
+As an example of a nonlinear erosion model, we consider a shear-dependent erosion
+%
+\begin{align}
+    \frac{dr}{dt} = f(\tau),
+\end{align}
+%
+where $\tau=\tau(q,r) = 4\mu q/\pi r^3$ is the shear stress at the tube's wall assuming Poiseuille flow.
+It is to be noted that a shear-dependent erosion model is commonly used in studying erosion  \cite{jager2017channelization,bonelli2011micromechanical,parker2000purely} wherein such models erosion happens linearly proportional to the shear stress at the wall only after a certain threshold value $\tau_0$ (see main text for more information).
+Such linear models, however, ignore the maximum detachment rate of particles at the pore's boundary which would effectively limit the pore's radius maximum rate of change.
+To address this, we use a nonlinear erosion model
+%
+\begin{align}
+    f(\tau) = \alpha \left( \tanh{\left[ \beta(\tau - \tau_0)\right]}+1\right),
+    \label{eq:sigmoidErosion}
+\end{align}
+%
+where $\beta$ determines the shear rate scale and $\alpha$ determines the erosion rate scale.
+Note that the erosion rate scale $\alpha$ only affects the timescale at which the final state is reached and has no effect on the pattern formation.
+Without loss of generality we set $\alpha = 1$.
+Following the local dynamics model discussion in the main text, one can find that the homogenization condition reduces to
+%
+\begin{align}
+    f(\tau)>\tau \frac{df(\tau)}{d \tau}.
+    \label{eq:sigmoidCondition}
+\end{align}
+%
+Assuming a random network (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}a), the initial values of shear stress at the walls have a  decaying distribution over a large set of values (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}b).
+%Assuming nonlinear shear dependent erosion model (Eq.
+\eqref{eq:sigmoidErosion}) three regions of erosion can be identified: (i) The constant erosion region as $\tau\to\infty$.
+In this region the erosion happens at a constant rate $\lim_{\tau \to \infty} f(\tau) = 2$ and additionally the homogenization condition (Eq.~\eqref{eq:sigmoidCondition}) is satisfied (since $\lim_{\tau \to \infty} f(\tau) = 2$ and $\lim_{\tau \to \infty} f'(\tau) = 0$).
+It is to be noted that the homogenization effect for the constant erosion rate is similar to $m=0,n=0$ case for the erosion model discussed in the main text; (ii)  The slow-erosion region as $\tau\to 0$.
+In this region both $f(\tau)$ and $\tau f'(\tau)$ are close to 0 and since $f(\tau)$ is bounded in-between 0 and 2, erosion in the edges at this region happens at a very slower rate compared to other edges with nonzero shear-rate; (iii) The finite erosion-rate region near $\tau = \tau_0$, where $f(\tau)$ is an increasing function.
+In this region $\tau f'(\tau)$ has a maximum at $\beta \tau_0$ with a bandwidth of $1/\beta$.
+If $\beta \tau_0 < 1$, then the maximum $\tau f'(\tau)$ does not exceed 1, and the homogenization condition holds true for any $\tau$.
+As the value of $\tau_0$ increases, the homogenization region moves towards larger values of $\tau$ where edges with smaller values of $\tau$ would result in channelization.
+It can be seen that varying $\beta$ and $\tau_0$ changes the network behavior.
+To test our local dynamics model, we vary $\beta$ and $\tau_0$ and run three different tests: (i) $\beta=1,\tau_0=1$: For such values of $\beta,\tau$, almost all the tubes are in the homogenization region corresponding to Eq.~\eqref{eq:sigmoidCondition} (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}c) and the network moves toward homogenization (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}d).
+The final PDF of the network after erosion is further shown in (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}e).
+(ii) $\beta=1, \tau_0=12$: In this case, the homogenization condition is satisfied at some finite value of shear stress $\tau_0$ where $f(\tau_0) = \tau_0 f(\tau_0)$.
+As a result, some edges would homogenize, and some would channelize (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}f).
+Running the simulation over a random network, we find that a finite number of channels form (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}g).
+The PDF distribution of shear stress at the wall $\tau$ correspondingly becomes bimodal (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}h).
+(iii) $\beta=1, \tau_0=30$: In this case, almost all the edges in the network are in the channelization regime  (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}i), and performing the simulations we find that indeed one strong single channel is formed (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}j) and the PDF of shear stress $\tau$ shows a clear separation between flow in the channel versus flow in the rest of the system (Fig.~\ref{SIfig:fig9-sigmoidDelaunay}k).
+}
+   \begin{figure}[htp]
+     % \centering
+      \includegraphics[width = 0.8\textwidth]{sigmoidDelaunay.pdf}
+     \caption{\textcolor{blue}{(a) A 2D random network with $N_x=50$ and $N_y=50$ points.
+(b) The probability distribution function (PDF) of the shear stress for the edges of the network.
+(c)/(f)/(i) The PDF of the shear stress along with nonlinear erosion law $f(\tau)$ (solid red line) and $\tau f'(\tau)$ (dashed red line).
+The areas where the homogenization condition (i.e., $f(\tau)>\tau f'(\tau)$) is satisfied are shaded with green color, otherwise, the channelization condition is satisfied and the region is shaded with red color.
+(d)/(g)/(j) Snapshots of the 2D network after erosion using the nonlinear erosion law shown in the previous row until the average radius of the network is increased to twice its original size.
+(e)/(h)/(k) The PDF of the shear stress at the walls for the final snapshot of the network shown in the previous row.
+    }}
+     \label{SIfig:fig9-sigmoidDelaunay}
+ \end{figure}
+
+%  \begin{figure}[htp]
+%      % \centering
+%       \includegraphics[width = 1.0\textwidth]{sigmoidDelaunay_rev1.pdf}
+%      \caption{\add{Nonlionear erosion in a 2D random network of tubes with $N_x=50$ and $N_y=50$, where edge radii are sampled from a uniform distribution with $\mathcal{U}[1,14]$.
+Snapshots of the network after for different erosion rate $\beta$ and threshold values $\tau_0$ are shown after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle = 7.5$.
+The erosion law is based on Eq.
+\eqref{eq:sigmoidErosion}.
+As shown above, increasing $\tau_0$ results in a stronger channelization, while changing $\beta$ has a much smaller effect.
+Note that increasing $\tau_0$, increases the number of tubes in the channelization region, while increasing $\beta$ slightly shifts the region and has a much smaller effect.} }
+%      \label{SIfig:fig10-sigmoidDelaunay}
+%  \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{align}
+%     \frac{dr_i}{dt} = f(|q_i|,r_i),
+% \end{align}
+% %
+% where $i = 1$ and $2$ correspond to pipe 1 and pipe 2 respectively and $f(q,r)$ can be negative thus it allows clogging.
+In the toy model case $q_i = C p r_i^4$ where $p$ is the pressure difference between two terminals of the pipes.
+Therefore the erosion rate only depends on $r_i$
+% \begin{align}
+%     f(|q_i|,r_i) = g(r_i).
+% \end{align}
+% The time derivative of relative conductivity $\tilde{C}_1 = C_1/(C_1+C_2)$ can be written as
+% \begin{align}
+%     \frac{d\tilde{C}_1}{dt} = \frac{4C_1^{\frac{3}{4}} C_2^{\frac{3}{4}}}{(C_1+C_2)^2}(r_2 g(r_1)-r_1 g(r_2)).
+% \end{align}
+% It is obvious that in the toy model, $r_1=r_2$ is a fixed point, while its stability depends on the form of $f(q,r)$, or equivalently $g(r)$ in the parallel case.
+It can be shown that the condition for homogenization is
+% \begin{align}
+%     \frac{g(r_1)}{g(r_2)}<\frac{r_1}{r_2}, \forall r_1>r_2>0.
+% \end{align}
+% This is a strong constraint to $g(r)$, and in reality it might not hold true for arbitrary $r$'s when negative feedback over erosion rate is introduced.
+One generalization we can make is to expand the function near the value we are interested in.
+Let $r_0 = r_2$ be the initial value, and $r_1 = r_0 + \delta r$ to be the perturbation in one pipe.
+With Taylor series expansion the above condition can be written as
+% \begin{align}
+%     g(r_0)>g'(r_0) r_0.
+% \end{align}
+% Therefore, if the erosion rate is sub-linear locally near the initial radius, we can say it will drive the network towards homogenization in short time, while the long term behavior is less predictable.
+On the other hand, if the erosion rate is sup-linear, we expect to see channelization to some extent.
+
+% Applying the power law erosion model with $f(q,r)=C q^m/r^n$, it can be shown that $g(r) = C p r^(4m-n) $ and therefore homogenization condition is $4m-n<1$ as seen in simulations.
+
+% Although the result is derived under the constant pressure difference assumption, it holds validity for homogenization cases, where the pressure difference is going towards homogenization as well.
+However, for channelization cases, the pressure difference can be varied vastly inside the network, thus once the channelization happens, negative feedback effect of erosion rate might not be able to reverse that.
+
+% In the series toy model, we have $q_1=q_2 = q = p \frac{C_1 C_2}{C_1+C_2}$ and similar results can be derived so that the condition for homogenization is
+% \begin{align}
+%     \frac{f(q,r_1)}{f(q,r_2)}<\frac{r_1}{r_2}, \forall r_1>r_2>0.
+% \end{align}
+% Note that if the dependence of $f$ on $q$ is non-homogeneous, then this condition might be valid for some $q$'s but not the others.
+
+% Applying the power law erosion model with $f(q,r)=C q^m/r^n$, it can be shown that homogenization condition is $n>0$ as seen in simulations.
+
+\clearpage
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+
+% \bibliography{ref}% Produces the bibliography via BibTeX.
+%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{8}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{https://doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{git(2021)}]{githubrepo}%
+  \BibitemOpen
+  \href@noop {} {\bibinfo {title} {Network instability}},\ \bibinfo
+  {howpublished} {\url{https://github.com/ahmadzareei/networkInstability}}
+  (\bibinfo {year} {2021})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Liu}\ \emph {et~al.}(1995)\citenamefont {Liu},
+  \citenamefont {Nagel}, \citenamefont {Schecter}, \citenamefont {Coppersmith},
+  \citenamefont {Majumdar}, \citenamefont {Narayan},\ and\ \citenamefont
+  {Witten}}]{liu1995force}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.-h.}\ \bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont {Nagel}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Schecter}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Coppersmith}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Majumdar}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Narayan}},\ and\ \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Witten}},\ }\bibfield  {title} {\bibinfo
+  {title} {Force fluctuations in bead packs},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
+  {269}},\ \bibinfo {pages} {513} (\bibinfo {year} {1995})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Coppersmith}\ \emph {et~al.}(1996)\citenamefont
+  {Coppersmith}, \citenamefont {Liu}, \citenamefont {Majumdar}, \citenamefont
+  {Narayan},\ and\ \citenamefont {Witten}}]{coppersmith1996model}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Coppersmith}}, \bibinfo {author} {\bibfnamefont {C.-h.}\ \bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Majumdar}},
+  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Narayan}},\ and\ \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {Witten}},\ }\bibfield  {title}
+  {\bibinfo {title} {Model for force fluctuations in bead packs},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review E}\ }\textbf
+  {\bibinfo {volume} {53}},\ \bibinfo {pages} {4673} (\bibinfo {year}
+  {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alim}\ \emph {et~al.}(2017)\citenamefont {Alim},
+  \citenamefont {Parsa}, \citenamefont {Weitz},\ and\ \citenamefont
+  {Brenner}}]{alim2017local}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Alim}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Parsa}},
+  \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont {Brenner}},\
+  }\bibfield  {title} {\bibinfo {title} {Local pore size correlations determine
+  flow distributions in porous media},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
+  {119}},\ \bibinfo {pages} {144501} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Parsa}\ \emph {et~al.}(2021)\citenamefont {Parsa},
+  \citenamefont {Zareei}, \citenamefont {Santanach-Carreras}, \citenamefont
+  {Morris}, \citenamefont {Amir}, \citenamefont {Xiao},\ and\ \citenamefont
+  {Weitz}}]{shima2021}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Parsa}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zareei}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Santanach-Carreras}},
+  \bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont {Morris}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Amir}}, \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Xiao}},\ and\ \bibinfo {author}
+  {\bibfnamefont {D.~A.}\ \bibnamefont {Weitz}},\ }\bibfield  {title} {\bibinfo
+  {title} {Unexpected scaling of interstitial velocities with permeability due
+  to polymer retention in porous media},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review Fluids}\ }\textbf {\bibinfo {volume}
+  {6}},\ \bibinfo {pages} {L082302} (\bibinfo {year} {2021})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {J{\"a}ger}\ \emph {et~al.}(2017)\citenamefont
+  {J{\"a}ger}, \citenamefont {Mendoza},\ and\ \citenamefont
+  {Herrmann}}]{jager2017channelization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {J{\"a}ger}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Mendoza}},\
+  and\ \bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont {Herrmann}},\
+  }\bibfield  {title} {\bibinfo {title} {Channelization in porous media driven
+  by erosion and deposition},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Physical Review E}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo
+  {pages} {013110} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bonelli}\ and\ \citenamefont
+  {Marot}(2011)}]{bonelli2011micromechanical}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Bonelli}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Marot}},\ }\bibfield  {title} {\bibinfo {title} {Micromechanical modeling of
+  internal erosion},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {European Journal of Environmental and Civil Engineering}\ }\textbf {\bibinfo
+  {volume} {15}},\ \bibinfo {pages} {1207} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Parker}\ and\ \citenamefont
+  {Izumi}(2000)}]{parker2000purely}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Parker}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Izumi}},\
+  }\bibfield  {title} {\bibinfo {title} {Purely erosional cyclic and solitary
+  steps created by flow over a cohesive bed},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Fluid Mechanics}\ }\textbf
+  {\bibinfo {volume} {419}},\ \bibinfo {pages} {203} (\bibinfo {year}
+  {2000})}\BibitemShut {NoStop}%
+\end{thebibliography}%
 
 \end{document}
-%
 
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
-%###############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
+%#############################################################
 
@@
 % 
-Considering a small change in the radius of edges, and as a result, the conductance of the edges $\mathbf{C}+\delta \mathbf{C}$, using Eq. \eqref{eq:main-network} we find that 
+Considering a small change in the radius of edges, and as a result, the conductance of the edges $\mathbf{C}+\delta \mathbf{C}$, using Eq. \eqref{main-solve-eq} we find that 
 %

### 2022-04-12 CL/CLResponse2.tex
BeforePublication

--- 2022-03-06 CL/CoverLetterResponse.tex
@@
 \newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}
+\newcommand{\add}[1]{\noindent \color{blue} #1 \normalcolor}
 
@@
 \opening{Dear Editor,}
+\add{
+We would like to thank for reviewers' careful reading and valuable comments.
+We appreciate that our revised work ``Temporal Evolution of Erosion in Pore-Networks: From Homogenization to Instability'' was found  ``greatly improved'', ``to achieve the level of significance that it can be published PRL'' and ``is a substantial advance in the field''.
+The remaining most significant concern expressed by all reviewers is a convincing experiment test that our theory can directly apply to.
+Unfortunately our group is a theory group and lack of lab space.
+}
 
@@
 %
+\add{
 \begin{itemize}
-    \item Generalization of the results for an arbitrary erosion law.
-    \item Identifying the transition condition between homogenization and channelization for a general erosion law.
-    \item Showing the prediction power of our local dynamics model for a nonlinear erosion model.
-    \item Showing robustness of the phase transition to boundary condition changes and thresholding effects.
+    \item Acknowledging and discussion of the limitations of the general erosion law.
+
 \end{itemize}
+}
 
@@
 \end{document}
-in

### 2022-04-12 prl_paper.tex
BeforePublication

@@
 }
-%
-% Lastly, we show that the initial stages of pores clogging show analogous behaviors which depends on the clogging dynamics.
-
-% Lastly, we show that pores clogging at the initial stages show analogous behaviors depending on clogging dynamics.
-% , however, due to the pore throat blockages and changes in the network connections the evolution diverges from its initial trend.
-
-% \begin{description}
-% \item[Usage] Secondary publications and information retrieval purposes.
-% \item[PACS numbers] May be entered using the \verb+\pacs{#1}+ command.
-% \item[Structure] You may use the \texttt{description} environment to structure your abstract; use the optional argument of the \verb+\item+ command to give the category of each item.
-% \end{description}
 	\end{abstract}
@@
 		\includegraphics[width = 0.45\textwidth]{Fig1.pdf}
-    % \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}.
-The scale in the bottom left shows $1$mm.
-The network of pores and throats is highlighted in blue.
-In the network model, the pores are represented with nodes and the throats between pores are approximated with tubes connecting the pores together.
-(b) Schematic of a topologically random network (i); and a structured diamond grid network (ii).
-The edge diameters in both networks are randomly distributed.
-The inset figure shows the conservation of mass at each node.
-(c) The universal probability distribution function (PDF) of fluid flux for a topologically random (in blue) or diamond network (red) with a highly disordered random network including uniform (triangles), log-normal (circles), and truncated normal (plus) distributions.}
-    \caption{(a) Cross section of a porous sandstone sample obtained using  computerized tomography~\cite{akanji2010finite}.
-The scale in the bottom left shows $1$mm.
-The network of pores and throats is highlighted in blue.
+		\caption{(a) Cross section of a porous sandstone sample%obtained using  computerized tomography
+		~\cite{akanji2010finite}. The scale bar shows $1$mm. 
+		% The network of pores and throats is highlighted in blue. 
 		In the network model, the pores are represented with nodes and the throats between pores are approximated with tubes.
@@
 	\emph{Network approach}-- We approach this long-standing problem using a network model for the porous structure~\cite{fatt1956network, blunt2013pore,stoop2019disorder,bryant1993network,blunt2013pore,dong2009pore,blunt2013pore,blunt1995pore,alim2017local}.
-% Before discussing the dynamics, we briefly review the results of flow in random networks.
 	The network of pores inside the solid structure is connected together through pore-throats that effectively show resistance to the fluid flow between the pores (Fig.~\ref{fig:fig1}a).
@@
 \ref{fig:fig1}b).
-The pore-throats or radii of the edges are considered as independent and identically distributed random variables and fluid flow in the edges are obtained by solving for conservation of mass at all nodes given a pressure difference between the nodes on the boundaries (supplementary material, SM, \S1).
+The pore-throats or radii of the edges are considered as independent and identically distributed random variables and fluid flow in the edges are obtained by solving for conservation of mass at all nodes given a pressure difference between the nodes on the boundaries (supplementary material, SM, S1).
 Independent of edge radius distribution, the probability density function (PDF) of normalized fluid flux is well described by a single exponential distribution shown in Fig.
@@
 Considering a structured diamond-grid of pores (Fig.
-\ref{fig:fig1}c) which significantly simplifies the geometrical complexity of the network and allows for analytical tractability, one finds that the PDF of normalized fluid flux remains unchanged for various distributions suggesting robustness to network topology (Fig.~\ref{fig:fig1}d and SM \S2).
-In the following, we will study, analytically and numerically, how this universal distribution evolves as the network is modified based on a local constitutive law.
-
-\textit{Network evolution model}-- The degradation of the solid skeleton (i.e., erosion) or deposition of material on the pore throats (i.e., clogging) in the network of pores is modeled by the change (increase or decrease) in the radii of the edges connecting the pores which translates into changes in the flow resistance between the pores.
+\ref{fig:fig1}c) which significantly simplifies the geometrical complexity of the network and allows for analytical tractability, one finds that the PDF of normalized fluid flux remains unchanged for various distributions suggesting robustness to network topology (Fig.~\ref{fig:fig1}d and SM S2).
+In the following, we study, analytically and numerically, how this universal distribution evolves as the network is modified based on a local constitutive law.
+
+	\textit{Network evolution model}-- The degradation of the solid skeleton (i.e., erosion) or deposition of material on the pore throats (i.e., clogging) in the network of pores is modeled by the change (increase or decrease) in the radii of the edges connecting the pores.
+	%which translates into changes in the flow resistance between the pores. 
 	The rate of change of the radii depends on local fluid flow parameters (i.e., $q, r$), however, the exact dependence is unknown.
-A general constitutive model for erosion can be written as $dr_{ij}/dt = f(q_{ij},r_{ij})$, where $f(q_{ij},r_{ij})$ represents the functional dependence of erosion on the fluid flux $q_{ij}$ and the tube radius $r_{ij}$.
+A general constitutive model for erosion can be written as $dr_{ij}/dt = f(q_{ij},r_{ij})$, where $f(q_{ij},r_{ij})$ represents the functional dependence of erosion on the fluid flow parameters.
+	%flux $q_{ij}$ and the tube radius $r_{ij}$. 
 	Erosion in saturated, granular, porous medium occurs when the shear stress  at the walls $\tau_w$ exerted by the fluid overcomes the cohesive strength of the solid matter $\tau_c$.
-In a class of erosion models previously studied~\cite{jager2017channelization,ristroph2012sculpting,wan2004investigation} the eroded mass per unit area is linearly proportional to the excess shear, i.e.,  $\dot{m}  = -\kappa  (\tau_w-\tau_c)$ where $\kappa$ is the linear proportionality constant.
-This erosion model effectively results in an increase in the radius of the edges in our network model where \add{$\dot{r} \propto \kappa/r (|q|/r^3 - \tau_c)$ , where $1/r$ factor comes from the eroded mass $dm =2\pi\rho r l dr$ for a cylindrical pipe and $|q|/r^3$ comes from the known result of shear stress of laminar flow in pipes \cite{white2006viscous}}.
-Similar models have further been used in biological models for the growth of vascular networks~\cite{chen2012haemodynamics,hacking1996shear}.
+In a class of erosion models previously studied~\cite{jager2017channelization,ristroph2012sculpting,wan2004investigation} the eroded mass per unit area is linearly proportional to the excess shear, i.e.,  $\dot{m}  = \kappa  (\tau_w-\tau_c)$ where $\kappa$ is the linear proportionality constant.
+This erosion model effectively results in an increase in the radius of the edges in our network model where \add{$\dot{r} \propto \kappa/r (|q|/r^3 - \tau_c)$, where the $1/r$ factor comes from the eroded mass $dm =2\pi\rho r l dr$ for a cylindrical pipe and $|q|/r^3$ comes from the shear stress of laminar flow in pipes \cite{white2006viscous}.} Similar models have further been used in biological models for the growth of vascular networks~\cite{chen2012haemodynamics,hacking1996shear}.
 In addition to local shear stress, erosion based on local fluid velocity ($v \propto |q|/r^2$) \cite{kudrolli2016evolution}, local pressure difference ($\Delta p \propto |q|/r^4$) \cite{derr2020flow,mahadevan2012flow}, and power dissipation ($P \propto q^2/r^4$ ) ~\cite{steeb2007modeling,marot2012study,sibille2015internal} have also been considered as alternative models.
@@
 Later we will generalize the models to include other forms of nonlinearities.
-% We use a general constitutive  model which may implement a diverse set of erosion or clogging dynamics and thus allows us to study the effect of different laws in a unified way.
 	%
 	\begin{figure}[!h]
-    % \centering
-    % \includegraphics[width = 0.48\textwidth]{Figs/Fig_2_Random_Network.png}
 		\includegraphics[width = 0.48\textwidth]{Fig2_.pdf}
@@
 	\end{figure}
-%
-% 
-% \begin{figure*}[htp]
-%      % \centering
-%       \includegraphics[width = 1.0\textwidth]{FigS2.pdf}
-%      \caption{\add{Erosion in a topologically random 3D network of tubes with $N_x=20, N_y=12, N_z=12$ points for Voronoi cell initialization and an initial uniform broad distribution of tube diameters randomly sampled from $\mathcal{U}(1,14)$.
-Snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$ are shown.
-We stop the erosion after $N$ steps such that $\langle r\rangle=2r_0$ where $r_0 = \langle r_{t=0}\rangle$.
-The erosion law is based on Eq.
-(1) \del{in the main text} where different powers of $n$ correspond to different models of erosion.}}\label{SIfig:fig2-3d}
-%  \end{figure*}
-%
-% In order to model erosion in porous media, we consider the abrasion in the throats leading to decrease in the tube radii. We model the dynamics as 
-%
-% \begin{align}
-%   \frac{dr_{ij}}{dt} = \alpha  \frac{|q_{ij}|^m}{r_{ij}^n}, \label{eq:erosion-law}
-% \end{align}
-%
-% where $m,n,\alpha$ are constants. Different values of $m$ and $n$ along with a positive $\alpha>0$ correspond to different erosion physics (analogously, $\alpha<0$ corresponds to clogging).
-Particularly, the erosion when $m=1$ and  (i) $n=0$ depends on the amount of flux $q_{ij}$ passing through the edge; (ii) $n=2$ depends on the local velocities  \cite{kudrolli2016evolution}; (iii) $n=3$ depends on the shear force at the boundary of the throat~ \cite{bonelli2011micromechanical,parker2000purely,jager2017channelization}.
-{Additionally, $m=2$ and $n=6$ corresponds to models considered in biological transport networks where the radii changes are {proportional to the square of shear stress at the boundary walls}~\cite{hu2013adaptation,ronellenfitsch2016global}.}  We later address the effect of incorporating the threshold discussed above into our model.
-We consider a randomly initialized network with disordered diameters obtained from a uniform distribution (SM S1). 
+	% Particularly, the erosion when $m=1$ and  (i) $n=0$ depends on the amount of flux $q_{ij}$ passing through the edge; (ii) $n=2$ depends on the local velocities  \cite{kudrolli2016evolution}; (iii) $n=3$ depends on the shear force at the boundary of the throat~ \cite{bonelli2011micromechanical,parker2000purely,jager2017channelization}.
+{Additionally, $m=2$ and $n=6$ corresponds to models considered in biological transport networks where the radii changes are {proportional to the square of shear stress at the boundary walls}~\cite{hu2013adaptation,ronellenfitsch2016global}.}
+	% We later address the effect of incorporating the threshold discussed above into our model.  
+	We consider a randomly initialized network with disordered diameters obtained from a uniform distribution (SM, S1). 
 	The flow inside the pores, PDF of flux in the tubes, and PDF of tube radii are shown in Fig.
@@
 In each time step, we increase the local radii of the tubes based on the erosion law $dr_{ij}/dt = \alpha q_{ij}^m/r_{ij}^n$, assuming erosion is linear in the flux ($m=1$).
-Later we will consider the network behavior for other powers of $m$.
+	% Later we will consider the network behavior for other powers of $m$. 
 	We continue the simulations until $\langle r \rangle = 2 r_0$. 
@@
 Similarly, the PDF of the tube diameters becomes narrower.
-It is to be noted that the different distributions obtained for different powers of $m,n$ represent different statistics that cannot be collapsed.
-
-We found that similar results uphold in a 3d random tube network  (see SM, Fig.~S2) as well as a 2d topologically ordered (diamond grid) network, illustrating the robustness of the results to the network topology (SM, Fig.~S3).
+
+	% It is to be noted that the different distributions obtained for different powers of $m,n$ represent different statistics that cannot be collapsed.
+
+	We found that similar results uphold in a 3d random tube network  (SM, Fig.~S2) as well as a 2d topologically ordered (diamond grid) network, illustrating the robustness of the results to the network topology (SM, Fig.~S3).
 Similarly, we found that the results hold also when using an initial narrow distribution of diameters (SM, Fig.~S4), showing robustness with respect to the strength of the disorder.
@@
 
-\textit{Phase transition and order parameter}-- {To quantify the transition of the network between the channeling instability and homogenization, we define an order parameter % $\mathcal{O}$ 
-%
-\begin{align}
-\mathcal{O} = \frac{1}{N-1} \left( N - \frac{\left( \sum_{ij} q^2_{ij}\right)^2}{ \sum_{ij} q^4_{ij}}\right),
-\end{align}
-%
-where $N$ is the number of edges.} {The order parameter defined here is inspired by the participation ratio (PR) employed to quantify the localization of an eigenstate in the analysis of Anderson localization~\cite{kramer1993localization}.}  The order parameter $\mathcal{O}=0 $ when the flux through every edge is identical.
+	To quantify the transition of the network between the channeling instability and homogenization, we numerically define an order parameter $\mathcal{O}$ that varies between zero when flux through every edge is identical and one when the flow is highly localized (SM, S4).
+Calculating the order parameter over different simulations, we find a phase transition happens at $n \approx 3$ (SM, Fig.
+S6).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%   PHASE TRANSITION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+% To quantify the transition of the network between the channeling instability and homogenization, we define an order parameter~\footnote{The order parameter defined here is inspired by the participation ratio (PR) employed to quantify the localization of an eigenstate in the analysis of Anderson localization~\cite{kramer1993localization}.} % $\mathcal{O}$
+% 		%
+% 		\begin{align}
+% 			\mathcal{O} = \frac{1}{N-1} \left( N - \frac{\left( \sum_{ij} q^2_{ij}\right)^2}{ \sum_{ij} q^4_{ij}}\right),
+% 		\end{align}
+% 		%
+% where $N$ is the number of edges.
+The order parameter $\mathcal{O}=0 $ when the flux through every edge is identical.
 On the other hand, when fluid flux becomes highly localized with only a few edges with non-zero flux, $\mathcal{O}\to 1$.
-We numerically calculated the  order parameter $\mathcal{O}$ for {randomly initialized networks, averaged over 20 different realization}.
-The results are shown in Fig. \ref{fig:fig3}a for different amounts of erosion measured by the increase in the average diameter $\langle r\rangle /r_0$. As shown in 
- Fig.
-\ref{fig:fig3}c, at $n\approx 3$ the order parameter, remains unchanged; however for $n>3$ the order parameter moves toward zero, where the flow becomes more uniform, and for $n<3$ the order parameter goes toward unity, where channels are developed.
+We numerically calculated the  order parameter $\mathcal{O}$ for {randomly initialized networks, averaged over 20 different realization} (Fig.
+S6).
+We find that at $n\approx 3$ the order parameter, remains unchanged; however for $n>3$ the order parameter moves toward zero, where the flow becomes more uniform, and for $n<3$ the order parameter goes toward unity, where channels are developed.
 This indicates a phase transition at $n=3$ in the long-time behavior of the network.
 	%
-
-\begin{figure}[!h]
-    % \centering
-     \includegraphics[width = 0.45\textwidth]{Fig3.pdf}
-    \caption{ (a) Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig.
-\ref{fig:fig2} for different powers of $n$ with $m=1$ plotted over time.
-(b,c) Tubes in series (b) or parallel (c) configuration.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+
+% 	\begin{figure}[!h]
+% 		% \centering
+% 		\includegraphics[width = 0.45\textwidth]{Fig3-Main.pdf}
+% 		\caption{ Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig. \ref{fig:fig2} for different powers of $n$ with $m=1$ plotted over time.  
+% 		% (b,c) Tubes in series (b) or parallel (c) configuration.
 The tube radius dynamically change with the erosion law, i.e., $f(q,r) = \alpha |q|^m/r^n$.
@@
 When the tubes are in parallel, for (c$_1$) $m=(n+1)/4$, the flow ratio between the pipes does not change over time; (c$_2$)  $m<(n+1)/4$ the flow distributes between the tubes equally and  $q_1/(q_1+q_2) \to 1$ which results in the homogenization of the network; (c$_3$) $m>(n+1)/4 $, the entire flow eventually passes through one of the tubes, and channeling occurs.
-}\label{fig:fig3}
-\end{figure}
-
-\textit{Local Dynamics Model}--  To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes \add{of the same length $L$} in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Figs.
-\ref{fig:fig3}b-c).
-First, assuming two cylindrical tubes with radii $r_1,r_2$ in series with a given pressure difference of $\delta p = p_r- p_l$, the radius of each tube changes as $dr_i/dt = f(q,r_i),~i=1,2$ (Fig.
-\ref{fig:fig3}b) where $q=q_1=q_2$.
+% 		}\label{fig:fig3}
+% 	\end{figure}
+
+	\textit{Local Dynamics Model}--  \add{To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes of the same length $L$ in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Fig.
+S7)}.
+First, assuming two cylindrical tubes with radii $r_1,r_2$ in series with a given pressure difference of $\delta p = p_r- p_l$, the radius of each tube changes as $dr_i/dt = f(q,r_i),~i=1,2$ where $q=q_1=q_2$.
 Without loss of generality we assume $r_1>r_2$.
@@
 Since we assumed $r_1>r_2$, we can see that $\tilde p_m <1/2$, and if ${d\tilde{p}_m}/{dt}>0$, then $\tilde p_m \to 1/2$ and the flow homogenizes.
-Note that if $f(q,r) = \alpha q^m/r^n$, we find that for any $n>0$ the network homogenizes (see Fig.
-\ref{fig:fig3}b).
-Contrary to tubes in series, when the tubes are in parallel (Fig.
-\ref{fig:fig3}c), the net flow $q$ divides between the two tubes in proportion to their conductivity, i.e., $ q_1/q_2 = C_1/C_2$ which results in $q_1/q = \tilde C_1$, where $\tilde C_1 = C_1/(C_1+C_2)$.
+Note that if $f(q,r) = \alpha q^m/r^n$, we find that for any $n>0$ the network homogenizes (SM, Fig.
+S7).
+Contrary to tubes in series, when the tubes are in parallel, the net flow $q$ divides between the two tubes in proportion to their conductivity, i.e., $ q_1/q_2 = C_1/C_2$ which results in $q_1/q = \tilde C_1$, where $\tilde C_1 = C_1/(C_1+C_2)$.
 Note that the dynamics for each pipe in the parallel case can be simplified to $dr_i/dt = g(r_i)$ where $g(r_i) \equiv f(q_i, r_i)$ in which $q_i = \pi r_i^4 \Delta p / 8\mu L$.
@@
 	%
-\add{In fact, this condition will hold for nonlaminar flow as long as $C \propto r^k (k>0).$ The power law dependence of conductance with respect to radius leads to the scale-free criteria $r_1/r_2$.}
-Note that if $d\left(g(r)/r\right)/dr<0$, then Eq.~\eqref{eq:condition} is satisfied, and homogenization would occur. 
+	\add{Note that the scale-free criteria here (i.e., the dependence on the dimensionless factor $r_1/r_2$) results from the power-law dependence of conductance on radius, i.e., $C\propto r^k (k > 0)$.
+As a result, in addition to laminar flow (where $C\propto r^4$), the above condition also holds true for nonlaminar flow examples such as molecular flow where $C\propto r^3$ \cite{steckelmacher1966review}.
+}
+	In addition, if $d\left(g(r)/r\right)/dr<0$, then Eq.~\eqref{eq:condition} is satisfied, and homogenization would occur. 
 	The above homogenization condition can further be simplified as $g(r)>g'(r)r$, which can also be obtained directly using a linear stability analysis.
@@
 On the other hand, if the erosion rate is super-linear, we expect the parallel tubes to move away from homogenization and channelization occurs.
-Applying the power law erosion model with $f(q_{i},r_i)=\alpha q_i^m/r_i^n$, it can be shown that $g(r) \propto  r^{4m-n} $, and therefore $4m-n=1$ results in no change in the flow ratio $q_1/q$ (Fig.
-\ref{fig:fig3}c$_1$), while $4m-n<1$ results in homogenization condition (Fig.~\ref{fig:fig3}c$_2$), and $4m-n>1$ results in channelization (Fig.
-\ref{fig:fig3}c$_3$).
+Applying the power law erosion model with $f(q_{i},r_i)=\alpha q_i^m/r_i^n$, it can be shown that $g(r) \propto  r^{4m-n} $, and therefore $4m-n=1$ results in no change in the flow ratio $q_1/q$, while $4m-n<1$ results in homogenization condition, and $4m-n>1$ results in channelization (Fig.
+S7).
 Since a complex network includes both series and parallel connections, it is plausible that the whole network structure will behave in a similar manner, with an approximate transition in the network's behavior at $ m = (n+1)/4$.
 This result for $m=1$ reduces to a transition at $n=3$.
-It is to be noted that while the flow ratio remains constant for parallel edges, the connections in series are evolving toward homogenization and that is why we find a difference between evolved network for $n=3$ and the network at $t=0$.
+	% It is to be noted that while the flow ratio remains constant for parallel edges, the connections in series are evolving toward homogenization and that is why we find a difference between evolved network for $n=3$ and the network at $t=0$.
 	Since series connections are always moving toward homogenization, while parallel connections show a phase transition, we expect the phase transition to be at approximately $n\approx 3$, governed by the parallel connections.
-This observation  is consistent with the numerical simulation results shown in Figs.~\ref{fig:fig2} and \ref{fig:fig3}a (for $m=1$) as well as for additional values of $m$ (Fig.~\ref{fig:fig4}).
-Note, however, that the local dynamics model is only approximate and the numerically observed value of the phase transition happens for a value slightly larger than $n=3$ in Fig.
-\ref{fig:fig3}.
-% consistent with the homogenizing effect of the series connections. }
-% Although the result is derived under the constant pressure difference assumption, it holds validity for homogenization cases, where the pressure difference is going towards homogenization as well.
-
-% \textit{Simplified Model}-- {To understand the transition in network behavior during erosion for different powers of $n$, we focus on a simplified model with only two tubes in parallel or series (Figs.
-\ref{fig:fig3}b-c).
-First, assuming two cylindrical tubes with radii $r_1,r_2$ in series, the flow is the same for the two tubes $ q_1 = q_2 = q$ (Fig.
-\ref{fig:fig3}b).
-The radius of each tube then changes as $dr_i/dt = \alpha q^m /r_i^n$ where $i=1,2$.
-% As a result, we find that the conductivity of each tube changes as $dC_i/dt \propto q^m C_i^{(3-n)/4}$, where each tube's conductivity increases.
-Considering the pressure at the junction between tubes, we find that it moves toward the average value of pressure on both sides (Fig.
-\ref{fig:fig3}(b$_1$)).
-Contrary to tubes in series, when the tubes are in parallel (Fig.
-\ref{fig:fig3}c), the flow divides between the two tubes in proportion to their conductivity, i.e., $q_1/q_2 = C_1/C_2$.
-Since each tube's radius changes as $dr_i/dt = \alpha q^m_i/r_i^n$, the evolution of the fluid flow ratio becomes
-% % %% 
-% \begin{align}
-% \frac{d}{dt}\left( \frac{C_1}{C_2}\right) \propto  \frac{C_1}{C^{n/4+1}_2} \left( \left( \frac{C_1}{C_2}\right)^{m-\frac{n+1}{4}} - 1 \right). \label{eq:dyn-paral}
-% \end{align}
-% %%
-% When $m=(n+1)/4$ in Eq.
-\eqref{eq:dyn-paral}, the right-hand-side vanishes and as a result the flow ratio $C_1/C_2$ remains constant \add{while the radius keeps changing} (Fig.~\ref{fig:fig3}c$_1$).
-However, when $m \neq (n+1)/4$, we find that $C_1/C_2 = 1$ is an equilibrium point.
-When $m<(n+1)/4$ this equilibrium solution is stable and the flow moves toward homogenization (Fig.
-\ref{fig:fig3}c$_2$); however, when $m>(n+1)/4$ this equilibrium solution becomes unstable and the solution moves toward $C_1/C_2 \to 0$ or $\infty$ which means that the entire flow passes through one of the tubes (Fig.
-\ref{fig:fig3}c$_3$).
-In summary, when the tubes are in series any erosion law makes flow become more uniform; however, when the tubes are in parallel depending on the powers $m,n$ the flow in the tubes can move toward becoming more uniform ($m<(n+1)/4$), maintain the same ratio ($m=(n+1)/4$), or move toward instability and channel development ($m>(n+1)/4$).
-{Since a complex network includes both series and parallel connections, it is plausible that the whole network structure will behave in a similar manner, with \add{an approximate} transition in the networks behavior at $ m = (n+1)/4$}.
-\add{It is to be noted that the series connection are always moving toward homogenization, while only parallel connections showing a phase transition.
-As a result, we expect the phase transition to be happening close at approximately $n\approx 3$, where the parallel connections reflect this transition.} This observation  is consistent with the numerical simulation results shown in Figs.~\ref{fig:fig2} and \ref{fig:fig3}a (for $m=1$) as well as for additional values of $m$ (Fig.~\ref{fig:fig4}).} \add{Note that the true phase transition happens for a value slightly smaller than $n=3$ in Fig.
-\ref{fig:fig3} and the the order parameter for $n=3$ slightly moves toward homogenization.
-This is due to the fact that the series connections are homogenizing while the parallel connections grow in proportion.}
+This observation  is consistent with the numerical simulation results shown in Figs.~\ref{fig:fig2} and S6 (for $m=1$) as well as for additional values of $m$ (Fig.~\ref{fig:fig4}).
+	% Note, however, that the local dynamics model is only approximate and the numerically observed value of the phase transition happens for a value slightly larger than $n=3$ in Fig. S6.
+	\add{Note that the fact that local dynamics predict the fate of the overall network in the way described above is a result of the scale-free nature of the aforementioned power-law erosion model.
+Later, we will discuss richer phenomenology that may arise in the case of physical erosion laws possessing an intrinsic scale.}
+
 % %
@@
 Considering $m=2$, our model aligns with the transport optimization problem in biological networks~\cite{ronellenfitsch2016global,corson2010fluctuations,hu2013adaptation}. 
-% Previous works have suggested that in the context of biological transport networks, the network is optimized to minimize its dissipation energy with regards to some constraint (such as constant material or metabolic cost).
-Interestingly, the gradient descent method utilized to find the minimal energy configurations maps to Eq.
-\eqref{eq:erosion-law} with $m=2$, albeit with additional regularizing terms.
-While under the dynamics we study here erosion will occur indefinitely, in these biological network models a minimal energy configuration exists due to these additional constraints.
-Nonetheless, the minimal energy configurations manifest a phase transition reminiscent of the one we observe in our model.
 To test the role of the parameter $m$ in our model, we simulated the general form of erosion dynamics with $f(|q_{ij}|,r_{ij}) = \alpha |q_{ij}|^m/r_{ij}^n$.
@@
 \ref{fig:fig4}, where each box shows the final snapshot of the network eroded with the corresponding $m$ and $n$.
-% We further compare the network's simulation result with the simplified model's prediction.
-for the fate of the network for each pair of $m,n$.
 Additionally, the prediction of the local dynamics model is shown using the bounding box color (red for channelization and green for homogenization) in Fig.
-\ref{fig:fig4} (cf., Fig.~S8 in SM showing the heat map for the average change in the order parameter).
+\ref{fig:fig4} (cf., Fig.~S9 showing the heat map for the average change in the order parameter).
 The dashed black line in Fig.
 \ref{fig:fig4} shows the  the local dynamics model's prediction for the boundary between network's transition to homogeneity or channelization (i.e., $m = (n+1)/4$).
-% Although the simplified model is based on the erosion dynamics of two edges in a parallel or series configuration, it still 
 We find that the local dynamics model correctly predicts the fate of the network with the complex topology for different values of $m$ and $n$, and captures the boundary separating channelization/homogenization.
-We further consider a model where the onset of erosion happens only after  a certain threshold (see SM \S4 and Figs.
-S6 and S7) and find that the transition remains unchanged at $m=(n+1)/4$, showing robustness to thresholding effects.
+We further consider a model where the onset of erosion happens only after  a certain threshold (SM, S6 and Fig.
+S8) and find that the transition remains unchanged at $m=(n+1)/4$, showing robustness to thresholding effects.
 Additionally, to further test the generality of the local dynamics model, we used a nonlinear function of shear rate as $dr/dt = h(\tau)$ where $\tau=q/r^3$.
-We found that the prediction of the local dynamics model matches with the direct simulations (see SM \S7 and Figs.
-S9 and S10) where it can be used to predict the fate of a network given a general erosion law.
+We found that the prediction of the local dynamics model matches with the direct simulations (SM, S9 and Fig.
+S10) where it can be used to predict the fate of a network given a general erosion law.
+\add{Note that for general erosion dynamics, the condition in Eq.
+\eqref{eq:condition} might hold for some but not all of the pipes at a given time.
+Furthermore, during the process of erosion, flow is redistributed throughout the network and therefore the flow distribution changes.
+This dynamical process enables the formation of \emph{multiple} channels, in contrast to the single channels observed for the scale-free erosion laws (SM, S9 and Fig.
+S10)}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the case of clogging, the initial dynamics can similarly be captured using our model, however, due to the change in the connectivity of the network, our local dynamics model cannot extend to large time behaviors (SM, \S5).
-
-%
-\textit{Conclusion}-- {We analyzed the dynamics of porous networks during erosion.
-We showed that depending on the form of the erosion law (namely, its dependence on flux and tube radius) the network can either move towards homogenization or towards developing a channeling instability.
+In the case of clogging, the initial dynamics can similarly be captured using our model, however, due to the change in the connectivity of the network, our local dynamics model cannot extend to large time behaviors (SM, S8).
+
+%
+\textit{Conclusion}-- {We analyzed the dynamics of porous networks during erosion.  We showed that depending on the form of the erosion law 
+% (namely, its dependence on flux and tube radius) 
+the network can either move towards homogenization or 
+% towards developing a 
+channeling instability.
 We elucidated the physical origin of this phase transition and how it is achieved using a simplified model.
@@
 However, we note that if the dependence on the shear rate is non-linear, it will qualitatively map to our model albeit with renormalized values of $n$ and $m$: e.g., a power-law dependence on shear rate with exponent $s$ would lead to $m =s$, $n = 3 s$, implying channelization when $s>1$.
-In the future, it would be exciting to test this and other predictions experimentally on model systems, relying on the technological advances in imaging flow profiles in porous materials, as well as extend the study to the geologically relevant case of chemical erosion \cite{edery2014origins,edery2016characterization}, and wormhole formation in geologic formations during CO$_2$ injection \cite{ott2015wormhole,szymczak2009wormhole}.
+\add{It is to be noted that the scale-free nature of our model as discussed after Eq.
+\eqref{eq:condition} is the main reason for the local dynamics setting the behavior of the whole network.
+Physical systems often have a scale associated with them, and in such cases, Eq.
+\eqref{eq:condition} and the condition described just after hold true for some flow rates but not all.
+Investigating nonlinear erosion dynamics, we found that transitional states are then possible.} Additionally, it would be exciting to test this and other predictions experimentally on model systems, relying on the technological advances in imaging flow profiles in porous materials, as well as extend the study to the geologically relevant case of chemical erosion \cite{edery2014origins,edery2016characterization}, and wormhole formation in geologic formations during CO$_2$ injection \cite{ott2015wormhole,szymczak2009wormhole}.
 Additionally, the model studied here could become richer by tracking the solute
@@
 	We thank the Kavli Foundation, MRSEC  DMR-2011754, and DMR-1420570 for their support. We thank Yaniv Edery,  Eleni Katifori, and Chris Rycroft
-for useful discussions.
+	for useful discussions. \add{We would like to thank the anonymous referees for their valuable comments.}
 \end{acknowledgments}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \bibliography{ref}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{58}%
+\begin{thebibliography}{59}%
 \makeatletter
@@
   {NoStop}%
+\bibitem [{\citenamefont {White}\ and\ \citenamefont
+  {Majdalani}(2006)}]{white2006viscous}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~M.}\ \bibnamefont
+  {White}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Majdalani}},\ }\href@noop {} {\emph {\bibinfo {title} {Viscous fluid
+  flow}}},\ Vol.~\bibinfo {volume} {3}\ (\bibinfo  {publisher} {McGraw-Hill New
+  York},\ \bibinfo {year} {2006})\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2012)\citenamefont {Chen},
@@
   {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bonelli}\ and\ \citenamefont
-  {Marot}(2011)}]{bonelli2011micromechanical}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Bonelli}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Marot}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {European Journal of Environmental and Civil Engineering}\ }\textbf {\bibinfo
-  {volume} {15}},\ \bibinfo {pages} {1207} (\bibinfo {year}
-  {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Parker}\ and\ \citenamefont
-  {Izumi}(2000)}]{parker2000purely}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Parker}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Izumi}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Journal of Fluid
-  Mechanics}\ }\textbf {\bibinfo {volume} {419}},\ \bibinfo {pages} {203}
-  (\bibinfo {year} {2000})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hu}\ and\ \citenamefont
-  {Cai}(2013)}]{hu2013adaptation}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Hu}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Cai}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-  Letters}\ }\textbf {\bibinfo {volume} {111}},\ \bibinfo {pages} {138701}
-  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{Note1()}]{Note1}%
+  \BibitemOpen
+  \bibinfo {note} {The order parameter defined here is inspired by the
+  participation ratio (PR) employed to quantify the localization of an
+  eigenstate in the analysis of Anderson localization~\cite
+  {kramer1993localization}.}\BibitemShut {Stop}%
+\bibitem [{\citenamefont {Steckelmacher}(1966)}]{steckelmacher1966review}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Steckelmacher}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Vacuum}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {561}
+  (\bibinfo {year} {1966})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Ronellenfitsch}\ and\ \citenamefont
@@
   {pages} {138301} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kramer}\ and\ \citenamefont
-  {MacKinnon}(1993)}]{kramer1993localization}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Kramer}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {MacKinnon}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Reports on Progress in Physics}\ }\textbf {\bibinfo {volume} {56}},\
-  \bibinfo {pages} {1469} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Corson}(2010)}]{corson2010fluctuations}%
@@
   \bibinfo {pages} {048704} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hu}\ and\ \citenamefont
+  {Cai}(2013)}]{hu2013adaptation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Hu}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Cai}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  Letters}\ }\textbf {\bibinfo {volume} {111}},\ \bibinfo {pages} {138701}
+  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Ocko}\ and\ \citenamefont
@@
   (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kramer}\ and\ \citenamefont
+  {MacKinnon}(1993)}]{kramer1993localization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Kramer}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {MacKinnon}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Reports on Progress in Physics}\ }\textbf {\bibinfo {volume} {56}},\
+  \bibinfo {pages} {1469} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
 \end{thebibliography}%
 
-%\bibliography{ref.bib}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-04-12 review_response/Response2.tex
BeforePublication

@@
 
+\Question{I have read the three referee reports
+and the authors' answers to all questions and criticisms. I think the
+authors have tried to answer all the referee's points and most answers
+are satisfactory to me.}
+
+\vspace{0.3 cm}
+
+\Answer{We appreciate the referee's thorough reviews.}
+\vspace{0.3 cm}
+
 \Question{
 The only answer that I do not find completely satisfying is to this
-point: ``…since the authors have access to experimental setups, it
+point: ``...since the authors have access to experimental setups, it
 would greatly improve this work if they could provide experimental
@@
 empirical observations relating the mean velocity and permeability as
-flow in a porous material is clogged with a polymer. Dr. Ahmad Zareii,
+flow in a porous material is clogged with a polymer. Dr. Ahmad Zareei,
 working under the guidance of Prof. Ariel Amir, set out to explain the
@@
 Technology, and therefore the experimental system associated with Ref.
-[31] is no longer active at Harvard. We also resonated with the
-comments of Referee D: "Experiments are notoriously hard to perform
-and can not be produced easily, especially when the parameter space
-that needs to be explored is as wide as in this study (without
-considering the 3D and polar simulations in the supplementary). I
-believe that the results are convincing, and requiring an experiment
-is somewhat unrealistic for the scope of this study. In many ways,
-this study can trigger the community to search for this ordering
-parameter in existing experimental setups, which will advance the
-field further by exploring the role of flow rate to shear rate or mean
-pore size." Indeed, we hope that as Referee D mentioned our
-theoretical study will trigger further experimental work in the
-future.}
+[31] is no longer active at Harvard. We hope that as Referee D mentioned our theoretical study will trigger further experimental work in the future.}
 
@@
 
-\Answer{We thank the reviewer for their thoughtful and thorough comments.}
+\Answer{We thank the reviewer for their thoughtful comments.}
 
@@
 flow rates but not all. This dependence on flow rate (or applied
-pressure drop) is not well explained in the manuscript. Also, the new
-investigation of a tanh profile shows that intermediate states are
+pressure drop) is not well explained in the manuscript. Also, the new investigation of a tanh profile shows that intermediate states are
 possible - i.e. states that lie somewhere between homogenization and
 instability. It would be good for the manuscript to acknowledge some
-of these limitations of their result - which remains interesting.\newline}
+of these limitations of their result - which remains interesting.
+\newline}
 
-\Answer{We thank the reviewer for the valuable comment. Indeed our model has limitations. We have now expanded our conclusion to include such limitations as mentioned by the reviewer.
+\Answer{We thank the reviewer for the valuable comment.
+Indeed for a more general erosion dynamics the condition in Eq.~(3) might not hold for all the local connections and as noted a transitional region is observed; in other words, the stability criterion is obeyed initially for some pipes (below a threshold shear stress/radius) but does not hold above it.
+Naively, one would expect flow in the stable pipes to be maintained over time, while channelization would occur for the others.
+However, during the process of channelization, flow is redistributed throughout the network and the flow distribution therefore changes -- implying that some pipes that were initially in the stable regime may become unstable at later times.
+This is indeed what we observe in our simulations, for non-scale-free erosion laws.
+Furthermore, it is precisely this dynamics which enables the formation of \emph{multiple} channels, in contrast to the single channels observed for the scale-free erosion laws.
 
-admit scale free after Eq. 3
+We have now included the remarks from the supplementary material in the main text.
+With regards to addressing the limitations, we have now expanded our conclusion to address the limitations of our model.
+The relevant parts from the main text are included here for completeness.\newline}
+% our model has limitations
+% .
+We have now expanded our conclusion to include such limitations as mentioned by the reviewer.
+admit scale free after Eq.
+3 If not parallel, g(r) can be more complex acknowledge inbetween cases in the main text ...
 
-If not parallel, g(r) can be more complex
-
-acknowledge inbetween cases in the main text ...
+\Answer{From \p3 of the main text:}
+\AnswerQ{
+\begin{quote}
+   ``Note that, the fact that local dynamics predict the fate of the overall network in the way described above is a result of the scale-free nature of the aforementioned power-law erosion model.
+Later, we will discuss richer phenomenology that may arise in the case of physical erosion laws possessing an intrinsic scale.''
+\end{quote}
+}
+\Answer{From \p4 of the main text:}
+\AnswerQ{
+\begin{quote}
+    ``It is to be noted that the scale-free nature of our model as discussed after Eq.
+(3) is the main reason for the local dynamics setting the behavior of the whole network.
+Physical systems often have a scale associated with them, and in such cases, Eq.~(3) and the condition described just after hold true for some flow rates but not all.
+Investigating nonlinear erosion dynamics, we found that transitional states are then possible.''
+\end{quote}
+\AnswerQ{
+\begin{quote}
+    ``Note that for general erosion dynamics, the condition in Eq.
+(3) might hold for some but not all of the pipes at a given time.
+Furthermore, during the process of erosion, flow is redistributed throughout the network and therefore the flow distribution changes.
+This dynamical process enables the formation of \emph{multiple} channels, in contrast to the single channels observed for the scale-free erosion laws (see SM \S7 and Fig.
+S10).''
+\end{quote}
+}
 }
@@
 
-\Answer{We would like to point out that for $n=3$ the network does not stay the same, since series connections are always moving toward homogenization, while parallel connections are staying in a constant proportion.
-This results in seeing differences between the statistics of the network at $t=0$ and the evolved network at later stages for $n=3$ (see Fig.
-2 in the main text).
-Additionally, we expect the transition to happen at  approximate $n\approx3$ (see comment 2G for more details).
-We have now included this point in the main manuscript to avoid confusion.}
+\Answer{We would like to thank the reviewer for their thorough reading.
+In fact, moving from $\dot{m}$ to $\dot{r}$, a factor of $1/r$ is introduced, since $dm=2\pi \rho rl dr$ in a cylindrical pipe.
+There is a typo in this equation and the factor should read $\kappa/r$.
+We have corrected the equation and additionally included more information to make the derivation clearer.
+The reference for the shear stress proportionality with $q/r^3$ is now added to the main text.
+The relevant part of the manuscript is included below.}
 %
@@
 
-\Answer{From \p4 of the main text:}
+\Answer{From \p2 of the main text:}
 \AnswerQ{
 \begin{quote}
-    ``It is to be noted that while the flow ratio remains constant for parallel edges, the connection in series are evolving toward homogenization and that is why we find a difference between evolved network for $n=3$ and the network at $t=0$.''
+    ``In a class of erosion models previously studied [34-36] the eroded mass per unit area is linearly proportional to the excess shear, i.e.,  $\dot{m}  = \kappa  (\tau_w-\tau_c)$ where $\kappa$ is the linear proportionality constant.
+This erosion model effectively results in an increase in the radius of the edges in our network model where $\dot{r} \propto \kappa/r (|q|/r^3 - \tau_c)$ , where the $1/r$ factor comes from the eroded mass $dm =2\pi\rho r l dr$ for a cylindrical pipe and $|q|/r^3$ comes from the shear stress of laminar flow in pipes [37].''
 \end{quote}
@@
 \vspace{0.5cm}
-\textbf{Comment C3}
+\textbf{Comment C4}
 \noindent \vspace{-0.2cm}\\ \Hline\\
@@
 
-\Answer{We thank the reviewer for their careful comment. We have now included the definition in the main text.}%
+\Answer{We thank the reviewer for the comment. We have now included the definition in the main text.}%
 
+\Answer{From \p3 of the main text:}
 \AnswerQ{
 \begin{quote}
-    ``To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes \add{of the same length $L$} in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$ (Figs.
-\ref{fig:fig3}b-c)''
+    ``To understand the transition in network behavior during erosion, we focus on a simplified model with only two tubes of the same length $L$ in parallel or series with a general erosion dynamics as $dr_{i}/dt = f(q_{i},r_{i}), i=1,2$.''
 \end{quote}
@@
 \vspace{0.5cm}
-\textbf{Comment C4}
+\textbf{Comment C5}
 \noindent \vspace{-0.2cm}\\ \Hline\\
@@
 
-\Answer{We thank the reviewer for their valuable recommendations.
-The physical origin the scale-free criteria $r_1/r_2$ turns out to be the result of power law dependence of conductance with respect to radius, meaning that our homogenization condition can be generalized to nonlaminar flow as well.
-The relevant part is attached.
-}
+\Answer{We thank the reviewer for their valuable suggestion.
+The physical origin of the scale-free criteria $r_1/r_2$ turns out to be a result of power-law dependence of conductance with respect to radius (i.e., $C\propto r^k$).
+Interestingly, this indicates that our homogenization condition can be generalized to non-laminar flow where conductance has again a power-law dependence on the radius [50].
+The relevant part is attached here for completeness.
+\newline }
+\\
+
+\Answer{From \p3 of the main text:}
 \AnswerQ{
 \begin{quote}
-    ``In fact, this condition will hold for nonlaminar flow as long as $C\propto r^k (k > 0)$.
-The power law dependence of conductance with respect to radius leads to the scale-free criteria $r_1/r_2$.
-''
+    ``Note that the scale-free criteria here (i.e., the dependence on the dimensionless factor $r_1/r_2$) results from the power-law dependence of conductance on radius, i.e., $C\propto r^k (k > 0)$.
+As a result, in addition to laminar flow (where $C\propto r^4$), the above condition also holds true for nonlaminar flow examples such as molecular flow where $C\propto r^3$ [50].''
+    % ``In fact, this condition will hold for nonlaminar flow as long as . The power law dependence of conductance with respect to radius leads to the scale-free criteria $r_1/r_2$. ''
 \end{quote}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage 
-\vspace{10 mm}
-\noindent
-\Hline \\
-\textbf{Response to Reviewer D} \\
-\Hline
-\\
-
-\Question{This paper presents 2D and 3D pore-network models of single-phase flow through porous media, involving channel erosion.
-The erosion rate in a channel is modeled as a function of the flow rate through the channel and the radius of the channel.The manuscript presents an interesting transition in the behaviour of these models from a stabilizing behavior where narrow channels erode more quickly than wider ones (``homogenization'') to an unstable regime where all the flow ends up in a few pathways ``instability'').
-Overall I judge this to be an interesting paper that may be worth publishing in a journal such as PRFluids, but falls short of the level of impact required for PRL.
-I explain this below.
-The manuscript has many strengths which include: - it's very clearly written and with excellent figures that clearly demonstrate the phenomena being explored; - good numerical modeling that includes 2D and 3D simulations in random and regular network topologies; - results which are universal within the class of models being considered here, being valid 2D and 3D and in regular and random networks; - a clear theory to explain the results using a local analysis,suggesting links between global and local dynamics even in quite complex systems; - links to flow in biological systems
-\newline}
-
-\Answer{We thank the reviewer for their careful reading of the manuscript and their constructive
-remarks.}
-
-\vspace{0.5cm}
-\textbf{Comment 3A}
-\noindent \vspace{-0.2cm}\\ \Hline\\
-\Question{The weaknesses in the work include: the physical relevance of the model is not clear, except for the specific biological case ...
-more specifics in studies of models that are closest to this one are needed, particularly also mentioning the outcomes of those studies.
-Some of the model's (apparent) weaknesses are being a pure power law, its scaling with pressure is unphysical: the erosion rate in all channels merely increases uniformly with applied pressure, meaning that erosion occurs even at near-zero speed/stress; there is no onset threshold.\newline}
-
-\Answer{We appreciate the reviewers comment.
-The concern here is similar to comment 2F of Reviewer 2, and we repeat our reply here.
-Erosion in saturated granular materials occurs when the shear stress at the wall exceeds the cohesive strength of the solid matter.
-In the revised version, we study more realistic models including: (i) a model where the onset of erosion happens after reaching a threshold value; (ii) a model with a different (nonlinear) functional dependence on shear stress, where erosion starts after a certain threshold and eventually saturates to a maximum value which is determined by the maximal detachment rate of particles at the tube's boundary.
-We make predictions for both models using our analysis and find that the analytical results agree well with the numerical simulations.
-These results illustrate the generality of our model in relating to various physical models.
-(iii) Additionally, we expand our discussion before introducing the model to make a better connection with relevant studies of erosion.
-We believe that these new results illustrate that the phase transition is a general effect, and that our analysis using the local dynamics model has the predictive power of identifying the phase transition condition.
-In the following we attach the relevant excerpts of the main text and the supplementary material.}
 

### 2022-04-12 supp.tex
BeforePublication

@@
 In either case, the network has an order of $10^3$ edges.
-\add{Note that the physical assumption of low Reynolds regime Re$\ll$1 at all times ensures that the Poisoulle flow assumption remains valid.
+{Note that the physical assumption of low Reynolds regime Re$\ll$1 at all times ensures that the Poisoulle flow assumption remains valid.
 Additional dimensionless transport numbers such as the P\'eclet number (ratio of advection to diffusion) or the Damkohler number (ratio of chemical reaction rate to the transport phenomena rate) are assumed to be respectively very large and very small, resulting in advection to be much stronger than diffusion and chemical reaction.
@@
 We find that regardless of the topology of the network, an erosion dynamics with $n>3$ results in a homogenized network, while $n<3$ results in the channelization instability.
+It is to be noted that the different distributions obtained for different powers of $n$ represent different statistics that cannot be collapsed.
 We further check the effect of initial randomness on the fate of the network.
@@
 We again find that for the networks with $n<3$ channels are formed, while for $n>3$ the network stays homogenized.
-\add{In addition to the network topology and initial condition, we test the robustness of our results to changes in the boundary condition.
+{In addition to the network topology and initial condition, we test the robustness of our results to changes in the boundary condition.
 We choose a circular domain, with the central node being the inlet and all the nodes at the outer boundary being outlets.
@@
       \includegraphics[width = 0.70\textwidth]{./circular3.pdf}
-     \caption{\textcolor{blue}{Erosion in a topologically random 3D network of tubes with a circular topology with $N = 3000 $ randomly distributed nodes and an initial uniform broad distribution of tube diameters randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$.
+     \caption{Erosion in a topologically random 3D network of tubes with a circular topology with $N = 3000 $ randomly distributed nodes and an initial uniform broad distribution of tube diameters randomly sampled from a uniform distribution with $\mathcal{U}(1,14)$.
 Shown are snapshots of the network, PDF of normalized fluid flux $q/\langle q \rangle$, and normalized edge radius distribution $r/\langle r \rangle$ at the initial time $t=0$, and also after $N$ erosion steps for different powers of erosion $n$.
@@
 The erosion law is based on Eq.
-(1) in the main text where different powers of $n$ correspond to different models of erosion.}}\label{SIfig:fig2-3d_circular}
+(1) in the main text where different powers of $n$ correspond to different models of erosion.}\label{SIfig:fig2-3d_circular}
  \end{figure}
@@
 \clearpage
+\section{Order parameter and Phase transition}
+
+To quantify the transition of the network between the channeling instability and homogenization, we define an order parameter~\footnote{The order parameter defined here is inspired by the participation ratio (PR) employed to quantify the localization of an eigenstate in the analysis of Anderson localization~\cite{kramer1993localization}.} % $\mathcal{O}$
+		%
+		\begin{align}
+			\mathcal{O} = \frac{1}{N-1} \left( N - \frac{\left( \sum_{ij} q^2_{ij}\right)^2}{ \sum_{ij} q^4_{ij}}\right),
+		\end{align}
+		%
+where $N$ is the number of edges.
+The order parameter $\mathcal{O}=0 $ when the flux through every edge is identical.
+On the other hand, when fluid flux becomes highly localized with only a few edges with non-zero flux, $\mathcal{O}\to 1$.
+We numerically calculated the  order parameter $\mathcal{O}$ for {randomly initialized networks, averaged over 20 different realization} and the results are shown in Fig.
+\ref{fig:fig3-SIa}.
+We find that at $n\approx 3$ the order parameter remains unchanged; however for $n>3$ the order parameter moves toward zero, where the flow becomes more uniform, and for $n<3$ the order parameter goes toward unity, where channels are developed.
+This indicates a phase transition at $n \approx 3$ in the long-time behavior of the network.
+
+% To quantify the transition of the network between the channeling instability and homogenization, we numerically calculated the order parameter $\mathcal{O}$ for randomly initialized networks, averaged over 20 different realization and the results are shown in Fig.
+\ref{fig:fig3-SI}a.
+The results indicate a phase transition at $n\approx 3$ where at $n\approx 3$ the order parameter remains unchanged; while for $n > 3$ the order parameter moves toward zero and the flow becomes more uniform, and for $n < 3$ the order\ parameter goes toward unity and channels are developed.
+Additionally, as discussed in section \textit{Local Dynamics Model} of the main text, to understand the transition in network behavior during erosion, we study a simplified model with only two tubes, where the results are illustrated in Fig.~\ref{fig:fig3-SI}b-c.
+Assuming two cylindrical tubes in series (Fig.
+\ref{fig:fig3-SI}b), the normalized pressure at the middle junction between the tubes approaches the average of pressure at both sides of the tube resulting in a homogenized pressure distribution.
+Contrary to tubes in series, when the tubes are in parallel, depending on the erosion dynamics, different behaviors of homogenization, channelization, or staying the same can be observed.
+
+\begin{figure}[!h]
+	% \centering
+	\includegraphics[width = 0.55\textwidth]{Fig3-order.pdf}
+	\caption{ Order parameter $\mathcal{O}$ calculated from simulation results presented in Fig. 2 of the main text for different powers of $n$ with $m=1$ plotted over time.  
+    % 	Local Dynamics Model: Tubes in series (a) or parallel (b) configuration.
+The tube radius dynamically change with the erosion law, i.e., $f(q,r) = \alpha |q|^m/r^n$.
+When the tubes are in series, for any $m,n$, (a$_1$) the normalized pressure at the middle junction between the tubes $\tilde p_m = (p_m - p_l)/(p_r-p_l)$ approaches $1/2$ which results in a homogenized pressure distribution.
+When the tubes are in parallel, for (b$_1$) $m=(n+1)/4$, the flow ratio between the pipes does not change over time; (b$_2$)  $m<(n+1)/4$ the flow distributes between the tubes equally and  $q_1/(q_1+q_2) \to 1$ which results in the homogenization of the network; (b$_3$) $m>(n+1)/4 $, the entire flow eventually passes through one of the tubes, and channeling occurs.
+	}\label{fig:fig3-SIa}
+\end{figure}
+
+\section{Local Dynamics Model}
+As discussed in section \textit{Local Dynamics Model} of the main text, to understand the transition in network behavior during erosion, we study a simplified model with only two tubes, where the results are illustrated in Fig.~\ref{fig:fig3-SIb}a-b.
+Assuming two cylindrical tubes in series (Fig.
+\ref{fig:fig3-SIb}a), the normalized pressure at the middle junction between the tubes approaches the average of pressure at both sides of the tube resulting in a homogenized pressure distribution.
+Contrary to tubes in series, when the tubes are in parallel (Fig.~\ref{fig:fig3-SIb}b), depending on the erosion dynamics, different behaviors of homogenization, channelization, or staying the same can be observed.
+
+\begin{figure}[!h]
+	% \centering
+	\includegraphics[width = 0.95\textwidth]{Fig3-model.pdf}
+	\caption{Local Dynamics Model: Tubes in series (a) or parallel (b) configuration.
+The tube radius dynamically change with the erosion law, i.e., $f(q,r) = \alpha |q|^m/r^n$.
+When the tubes are in series, for any $m,n$, (a$_1$) the normalized pressure at the middle junction between the tubes $\tilde p_m = (p_m - p_l)/(p_r-p_l)$ approaches $1/2$ which results in a homogenized pressure distribution.
+When the tubes are in parallel, for (b$_1$) $m=(n+1)/4$, the flow ratio between the pipes does not change over time; (b$_2$)  $m<(n+1)/4$ the flow distributes between the tubes equally and  $q_1/(q_1+q_2) \to 1$ which results in the homogenization of the network; (b$_3$) $m>(n+1)/4 $, the entire flow eventually passes through one of the tubes, and channeling occurs.
+	}\label{fig:fig3-SIb}
+\end{figure}
+
 \section{Erosion with a threshold}
 %
-\add{In order to make our erosion model more realistic, we modify the model as  
+{In order to make our erosion model more realistic, we modify the model as  
 %
@@
   \includegraphics[width=0.45\textwidth]{./Fig_thresh0.9.pdf}
-     \caption{\add{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
+     \caption{Evolution of a randomly initialized network for various powers of $m$ and $n$ in Eq.
 \eqref{eq:thresh} with a small threshold value of $\beta = 0.25\langle q^m/r^n\rangle $ (left figure), and a large threshold value of $\beta = 0.9\langle q^m/r^n\rangle$ at $t=0$.
 The network is randomly initialized with $50\times 50$ randomly distributed pores.
-The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using local dynamics model, i.e., $4m-n=0.75$ (left figure), and $4m-n=0.1$ (right figure).} }\label{fig:figthresh1}%
+The black line shows the theoretical transition boundary between channelization instability and homogenization obtained using local dynamics model, i.e., $4m-n=0.75$ (left figure), and $4m-n=0.1$ (right figure).
+}\label{fig:figthresh1}%
 \end{figure}
@@
 
-\add{\section{General shear dependent erosion model}}
-\add{
+\section{General shear dependent erosion model}
+{
 As an example of a nonlinear erosion model, we consider a shear-dependent erosion
@@
       \includegraphics[width = 0.8\textwidth]{sigmoidDelaunay.pdf}
-     \caption{\textcolor{blue}{(a) A 2D random network with $N_x=50$ and $N_y=50$ points.
+     \caption{(a) A 2D random network with $N_x=50$ and $N_y=50$ points.
 (b) The probability distribution function (PDF) of the shear stress for the edges of the network.
@@
 (e)/(h)/(k) The PDF of the shear stress at the walls for the final snapshot of the network shown in the previous row.
-    }}
+    }
      \label{SIfig:fig9-sigmoidDelaunay}
@@
 % \bibliography{ref}% Produces the bibliography via BibTeX.
+
 %apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{8}%
+\begin{thebibliography}{10}%
 \makeatletter
@@
   {NoStop}%
+\bibitem [{Note1()}]{Note1}%
+  \BibitemOpen
+  \bibinfo {note} {The order parameter defined here is inspired by the
+  participation ratio (PR) employed to quantify the localization of an
+  eigenstate in the analysis of Anderson localization~\cite
+  {kramer1993localization}.}\BibitemShut {Stop}%
 \bibitem [{\citenamefont {Parsa}\ \emph {et~al.}(2021)\citenamefont {Parsa},
@@
   {2000})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kramer}\ and\ \citenamefont
+  {MacKinnon}(1993)}]{kramer1993localization}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Kramer}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {MacKinnon}},\ }\bibfield  {title} {\bibinfo {title} {Localization: theory
+  and experiment},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Reports on Progress in Physics}\ }\textbf {\bibinfo {volume} {56}},\
+  \bibinfo {pages} {1469} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
 \end{thebibliography}%
